---
title: "Covid CNS Covid-19"
author: "Alish Palmos"
date: "14/01/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = "../functions/add_numeric.R")
source(file = "../functions/remove_duplicates.R")
source(file = "../functions/sumscores.R")
source(file = "../functions/package_check.R")
source(file = "../functions/imp_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in file with path to ilovecovidcns channel on teams}
source(file = "../credentials/paths.R")
```

# Read in the data: Full Name of Questionnaire/Demographic
Change this heading to the name of your questionnaire/demographic

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the issues spreadsheet "https://docs.google.com/spreadsheets/d/1a2gL8c0eH2pZXNTbnPzkDYQGeeVXbLKU8BUpYM0moe8/edit?usp=sharing"

- For variable names, use ONLY 'questionnaire.variable_name'
- For dataset, only use snake_case naming
- When using pipe operator '%>%', each function should begin on a new line
- Do not add empty lines at the beginning or end of a chunk
- Use only tidyverse functions wherever possible

## Data
```{r load data}
covidcns_dat <- read_rds(
  file = paste0(ilovecovidcns, "/data_raw/latest_freeze/baseline/covid19_covid_cns.rds")
  )
  
# Check variable names in dataframe
covidcns_dat %>%
  colnames()
# Inspect dimensions of dataframe 
covidcns_dat %>%
  dim()
```

Specify columns to be excluded from add_numeric function
Continuous variables should be excluded, as they are already numeric
NB: If this is data from the COPING survey, add "_cop" to the end of each variable name
```{r specify excluded columns}
exclude_cols_numeric <- c(
  "ID",
  "sample",
  "startDate",
  "endDate",
  "covid19.exact_date_symptoms_start.txt",
  "covid19.latest_test_date_yyyy.txt",
  "covid19.please_describe_your_other_symptoms.txt"
 # other columns as required
  )
```

Select & rename relevant columns
```{r select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "COVID-CNS",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         sample,
         startDate,
         endDate,
         covid19.have_you_had_suspected_covid19_symptoms,
         covid19.exact_date_symptoms_start.txt,
         covid19.tested_covid,
         covid19.what_test_did_you_have,
         covid19.test_positive_covid,
         covid19.coivd_occasion_test_positive,
         covid19.latest_test_date_yyyy.txt,
         covid19.recover_home_stay_time,
         covid19.get_treatment_at_hospital_,
         covid19.get_treatment_in_intensive_care_unit,
         covid19.persistent_cough,
         covid19.persistent_cough.1,
         covid19.fever,
         covid19.fever.1,
         covid19.loss_of_tasteloss_of_smell,
         covid19.loss_of_tasteloss_of_smell.1,
         covid19.intermittent_cough,
         covid19.intermittent_cough.1,
         covid19.hoarseness,
         covid19.hoarseness.1,
         covid19.sore_throat,
         covid19.sore_throat.1,
         covid19.nasal_dischargecongestion,
         covid19.nasal_dischargecongestion.1,
         covid19.wheeze,
         covid19.wheeze.1,
         covid19.shortness_of_breath,
         covid19.shortness_of_breath.1,
         covid19.headache,
         covid19.headache.1,
         covid19.muscle_aches,
         covid19.muscle_aches.1,
         covid19.nausea,
         covid19.nausea.1,
         covid19.diarrhoea,
         covid19.diarrhoea.1,
         covid19.other,
         covid19.other.1,
         covid19.please_describe_your_other_symptoms.txt,
         covid19.individual_contact_positive_test 
         # other columns as necessary
         ) %>%
  add_numeric(exclude = exclude_cols_numeric)
# Inspect colnames
covidcns_dat_id %>%
  colnames()
```

Look at number of people excluded
The number of people to be excluded should be negative
```{r number excluded}
# Inspect dimensions of new data set
covidcns_dat_id %>%
  dim()
# Inspect number of rows dropped
covidcns_excluded <- dim(covidcns_dat_id)[1] - dim(covidcns_dat)[1]
covidcns_excluded
```

Inspect numeric variables
```{r inspect numeric variables}
covidcns_dat_id %>%
  select(all_of(ends_with("numeric"))) %>%
  tbl_summary(missing_text = "Missing")
```

Check missingness by missmap
```{r GLAD inspect missingness}
covidcns_miss_map <- covidcns_dat_id %>% 
  missmap()
covidcns_miss_map
```

Recode incorrect variable
Can be removed after data recoded in qualtrics and after data export
If variables are found to be incorrect:
Report the error in the qualtrics issues spreadsheet
Add as action point on teams with yourself and Molly tagged
Recode the variable yourself using `case_when` as below
Continue cleaning your script with the recoded variable until fixed from source
DO NOT run this chunk multiple times: it will mess up the variable coding, requiring you to run the script again from the beginning
```{r recode incorrect variable}
# Have you had suspected COVID-19 symptoms?

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.have_you_had_suspected_covid19_symptoms_numeric =
        case_when(
        covid19.have_you_had_suspected_covid19_symptoms_numeric == "2" ~ 0,
        covid19.have_you_had_suspected_covid19_symptoms_numeric == "1" ~ 1,
        covid19.have_you_had_suspected_covid19_symptoms_numeric == "-77" ~ -77
           ) 
        )
    
covidcns_dat_id %>%
   freq(covid19.have_you_had_suspected_covid19_symptoms_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.have_you_had_suspected_covid19_symptoms =
        recode_factor(covid19.have_you_had_suspected_covid19_symptoms_numeric,
                      "0" = "No I haven't had tCOVID19 symptoms",
                      "1" = "Yes I've had COVID19 symptoms",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.have_you_had_suspected_covid19_symptoms)
   

#### When did your symptoms start? 
   
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.exact_date_symptoms_start =
        as.Date(covid19.exact_date_symptoms_start.txt,
  format = "%d/%m/%Y")
    )
       

covidcns_dat_id %>%
   freq(covid19.exact_date_symptoms_start)
```

# Variable cleaning COVID19 testing 

```{r}

# Have you been tested for COVID19
  
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.tested_covid_numeric =
          case_when(
            covid19.tested_covid_numeric == "2" ~ 0,
            covid19.tested_covid_numeric == "1" ~ 1,
            covid19.tested_covid_numeric == "-77" ~ -77
           ) 
        )
    

covidcns_dat_id %>%
   freq(covid19.tested_covid_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.tested_covid =
        recode_factor(covid19.tested_covid_numeric,
                      "0" = "No I haven't been tested for COVID19",
                      "1" = "Yes I've been tested for COVID19",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.tested_covid)
   
### What test did you have? 
   
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.what_test_did_you_have_numeric =
        case_when(
        covid19.what_test_did_you_have_numeric == "1" ~ 1,
        covid19.what_test_did_you_have_numeric == "2" ~ 2,
        covid19.what_test_did_you_have_numeric == "3" ~ 3,
        covid19.what_test_did_you_have_numeric == "-77" ~ -77
           ) 
        )
    

covidcns_dat_id %>%
   freq(covid19.what_test_did_you_have_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.what_test_did_you_have =
        recode_factor(covid19.what_test_did_you_have_numeric,
                      "1" = "Swab test",
                      "2" = "Lateral flow test",
                      "3" = "Antibody test",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.what_test_did_you_have)
   
### Did you [ever] test positive for COVID-19?
   
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.test_positive_covid_numeric =
        case_when(
        covid19.test_positive_covid_numeric == "2" ~ 0,
        covid19.test_positive_covid_numeric == "1" ~ 1,
        covid19.test_positive_covid_numeric == "-77" ~ -77
           ) 
        )
    

covidcns_dat_id %>%
   freq(covid19.test_positive_covid_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.test_positive_covid =
        recode_factor(covid19.test_positive_covid_numeric,
                      "0" = "No I haven't tested positive for COVID19",
                      "1" = "Yes I've  tested positive for COVID19",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.test_positive_covid)

### Did you test positive for COIVD-19 on more than one occasion?
   
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.coivd_occasion_test_positive_numeric =
        case_when(
          covid19.coivd_occasion_test_positive_numeric == "2" ~ 0,
          covid19.coivd_occasion_test_positive_numeric == "1" ~ 1,
          covid19.coivd_occasion_test_positive_numeric == "-77" ~ -77
           ) 
        )
    

covidcns_dat_id %>%
   freq(covid19.coivd_occasion_test_positive_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.coivd_occasion_test_positive =
        recode_factor(covid19.coivd_occasion_test_positive_numeric,
                      "0" = "No I haven't tested positive more than once for COVID19",
                      "1" = "Yes I've  tested positive more than once for COVID19",
                       "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.coivd_occasion_test_positive)
   

#### Date of positive or latest test Please provide at least month and year. Please enter as dd/mm/yyyy and enter 01/mm/yyyy for the day if you do not know.
   
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.latest_test_date =
        as.Date(covid19.latest_test_date_yyyy.txt,
  format = "%d/%m/%Y")
    )
       
    
covidcns_dat_id %>%
   freq(covid19.latest_test_date)
```

# Variable cleaning COVID19 symptoms 

```{r}

# Severity of treatment - where did you seek treatment:

### Stay at home the whole time to recover?
   
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.recover_home_stay_time_numeric =
          case_when(
            covid19.recover_home_stay_time_numeric == "1" ~ 1,
            covid19.recover_home_stay_time_numeric == "2" ~ 0,
            covid19.recover_home_stay_time_numeric == "-77" ~ -77,
          )
    )


covidcns_dat_id %>%
   freq(covid19.recover_home_stay_time_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.recover_home_stay_time =
        recode_factor(covid19.recover_home_stay_time_numeric,
                       "1" = "Yes",
                       "0" = "No",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.recover_home_stay_time)

### Get treatment at hospital ?

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.get_treatment_at_hospital__numeric =
          case_when(
            covid19.get_treatment_at_hospital__numeric == "1" ~ 1,
            covid19.get_treatment_at_hospital__numeric == "2" ~ 0,
            covid19.get_treatment_at_hospital__numeric == "-77" ~ -77,
          )
    )


covidcns_dat_id %>%
   freq(covid19.get_treatment_at_hospital__numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.get_treatment_at_hospital_ =
        recode_factor(covid19.get_treatment_at_hospital__numeric,
                       "1" = "Yes",
                       "0" = "No",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.get_treatment_at_hospital_)

### Get treatment in Intensive Care Unit?

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.get_treatment_in_intensive_care_unit_numeric =
          case_when(
            covid19.get_treatment_in_intensive_care_unit_numeric == "1" ~ 1,
            covid19.get_treatment_in_intensive_care_unit_numeric == "2" ~ 0,
            covid19.get_treatment_in_intensive_care_unit_numeric == "-77" ~ -77,
          )
    )


covidcns_dat_id %>%
   freq(covid19.get_treatment_in_intensive_care_unit_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.get_treatment_in_intensive_care_unit =
        recode_factor(covid19.get_treatment_in_intensive_care_unit_numeric,
                       "1" = "Yes",
                       "0" = "No",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.get_treatment_in_intensive_care_unit)

# If you had symptoms or a confirmed diagnosis of COVID-19, did you:

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.where_did_you_seek_treatment_numeric =
        case_when(
        covid19.get_treatment_in_intensive_care_unit_numeric == "1" ~ 3,
        covid19.get_treatment_at_hospital__numeric == "1" ~ 2,
        covid19.recover_home_stay_time_numeric == "1" ~ 1,
        covid19.get_treatment_in_intensive_care_unit_numeric == "-77" ~ -77,
        covid19.get_treatment_at_hospital__numeric == "-77" ~ -77,
        covid19.recover_home_stay_time_numeric == "-77" ~ -77
           ) 
        )
    

covidcns_dat_id %>%
   freq(covid19.where_did_you_seek_treatment_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.where_did_you_seek_treatment =
        recode_factor(covid19.where_did_you_seek_treatment_numeric,
                      "1" = "Stay at home the whole time to recover",
                      "2" = "Get treatment at hospital",
                      "3" = "Get treatment in Intensive Care Unit",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.where_did_you_seek_treatment)
   
   ### What symptoms did you have? 
   
   ### Persistent cough
   
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.persistent_cough_numeric =
          case_when(
            covid19.persistent_cough.1_numeric == "1" ~ 0,
            covid19.persistent_cough_numeric == "1" ~ 1,
            covid19.persistent_cough.1_numeric == "-77" ~ -77,
            covid19.persistent_cough_numeric == "-77" ~ -77

          )
    )


 covidcns_dat_id %>%
   freq(covid19.persistent_cough_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.persistent_cough =
        recode_factor(covid19.persistent_cough_numeric,
                       "0" = "No persistent cough",
                       "1" = "Yes persistant cough",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.persistent_cough)
   
### Fever
   
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.fever_numeric =
          case_when(
            covid19.fever.1_numeric == "1" ~ 0,
            covid19.fever_numeric == "1" ~ 1,
            covid19.fever.1_numeric == "-77" ~ -77,
            covid19.fever.1_numeric == "-77" ~ -77
          )
    )


covidcns_dat_id %>%
   freq(covid19.fever_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.fever =
        recode_factor(covid19.fever_numeric,
                      "0" = "No fever",
                      "1" = "Yes fever",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.fever)
   
   
### Loss of taste/smell
   
      
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.loss_of_tasteloss_of_smell_numeric =
          case_when(
        covid19.loss_of_tasteloss_of_smell_numeric == "1" ~ 1,
        covid19.loss_of_tasteloss_of_smell.1_numeric == "1" ~ 0,
        covid19.loss_of_tasteloss_of_smell_numeric == "-77" ~ -77,
        covid19.loss_of_tasteloss_of_smell.1_numeric == "-77" ~ -77
          )
    )


covidcns_dat_id %>%
   freq(covid19.loss_of_tasteloss_of_smell_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.loss_of_tasteloss_of_smell =
        recode_factor(covid19.loss_of_tasteloss_of_smell_numeric,
                      "1" = "Yes loss of taste/smell",
                      "0" = "No loss of taste/smell",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.loss_of_tasteloss_of_smell)
   
### Intermittent cough
   
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.intermittent_cough_numeric =
          case_when(
        covid19.intermittent_cough_numeric == "1" ~ 1,
        covid19.intermittent_cough.1_numeric == "1" ~ 0,
        covid19.intermittent_cough_numeric == "-77" ~ -77,
        covid19.intermittent_cough.1_numeric == "-77" ~ -77
          )
    )


covidcns_dat_id %>%
   freq(covid19.intermittent_cough_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.intermittent_cough =
        recode_factor(covid19.intermittent_cough_numeric,
                      "1" = "Yes intermittent cough",
                      "0" = "No intermittent cough",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.intermittent_cough)
   
   
### Hoarseness
   
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.hoarseness_numeric =
          case_when(
        covid19.hoarseness_numeric == "1" ~ 1,
        covid19.hoarseness.1_numeric == "1" ~ 0,
        covid19.hoarseness_numeric == "-77" ~ -77,
        covid19.hoarseness.1_numeric == "-77" ~ -77
          )
    )


covidcns_dat_id %>%
   freq(covid19.hoarseness_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.hoarseness =
        recode_factor(covid19.hoarseness_numeric,
                      "1" = "Yes hoarseness",
                      "0" = "No hoarseness",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.hoarseness)
   
### Sore throat
   
      
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.sore_throat_numeric =
          case_when(
        covid19.sore_throat_numeric == "1" ~ 1,
        covid19.sore_throat.1_numeric == "1" ~ 0,
        covid19.sore_throat_numeric == "-77" ~ -77,
        covid19.sore_throat.1_numeric == "-77" ~ -77
          )
    )


covidcns_dat_id %>%
   freq(covid19.sore_throat_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.sore_throat =
        recode_factor(covid19.sore_throat_numeric,
                      "1" = "Yes sore throat",
                      "0" = "No sore throat",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.sore_throat)
   
   
### Nasal discharge / congestion
   
      
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.nasal_dischargecongestion_numeric =
          case_when(
        covid19.nasal_dischargecongestion_numeric == "1" ~ 1,
        covid19.nasal_dischargecongestion.1_numeric == "1" ~ 0,
        covid19.nasal_dischargecongestion_numeric == "-77" ~ -77,
        covid19.nasal_dischargecongestion_numeric == "-77" ~ -77
          )
    )


covidcns_dat_id %>%
   freq(covid19.nasal_dischargecongestion_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.nasal_dischargecongestion =
        recode_factor(covid19.nasal_dischargecongestion_numeric,
                      "1" = "Yes nasal discharge/congestion",
                      "0" = "No nasal discharge/congestion",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.nasal_dischargecongestion)
   
   
### Wheeze
   
      
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.wheeze_numeric =
          case_when(
        covid19.wheeze_numeric == "1" ~ 1,
        covid19.wheeze.1_numeric == "1" ~ 0,
        covid19.wheeze_numeric == "-77" ~ -77,
        covid19.wheeze.1_numeric == "-77" ~ -77
          )
    )


covidcns_dat_id %>%
   freq(covid19.wheeze_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.wheeze =
        recode_factor(covid19.wheeze_numeric,
                      "1" = "Yes wheeze",
                      "0" = "No wheeze",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.wheeze)
   
   
### Shortness of breath
   
      
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.shortness_of_breath_numeric =
          case_when(
        covid19.shortness_of_breath_numeric == "1" ~ 1,
        covid19.shortness_of_breath.1_numeric == "1" ~ 0,
        covid19.shortness_of_breath_numeric == "-77" ~ -77,
        covid19.shortness_of_breath.1_numeric == "-77" ~ -77
          )
    )


covidcns_dat_id %>%
   freq(covid19.shortness_of_breath_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.shortness_of_breath =
        recode_factor(covid19.shortness_of_breath_numeric,
                      "1" = "Yes shortness of breath",
                      "0" = "No shortness of breath",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.shortness_of_breath)
   
   
### Headache
   
      
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.headache_numeric =
          case_when(
        covid19.headache_numeric == "1" ~ 1,
        covid19.headache.1_numeric == "1" ~ 0,
        covid19.headache_numeric == "-77" ~ -77,
        covid19.headache.1_numeric == "-77" ~ -77
          )
    )


covidcns_dat_id %>%
   freq(covid19.headache_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.headache =
        recode_factor(covid19.headache_numeric,
                      "1" = "Yes headache",
                      "0" = "No headache",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.headache)
   
### Muscle ache
   
      
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.muscle_aches_numeric =
          case_when(
        covid19.muscle_aches_numeric == "1" ~ 1,
        covid19.muscle_aches.1_numeric == "1" ~ 0,
        covid19.muscle_aches_numeric == "-77" ~ -77,
        covid19.muscle_aches.1_numeric == "-77" ~ -77
          )
    )


covidcns_dat_id %>%
   freq(covid19.muscle_aches_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.muscle_aches =
        recode_factor(covid19.muscle_aches_numeric,
                      "1" = "Yes muscle ache",
                      "0" = "No mucle ache",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.muscle_aches)
   
   
### Nausea
   
      
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.nausea_numeric =
          case_when(
        covid19.nausea_numeric == "1" ~ 1,
        covid19.nausea.1_numeric == "1" ~ 0,
        covid19.nausea_numeric == "-77" ~ -77,
        covid19.nausea.1_numeric == "-77" ~ -77
          )
    )


covidcns_dat_id %>%
   freq(covid19.nausea_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.nausea =
        recode_factor(covid19.nausea_numeric,
                      "1" = "Yes nausea",
                      "0" = "No nausea",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )

covidcns_dat_id %>%
   freq(covid19.nausea)
   
   
### Diarhoea
   
      
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.diarrhoea_numeric =
          case_when(
        covid19.diarrhoea_numeric == "1" ~ 1,
        covid19.diarrhoea.1_numeric == "1" ~ 0,
        covid19.diarrhoea_numeric == "-77" ~ -77,
        covid19.diarrhoea.1_numeric == "-77" ~ -77
          )
    )


covidcns_dat_id %>%
   freq(covid19.diarrhoea_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.diarrhoea =
        recode_factor(covid19.diarrhoea_numeric,
                      "1" = "Yes diarrhoea",
                      "0" = "No diarrhoea",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.diarrhoea)
   
   
### Other
   
      
ovidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.please_describe_your_other_symptoms =
                  covid19.please_describe_your_other_symptoms.txt
          )
    
print(covidcns_dat_id$covid19.other)


      
### At the time of your symptoms, were you a contact of an individual who had COVID-19 symptoms or a positive test?
   
      
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.individual_contact_positive_test_numeric =
          case_when(
        covid19.individual_contact_positive_test_numeric == "1" ~ 1,
        covid19.individual_contact_positive_test_numeric == "3" ~ 0,
        covid19.individual_contact_positive_test_numeric == "-77" ~ -77
          )
    )


covidcns_dat_id %>%
   freq(covid19.individual_contact_positive_test_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.individual_contact_positive_test =
        recode_factor(covid19.individual_contact_positive_test_numeric,
                      "1" = "Yes contact with an individual with COVID19",
                      "0" = "No contact with an individual with COVID19",
                      "-77" = "Seen but not answered",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.individual_contact_positive_test)
   
```

Re-check variable coding
```{r recheck variable coding}
covidcns_dat_id %>%
  select(all_of(starts_with("covid19"))) %>%
  tbl_summary(missing_text = "Missing")
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
covidcns_dat_id <- covidcns_dat_id %>%
  mutate(across(ends_with("numeric"),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)))
```

# Produce sumscores
Reference the scoring guidance that you have used for your questionnaire here "link"

If changing na_limit, CHECK your guidance, na_limit > 0 will replace NAs with 0, ensure that this is correct for your scoring guidance before proceeding

Create vector of item coding
The coding_keys vector must contain 1s for all variables to be added and -1 for all variables to be subtracted.
Putting 0 in the vector will omit the variable at that position.
length(coding_keys) MUST be the same as the number of variables to be summed

sum_vars vector should contain ONLY and ALL variable names needed for scoring, do not add "ID" or "sample" etc.

If using reverse keying:
MAKE SURE that Reverse = TRUE is included as an argument, reverse keying will not work without this
reverse_vars should contain all variable names to be reverse keyed
If running multiple sumscores requiring reverse keying, a single reverse_vars vector containing all of the variable names to be reverse keyed is sufficient: `%in%` will pick the relevant variables for each sumscore

The warnings "Scores vector contains missing values." and "Input contains non-answer values. These will be converted to NA_real_ for this calculation." are normal. They are there to inform you that some sumscores have not been calculated due to non-answer values (e.g. -777) being present. Any other errors or warnings need to be investigated.

Create required variables for sumscore arguments
```{r Sumscores inputs}
keys <- c(
  1,1,1,1,1,1,1,1,1,1,1,1,1,1
  )
sum_vars <- c(
    "covid19.persistent_cough_numeric",
    "covid19.fever_numeric",
    "covid19.loss_of_tasteloss_of_smell_numeric",
    "covid19.intermittent_cough_numeric",
    "covid19.hoarseness_numeric",
    "covid19.sore_throat_numeric",
    "covid19.nasal_dischargecongestion_numeric",
    "covid19.wheeze_numeric",
    "covid19.shortness_of_breath_numeric",
    "covid19.headache_numeric",
    "covid19.muscle_aches_numeric",
    "covid19.nausea_numeric",
    "covid19.diarrhoea_numeric",
    "covid19.other_numeric"
  )
```


Generate sumscores from questionnaire data and use mutate onto dat as new column
sumscores assumes that all items in the questionnaire have the SAME minimum and maximum scores for ALL items, ensure that this is correct before proceeding

When adding the column name for your sumscore use "questionnaire.score_name"

Generate sumscores and add as new column
```{r generate sumscores}
covidcns_dat_id <- covidcns_dat_id %>% 
  mutate(
    covid19.sum_score = 
         sumscores(input = covidcns_dat_id,
                   sum_vars = sum_vars,
                   reverse = FALSE,
                   coding_keys = keys,
                   # method = zero_replace,
                   na_limit = 0.01,
                   min_item = 0,
                   max_item = 1,
                   min_score = 0,
                   max_score = 14
                   )
         )

freq(covidcns_dat_id$covid19.sum_score)

```


```{r severity}

### Measure of COVID19 severity
   
covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
        covid19.severity_numeric =
          case_when(
            covid19.sum_score == 0 ~ '0',
            covid19.sum_score >= 1 & covid19.sum_score <= 4 ~ '1',
            covid19.sum_score >= 4 & covid19.sum_score <= 7 ~ '2',
            covid19.sum_score >= 7 & covid19.sum_score <= 10 ~ '3',
            covid19.sum_score >= 10 & covid19.sum_score <= 14 ~ '4'
          )
    )


covidcns_dat_id %>%
   freq(covid19.severity_numeric)

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(
      covid19.severity =
        recode_factor(covid19.severity_numeric,
                      "0" = "No Symptoms",
                      "1" = "Mild Symptoms",
                      "2" = "Moderate Symptoms",
                      "3" = "Severe Symptoms",
                      "4" = "Very Severe Symptoms",
                      missing = NA_character_
        )
    )
  
covidcns_dat_id %>%
   freq(covid19.severity)
   
```

# Save cleaned data

Check colnames before exporting final dataset
```{r check colnames}
colnames(covidcns_dat_id)
```

# COVID-CNS
```{r Write cleaned GLAD variables to a .rds file}
covidcns_dat_id %>% 
  filter(sample == "COVID-CNS") %>%  # select only GLAD participants
  saveRDS(
    file = paste0(ilovecovidcns, "/data/latest_freeze/baseline/covid19_covid_cns_clean.rds")
    )
```

