---
title: "COVIDCNS Demographics"
author: "Zain Ahmad"
date: "03/09/2022"
output: html_document
---


All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except capitalised first word
Chunk names MUST be unique
Points requiring user input are enclosed thus <>

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_labelled_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the recode_check function - used to check for implausible values when recoding
Add the imp_clean function - used to check variables for implausible values
Add the cont_clean function - used to check continuous variables for implausible values
```{r Read in functions}
source(file = "scripts/functions/add_labelled_numeric.R")
source(file = "scripts/functions/remove_duplicates.R")
source(file = "scripts/functions/sumscores.R")
source(file = "scripts/functions/package_check.R")
source(file = "scripts/functions/recode_check.R")
source(file = "scripts/functions/cont_clean.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("sjlabelled",
              "Amelia",
              "gtsummary",
              "tidyverse")

package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Source filepath to ilovecovidcns OneDrive}
source(file = "scripts/credentials/paths.R")
```

# Read in the data: COVIDCNS Demographics

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the Teams Data Issues Tracker

- For variable names, use ONLY 'questionnaire.variable_name' syntax
- When using pipe operator '%>%', each function should begin on a new line for clarity
- Do not add empty lines at the beginning or end of a chunk to keep the markdown as short as possible
- Use only tidyverse functions wherever possible, they run faster than base R

COVIDCNS data
```{r COVIDCNS load data}
covidcns_dat <- read_rds(
  file = paste0(ilovecovidcns, "/data_raw/2022-05-28/baseline/dem_covid_cns.rds")
  )
  
# Check variable names in dataframe
covidcns_dat %>%
  colnames()

# Inspect dimensions of dataframe 
covidcns_dat %>%
  dim()

# Report counts of duplicates in ID column
covidcns_dat %>%
  select(externalDataReference) %>%
  filter(duplicated(.)) %>%
  count(., externalDataReference)

# Report number of IDs to be dropped
covidcns_excluded <- covidcns_dat %>%
  select(externalDataReference) %>%
  filter(duplicated(.)) %>%
  count(., externalDataReference) %>%
  select("Dropped IDs" = "n") %>%
  colSums() + 1

covidcns_excluded
```

Create new df with renamed and de-duplicated/NA-removed ID column
```{r COVIDCNS select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  dplyr::rename(
    "ID" = "externalDataReference",
    "dem.how_old_are_you_now.txt" = "dem.required_question_eligibility_criteria.txt",
    "dem.sex_at_birth" = "dem.medical_history_birth_relevant",
    "dem.country_of_residence" = "dem.based_confirm_living_question",
    "dem.turkish" = "QID126489347_22",
    "dem.turkish_cypriot" = "QID126489347_23",
    "dem.sri_lankan" = "QID126489349_11",
    "dem.japanese" = "QID126489349_10",
    "dem.current_weight" = "dem.pregnant_weigh_weight_provide",
    "dem.current_weight.1" = "dem.pregnant_weigh_weight_provide.1",
    "dem.current_weight.2" = "dem.pregnant_weigh_weight_provide.2",
    "dem.highest_weight" = "dem.pregnant_weighed_weight_provide",
    "dem.highest_weight.1" = "dem.pregnant_weighed_weight_provide.1",
    "dem.highest_weight.2" = "dem.pregnant_weighed_weight_provide.2",
    "dem.highest_weight_age" = "dem.highest_weight",
    "dem.lowest_weight_adult_height" = "dem.stopped_growing_adult_height",
    "dem.lowest_weight_adult_height.1" = "dem.stopped_growing_adult_height.1",
    "dem.lowest_weight_adult_height.2" = "dem.stopped_growing_adult_height.2",
    "dem.lowest_weight_age" = "dem.lowest_weight_adult_height",
    "dem.metal_implants" = "dem.body_suffered_injury_involving",
    "dem.concerned_memory" = "dem.affects_concerned_live_memory.1",
    "dem.concerned_memory_before_covid" = "dem.affects_concerned_live_memory.2",
    "dem.concerned_memory_after_covid" = "dem.affects_concerned_live_memory",
    "dem.long_ago_diagnosed_years" = "dem.long_ago_diagnosed_required",
    "dem.long_ago_diagnosed_months" = "dem.long_ago_diagnosed_required.1",
    "dem.family_diagnosed_covid19" = "dem.diagnosed_covid19_experienced_similar",
    "dem.middle_wake_night_before_covid" = "dem.middle_wake_night_covid19",
    "dem.middle_wake_night_after_covid" = "dem.middle_wake_night_covid19.1",
  ) %>%
  dplyr::select(
    "ID",
    "startDate",
    "endDate",
    
    #dob/age - clean/create age
    "dem.day",
    "dem.month",
    "dem.year",
    "dem.how_old_are_you_now.txt",
    
    #sex/gender/sexuality/relationship status
    "dem.what_gender_do_you_identify_with",
    "dem.what_gender_do_you_identify_with.txt",
    "dem.do_you_consider_yourself_to_be_transgender",
    "dem.sex_at_birth",
    "dem.have_you_ever_been_pregnant",
    "dem.what_is_your_sexual_orientation",
    "dem.what_is_your_sexual_orientation.txt",
    "dem.what_is_your_current_maritalrelationship_status",
    "dem.what_is_your_current_maritalrelationship_status.txt",
    
    #country of residence
    "dem.country_of_residence",
    
    #education - create unified variable
    "dem.college_or_university_degree",
    "dem.a_levelsas_levels_or_equivalent",
    "dem.o_levelsgcses_or_equivalent",
    "dem.cses_or_equivalent",
    "dem.nvq_or_hnd_or_hnc_or_equivalent",
    "dem.other_professional_qualifications_",
    "dem.other_professional_qualifications_text.txt",
    "dem.none_of_the_above",
    "dem.prefer_not_to_say",
    
    #ethnicity
    "dem.british_mixed_british",
    "dem.irish",
    "dem.northern_irish",
    "dem.any_other_white_background",
    "dem.white_and_black_caribbean",
    "dem.white_and_black_africa",
    "dem.white_and_asian",
    "dem.any_other_mixed_background",
    "dem.indian_or_british_indian",
    "dem.pakistani_or_british_pakistani",
    "dem.bangladeshi_or_british_bangladeshi",
    "dem.any_other_asian_background",
    "dem.caribbean",
    "dem.african",
    "dem.any_other_black_background",
    "dem.chinese",
    "dem.any_other_ethnic_group",
    "dem.other",
    "dem.othertext.txt",
    "dem.english",
    "dem.scottish",
    "dem.welsh",
    "dem.cornish",
    "dem.cypriot_",
    "dem.greek",
    "dem.greek_cypriot",
    "dem.turkish",
    "dem.turkish_cypriot",
    "dem.italian",
    "dem.irish_traveller",
    "dem.traveller",
    "dem.gypsyromany",
    "dem.polish",
    "dem.republics_made_ussr",
    "dem.kosovan",
    "dem.albanian",
    "dem.bosnian",
    "dem.croatian",
    "dem.serbian",
    "dem.republics_made_yugoslavia",
    "dem.mixed_white",
    "dem.other_white_european_european_unspecified_european_mix",
    "dem.black_and_asian",
    "dem.black_and_chinese",
    "dem.black_and_white",
    "dem.chinese_and_white",
    "dem.asian_and_chinese",
    "dem.other_mixed_mixed_unspecified",
    "dem.other_mixed_mixed_unspecifiedtext.txt",
    "dem.mixed_asian",
    "dem.punjabi",
    "dem.kashmiri",
    "dem.east_african_asian",
    "dem.tamil",
    "dem.sinhalese",
    "dem.sri_lankan",
    "dem.japanese",
    "dem.british_asian",
    "dem.caribbean_asian",
    "dem.other_asian_asian_unspecified",
    "dem.other_asian_asian_unspecifiedtext.txt",
    "dem.somali",
    "dem.mixed_black",
    "dem.nigerian",
    "dem.black_british",
    "dem.other_black_black_unspecified",
    "dem.other_black_black_unspecifiedtext.txt",
    "dem.vietnamese",
    "dem.filipino",
    "dem.malaysian",
    "dem.any_other_group",
    "dem.any_other_grouptext.txt",
    
    #language
    "dem.is_english_your_first_language",
    "dem.what_is_your_first_language",
    "dem.what_is_your_first_language.txt",
    
    #height/weight - clean numeric vars
    "dem.please_select_your_preferred_units_of_measurement",
    "dem.what_is_your_current_height",
    "dem.what_is_your_current_height.1",
    "dem.what_is_your_current_height.2",
    "dem.current_weight",
    "dem.current_weight.1",
    "dem.current_weight.2",
    "dem.highest_weight",
    "dem.highest_weight.1",
    "dem.highest_weight.2",
    "dem.highest_weight_age",
    "dem.lowest_weight_adult_height",
    "dem.lowest_weight_adult_height.1",
    "dem.lowest_weight_adult_height.2",
    "dem.lowest_weight_age",
    
    #vision/hearing/handedness
    "dem.how_would_you_describe_your_vision",
    "dem.how_would_you_describe_your_hearing",
    "dem.which_hand_do_you_usually_write_with",
    
    "dem.metal_implants",
    
    #memory
    "dem.concerned_memory",
    "dem.concerned_memory_before_covid",
    "dem.concerned_memory_after_covid",
    "dem.memory_problem_worse_year",
    "dem.has_your_memory_got_progressively_worse",
    
    #covid19
    "dem.diagnosed_required_question_covid19",
    "dem.long_ago_diagnosed_years",
    "dem.long_ago_diagnosed_months",
    "dem.family_diagnosed_covid19",
    
    #quality of life
    "dem.quality_rate_life",
    "dem.happy_general_health",
    "dem.energy_everyday_life",
    "dem.opportunity_leisure_activities",
    "dem.money_day",
    "dem.middle_wake_night_trouble",
    "dem.middle_wake_night_before_covid",
    "dem.middle_wake_night_after_covid"
    
  )

# Inspect colnames
covidcns_dat_id %>%
  colnames()

# Inspect dimensions of new data set
covidcns_dat_id %>%
  dim()
```

Check missingness by missmap
```{r COVIDCNS missmap}
covidcns_dat_id %>% 
  missmap()
```

Create dat as copy of covidcns_dat_id for brevity
This step gives you a 'reset' point: if your variable recoding screws up, re-run this chunk to give you a fresh 'dat' dataframe
```{r Create dat}
dat <- covidcns_dat_id 
```

Extract and save labels
```{r Extract save labels}
# Save variable labels
question_labels <- sjlabelled::get_label(dat)

# Save value labels
answer_labels <- sjlabelled::get_labels(dat, values = "as.name")

# Change -77 to -777 in value labels names
chng <- rapply(sapply(answer_labels, names),
               function(x) ifelse(x==-77, -777, x),
               how = "replace")

#names(answer_labels) <- chng
# Add multiple lines here as necessary to change other nonanswer values in labels
# chng <- rapply(chng,
#                function(x) ifelse(x==-88, -888, x),
#                how = "replace")

# Substitute new value labels into answer_labels
for (i in 1:length(chng)){
  if(!is.null(answer_labels[[i]])){
  names(answer_labels[[i]]) <- chng[[i]]
  }
}
# NA coercion warning is due to text variables containing nothing except -77/NA
# which causes coercion to numeric in get_labels_helper
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(where(is.numeric),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)
                )
         )

# Re-add labels after mutate
dat <- sjlabelled::set_label(dat, question_labels)
dat <- sjlabelled::set_labels(dat, labels = answer_labels)
```

Create list of all labels and attributes
This chunk supersedes all categorical/numeric cleaning
It gives you an output of c(the question label, all value-label pairs)
for each variable
Check for errors in the output of this chunk, including:
- Label spelling errors (for questions and answers)
- Incorrect values
- Mismatches between labels and values
- Scale errors
- Variable naming issues from the data extraction
- Any other issues you can see
All issues/changes need to be logged as a to-do on Teams
At this point, you also need to pick out any continuous, date or text variables 
to be cleaned in the later chunks
```{r List labels attrs}
label_list <- sapply(dat, function(x) c(attr(x, "label"), attr(x, "labels")))
label_list
```


# Recoding Incorrect Variables

## Memory

View dem.concerned_memory
No should be 0 not 2
```{r View dem.concerned_memory values and labels}
attr(dat$dem.concerned_memory, "labels")
```

Recode incorrect variable
Can be removed after data recoded in qualtrics and after data export
If variables are found to be incorrect:
Report the error on Teams
Recode the variable yourself using `case_when` as below
Continue cleaning your script with the recoded variable until fixed from source
DO NOT run this chunk multiple times: it will mess up the variable coding, requiring you to run the script again from the beginning
```{r Recode dem.concerned_memory}
dat <- dat %>% 
  mutate(across(dem.concerned_memory,
                ~case_when(
                  . == 2 ~ 0,
                  TRUE ~ .)))
```

Rename value labels of dem.concerned_memory
```{r Relabel dem.concerned_memory}
# Named vector of correct labels
new_levels_vec <- c("Prefer not to say" = -999,
                    "Seen but not answered" = -777,
                    "Yes" = 1,
                    "No" = 0)

# Assign new labels
dat$dem.concerned_memory <- set_labels(dat$dem.concerned_memory, labels = new_levels_vec)

# Remove labels vector
rm(new_levels_vec)
```

Recheck variable coding
```{r Recheck dem.concerned_memory values and labels}
attr(dat$dem.concerned_memory, "labels")
```


## Pregnancy

View dem.have_you_ever_been_pregnant
Prefer not to say should be -999 not 2
```{r View dem.have_you_ever_been_pregnant values and labels}
attr(dat$dem.have_you_ever_been_pregnant, "labels")
```

Recode incorrect variable
Can be removed after data recoded in qualtrics and after data export
If variables are found to be incorrect:
Report the error on Teams
Recode the variable yourself using `case_when` as below
Continue cleaning your script with the recoded variable until fixed from source
DO NOT run this chunk multiple times: it will mess up the variable coding, requiring you to run the script again from the beginning
```{r Recode dem.have_you_ever_been_pregnant}
dat <- dat %>% 
  mutate(across(dem.have_you_ever_been_pregnant,
                ~case_when(
                  . == 2 ~ -999,
                  TRUE ~ .)))
```

Rename value labels of dem.have_you_ever_been_pregnant
```{r Relabel dem.have_you_ever_been_pregnant}
# Named vector of correct labels
new_levels_vec <- c("Prefer not to say" = -999,
                    "Seen but not answered" = -777,
                    "Yes" = 1,
                    "No" = 0)

# Assign new labels
dat$dem.have_you_ever_been_pregnant <- set_labels(dat$dem.have_you_ever_been_pregnant, labels = new_levels_vec)

# Remove labels vector
rm(new_levels_vec)
```

Recheck variable coding
```{r Recheck dem.have_you_ever_been_pregnant values and labels}
attr(dat$dem.have_you_ever_been_pregnant, "labels")
```


# Create DOB from day/month/year columns

Add 1919 to year column
This needs to be remediated in Qualtrics, current format is unacceptable
```{r Year col add 1919}
dat <- dat %>%
  mutate(
    dem.year = dem.year + 1919
  )
```


Unite columns on "/" using tidyr to create DOB
```{r Unite dob columns}
dob_cols <- c(
  "dem.day",
  "dem.month",
  "dem.year"
)

dat <- dat %>%
  unite(.,
        col = dem.date_of_birth,
        all_of(dob_cols),
        sep = "/",
        remove = FALSE)

dat$dem.date_of_birth <- set_label(dat$dem.date_of_birth, "Date of birth")
```

Parse dob using lubridate
```{r Parse dob}
dat <- dat %>% 
  mutate(dem.date_of_birth = lubridate::parse_date_time(x = dem.date_of_birth,
                                              orders = c("d/m/y"),
                                              tz = "Europe/London")
         )

dat$dem.date_of_birth <- set_label(dat$dem.date_of_birth, "Date of birth")
```

Create dob age using startDate difference
```{r Create dob age}
dat <- dat %>%
  mutate(dem.dob_age = floor((startDate - dem.date_of_birth)/lubridate::dyears(1)))

dat$dem.dob_age <- set_label(dat$dem.dob_age, "Age")

str(dat$dem.dob_age)
```


# Create education unified variable

Categorical variable where highest_education is the variable and qualifications are categories
```{r Create highest qualification variable}
dat <- dat %>%
  mutate(
    dem.highest_education =
      case_when(
        dem.none_of_the_above == 1 ~ 0,
        dem.college_or_university_degree == 1 ~ 1,
        dem.a_levelsas_levels_or_equivalent == 1 ~ 2,
        dem.o_levelsgcses_or_equivalent == 1 ~ 3,
        dem.cses_or_equivalent == 1 ~ 4,
        dem.nvq_or_hnd_or_hnc_or_equivalent == 1 ~ 5,
        dem.other_professional_qualifications_ == 1 ~ 6,
        dem.prefer_not_to_say == 1 ~ -999
        )
    )

# Named vector of labels
new_levels_vec <- c("None of the above" = 0,
                    "College or university degree" = 1,
                    "A levels/AS levels or equivalent" = 2,
                    "O levels/GCSEs or equivalent" = 3,
                    "CSEs or equivalent" = 4,
                    "NVQ or HND or HNC or equivalent" = 5,
                    "Other professional qualifications" = 6,
                    "Prefer not to say" = -999)

# Assign new labels
dat$dem.highest_education <- set_labels(dat$dem.highest_education,
                                        labels = new_levels_vec)
dat$dem.highest_education <- set_label(dat$dem.highest_education,
                                       label = "Highest level of education")

# Remove labels vector
rm(new_levels_vec)

# Check output
sjlabelled::as_label(dat) %>%
  tbl_summary(include = dem.highest_education,
              missing_text = "Missing")
```

# Cleaning Continuous Variables

Create vector of continuous variables
(I suggest adding variable names sorted by type e.g. all ages then all years
etc. to make your life easier when creating limits_mat)
```{r Create cont vars vector}
variables_cont <- c(
  "dem.how_old_are_you_now.txt",
  "dem.dob_age",
  "dem.long_ago_diagnosed_years",
  "dem.long_ago_diagnosed_months"
)

# Check length of vector (must match dim(limits_mat)[1])
length(variables_cont)
```

Create matrix of limits for continuous variables
Matrix is series of vectors (lower, upper)
Define limits for variable and list reasoning below
Variable: Age
- Lower: 16 youngest allowed in study
- Upper: 117 oldest person in world

Variable: Years ago diagnosed with COVID
- Lower: 0 
- Upper: 2 cannot be diagnosed before 2020

Variable: Months ago diagnosed with COVID
- Lower: 0
- Upper: 12 months in a year
```{r Create matrix limits}
# Combine the vectors together
limits_vec <- c(c(16, 117),
                c(16, 117),
                c(0, 2),
                c(0, 12)
                )

# Create matrix, matrices are filled by columns, not rows, so must transpose
limits_mat <- t(matrix(limits_vec, # take values from your vector of limits
                       nrow = 2, # upper and lower bounds
                       ncol = length(variables_cont) # number of variables total
                       ))

# Check dimensions
dim(limits_mat)
```

Set row and col names of limits_mat
This allows your to easily refer back to limits_mat for a summary
```{r Set lim_mat names}
rownames(limits_mat) <- variables_cont
colnames(limits_mat) <- c("Lower", "Upper")
```

Use cont_clean to check if any implausible values and provide replacement vectors
Cont_clean will not proceed if variables are not numeric type, clean manually above if necessary
This chunk reports any variables that contain implausible values
```{r Cont_clean cont vars}
# Execute cleaning function
cont_list <- cont_clean(
  variables = variables_cont,
  limits_mat = limits_mat,
  dat = dat
)

# Create empty list of variable names to check
implaus_checklist <- c()

# Loop through function output
for (i in 1:length(variables_cont)){
  
  # Report only variables containing implausibles
  if(cont_list[[variables_cont[i]]]$Count > 0){
    
    # Add variable name to imp_checklist
    implaus_checklist <- append(x = implaus_checklist, variables_cont[i])
    
    # Report readout of implausible values
    print(paste0("Implausibles in ", variables_cont[i], ": ", cont_list[[variables_cont[i]]]$Count))
  }
}
```

Mutate variables with implausible values removed
Repeat the mutate statements for as many variables as necessary
```{r Mutate cont vars}
dat <- dat %>%
  mutate(
    dem.long_ago_diagnosed_years = cont_list$dem.long_ago_diagnosed_years$Replacement
  )

dat <- dat %>%
  mutate(
    dem.long_ago_diagnosed_months = cont_list$dem.long_ago_diagnosed_months$Replacement
  )
```

Re-inspect variables after cleaning
```{r Cont vars inspect after cleaning}
dat %>%
  select(all_of(variables_cont)) %>%
  tbl_summary(
    missing_text = "Missing",
    statistic = list(all_continuous() ~ "{median} ({p0}, {p5}, {p95}, {p100})")
  )
```


# Add Numeric Variables

Specify columns to be excluded from add_numeric function
Continuous variables should be excluded, as they are already numeric
Text variables also need to be excluded
Do not include ID and sample here
```{r Specify excluded columns}
exclude_cols_numeric <- c(
  "dem.day",
  "dem.month",
  "dem.year",
  "dem.dob_age",
  "dem.how_old_are_you_now.txt",
  "dem.what_gender_do_you_identify_with.txt",
  "dem.what_is_your_sexual_orientation.txt",
  "dem.what_is_your_current_maritalrelationship_status.txt",
  "dem.other_professional_qualifications_text.txt",
  "dem.othertext.txt",
  "dem.other_mixed_mixed_unspecifiedtext.txt",
  "dem.other_asian_asian_unspecifiedtext.txt",
  "dem.other_black_black_unspecifiedtext.txt",
  "dem.any_other_grouptext.txt",
  "dem.what_is_your_first_language.txt",
  "dem.what_is_your_current_height",
  "dem.what_is_your_current_height.1",
  "dem.what_is_your_current_height.2",
  "dem.current_weight",
  "dem.current_weight.1",
  "dem.current_weight.2",
  "dem.highest_weight",
  "dem.highest_weight.1",
  "dem.highest_weight.2",
  "dem.highest_weight_age",
  "dem.lowest_weight_adult_height",
  "dem.lowest_weight_adult_height.1",
  "dem.lowest_weight_adult_height.2",
  "dem.lowest_weight_age",
  "dem.long_ago_diagnosed_years",
  "dem.long_ago_diagnosed_months"
  )
```

Add labelled/numeric columns
Modify the leaders argument if necessary
```{r Add columns}
dat <- dat %>% 
  add_labelled_numeric(exclude = exclude_cols_numeric)

# Inspect colnames
dat %>%
  colnames()
```


# Save cleaned data

# COVIDCNS
```{r Write cleaned COVIDCNS variables to a .rds file}
dat %>%
  saveRDS(
    file = paste0(ilovecovidcns, "/data/latest_freeze/baseline/dem_covidcns_clean.rds")
    )
```