---
title: "COVID CNS: Cleaning employment"
author: "Alish Palmos"
date: "14/01/2022"
output: html_document
---

# Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

```{r Clear global environment}
rm(list=ls())
```

```{r Read in functions}
source(file = "../functions/add_numeric.R")
source(file = "../functions/sumscores.R")
source(file = "../functions/package_check.R")
source(file = "../functions/remove_duplicates.R")
source(file = "../functions/imp_check.R")
```

Note: always load tidyverse last
```{r Install load dependencies}
packages = c(
  "summarytools",
  "sjlabelled",
  "Amelia",
  "knitr",
  "gtsummary",
  "tidyverse"
  )
package_check(packages)
```

```{r Get system date}
date <- Sys.Date()
date
```

```{r Source the credentials file}
source("../credentials/paths.R")
```

# Read in the data 
```{r COVID CNS employment data}
covidcns_dat <- read_rds(file = 
                   paste0(ilovedata, "/data_raw/latest_freeze/covid_cns/baseline/impact_covid_cns.rds")
                 )

# check
covidcns_dat %>% 
  dim()

covidcns_dat %>% 
  colnames()
```

Specify columns to be excluded from add_numeric function
Continuous variables should be excluded, as they are already numeric
```{r COVID CNS specify excluded columns}
exclude_cols_numeric <- c(
  "ID",
  "sample",
  "startDate",
  "endDate",
  "impact.othertext.txt"
  )
```

Select & rename relevant columns
```{r COVID CNS select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "COVID-CNS",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         startDate,
         endDate,
         sample,
         impact.fulltime_employed,
         impact.unemployed,
         impact.stayathome_parent_or_carer,
         impact.contract_or_freelance_work,
         impact.receiving_state_income,
         impact.student_,
         impact.prefer_not_to_say,
         impact.parttime_employed,
         impact.zerohours_contract,
         impact.selfemployed,
         impact.small_buisness_owner,
         impact.retired,
         impact.student_.1,
         #employment chnage: 
         impact.my_employment_status_has_not_changed,
         impact.become_unemployed,
         impact.become_employed,
         impact.reduction_in_hours,
         impact.increased_hours,
         impact.benefits_increased,
         impact.furloughed_or_paid_leave_,
         impact.paid_leave_furloughed,
         impact.other,
         impact.changes_in_duties_or_responsibilities,
         impact.reduction_in_salary,
         impact.increased_salary,
         impact.benefits_decreased,
         impact.furloughed_or_paid_leave_.1,
         impact.taking_unpaid_leave,
         impact.prefer_not_to_say.1,
         impact.losing_skip_risk_prefer,
         impact.symptoms_impacted_carry_employment,
         impact.employment_status_changed_contracting
         ) %>%
  add_numeric(exclude = exclude_cols_numeric)
# Inspect colnames
covidcns_dat_id %>%
  colnames()
```

Look at number of people excluded
The number of people to be excluded should be negative
```{r COVID CNS number excluded}
# Inspect dimensions of new data set
covidcns_dat_id %>%
  dim()
# Inspect number of rows dropped
covidcns_excluded <- dim(covidcns_dat_id)[1] - dim(covidcns_dat)[1]
covidcns_excluded
```

Inspect numeric variables
```{r COVID CNS inspect numeric variables}
covidcns_dat_id %>%
  select(all_of(ends_with("numeric"))) %>%
  tbl_summary(missing_text = "Missing")
```

Check missingness by missmap
```{r COVID CNS inspect missingness}
covidcns_miss_map <- covidcns_dat_id %>% 
  missmap()
covidcns_miss_map
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
covidcns_dat_id <- covidcns_dat_id %>%
  mutate(across(ends_with("numeric"),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)))
```


Cleaning Numeric 0-1 variables
```{r vector of numeric values}
values_numeric_0_1 <- c(
  0,
  1,
  -777,
  NA
  )
values_numeric_0_1
```


Create vector of variable names for numeric variables
```{r vector numeric variables}
variables_numeric_0_1 <- c(
  "impact.fulltime_employed_numeric",
  "impact.unemployed_numeric",
  "impact.stayathome_parent_or_carer_numeric",
  "impact.contract_or_freelance_work_numeric",
  "impact.receiving_state_income_numeric",
  "impact.student__numeric",
  "impact.prefer_not_to_say_numeric",
  "impact.parttime_employed_numeric",
  "impact.zerohours_contract_numeric",
  "impact.selfemployed_numeric",
  "impact.small_buisness_owner_numeric",
  "impact.retired_numeric",
  "impact.student_.1_numeric",
  "impact.my_employment_status_has_not_changed_numeric",
  "impact.become_unemployed_numeric",
  "impact.become_employed_numeric",
  "impact.reduction_in_hours_numeric",
  "impact.increased_hours_numeric",
  "impact.benefits_increased_numeric",
  "impact.furloughed_or_paid_leave__numeric",
  "impact.paid_leave_furloughed_numeric",
  "impact.other_numeric",
  "impact.changes_in_duties_or_responsibilities_numeric",
  "impact.reduction_in_salary_numeric",
  "impact.increased_salary_numeric",
  "impact.benefits_decreased_numeric",
  "impact.furloughed_or_paid_leave_.1_numeric",
  "impact.taking_unpaid_leave_numeric",
  "impact.prefer_not_to_say.1_numeric",
  "impact.my_employment_status_has_not_changed_numeric",
  "impact.become_unemployed_numeric",
  "impact.become_employed_numeric",
  "impact.reduction_in_hours_numeric",
  "impact.increased_hours_numeric",
  "impact.benefits_increased_numeric",
  "impact.furloughed_or_paid_leave__numeric",
  "impact.paid_leave_furloughed_numeric",
  "impact.other_numeric",
  "impact.changes_in_duties_or_responsibilities_numeric",
  "impact.reduction_in_salary_numeric",
  "impact.increased_salary_numeric",
  "impact.benefits_decreased_numeric",
  "impact.furloughed_or_paid_leave_.1_numeric",
  "impact.taking_unpaid_leave_numeric",
  "impact.prefer_not_to_say.1_numeric",
  "impact.symptoms_impacted_carry_employment_numeric"
  )
variables_numeric_0_1
```

Use imp_check function to find if any implausible values and obtain summary table of variables
```{r imp_check numeric variables}
imp_check(data = covidcns_dat_id,
           variables = variables_numeric_0_1,
          values = values_numeric_0_1)
```


Name your vectors in line with the chunks below
Number the vectors or name them intuitively if you have multiple vectors
Vectors of potential values should only contain possible values (exclude nonanswer values as appropriate)

Create vector of categorical values for  variables
```{r vector categorical values}
values_categorical_0_1 <- c(
  "Yes",
  "No",
  "Prefer not to answer",
  "Seen but not answered",
  NA
  )
values_categorical_0_1
```

Create vector of variable names for categorical  variables
```{r vector categorical variables}
variables_categorical_0_1 <-
  c(
    "impact.symptoms_impacted_carry_employment",
    "impact.employment_status_changed_contracting"
    )
variables_categorical_0_1
```

Use imp_check function to find if any implausible values and obtain summary
table of variables
```{r imp_check categorical variables}
imp_check(data = covidcns_dat_id,
          variables = variables_categorical_0_1,
          values = values_categorical_0_1)
```

# Change the COVID CNS variables to mactch GLAD

1	In paid employment or self-employed
2	Retired
3	Looking after home and/or family
4	Unable to work because of sickness or disability
5	Unemployed
6	Doing unpaid or voluntary work
7	Full or part-time student
8	None of the above
-99	Prefer not to answer

#Employment 
```{r change COVID CNS variables to match GLAD}

covidcns_dat_id <- covidcns_dat_id %>%
  mutate(
    impact.what_is_your_current_employment_status_numeric = 
      case_when(
         impact.fulltime_employed_numeric == 1 ~ 1,
         impact.parttime_employed_numeric == 1 ~ 1,
         impact.unemployed_numeric == 1 ~ 5,
         impact.zerohours_contract_numeric == 1 ~ 1,
         impact.stayathome_parent_or_carer_numeric == 1 ~ 3,
         impact.selfemployed_numeric == 1 ~ 1,
         impact.contract_or_freelance_work_numeric == 1 ~ 1,
         impact.small_buisness_owner_numeric == 1 ~ 1,
         impact.receiving_state_income_numeric == 1 ~ 4,
         impact.retired_numeric == 1 ~ 2,
         impact.student__numeric == 1 ~ 7,
         impact.student_.1_numeric == 1 ~ 7,
           (impact.fulltime_employed_numeric == -77 |
            impact.parttime_employed_numeric == -77 |
            impact.unemployed_numeric == -77 |
            impact.zerohours_contract_numeric == -77 |
            impact.stayathome_parent_or_carer_numeric == -77 |
            impact.selfemployed_numeric == -77 |
            impact.contract_or_freelance_work_numeric == -77 |
            impact.small_buisness_owner_numeric == -77 |
            impact.receiving_state_income_numeric == -77 |
            impact.retired_numeric == -77 |
            impact.student__numeric == -77 |
            impact.student_.1_numeric == -77) ~ -77
      )
  )

covidcns_dat_id <- covidcns_dat_id %>%
  mutate(
    impact.what_is_your_current_employment_status =
      recode_factor(impact.what_is_your_current_employment_status_numeric,
                    "1" = "In paid employment or self-employed",
                    "2" = "Retired",
                    "3" = "Looking after home and/or family",
                    "4" = "Unable to work because of sickness or disability",
                    "5" = "Unemployed",
                    "6" = "Doing unpaid or voluntary work",
                    "7" = "Full or part-time student",
                    "8" = "None of the above",
                    "-77" = "Seen not to answered",
                    missing = NA_character_
      )
  )
```

#Employment change due to covid
```{r change COVID CNS variables to match GLAD}

covidcns_dat_id <- covidcns_dat_id %>%
  mutate(
    impact.employment_changed_due_to_covid_numeric = 
      case_when(
         impact.my_employment_status_has_not_changed_numeric == 1 ~ 0,
         impact.become_unemployed_numeric == 1 ~ 1,
         impact.become_employed_numeric == 1 ~ 2,
         impact.reduction_in_hours_numeric == 1 ~ 3,
         impact.increased_hours_numeric == 1 ~ 4,
         impact.benefits_increased_numeric == 1 ~ 5,
         impact.furloughed_or_paid_leave__numeric == 1 ~ 6,
         impact.paid_leave_furloughed_numeric == 1 ~ 7,
         impact.other_numeric == 1 ~ 8,
         impact.changes_in_duties_or_responsibilities_numeric == 1 ~ 9,
         impact.reduction_in_salary_numeric == 1 ~ 10,
         impact.increased_salary_numeric == 1 ~ 11,
         impact.benefits_decreased_numeric == 1 ~ 12,
         impact.furloughed_or_paid_leave_.1_numeric == 1 ~ 13,
         impact.taking_unpaid_leave_numeric == 1 ~ 14,
         impact.prefer_not_to_say.1_numeric == 1 ~ -999,
           (impact.my_employment_status_has_not_changed_numeric == -777 |
            impact.become_unemployed_numeric == -777 |
            impact.become_employed_numeric == -777 |
            impact.reduction_in_hours_numeric == -777 |
            impact.increased_hours_numeric == -777 |
            impact.benefits_increased_numeric == -777 |
            impact.furloughed_or_paid_leave__numeric == -777 |
            impact.paid_leave_furloughed_numeric == -777 |
            impact.other_numeric == -777 |
            impact.changes_in_duties_or_responsibilities_numeric == -777 |
            impact.reduction_in_salary_numeric == -777 |
            impact.increased_salary_numeric == -777 |
            impact.benefits_decreased_numeric == -777 |
            impact.furloughed_or_paid_leave_.1_numeric == -777 |
            impact.taking_unpaid_leave_numeric == -777 |
            impact.prefer_not_to_say.1_numeric == -777) ~ -777
      )
)
  

covidcns_dat_id <- covidcns_dat_id %>%
  mutate(
    impact.employment_changed_due_to_covid =
      recode_factor(impact.employment_changed_due_to_covid_numeric,
                    "0" = "My employment status has not changed",
                    "1" = "Become unemployed",
                    "2" = "Become employed",
                    "3" = "Reduction in hours",
                    "4" = "Increased hours",
                    "5" = "Benefits increased",
                    "6" = "Furloughed or paid leave (Government funded)",
                    "7" = "Furloughed or paid leave (Government funded with company supplement)",
                    "8" = "Other",
                    "9" = "Changes in duties or responsibilities",
                    "10" = "Reduction in salary", 
                    "11" = "Increased Salary", 
                    "12" = "Benefits decreased",
                    "13" = "Furloughed or paid leave (Company funded)", 
                    "14" = "Taking unpaid leave", 
                    "-777" = "Seen not to answered",
                    "-999" = "Prefer not to say",
                    missing = NA_character_
      )
  )
```

# Save cleaned data
Check colnames before exporting final dataset
```{r check colnames}
colnames(covidcns_dat_id)
```

# COVID-CNS
```{r Write cleaned COVID-CNS variables to a .rds file}
covidcns_dat_id %>% 
  filter(sample == "COVID-CNS") %>%  # select only COVID-CNS participants
  saveRDS(file = 
            paste0(ilovedata, "/data/latest_freeze/covidcns/employment_covidcns_clean.rds")
    )
```


