---
title: "COVIDCNS Impact Cleaning Script"
author: "Zain Ahmad"
date: "21/05/2022"
output: html_document
---


All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except:
Study name (COVIDCNS) all caps
Capitalised first word
Chunk names MUST be unique
Points requiring user input are enclosed thus <>

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the recode_check function - used to check for implausible values when recoding
Add the imp_clean function - used to check variables for implausible values
Add the cont_clean function - used to check continuous variables for implausible values
```{r Read in functions}
source(file = "scripts/functions/add_numeric_3.R")
source(file = "scripts/functions/remove_duplicates.R")
source(file = "scripts/functions/sumscores.R")
source(file = "scripts/functions/package_check.R")
source(file = "scripts/functions/recode_check.R")
source(file = "scripts/functions/cont_clean.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("sjlabelled",
              "Amelia",
              "gtsummary",
              "tidyverse")
package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Source filepath to ilovecovidcns OneDrive}
source(file = "scripts/credentials/paths.R")
```

# Read in the data: COVIDCNS Impact

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the Teams Data Issues Tracker

- For variable names, use ONLY 'questionnaire.variable_name' syntax
- For dataset, only use snake_case naming
- When using pipe operator '%>%', each function should begin on a new line
- Do not add empty lines at the beginning or end of a chunk
- Use only tidyverse functions wherever possible

COVIDCNS data
```{r COVIDCNS load data}
covidcns_dat <- read_rds(
  file = paste0(ilovecovidcns,"/data_raw/latest_freeze/baseline/impact_covid_cns.rds")
  )
  
# Check variable names in dataframe
covidcns_dat %>%
  colnames()

# Inspect dimensions of dataframe 
covidcns_dat %>%
  dim()

# Count NAs in ID column
sum(is.na(covidcns_dat$externalDataReference))

# Count duplicates in ID column
sum(table(covidcns_dat$externalDataReference)-1)

# Report duplicates in ID column
table(covidcns_dat$externalDataReference)[table(covidcns_dat$externalDataReference)>1]
```

Create new df with renamed and de-duplicated/NA-removed ID column
```{r COVIDCNS select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  dplyr::rename(
    "ID" = "externalDataReference"
  )

# Inspect colnames
covidcns_dat_id %>%
  colnames()
```

Look at number of people excluded
The number of people to be excluded should be negative
```{r COVIDCNS number excluded}
# Inspect dimensions of new data set
covidcns_dat_id %>%
  dim()

# Inspect number of rows dropped
covidcns_excluded <- dim(covidcns_dat_id)[1] - dim(covidcns_dat)[1]
covidcns_excluded
```

Check missingness by missmap
```{r COVIDCNS missmap}
covidcns_dat_id %>% 
  missmap()
```

Create dat as copy of covidcns_dat_id for brevity
This step gives you a 'reset' point: if your variable recoding screws up, re-run this chunk to give you a fresh 'dat' dataframe
```{r Create dat}
dat <- covidcns_dat_id 
```

Extract and save labels
```{r Extract save labels}
# Save variable labels
question_labels <- sjlabelled::get_label(dat)

# Save value labels
answer_labels <- sjlabelled::get_labels(dat, values = "as.name")
```

Change answer_labels to fit 3 digit non-answer values
```{r Modify answer_labels}
# Change non-answers in value labels names
chng <- rapply(sapply(answer_labels, names), function(x) ifelse(x==-77,-777,x), how = "replace")
chng <- rapply(chng, function(x) ifelse(x==-55,-555,x), how = "replace")
chng <- rapply(chng, function(x) ifelse(x==-88,-888,x), how = "replace")
chng <- rapply(chng, function(x) ifelse(x==-99,-999,x), how = "replace")

# Substitute new value labels into answer_labels
for (i in 5:length(chng)){
  names(answer_labels[[i]]) <- chng[[i]]
}

# Remove chng
rm(chng)
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(where(is.numeric),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)
                )
         )

# Re-add labels after mutate
dat <- sjlabelled::set_label(dat, question_labels)
dat <- sjlabelled::set_labels(dat, labels = answer_labels)
```

Create list of all labels and attributes
This chunk supersedes all categorical/numeric cleaning
It gives you an output of c(the question label, all value-label pairs)
for each variable
Check for errors in the output of this chunk, including:
- Label spelling errors (for questions and answers)
- Incorrect values
- Mismatches between labels and values
- Scale errors
- Variable naming issues from the data extraction
- Any other issues you can see
All issues/changes need to be logged as a to-do on Teams
At this point, you also need to pick out any continuous, date or text variables 
to be cleaned in the later chunks
```{r List labels attrs}
lablst <- sapply(dat, function(x) c(attr(x, "label"), attr(x, "labels")))
lablst
```


# Rectifying incorrect variable naming

View impact.small_buisness_owner
Misspelled variable name and associated label
```{r View impact.small_buisness_owner}
str(dat$impact.small_buisness_owner)
```

Rename impact.small_buisness_owner using dplyr rename
```{r Rename impact.small_buisness_owner}
dat <- dat %>%
  rename("impact.small_business_owner" = "impact.small_buisness_owner")
```

Reset impact.small_business_owner variable label
```{r Reset impact.small_business_owner label}
dat$impact.small_business_owner <- set_label(dat$impact.small_business_owner, c("impact.small_business_owner" = "What was your employment status prior to contracting COVID-19 ?"))
```

Check impact.small_business_owner naming
```{r Recheck impact.small_business_owner naming}
str(dat$impact.small_business_owner)
```


# Rectifying incorrect variable labelling

Check impact.small_business_owner labels
Misspelled variable labels
Misspelled variable name and associated label also requires noting
```{r Check impact.small_business_owner labelling}
str(dat$impact.small_business_owner)
```

Rename value labels of impact.small_business_owner
```{r Rename impact.small_business_owner value labels}
# Named vector of correct labels
new_levels_vec <- c("Not Small business owner" = 0, "Small business owner" = 1)

# Assign new labels
dat$impact.small_business_owner <- set_labels(dat$impact.small_business_owner, labels = new_levels_vec)

# Remove labels vector
rm(new_levels_vec)
```

Recheck impact.small_business_owner labelling
```{r Recheck impact.small_business_owner labelling}
str(dat$impact.small_business_owner)
```


# Create phenotypes

# Employment
Change the COVID CNS variables to match GLAD

1	In paid employment or self-employed
2	Retired
3	Looking after home and/or family
4	Unable to work because of sickness or disability
5	Unemployed
6	Doing unpaid or voluntary work
7	Full or part-time student
8	None of the above
-99	Prefer not to answer

Create current employment status variable
```{r Create emp status}
dat <- dat %>%
  mutate(
    impact.current_employment_status =
      case_when(
        # cat 1 paid emp/self-emp
        impact.fulltime_employed == 1 ~ 1,
        impact.parttime_employed == 1 ~ 1,
        impact.zerohours_contract == 1 ~ 1,
        impact.selfemployed == 1 ~ 1,
        impact.contract_or_freelance_work == 1 ~ 1,
        impact.small_business_owner == 1 ~ 1,
        # cat 2 retired
        impact.retired == 1 ~ 2,
        # cat 3 looking after home/family
        impact.stayathome_parent_or_carer == 1 ~ 3,
        # cat 4 unable to work sick/disabled
        impact.receiving_state_income == 1 ~ 4,
        # cat 5 unemployed
        impact.unemployed == 1 ~ 5,
        # cat 6 unpaid/voluntary not covered
        # cat 7 student
        impact.student_ == 1 ~ 7, #school
        impact.student_.1 == 1 ~ 7, #uni
        
        # prefer not to say
        impact.prefer_not_to_say == 1 ~ -999,
        
        impact.fulltime_employed == -777 |
        impact.parttime_employed == -777 |
        impact.unemployed == -777 |
        impact.zerohours_contract == -777 |
        impact.stayathome_parent_or_carer == -777 |
        impact.selfemployed == -777 |
        impact.contract_or_freelance_work == -777 |
        impact.small_business_owner == -777 |
        impact.receiving_state_income == -777 |
        impact.retired == -777 |
        impact.student_ == -777 |
        impact.student_.1 == -777 ~ -777
      )
  )
dat %>%
  select(impact.current_employment_status) %>%
  tbl_summary(missing_text = "Missing")
```

Label current employment status
```{r Label emp status}
# Set question label
dat$impact.current_employment_status <- sjlabelled::set_label(dat$impact.current_employment_status, "What is your current employment status?")

# Create vector of answer labels
emp_status_labels <- c("In paid employment or self-employed" = 1,
                       "Retired" = 2,
                       "Looking after home and/or family" = 3,
                       "Unable to work because of sickness or disability" = 4,
                       "Unemployed" = 5,
                       "Full or part-time student" = 7,
                       "Prefer not to say" = -999,
                       "Seen but not answered" = -777)

# Set answer labels
dat$impact.current_employment_status <- sjlabelled::set_labels(dat$impact.current_employment_status,
                                                        labels = emp_status_labels)

# Remove vector of answer labels
rm(emp_status_labels)

# View variable to check
sjlabelled::as_label(dat) %>%
  select(impact.current_employment_status) %>%
  tbl_summary(missing_text = "Missing")
```

Employment change due to covid collapsed to single factor

Create employment change covid variable
```{r Create emp change}
dat <- dat %>%
  mutate(
    impact.employment_change_covid =
      case_when(
        impact.my_employment_status_has_not_changed == 1 ~ 0,
        impact.become_unemployed == 1 ~ 1,
        impact.become_employed == 1 ~ 2,
        impact.reduction_in_hours == 1 ~ 3,
        impact.increased_hours == 1 ~ 4,
        impact.benefits_increased == 1 ~ 5,
        impact.furloughed_or_paid_leave_ == 1 ~ 6,
        impact.paid_leave_furloughed == 1 ~ 7,
        impact.other == 1 ~ 8,
        impact.changes_in_duties_or_responsibilities == 1 ~ 9,
        impact.reduction_in_salary == 1 ~ 10,
        impact.increased_salary == 1 ~ 11,
        impact.benefits_decreased == 1 ~ 12,
        impact.furloughed_or_paid_leave_.1 == 1 ~ 13,
        impact.taking_unpaid_leave == 1 ~ 14,
        impact.prefer_not_to_say.1 == 1 ~ -999,
        impact.my_employment_status_has_not_changed == -777 |
        impact.become_unemployed == -777 |
        impact.become_employed == -777 |
        impact.reduction_in_hours == -777 |
        impact.increased_hours == -777 |
        impact.benefits_increased == -777 |
        impact.furloughed_or_paid_leave_ == -777 |
        impact.paid_leave_furloughed == -777 |
        impact.other == -777 |
        impact.changes_in_duties_or_responsibilities == -777 |
        impact.reduction_in_salary == -777 |
        impact.increased_salary == -777 |
        impact.benefits_decreased == -777 |
        impact.furloughed_or_paid_leave_.1 == -777 |
        impact.taking_unpaid_leave == -777 |
        impact.prefer_not_to_say.1 == -777 ~ -777
      )
  )
dat %>%
  select(impact.employment_change_covid) %>%
  tbl_summary()
```

Label employment change covid variable
```{r Label emp change}
# Set question label
dat$impact.employment_change_covid <- sjlabelled::set_label(dat$impact.employment_change_covid, "Did your employment status change due to COVID?")

# Create vector of answer labels
emp_change_labels <- c("My employment status has not changed" = 0,
                       "Become unemployed" = 1,
                       "Become employed" = 2,
                       "Reduction in hours" = 3,
                       "Increased hours" = 4,
                       "Benefits increased" = 5,
                       "Furloughed or paid leave (Government funded)" = 6,
                       "Furloughed or paid leave (Government funded with company supplement)" = 7,
                       "Other" = 8,
                       "Changes in duties or responsibilities" = 9,
                       "Reduction in salary" = 10,
                       "Increased Salary" = 11,
                       "Benefits decreased" = 12,
                       "Furloughed or paid leave (Company funded)" = 13,
                       "Taking unpaid leave" = 14,
                       "Seen but not answered" = -777,
                       "Prefer not to say" = -999)

# Set answer labels
dat$impact.employment_change_covid <- sjlabelled::set_labels(dat$impact.employment_change_covid,
                                                        labels = emp_change_labels)

# Remove vector of answer labels
rm(emp_change_labels)

# Check attributes
c(attr(dat$impact.employment_change_covid, "label"), attr(dat$impact.employment_change_covid, "labels"))

# View variable to check
sjlabelled::as_label(dat) %>%
  select(impact.employment_change_covid) %>%
  tbl_summary(missing_text = "Missing")
```

# Add Numeric Variables

Specify columns to be excluded from add_numeric function
Continuous variables should be excluded, as they are already numeric
Text variables also need to be excluded
```{r Specify excluded columns}
exclude_cols_numeric <- c(
  "impact.othertext.txt"
  )
```

Add numeric columns
```{r Add numeric}
dat <- dat %>% 
  add_numeric_3(exclude = exclude_cols_numeric)

# Inspect colnames
dat %>%
  colnames()
```


# Save cleaned data

# COVIDCNS
```{r Write cleaned COVIDCNS variables to a .rds file}
dat %>%
  saveRDS(
    file = paste0(ilovecovidcns, "/data/latest_freeze/baseline/impact_covidcns_clean.rds")
    )
```