---
title: "PCL5 COVID CNS"
author: "Chelsea Mika Malouf"
date: "04/03/2022"
output: html_document
---

Cleaning script for PCL-5 following Zain's template script: https://github.com/tnggroup/ilovedata/pull/122/files.

# Set up
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

```{r Clear global environment}
remove(list = ls())
```

```{r Read in functions}
source(file = "../../functions/add_numeric.R")
source(file = "../../functions/remove_duplicates.R")
source(file = "../../functions/sumscores.R")
source(file = "../../functions/package_check.R")
source(file = "../../functions/imp_check.R")
```

```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

```{r Recent date}
date <- Sys.Date()
date
```

```{r Read in file with path to ilovedata channel on teams}
source(file = "../../credentials/paths.R")
```

# Read in the data: CNS PTSD Checklist (PCL-5)

## CNS
```{r CNS load data}
covidcns_dat <- read_rds(
  file = paste0(ilovedata, "/data_raw/latest_freeze/covid_cns/baseline/pcl5_covid_cns.rds")
  )
  
# Check variable names in dataframe
covidcns_dat %>%
  colnames()
# Inspect dimensions of dataframe 
covidcns_dat %>%
  dim()
```

```{r COVID CNS specify excluded columns}
exclude_cols_numeric <- c(
  "ID",
  "sample",
  "startDate",
  "endDate"
  )
```

```{r COVID CNS select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  distinct(externalDataReference,
           .keep_all = TRUE) %>% # Remove duplicate IDs
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "COVIDCNS",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         sample,
         startDate,
         endDate,
         pcl5.repeated_disturbing_stressful_experience,
         pcl5.repeated_disturbing_dreams_of_the_stressful_experience,
         pcl5.stressful_experience_acting_happening,
         pcl5.stressful_experience_reminded_upset,
         pcl5.stressful_experience_reminded_strong,
         pcl5.avoiding_memories_thoughts_stressful,
         pcl5.avoiding_external_reminders_of_the_stressful_experience_,
         pcl5.stressful_experience_trouble_remembering,
         pcl5.world_people_strong_negative,
         pcl5.stressful_experience_blaming_happened,
         pcl5.fear_horror_anger_guilt,
         pcl5.enjoy_activities_interest_loss,
         pcl5.cut_people_feeling_distant,
         pcl5.trouble_experiencing_positive_feelings_,
         pcl5.irritable_behaviour_angry_outburst_or_acting_aggressively,
         pcl5.risks_taking_harm_things,
         pcl5.being_superalert_or_watchful_or_on_guard,
         pcl5.feeling_jumpy_or_easily_startled,
         pcl5.having_difficulty_concentrating,
         pcl5.trouble_falling_or_staying_sleep
         ) %>%
  add_numeric(exclude = exclude_cols_numeric)
# Inspect colnames
covidcns_dat_id %>%
  colnames()
```

```{r COVIDCNS number excluded}
# Inspect dimensions of new data set
covidcns_dat_id %>%
  dim()
# Inspect number of rows dropped
covidcns_excluded <- dim(covidcns_dat_id)[1] - dim(covidcns_dat)[1]
covidcns_excluded
```

Check missingness by missmap
```{r COVIDCNS inspect missingness}
covidcns_miss_map <- covidcns_dat_id %>% 
  missmap()
covidcns_miss_map
```

Create dat as copy of covidcns_dat_id for brevity
This step gives you a 'reset' point: if your variable recoding screws up, re-run this chunk to give you a fresh 'dat' dataframe
```{r Create dat}
dat <- covidcns_dat_id 
# Check
dat %>% glimpse()
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(ends_with("numeric"),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)))
```

Create list of all unique values
```{r List unique values}
ulst <- sapply(dat, unique)
```


# Categorical variables 

## 0-4: 'Not at all' to 'Extremely'
Note: PCL-5 items are scored 0-4 (changed introduced for DSM-5), unlike PCL-6 items which are scored 1-5 as they are adapted from the PCL-C (DSM-IV): https://www.ptsd.va.gov/professional/assessment/adult-sr/ptsd-checklist.asp
```{r vector categorical variables 0_4}
variables_categorical_0_4 <-
  c(
    "pcl5.repeated_disturbing_stressful_experience",
    "pcl5.repeated_disturbing_dreams_of_the_stressful_experience",
    "pcl5.stressful_experience_acting_happening",
    "pcl5.stressful_experience_reminded_upset",
    "pcl5.stressful_experience_reminded_strong",
    "pcl5.avoiding_memories_thoughts_stressful",
    "pcl5.avoiding_external_reminders_of_the_stressful_experience_",
    "pcl5.stressful_experience_trouble_remembering",
    "pcl5.world_people_strong_negative",
    "pcl5.stressful_experience_blaming_happened",
    "pcl5.fear_horror_anger_guilt",
    "pcl5.enjoy_activities_interest_loss",
    "pcl5.cut_people_feeling_distant",
    "pcl5.trouble_experiencing_positive_feelings_",
    "pcl5.irritable_behaviour_angry_outburst_or_acting_aggressively",
    "pcl5.risks_taking_harm_things",
    "pcl5.being_superalert_or_watchful_or_on_guard",
    "pcl5.feeling_jumpy_or_easily_startled",
    "pcl5.having_difficulty_concentrating",
    "pcl5.trouble_falling_or_staying_sleep"
  )
variables_categorical_0_4
```

```{r vector categorical values}
values_categorical_0_4 <- c(
  "Seen but not answered",
  "Prefer not to answer",
  "Not at all",
  "A little bit",
  "Moderately",
  "Quite a bit",
  "Extremely",
  NA
  )
values_categorical_0_4
```

```{r imp_check categorical variables 0_4}
imp_check(data = dat,
          variables = variables_categorical_0_4,
          values = values_categorical_0_4)
#There are no implausible values in the dataset. Can leave these variables as they are
```



# Numeric variables

## 0-4
```{r vector numeric variables 0_4 numeric}
variables_numeric_0_4 <-
  c(
    "pcl5.repeated_disturbing_stressful_experience_numeric",
    "pcl5.repeated_disturbing_dreams_of_the_stressful_experience_numeric",
    "pcl5.stressful_experience_acting_happening_numeric",
    "pcl5.stressful_experience_reminded_upset_numeric",
    "pcl5.stressful_experience_reminded_strong_numeric",
    "pcl5.avoiding_memories_thoughts_stressful_numeric",
    "pcl5.avoiding_external_reminders_of_the_stressful_experience__numeric",
    "pcl5.stressful_experience_trouble_remembering_numeric",
    "pcl5.world_people_strong_negative_numeric",
    "pcl5.stressful_experience_blaming_happened_numeric",
    "pcl5.fear_horror_anger_guilt_numeric",
    "pcl5.enjoy_activities_interest_loss_numeric",
    "pcl5.cut_people_feeling_distant_numeric",
    "pcl5.trouble_experiencing_positive_feelings__numeric",
    "pcl5.irritable_behaviour_angry_outburst_or_acting_aggressively_numeric",
    "pcl5.risks_taking_harm_things_numeric",
    "pcl5.being_superalert_or_watchful_or_on_guard_numeric",
    "pcl5.feeling_jumpy_or_easily_startled_numeric",
    "pcl5.having_difficulty_concentrating_numeric",
    "pcl5.trouble_falling_or_staying_sleep_numeric"
    )
variables_numeric_0_4
```

```{r pcl-6 0-4 vector numeric values}
values_numeric_0_4 <- c(
  0,
  1,
  2,
  3,
  4,
  -777,
  NA
  )
values_numeric_0_4
```

```{r imp_check numeric variables}
imp_check(data = dat,
          variables = variables_numeric_0_4,
          values = values_numeric_0_4)
#There are no implausible values in the dataset. Can leave these variables as they are
```



# Produce sumscores

Create required variables for sumscore arguments
Note: Sumscore only includes the 20 items from PCL-5 DSM-5 checklist: https://www.ptsd.va.gov/professional/assessment/adult-sr/ptsd-checklist.asp. Does not include "Felt that there was no point in planning for the future?" item which was part of the PCL-5 for DSM-IV but not DSM-5.
```{r Sumscores inputs}
keys <- c(
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1
  )
sum_vars <- c(
    "pcl5.repeated_disturbing_stressful_experience_numeric",
    "pcl5.repeated_disturbing_dreams_of_the_stressful_experience_numeric",
    "pcl5.stressful_experience_acting_happening_numeric",
    "pcl5.stressful_experience_reminded_upset_numeric",
    "pcl5.stressful_experience_reminded_strong_numeric",
    "pcl5.avoiding_memories_thoughts_stressful_numeric",
    "pcl5.avoiding_external_reminders_of_the_stressful_experience__numeric",
    "pcl5.stressful_experience_trouble_remembering_numeric",
    "pcl5.world_people_strong_negative_numeric",
    "pcl5.stressful_experience_blaming_happened_numeric",
    "pcl5.fear_horror_anger_guilt_numeric",
    "pcl5.enjoy_activities_interest_loss_numeric",
    "pcl5.cut_people_feeling_distant_numeric",
    "pcl5.trouble_experiencing_positive_feelings__numeric",
    "pcl5.irritable_behaviour_angry_outburst_or_acting_aggressively_numeric",
    "pcl5.risks_taking_harm_things_numeric",
    "pcl5.being_superalert_or_watchful_or_on_guard_numeric",
    "pcl5.feeling_jumpy_or_easily_startled_numeric",
    "pcl5.having_difficulty_concentrating_numeric",
    "pcl5.trouble_falling_or_staying_sleep_numeric"
    )
```

```{r generate sumscores}
dat <- dat %>% 
  mutate(
    pcl5.sum_score = 
         sumscores(input = dat,
                   sum_vars = sum_vars,
                   coding_keys = keys,
                   na_limit = 0,
                   min_item = 0,
                   max_item = 4,
                   min_score = 0,
                   max_score = 80 #checkthis
                   )
         )
```

Phenotyping of PCL-5
Create binary phenotypes based on PCL-5 scoring criteria
Cutoff for meeting PTSD criteria is sumscore of 31-33 or more
Use "questionnaire.binary_score_name" when naming screener measures
```{r hazardous and harmful alcohol use behaviour}
dat <- dat %>% 
  mutate(
    pcl5.binary_PTSD =
      case_when(
        pcl5.sum_score >= 31 ~ 1,
        pcl5.sum_score < 31 ~ 0
        )
    )
```

# Save cleaned data
Check colnames before exporting final dataset
```{r check colnames}
colnames(dat)
```

# COVID CNS
```{r Write cleaned GLAD variables to a .rds file}
dat %>%
  saveRDS(
    file = paste0(ilovedata, "/data/latest_freeze/covidcns/baseline/pcl5_covidcns_clean.rds")
    )
```
