---
title: "COVIDCNS Physical Health History Cleaning Script"
author: "Zain Ahmad"
date: "14/03/2022"
output: html_document
---


All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except:
Study name (COVIDCNS) all caps
Capitalised first word

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_labelled_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the recode_check function - used to check for implausible values when recoding
Add the imp_clean function - used to check variables for implausible values
Add the cont_clean function - used to check continuous variables for implausible values
```{r Read in functions}
source(file = "scripts/functions/add_labelled_numeric.R")
source(file = "scripts/functions/remove_duplicates.R")
source(file = "scripts/functions/sumscores.R")
source(file = "scripts/functions/package_check.R")
source(file = "scripts/functions/recode_check.R")
source(file = "scripts/functions/cont_clean.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in file with path to ilovecovidcns channel on teams}
source(file = "scripts/credentials/paths.R")
```

# Read in the data: New Look PHH Script
Change this heading to the name of your questionnaire/demographic
Load COVIDCNS data

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the issues spreadsheet "https://docs.google.com/spreadsheets/d/1a2gL8c0eH2pZXNTbnPzkDYQGeeVXbLKU8BUpYM0moe8/edit?usp=sharing"

- For variable names, use ONLY 'questionnaire.variable_name'
- For dataset, only use snake_case naming
- When using pipe operator '%>%', each function should begin on a new line
- Do not add empty lines at the beginning or end of a chunk
- Use only tidyverse functions wherever possible
- When naming chunks, begin with the name of the dataset (COVIDCNS)

## COVIDCNS data
```{r COVIDCNS load data}
covidcns_dat <- read_rds(
  file = paste0(ilovecovidcns, "/data_raw/latest_freeze/baseline/phh_covid_cns.rds")
  )
  
# Check variable names in dataframe
covidcns_dat %>%
  colnames()

# Inspect dimensions of dataframe 
covidcns_dat %>%
  dim()

# Report counts of duplicates in ID column
covidcns_dat %>%
  select(externalDataReference) %>%
  filter(duplicated(.)) %>%
  count(., externalDataReference)

# Report number of IDs to be dropped
covidcns_excluded <- covidcns_dat %>%
  select(externalDataReference) %>%
  filter(duplicated(.)) %>%
  count(., externalDataReference) %>%
  select("Dropped IDs" = "n") %>%
  colSums() + 1

covidcns_excluded
```

Select & rename relevant columns
```{r COVIDCNS select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  dplyr::rename(
    "ID" = "externalDataReference"
  )

# Inspect colnames
covidcns_dat_id %>%
  colnames()

# Inspect dimensions
covidcns_dat_id %>%
  dim()
```

Check missingness by missmap
```{r COVIDCNS inspect missingness}
covidcns_miss_map <- covidcns_dat_id %>% 
  missmap()

covidcns_miss_map
```

Create dat as copy of covidcns_dat_id for brevity
This step gives you a 'reset' point: if your variable recoding screws up, re-run this chunk to give you a fresh 'dat' dataframe
```{r Create dat}
dat <- covidcns_dat_id 
```

Extract and save labels
```{r Extract save labels}
# Save variable labels
question_labels <- sjlabelled::get_label(dat)

# Save value labels
answer_labels <- sjlabelled::get_labels(dat, values = "as.name")

# Change -77 to -777 in value labels names
chng <- rapply(sapply(answer_labels, names),
               function(x) ifelse(x==-77, -777, x),
               how = "replace")

# Add multiple lines here as necessary to change other nonanswer values in labels
# chng <- rapply(chng,
#                function(x) ifelse(x==-88, -888, x),
#                how = "replace")

# Substitute new value labels into answer_labels
for (i in 1:length(chng)){
  if(!is.null(answer_labels[[i]])){
  names(answer_labels[[i]]) <- chng[[i]]
  }
}
```

Create list of all labels and attributes
```{r List labels attrs, eval=FALSE, include=FALSE}
label_list <- sapply(dat, function(x) c(attr(x, "label"), attr(x, "labels")))
label_list
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(where(is.numeric),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)
                )
         )

# Re-add labels after mutate
dat <- sjlabelled::set_label(dat, question_labels)
dat <- sjlabelled::set_labels(dat, labels = answer_labels)
```

# Cleaning Continuous Variables

Create vector of continuous variables
```{r Create cont vars vector}
variables_cont <- c(
  #ages
  #neuro
  "phh.epilepsy_or_convulsions.1",
  "phh.migraines.1",
  "phh.multiple_sclerosis.1",
  "phh.parkinsons_disease.1",
  "phh.brain_tumour.1",
  "phh.severe_memory_loss",
  "phh.cerebral_palsy.1",
  "phh.dont_know.7",
  "phh.prefer_not_to_answer.6",
  "phh.none_of_the_above.7",
  
  #osteo
  "phh.ankylosing_spondylitis.1",
  "phh.osteoporosis_or_thin_bones.1",
  "phh.hypermobility",
  "phh.osteoarthritis.1",
  "phh.rheumatoid_arthritis.1",
  "phh.other_arthritis.1",
  "phh.prefer_not_to_answer.9",
  "phh.none_of_the_above.10",
  "phh.dont_know.10",
  
  #resp
  "phh.asthma.1",
  "phh.pulmonary_fibrosis.1",
  "phh.chronic_obstructive_pulmonary_disease",
  "phh.cystic_fibrosis.1",
  "phh.pleural_effusion.1",
  "phh.pneumonia",
  "phh.pulmonary_embolus",
  "phh.emphysema_or_chronic_bronchitis.1",
  "phh.other.1",
  "phh.dont_know.13",
  "phh.prefer_not_to_say.1",
  "phh.none_of_the_above.13",
  
  #cardio
  "phh.heart_attack_angina.1",
  "phh.high_blood_cholesterol.1",
  "phh.high_blood_pressure.1",
  "phh.atrial_fibrillation.1",
  "phh.stroke.1",
  "phh.paroxysmal_tachycardia_sydrome",
  "phh.dont_know.16",
  "phh.prefer_not_to_answer.12",
  "phh.none_of_the_above.16",
  
  #cancer
  "phh.breast_cancer.1",
  "phh.lung_cancer.1",
  "phh.stomach_cancer.1",
  "phh.colon_cancer.1",
  "phh.uterus_cancer.1",
  "phh.prostate_cancer.1",
  "phh.bladder_cancer.1",
  "phh.bowel_cancer.1",
  "phh.rectal_cancer.1",
  "phh.lymphoma.1",
  "phh.melanoma.1",
  "phh.skin_cancer.1",
  "phh.ovarian_cancer.1",
  "phh.none_of_the_above.19",
  "phh.dont_know.19",
  "phh.prefer_not_to_answer.15",
  
  #derm
  "phh.psoriasis.1",
  "phh.vitiligo.1",
  "phh.eczema.1",
  "phh.thyroid_disease_.1",
  "phh.pain_due_to_virus",
  "phh.none_of_the_above.22",
  "phh.dont_know.22",
  "phh.prefer_not_to_answer.18",
  
  #allergy
  "phh.hay_fever.1",
  "phh.drug_allergy_",
  "phh.food_allergy_.1",
  "phh.any_other_allergy_.1",
  "phh.dont_know.25",
  "phh.prefer_not_to_answer.21",
  "phh.none_of_the_above.25",
  
  #gastro
  "phh.crohns_disease.1",
  "phh.ulcerative_colitis.1",
  "phh.irritable_bowel_disease",
  "phh.coeliac_disease.1",
  "phh.bacterial_stomach_infection",
  "phh.viral_weeks_bacterial_stomach.1",
  "phh.diabetes_type_1",
  "phh.diabetes_type_2",
  "phh.pain_due_to_diabetes",
  "phh.dont_know.29",
  "phh.prefer_not_to_answer.25",
  "phh.none_of_the_above.29"
)
length(variables_cont)
```

Inspect continuous variables
Use the question labels to ascertain context at this point and check for obvious outliers
The percentiles can be modified to exclude nonanswer values as appropriate to your data
```{r Inspect cont vars}
dat %>%
  select(all_of(variables_cont)) %>%
  tbl_summary(
    missing_text = "Missing",
    statistic = list(all_continuous() ~ "{median} ({p0}, {p5}, {p95}, {p100})"))
```

Check for text in continuous variables
If the fields contain text at this point, use the chunk below to clean manually
```{r Cont vars check text}
check_for_string <- function(x){
  sum(str_detect(x, "[a-zA-Z]"), na.rm = TRUE) > 0}

dat %>%
  select(all_of(variables_cont)) %>%
  select(where(check_for_string)) %>%
  filter(
    if_any(where(check_for_string),
           ~str_detect(., "[a-zA-Z\\s]+")
           )
    )
```

Remove text from numeric variables
```{r Cont vars remove text}
dat <- dat %>%
  mutate(across(all_of(variables_cont),
                ~str_remove(., "[a-zA-Z\\s]+")
                )
         )
```

Remove empty variables from variables_cont
These all contain only NAs and serve only to interfere with processing
```{r}
rem_vars <- dat %>%
  select(all_of(variables_cont)) %>%
  select(where(~all(is.na(.))
               )
         ) %>%
  colnames()

variables_cont <- variables_cont[!variables_cont %in% rem_vars]
length(variables_cont)
```

Mutate variables to numeric after cleaning out text
This step is necessary to check for non-integer values
Modify the all_of statement as required: DO NOT MUTATE TO NUMERIC UNNECESSARILY
REMOVE THIS CHUNK IF NOT NECESSARY

```{r Cont vars to numeric}
dat <- dat %>%
  mutate(across(all_of(variables_cont),
                ~as.numeric(.)
                )
         )

dat <- sjlabelled::set_label(dat, question_labels)
dat <- sjlabelled::set_labels(dat, labels = answer_labels)
```

Transform nonanswer values to 3 digit
```{r Cont vars nonanswer}
dat <- dat %>%
  mutate(across(where(is.numeric),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)
                )
         )

dat <- sjlabelled::set_label(dat, question_labels)
dat <- sjlabelled::set_labels(dat, labels = answer_labels)
```

Create matrix of limits for continuous variables
Matrix is series of vectors (lower, upper)
Define limits for variable and list reasoning below
Variable name: Age
- Lower: 0
- Upper: 117 (oldest person in the world)
```{r Create matrix limits}
limits_mat <- t(matrix(rep(c(0,117), 62), nrow = 2, ncol = 62))
dim(limits_mat)
```

Set row and col names of limits_mat
This allows your to easily refer back to limits_mat for a summary
```{r Set lim_mat names}
rownames(limits_mat) <- variables_cont
colnames(limits_mat) <- c("Lower", "Upper")
```

Use cont_clean to check if any implausible values and provide replacement vectors
Cont_clean will not proceed if variables are not numeric type, clean manually above if necessary
```{r Cont_clean cont vars}
cont_list <- cont_clean(
  variables = variables_cont,
  limits_mat = limits_mat,
  dat = dat
)

imp_checklist <- c()

for (i in 1:length(variables_cont)){
  if(cont_list[[variables_cont[i]]]$Count > 0){
    imp_checklist <- append(x = imp_checklist, variables_cont[i])
    print(paste0("Implausibles in ", variables_cont[i], ": ", cont_list[[variables_cont[i]]]$Count))
  }
}
```

Check unique values in variables containing implausible values
** Fields contain years which require import of dob data to extract age, transform to -666 for now
```{r Cont vars implausible unique}
dat %>%
  select(all_of(imp_checklist)) %>%
  sapply(., function(x) sort(unique(x)))
```

Mutate variables with implausible values removed
```{r Mutate cont vars}
dat <- dat %>%
  mutate(
    phh.asthma.1 = cont_list$phh.asthma.1$Replacement
  )

dat <- dat %>%
  mutate(
    phh.pulmonary_fibrosis.1 = cont_list$phh.pulmonary_fibrosis.1$Replacement
  )

dat <- dat %>%
  mutate(
    phh.pneumonia = cont_list$phh.pneumonia$Replacement
  )

dat <- dat %>%
  mutate(
    phh.high_blood_cholesterol.1 = cont_list$phh.high_blood_cholesterol.1$Replacement
  )

dat <- dat %>%
  mutate(
    phh.high_blood_pressure.1 = cont_list$phh.high_blood_pressure.1$Replacement
  )

dat <- dat %>%
  mutate(
    phh.atrial_fibrillation.1 = cont_list$phh.atrial_fibrillation.1$Replacement
  )

dat <- dat %>%
  mutate(
    phh.hay_fever.1 = cont_list$phh.hay_fever.1$Replacement
  )

dat <- dat %>%
  mutate(
    phh.drug_allergy_ = cont_list$phh.drug_allergy_$Replacement
  )

dat <- dat %>%
  mutate(
    phh.food_allergy_.1 = cont_list$phh.food_allergy_.1$Replacement
  )

dat <- dat %>%
  mutate(
    phh.irritable_bowel_disease = cont_list$phh.irritable_bowel_disease$Replacement
  )

dat <- dat %>%
  mutate(
    phh.diabetes_type_2 = cont_list$phh.diabetes_type_2$Replacement
  )
```

Re-inspect variables after cleaning
```{r Inspect after cleaning}
dat %>%
  select(all_of(variables_cont)) %>%
  tbl_summary(
    missing_text = "Missing",
    statistic = list(all_continuous() ~ "{median} ({p0}, {p5}, {p95}, {p100})")
  )
```


# Text variables

Inspect text variables
```{r Inspect text vars}
variables_text <- c(
  "phh.nbsp",
  "phh.nbsp.1",
  "phh.",
  "phh..1",
  "phh..2",
  "phh.nbsp.2",
  "phh.nbsp.3",
  "phh..3",
  "phh..4",
  "phh..5",
  "phh.nbsp.4",
  "phh.nbsp.5",
  "phh..6",
  "phh..7",
  "phh..8",
  "phh.drug_allergy_text.txt",
  "phh.food_allergy_text.txt",
  "phh.allergy_text.txt",
  "phh.other_arthritistext.txt",
  "phh.othertext.txt",
  "phh.thyroid_disease_text.txt",
  "phh.list_reason_taking_type.txt",
  "phh.chronic_medical_conditions_diagnosis.txt"
  )

dat %>%
  select(all_of(variables_text)) %>%
  tbl_summary(missing_text = "Missing")
```

Recode medications 1
```{r COVIDCNS recode medications 1 variable}
dat <- dat %>% 
  mutate(across(phh.nbsp,
                ~case_when(
                  str_detect(phh.nbsp, "Adeport")  ~ "Tacrolimus",
                  str_detect(phh.nbsp, "Adizem")  ~ "Diltiazem",
                  str_detect(phh.nbsp, "ALLOPUR")  ~ "Allopurinol",
                  str_detect(phh.nbsp, "mitr")  ~ "Amitriptyline",
                  str_detect(phh.nbsp, "Amilidopalin")  ~ "Amlodipine",
                  str_detect(phh.nbsp, "mlodip")  ~ "Amlodipine",
                  str_detect(phh.nbsp, "Amrizaprol")  ~ "Omeprazole",
                  str_detect(phh.nbsp, "Artorvostatin")  ~ "Atorvastatin",
                  str_detect(phh.nbsp, "spirin")  ~ "Aspirin",
                  str_detect(phh.nbsp, "Atanolel")  ~ "Atenolol",
                  str_detect(phh.nbsp, "torvastat")  ~ "Atorvastatin",
                  str_detect(phh.nbsp, "Cadesartan")  ~ "Candesartan",
                  str_detect(phh.nbsp, "Candesarten")  ~ "Candesartan",
                  str_detect(phh.nbsp, "Cerazette")  ~ "Desogestrel",
                  str_detect(phh.nbsp, "LOPIDOGR")  ~ "Clopidogrel",
                  str_detect(phh.nbsp, "cocodamol")  ~ "Co-codamol",
                  str_detect(phh.nbsp, "Doxacosin")  ~ "Doxazosin",
                  str_detect(phh.nbsp, "doxaban")  ~ "Edoxaban",
                  str_detect(phh.nbsp, "flecanide")  ~ "Flecainide",
                  str_detect(phh.nbsp, "ostair")  ~ "Beclometasone/Formoterol",
                  str_detect(phh.nbsp, "abape")  ~ "Gabapentin",
                  str_detect(phh.nbsp, "indapamide")  ~ "Indapamide",
                  str_detect(phh.nbsp, "EVETIRC")  ~ "Levetiracetam",
                  str_detect(phh.nbsp, "evothyro")  ~ "Levothyroxine",
                  str_detect(phh.nbsp, "Lipitor")  ~ "Atorvastatin",
                  str_detect(phh.nbsp, "loratadine")  ~ "Loratadine",
                  str_detect(phh.nbsp, "lozartan")  ~ "Lozartan",
                  str_detect(phh.nbsp, "Madopar")  ~ "Benserazide",
                  str_detect(phh.nbsp, "etformi")  ~ "Metformin",
                  str_detect(phh.nbsp, "irena")  ~ "Levonorgestrel",
                  str_detect(phh.nbsp, "nortryptiline")  ~ "Nortriptyline",
                  str_detect(phh.nbsp, "Olanzipine")  ~ "Olanzapine",
                  str_detect(phh.nbsp, "pantoprasole")  ~ "Pantoprazole",
                  str_detect(phh.nbsp, "Pentasa")  ~ "Mesalamine",
                  str_detect(phh.nbsp, "rednis")  ~ "Prednisolone",
                  str_detect(phh.nbsp, "regab")  ~ "Pregabalin",
                  str_detect(phh.nbsp, "Propraolol")  ~ "Propranolol",
                  str_detect(phh.nbsp, "ramapril")  ~ "Ramipril",
                  str_detect(phh.nbsp, "amipr")  ~ "Ramipril",
                  str_detect(phh.nbsp, "albutam")  ~ "Salbutamol",
                  str_detect(phh.nbsp, "teroid")  ~ "Steroids",
                  str_detect(phh.nbsp, "Sukkarto")  ~ "Metformin",
                  str_detect(phh.nbsp, "ymbicor")  ~ "Budesonide/Formoterol",
                  str_detect(phh.nbsp, "amsulos")  ~ "Tamsulosin",
                  str_detect(phh.nbsp, "TEGRETOL")  ~ "Carbamazepine",
                  str_detect(phh.nbsp, "Trelegy")  ~ "Fluticasone/Umeclinidium/Vilanterol",
                  str_detect(phh.nbsp, "nkno")  ~ "-77",
                  str_detect(phh.nbsp, "enlafaxin")  ~ "Venlafaxine",
                  str_detect(phh.nbsp, "Xaretto")  ~ "Rivaroxaban",
                  str_detect(phh.nbsp, "ivarox")  ~ "Rivaroxaban",
                  str_detect(phh.nbsp, "zinc")  ~ "Zinc",
                  str_detect(phh.nbsp, "On medica")  ~ "-77",
                  TRUE ~ .)))
```

Re-check coding
```{r COVIDCNS recheck coding 1}
dat %>%
  select(phh.nbsp) %>%
  tbl_summary(missing_text = "Missing")
```

Recode medications 2
```{r COVIDCNS recode medications 2 variable}
dat <- dat %>% 
  mutate(across(phh.nbsp.1,
                ~case_when(
                  str_detect(phh.nbsp.1, "Benzofibrate")  ~ "Bezafibrate",
                  str_detect(phh.nbsp.1, "Isporol")  ~ "Bisoprolol",
                  str_detect(phh.nbsp.1, "Questran")  ~ "Cholestyramine",
                  str_detect(phh.nbsp.1, "salbutomal")  ~ "Salbutamol",
                  str_detect(phh.nbsp.1, "imvast")  ~ "Simvastatin",
                  str_detect(phh.nbsp.1, "iotrop")  ~ "Tiotropium",
                  str_detect(phh.nbsp.1, "Yacella")  ~ "Ethinylestradiol/Drospirenone",
                  str_detect(phh.nbsp.1, "Statin")  ~ "Statins",
                  str_detect(phh.nbsp.1, "EDOXOBAN")  ~ "Edoxaban",
                  str_detect(phh.nbsp.1, "ESCITALOPRAM")  ~ "Escitalopram",
                  str_detect(phh.nbsp.1, "Flutiform")  ~ "Fluticasone/Formoterol",
                  str_detect(phh.nbsp.1, "Keppra")  ~ "Levetiracetam",
                  str_detect(phh.nbsp.1, "Leveciraterem")  ~ "Levetiracetam",
                  str_detect(phh.nbsp.1, "Levetiractam")  ~ "Levetiracetam",
                  str_detect(phh.nbsp.1, "evothryoxine")  ~ "Levothyroxine",
                  str_detect(phh.nbsp.1, "irtaz")  ~ "Mirtazapine",
                  str_detect(phh.nbsp.1, "ontelu")  ~ "Montelukast",
                  str_detect(phh.nbsp.1, "ycophen")  ~ "Mycophenolate",
                  str_detect(phh.nbsp.1, "mepr")  ~ "Omeprazole",
                  str_detect(phh.nbsp.1, "Bipisporol")  ~ "Bisoprolol",
                  str_detect(phh.nbsp.1, "isop")  ~ "Bisoprolol",
                  str_detect(phh.nbsp.1, "Adizem")  ~ "Diltiazem",
                  str_detect(phh.nbsp.1, "ALLOPUR")  ~ "Allopurinol",
                  str_detect(phh.nbsp.1, "mitr")  ~ "Amitriptyline",
                  str_detect(phh.nbsp.1, "Amilidopalin")  ~ "Amlodipine",
                  str_detect(phh.nbsp.1, "mlodip")  ~ "Amlodipine",
                  str_detect(phh.nbsp.1, "Amrizaprol")  ~ "Omeprazole",
                  str_detect(phh.nbsp.1, "Artorvostatin")  ~ "Atorvastatin",
                  str_detect(phh.nbsp.1, "atorvostatin")  ~ "Atorvastatin",
                  str_detect(phh.nbsp.1, "Atrovarstatin")  ~ "Atorvastatin",
                  str_detect(phh.nbsp.1, "ATORVASTATIN")  ~ "Atorvastatin",
                  str_detect(phh.nbsp.1, "spirin")  ~ "Aspirin",
                  str_detect(phh.nbsp.1, "Atanolel")  ~ "Atenolol",
                  str_detect(phh.nbsp.1, "torvastat")  ~ "Atorvastatin",
                  str_detect(phh.nbsp.1, "Cadesartan")  ~ "Candesartan",
                  str_detect(phh.nbsp.1, "Candersartan")  ~ "Candesartan",
                  str_detect(phh.nbsp.1, "Candesarten")  ~ "Candesartan",
                  str_detect(phh.nbsp.1, "Colafac")  ~ "Mebeverine",
                  str_detect(phh.nbsp.1, "Dueloxitine")  ~ "Duloxetine",
                  str_detect(phh.nbsp.1, "Ditropan")  ~ "Oxybutynin",
                  str_detect(phh.nbsp.1, "erazette")  ~ "Desogestrel",
                  str_detect(phh.nbsp.1, "LOPIDOGR")  ~ "Clopidogrel",
                  str_detect(phh.nbsp.1, "cocodamol")  ~ "Co-codamol",
                  str_detect(phh.nbsp.1, "Doxacosin")  ~ "Doxazosin",
                  str_detect(phh.nbsp.1, "doxaban")  ~ "Edoxaban",
                  str_detect(phh.nbsp.1, "flecanide")  ~ "Flecainide",
                  str_detect(phh.nbsp.1, "ostair")  ~ "Beclometasone/Formoterol",
                  str_detect(phh.nbsp.1, "abape")  ~ "Gabapentin",
                  str_detect(phh.nbsp.1, "indapamide")  ~ "Indapamide",
                  str_detect(phh.nbsp.1, "EVETIRC")  ~ "Levetiracetam",
                  str_detect(phh.nbsp.1, "evothyro")  ~ "Levothyroxine",
                  str_detect(phh.nbsp.1, "Lipitor")  ~ "Atorvastatin",
                  str_detect(phh.nbsp.1, "loratadine")  ~ "Loratadine",
                  str_detect(phh.nbsp.1, "lozartan")  ~ "Lozartan",
                  str_detect(phh.nbsp.1, "Madopar")  ~ "Benserazide",
                  str_detect(phh.nbsp.1, "etformi")  ~ "Metformin",
                  str_detect(phh.nbsp.1, "irena")  ~ "Levonorgestrel",
                  str_detect(phh.nbsp.1, "nortryptiline")  ~ "Nortriptyline",
                  str_detect(phh.nbsp.1, "Olanzipine")  ~ "Olanzapine",
                  str_detect(phh.nbsp.1, "pantoprasole")  ~ "Pantoprazole",
                  str_detect(phh.nbsp.1, "Pentasa")  ~ "Mesalamine",
                  str_detect(phh.nbsp.1, "rednis")  ~ "Prednisolone",
                  str_detect(phh.nbsp.1, "regab")  ~ "Pregabalin",
                  str_detect(phh.nbsp.1, "Propraolol")  ~ "Propranolol",
                  str_detect(phh.nbsp.1, "ramapril")  ~ "Ramipril",
                  str_detect(phh.nbsp.1, "amipr")  ~ "Ramipril",
                  str_detect(phh.nbsp.1, "albutam")  ~ "Salbutamol",
                  str_detect(phh.nbsp.1, "teroid")  ~ "Steroids",
                  str_detect(phh.nbsp.1, "Sukkarto")  ~ "Metformin",
                  str_detect(phh.nbsp.1, "ymbicor")  ~ "Budesonide/Formoterol",
                  str_detect(phh.nbsp.1, "amsulos")  ~ "Tamsulosin",
                  str_detect(phh.nbsp.1, "TEGRETOL")  ~ "Carbamazepine",
                  str_detect(phh.nbsp.1, "Trelegy")  ~ "Fluticasone/Umeclinidium/Vilanterol",
                  str_detect(phh.nbsp.1, "nkno")  ~ "-77",
                  str_detect(phh.nbsp.1, "enlafaxin")  ~ "Venlafaxine",
                  str_detect(phh.nbsp.1, "Xaretto")  ~ "Rivaroxaban",
                  str_detect(phh.nbsp.1, "ivarox")  ~ "Rivaroxaban",
                  str_detect(phh.nbsp.1, "zinc")  ~ "Zinc",
                  str_detect(phh.nbsp.1, "On medica")  ~ "-77",
                  TRUE ~ .)))
```

Re-check coding
```{r COVIDCNS recheck coding 2}
dat %>%
  select(phh.nbsp.1) %>%
  tbl_summary(missing_text = "Missing")
```

Recode medications 3
```{r COVIDCNS recode medications 3 variable}
dat <- dat %>% 
  mutate(across(phh.,
                ~case_when(
                  str_detect(phh., "Accrete")  ~ "Colecalciferol",
                  str_detect(phh., "Amatryptyline")  ~ "Amitriptyline",
                  str_detect(phh., "torvast")  ~ "Atorvastatin",
                  str_detect(phh., "endroflu")  ~ "Bendroflumethiazide",
                  str_detect(phh., "etahis")  ~ "Betahistine",
                  str_detect(phh., "BISOPROLOL")  ~ "Bisoprolol",
                  str_detect(phh., "lopido")  ~ "Clopidogrel",
                  str_detect(phh., "mespro")  ~ "Esomeprazole",
                  str_detect(phh., "zetim")  ~ "Ezetimibe",
                  str_detect(phh., "exof")  ~ "Fexofenadine",
                  str_detect(phh., "Fluox")  ~ "Fluoxetine",
                  str_detect(phh., "Flutiform")  ~ "Fluticasone/Formoterol",
                  str_detect(phh., "ostair")  ~ "Beclometasone/Formoterol",
                  str_detect(phh., "Fultium")  ~ "Colecalciferol",
                  str_detect(phh., "glickasade")  ~ "Gliclazide",
                  str_detect(phh., "glipizide")  ~ "Gliclazide",
                  str_detect(phh., "anzo")  ~ "Lansoprazole",
                  str_detect(phh., "anso")  ~ "Lansoprazole",
                  str_detect(phh., "ANSO")  ~ "Lansoprazole",
                  str_detect(phh., "Lipitor")  ~ "Atorvastatin",
                  str_detect(phh., "formin")  ~ "Metformin",
                  str_detect(phh., "mperazo")  ~ "Omeprazole",
                  str_detect(phh., "amip")  ~ "Ramipril",
                  str_detect(phh., "Rebar")  ~ "Fluticasone/Vilanterol",
                  str_detect(phh., "ymbicor")  ~ "Budesonide/Formoterol",
                  str_detect(phh., "Tamsolosin")  ~ "Tamsulosin",
                  str_detect(phh., "agife")  ~ "Estradiol",
                  TRUE ~ .)))
```

Re-check coding
```{r COVIDCNS recheck coding 3}
dat %>%
  select(phh.) %>%
  tbl_summary(missing_text = "Missing")
```

Recode medications 4
```{r COVIDCNS recode medications 4 variable}
dat <- dat %>% 
  mutate(across(phh..1,
                ~case_when(
                  str_detect(phh..1, "Ad-")  ~ "Colecalciferol",
                  str_detect(phh..1, "Adcal")  ~ "Colecalciferol",
                  str_detect(phh..1, "llopur")  ~ "Allopurinol",
                  str_detect(phh..1, "pixab")  ~ "Apixaban",
                  str_detect(phh..1, "spirin")  ~ "Aspirin",
                  str_detect(phh..1, "torv")  ~ "Atorvastatin",
                  str_detect(phh..1, "TORV")  ~ "Atorvastatin",
                  str_detect(phh..1, "torav")  ~ "Atorvastatin",
                  str_detect(phh..1, "tropin")  ~ "Atropine",
                  str_detect(phh..1, "ispro")  ~ "Bisoprolol",
                  str_detect(phh..1, "buprenorphine")  ~ "Buprenorphine",
                  str_detect(phh..1, "dorzolamide")  ~ "Dorzolamide",
                  str_detect(phh..1, "Dutesterdide")  ~ "Dutasteride",
                  str_detect(phh..1, "Furosmide")  ~ "Furosemide",
                  str_detect(phh..1, "insulin")  ~ "Insulin",
                  str_detect(phh..1, "ansopr")  ~ "Lansoprazole",
                  str_detect(phh..1, "Levetractam")  ~ "Levetiracetam",
                  str_detect(phh..1, "ormin")  ~ "Metformin",
                  str_detect(phh..1, "icrogyn")  ~ "Ethinylestradiol/Levonorgestrel",
                  str_detect(phh..1, "Mirtazipine")  ~ "Mirtazapine",
                  str_detect(phh..1, "fenolate")  ~ "Mycophenolate",
                  str_detect(phh..1, "Oxybutinin")  ~ "Oxybutynin",
                  str_detect(phh..1, "aracetamol")  ~ "Paracetamol",
                  str_detect(phh..1, "uinin")  ~ "Quinine",
                  str_detect(phh..1, "entoli")  ~ "Salbutamol",
                  str_detect(phh..1, "enna")  ~ "Senna",
                  str_detect(phh..1, "ertral")  ~ "Sertraline",
                  str_detect(phh..1, "it D")  ~ "Colecalciferol",
                  str_detect(phh..1, "eletran")  ~ "Buprenorphine",
                  TRUE ~ .)))
```

Re-check coding
```{r COVIDCNS recheck coding 4}
dat %>%
  select(phh..1) %>%
  tbl_summary(missing_text = "Missing")
```

Recode medications 5
```{r COVIDCNS recode medications 5 variable}
dat <- dat %>% 
  mutate(across(phh..2,
                ~case_when(
                  str_detect(phh..2, "Advograf")  ~ "Tacrolimus",
                  str_detect(phh..2, "statin")  ~ "Atorvastatin",
                  str_detect(phh..2, "pril")  ~ "Ramipril",
                  str_detect(phh..2, "PRIL")  ~ "Ramipril",
                  str_detect(phh..2, "lipti")  ~ "Sitagliptin",
                  str_detect(phh..2, "B12")  ~ "Cobalamin",
                  str_detect(phh.nbsp.1, "ostair")  ~ "Beclometasone/Formoterol",
                  str_detect(phh..2, "obala")  ~ "Cobalamin",
                  str_detect(phh..2, "odein")  ~ "Codeine",
                  str_detect(phh..2, "Famitidine")  ~ "Famotidine",
                  str_detect(phh..2, "Gaba")  ~ "Gabapentin",
                  str_detect(phh..2, "nsuli")  ~ "Insulin",
                  str_detect(phh..2, "Jardiance")  ~ "Empagliflozin",
                  str_detect(phh..2, "antan")  ~ "Latanoprost",
                  str_detect(phh..2, "Letrazole")  ~ "Letrozole",
                  str_detect(phh..2, "Ocrevus")  ~ "Ocrelizumab",
                  str_detect(phh..2, "stexerol")  ~ "Colecalciferol",
                  str_detect(phh..2, "sumatriptan")  ~ "Sumatriptan",
                  str_detect(phh..2, "Waferin")  ~ "Warfarin",
                  str_detect(phh..2, "Zapain")  ~ "Co-codamol",
                  TRUE ~ .)))
```

Re-check coding
```{r COVIDCNS recheck coding 5}
dat %>%
  select(phh..2) %>%
  tbl_summary(missing_text = "Missing")
```

Recode medications 6
```{r COVIDCNS recode medications 6 variable}
dat <- dat %>% 
  mutate(across(phh.nbsp.2,
                ~case_when(
                  str_detect(phh.nbsp.2, "abl")  ~ "Tablets",
                  str_detect(phh.nbsp.2, "aps")  ~ "Capsules",
                  str_detect(phh.nbsp.2, "ABL")  ~ "Tablets",
                  str_detect(phh.nbsp.2, "nha")  ~ "Inhaler",
                  
                  TRUE ~ .)))
```

Re-check coding
```{r COVIDCNS recheck coding 6}
dat %>%
  select(phh.nbsp.2) %>%
  tbl_summary(missing_text = "Missing")
```

Recode medications 7
```{r COVIDCNS recode medications 7 variable}
dat <- dat %>% 
  mutate(across(phh.nbsp.3,
                ~case_when(
                  str_detect(phh.nbsp.3, "abl")  ~ "Tablets",
                  str_detect(phh.nbsp.3, "ABL")  ~ "Tablets",
                  str_detect(phh.nbsp.3, "nha")  ~ "Inhaler",
                  
                  TRUE ~ .)))
```

Re-check coding
```{r COVIDCNS recheck coding 7}
dat %>%
  select(phh.nbsp.3) %>%
  tbl_summary(missing_text = "Missing")
```

Recode medications 8
```{r COVIDCNS recode medications 8 variable}
dat <- dat %>% 
  mutate(across(phh..3,
                ~case_when(
                  str_detect(phh..3, "ab")  ~ "Tablets",
                  str_detect(phh..3, "ABL")  ~ "Tablets",
                  str_detect(phh..3, "nha")  ~ "Inhaler",
                  
                  TRUE ~ .)))
```

Re-check coding
```{r COVIDCNS recheck coding 8}
dat %>%
  select(phh..3) %>%
  tbl_summary(missing_text = "Missing")
```

Recode medications 9
```{r COVIDCNS recode medications 9 variable}
dat <- dat %>% 
  mutate(across(phh..4,
                ~case_when(
                  str_detect(phh..4, "ab")  ~ "Tablets",
                  str_detect(phh..4, "ABL")  ~ "Tablets",
                  str_detect(phh..4, "nha")  ~ "Inhaler",
                  str_detect(phh..4, "atc")  ~ "Patch",
                  TRUE ~ .)))
```

Re-check coding
```{r COVIDCNS recheck coding 9}
dat %>%
  select(phh..4) %>%
  tbl_summary(missing_text = "Missing")
```

Recode medications 10
```{r COVIDCNS recode medications 10 variable}
dat <- dat %>% 
  mutate(across(phh..5,
                ~case_when(
                  str_detect(phh..5, "abl")  ~ "Tablets",
                  str_detect(phh..5, "ABL")  ~ "Tablets",
                  str_detect(phh..5, "nha")  ~ "Inhaler",
                  
                  TRUE ~ .)))
```

Re-check coding
```{r COVIDCNS recheck coding 10}
dat %>%
  select(phh..5) %>%
  tbl_summary(missing_text = "Missing")
```



Re-check coding
```{r COVIDCNS recheck coding final}
dat %>%
  select(all_of(variables_text)) %>%
  tbl_summary(missing_text = "Missing")
```


# Add Numeric Variables

Specify columns to be excluded from add_numeric function
Continuous variables should be excluded, as they are already numeric
```{r COVIDCNS specify excluded columns}
exclude_cols_numeric <- c(
  "phh.nbsp",
  "phh.nbsp.1",
  "phh.",
  "phh..1",
  "phh..2",
  "phh.nbsp.2",
  "phh.nbsp.3",
  "phh..3",
  "phh..4",
  "phh..5",
  "phh.nbsp.4",
  "phh.nbsp.5",
  "phh..6",
  "phh..7",
  "phh..8",
  "phh.epilepsy_or_convulsions.1",
  "phh.migraines.1",
  "phh.multiple_sclerosis.1",
  "phh.parkinsons_disease.1",
  "phh.brain_tumour.1",
  "phh.severe_memory_loss",
  "phh.cerebral_palsy.1",
  "phh.dont_know.7",
  "phh.prefer_not_to_answer.6",
  "phh.none_of_the_above.7",
  "phh.ankylosing_spondylitis.1",
  "phh.osteoporosis_or_thin_bones.1",
  "phh.hypermobility",
  "phh.osteoarthritis.1",
  "phh.rheumatoid_arthritis.1",
  "phh.other_arthritis.1",
  "phh.prefer_not_to_answer.9",
  "phh.none_of_the_above.10",
  "phh.dont_know.10",
  "phh.asthma.1",
  "phh.pulmonary_fibrosis.1",
  "phh.chronic_obstructive_pulmonary_disease",
  "phh.cystic_fibrosis.1",
  "phh.pleural_effusion.1",
  "phh.pneumonia",
  "phh.pulmonary_embolus",
  "phh.emphysema_or_chronic_bronchitis.1",
  "phh.other.1",
  "phh.dont_know.13",
  "phh.prefer_not_to_say.1",
  "phh.none_of_the_above.13",
  "phh.heart_attack_angina.1",
  "phh.high_blood_cholesterol.1",
  "phh.high_blood_pressure.1",
  "phh.atrial_fibrillation.1",
  "phh.stroke.1",
  "phh.paroxysmal_tachycardia_sydrome",
  "phh.dont_know.16",
  "phh.prefer_not_to_answer.12",
  "phh.none_of_the_above.16",
  "phh.breast_cancer.1",
  "phh.lung_cancer.1",
  "phh.stomach_cancer.1",
  "phh.colon_cancer.1",
  "phh.uterus_cancer.1",
  "phh.prostate_cancer.1",
  "phh.bladder_cancer.1",
  "phh.bowel_cancer.1",
  "phh.rectal_cancer.1",
  "phh.lymphoma.1",
  "phh.melanoma.1",
  "phh.skin_cancer.1",
  "phh.ovarian_cancer.1",
  "phh.none_of_the_above.19",
  "phh.dont_know.19",
  "phh.prefer_not_to_answer.15",
  "phh.psoriasis.1",
  "phh.vitiligo.1",
  "phh.eczema.1",
  "phh.thyroid_disease_.1",
  "phh.pain_due_to_virus",
  "phh.none_of_the_above.22",
  "phh.dont_know.22",
  "phh.prefer_not_to_answer.18",
  "phh.hay_fever.1",
  "phh.drug_allergy_",
  "phh.food_allergy_.1",
  "phh.any_other_allergy_.1",
  "phh.dont_know.25",
  "phh.prefer_not_to_answer.21",
  "phh.none_of_the_above.25",
  "phh.crohns_disease.1",
  "phh.ulcerative_colitis.1",
  "phh.irritable_bowel_disease",
  "phh.coeliac_disease.1",
  "phh.bacterial_stomach_infection",
  "phh.viral_weeks_bacterial_stomach.1",
  "phh.diabetes_type_1",
  "phh.diabetes_type_2",
  "phh.pain_due_to_diabetes",
  "phh.dont_know.29",
  "phh.prefer_not_to_answer.25",
  "phh.none_of_the_above.29",
  "phh.drug_allergy_text.txt",
  "phh.food_allergy_text.txt",
  "phh.allergy_text.txt",
  "phh.other_arthritistext.txt",
  "phh.othertext.txt",
  "phh.thyroid_disease_text.txt",
  "phh.list_reason_taking_type.txt",
  "phh.chronic_medical_conditions_diagnosis.txt"
  )
```

Select & rename relevant columns
```{r COVIDCNS add numeric}
dat <- dat %>% 
  add_labelled_numeric(exclude = exclude_cols_numeric)

# Inspect colnames
dat %>%
  colnames()
```


# Save cleaned data

# COVIDCNS
```{r Write cleaned COVIDCNS variables to a .rds file}
dat %>%
  saveRDS(
    file = paste0(ilovecovidcns, "/data/latest_freeze/baseline/phh_covidcns_clean.rds")
    )
```