---
title: "COVIDCNS Physical Health History Cleaning Script"
author: "Zain Ahmad"
date: "14/03/2022"
output: html_document
---

All

#neuro
"phh.epilepsy_or_convulsions",
"phh.migraines",
"phh.multiple_sclerosis",
"phh.parkinsons_disease",
"phh.brain_tumour",
"phh.severe_memory_loss_",
"phh.cerebral_palsy",
"phh.dont_know",
"phh.prefer_not_to_answer",
"phh.none_of_the_above",

#allergy
"phh.hay_fever",
"phh.drug_allergy",
"phh.drug_allergy_text.txt",
"phh.food_allergy_",
"phh.food_allergy_text.txt",
"phh.any_other_allergy_",
"phh.allergy_text.txt",
"phh.dont_know.1",
"phh.prefer_not_to_answer.1",
"phh.none_of_the_above.1",

#osteo
"phh.ankylosing_spondylitis",
"phh.osteoporosis_or_thin_bones",
"phh.hypermobility_",
"phh.osteoarthritis",
"phh.rheumatoid_arthritis",
"phh.other_arthritis",
"phh.other_arthritistext.txt",
"phh.none_of_the_above.2",
"phh.dont_know.2",

#resp
"phh.asthma",
"phh.pulmonary_fibrosis",
"phh.chronic_obstructive_pulmonary_disease_",
"phh.cystic_fibrosis",
"phh.pleural_effusion",
"phh.pneumonia_",
"phh.pulmonary_embolus_",
"phh.emphysema_or_chronic_bronchitis",
"phh.other",
"phh.othertext.txt",
"phh.dont_know.3",
"phh.prefer_not_to_say",
"phh.none_of_the_above.3",

#cardio
"phh.heart_attack_angina",
"phh.high_blood_cholesterol",
"phh.high_blood_pressure",
"phh.atrial_fibrillation",
"phh.stroke",
"phh.paroxysmal_tachycardia_sydrome_",
"phh.dont_know.4",
"phh.prefer_not_to_answer.3",
"phh.none_of_the_above.4",

#cancer
"phh.breast_cancer",
"phh.lung_cancer",
"phh.stomach_cancer",
"phh.colon_cancer",
"phh.uterus_cancer",
"phh.prostate_cancer",
"phh.bladder_cancer",
"phh.bowel_cancer",
"phh.rectal_cancer",
"phh.lymphoma",
"phh.melanoma",
"phh.skin_cancer",
"phh.ovarian_cancer",
"phh.none_of_the_above.5",
"phh.dont_know.5",
"phh.prefer_not_to_answer.4",

#derm
"phh.psoriasis",
"phh.vitiligo",
"phh.eczema",
"phh.thyroid_disease_",
"phh.thyroid_disease_text.txt",
"phh.pain_due_to_virus_",
"phh.none_of_the_above.6",
"phh.dont_know.6",
"phh.prefer_not_to_answer.5",

#medications
"phh.list_reason_taking_type.txt",
"phh.chronic_medical_conditions_mentioned",
"phh.chronic_medical_conditions_diagnosis.txt",
"phh.nbsp",
"phh.nbsp.1",
"phh.",
"phh..1",
"phh..2",
"phh.nbsp.2",
"phh.nbsp.3",
"phh..3",
"phh..4",
"phh..5",
"phh.nbsp.4",
"phh.nbsp.5",
"phh..6",
"phh..7",
"phh..8",
"phh.longterm_prescription_medication",
"phh.non_steroid_antiinflammatory_drugs",
"phh.steroids",
"phh.immunosuppressants",
"phh.htr",
"phh.thyroid_hormones",
"phh.contraceptive_pill",
"phh.intrauterine_device",
"phh.intrauterine_system",
"phh.bronchodilators",

#neuro
"phh.epilepsy_or_convulsions.1",
"phh.migraines.1",
"phh.multiple_sclerosis.1",
"phh.parkinsons_disease.1",
"phh.brain_tumour.1",
"phh.severe_memory_loss",
"phh.cerebral_palsy.1",
"phh.dont_know.7",
"phh.prefer_not_to_answer.6",
"phh.none_of_the_above.7",
"phh.epilepsy_or_convulsions.2",
"phh.migraines.2",
"phh.multiple_sclerosis.2",
"phh.parkinsons_disease.2",
"phh.brain_tumour.2",
"phh.severe_memory_loss.1",
"phh.cerebral_palsy.2",
"phh.dont_know.8",
"phh.prefer_not_to_answer.7",
"phh.none_of_the_above.8",
"phh.epilepsy_or_convulsions.3",
"phh.migraines.3",
"phh.multiple_sclerosis.3",
"phh.parkinsons_disease.3",
"phh.brain_tumour.3",
"phh.severe_memory_loss.2",
"phh.cerebral_palsy.3",
"phh.dont_know.9",
"phh.prefer_not_to_answer.8",
"phh.none_of_the_above.9",

#osteo
"phh.ankylosing_spondylitis.1",
"phh.osteoporosis_or_thin_bones.1",
"phh.hypermobility",
"phh.osteoarthritis.1",
"phh.rheumatoid_arthritis.1",
"phh.other_arthritis.1",
"phh.prefer_not_to_answer.9",
"phh.none_of_the_above.10",
"phh.dont_know.10",
"phh.ankylosing_spondylitis.2",
"phh.osteoporosis_or_thin_bones.2",
"phh.hypermobility.1",
"phh.osteoarthritis.2",
"phh.rheumatoid_arthritis.2",
"phh.other_arthritis.2",
"phh.prefer_not_to_answer.10",
"phh.none_of_the_above.11",
"phh.dont_know.11",
"phh.ankylosing_spondylitis.3",
"phh.osteoporosis_or_thin_bones.3",
"phh.hypermobility.2",
"phh.osteoarthritis.3",
"phh.rheumatoid_arthritis.3",
"phh.other_arthritis.3",
"phh.prefer_not_to_answer.11",
"phh.none_of_the_above.12",
"phh.dont_know.12",

#resp
"phh.asthma.1",
"phh.pulmonary_fibrosis.1",
"phh.chronic_obstructive_pulmonary_disease",
"phh.cystic_fibrosis.1",
"phh.pleural_effusion.1",
"phh.pneumonia",
"phh.pulmonary_embolus",
"phh.emphysema_or_chronic_bronchitis.1",
"phh.other.1",
"phh.dont_know.13",
"phh.prefer_not_to_say.1",
"phh.none_of_the_above.13",
"phh.asthma.2",
"phh.pulmonary_fibrosis.2",
"phh.chronic_obstructive_pulmonary_disease.1",
"phh.cystic_fibrosis.2",
"phh.pleural_effusion.2",
"phh.pneumonia.1",
"phh.pulmonary_embolus.1",
"phh.emphysema_or_chronic_bronchitis.2",
"phh.other.2",
"phh.dont_know.14",
"phh.prefer_not_to_say.2",
"phh.none_of_the_above.14",
"phh.asthma.3",
"phh.pulmonary_fibrosis.3",
"phh.chronic_obstructive_pulmonary_disease.2",
"phh.cystic_fibrosis.3",
"phh.pleural_effusion.3",
"phh.pneumonia.2",
"phh.pulmonary_embolus.2",
"phh.emphysema_or_chronic_bronchitis.3",
"phh.other.3",
"phh.dont_know.15",
"phh.prefer_not_to_say.3",
"phh.none_of_the_above.15",

#cardio
"phh.heart_attack_angina.1",
"phh.high_blood_cholesterol.1",
"phh.high_blood_pressure.1",
"phh.atrial_fibrillation.1",
"phh.stroke.1",
"phh.paroxysmal_tachycardia_sydrome",
"phh.dont_know.16",
"phh.prefer_not_to_answer.12",
"phh.none_of_the_above.16",
"phh.heart_attack_angina.2",
"phh.high_blood_cholesterol.2",
"phh.high_blood_pressure.2",
"phh.atrial_fibrillation.2",
"phh.stroke.2",
"phh.paroxysmal_tachycardia_sydrome.1",
"phh.dont_know.17",
"phh.prefer_not_to_answer.13",
"phh.none_of_the_above.17",
"phh.heart_attack_angina.3",
"phh.high_blood_cholesterol.3",
"phh.high_blood_pressure.3",
"phh.atrial_fibrillation.3",
"phh.stroke.3",
"phh.paroxysmal_tachycardia_sydrome.2",
"phh.dont_know.18",
"phh.prefer_not_to_answer.14",
"phh.none_of_the_above.18",

#cancer
"phh.breast_cancer.1",
"phh.lung_cancer.1",
"phh.stomach_cancer.1",
"phh.colon_cancer.1",
"phh.uterus_cancer.1",
"phh.prostate_cancer.1",
"phh.bladder_cancer.1",
"phh.bowel_cancer.1",
"phh.rectal_cancer.1",
"phh.lymphoma.1",
"phh.melanoma.1",
"phh.skin_cancer.1",
"phh.ovarian_cancer.1",
"phh.none_of_the_above.19",
"phh.dont_know.19",
"phh.prefer_not_to_answer.15",
"phh.breast_cancer.2",
"phh.lung_cancer.2",
"phh.stomach_cancer.2",
"phh.colon_cancer.2",
"phh.uterus_cancer.2",
"phh.prostate_cancer.2",
"phh.bladder_cancer.2",
"phh.bowel_cancer.2",
"phh.rectal_cancer.2",
"phh.lymphoma.2",
"phh.melanoma.2",
"phh.skin_cancer.2",
"phh.ovarian_cancer.2",
"phh.none_of_the_above.20",
"phh.dont_know.20",
"phh.prefer_not_to_answer.16",
"phh.breast_cancer.3",
"phh.lung_cancer.3",
"phh.stomach_cancer.3",
"phh.colon_cancer.3",
"phh.uterus_cancer.3",
"phh.prostate_cancer.3",
"phh.bladder_cancer.3",
"phh.bowel_cancer.3",
"phh.rectal_cancer.3",
"phh.lymphoma.3",
"phh.melanoma.3",
"phh.skin_cancer.3",
"phh.ovarian_cancer.3",
"phh.none_of_the_above.21",
"phh.dont_know.21",
"phh.prefer_not_to_answer.17",

#derm
"phh.psoriasis.1",
"phh.vitiligo.1",
"phh.eczema.1",
"phh.thyroid_disease_.1",
"phh.pain_due_to_virus",
"phh.none_of_the_above.22",
"phh.dont_know.22",
"phh.prefer_not_to_answer.18",
"phh.psoriasis.2",
"phh.vitiligo.2",
"phh.eczema.2",
"phh.thyroid_disease_.2",
"phh.pain_due_to_virus.1",
"phh.none_of_the_above.23",
"phh.dont_know.23",
"phh.prefer_not_to_answer.19",
"phh.psoriasis.3",
"phh.vitiligo.3",
"phh.eczema.3",
"phh.thyroid_disease_.3",
"phh.pain_due_to_virus.2",
"phh.none_of_the_above.24",
"phh.dont_know.24",
"phh.prefer_not_to_answer.20",

#allergy
"phh.hay_fever.1",
"phh.drug_allergy_",
"phh.food_allergy_.1",
"phh.any_other_allergy_.1",
"phh.dont_know.25",
"phh.prefer_not_to_answer.21",
"phh.none_of_the_above.25",
"phh.hay_fever.2",
"phh.drug_allergy_.1",
"phh.food_allergy_.2",
"phh.any_other_allergy_.2",
"phh.dont_know.26",
"phh.prefer_not_to_answer.22",
"phh.none_of_the_above.26",
"phh.hay_fever.3",
"phh.drug_allergy_.2",
"phh.food_allergy_.3",
"phh.any_other_allergy_.3",
"phh.dont_know.27",
"phh.prefer_not_to_answer.23",
"phh.none_of_the_above.27",

#gastro
"phh.crohns_disease",
"phh.ulcerative_colitis",
"phh.irritable_bowel_disease_",
"phh.coeliac_disease",
"phh.bacterial_stomach_infection_",
"phh.viral_weeks_bacterial_stomach",
"phh.diabetes_type_1_",
"phh.diabetes_type_2_",
"phh.pain_due_to_diabetes_",
"phh.dont_know.28",
"phh.prefer_not_to_answer.24",
"phh.none_of_the_above.28",
"phh.crohns_disease.1",
"phh.ulcerative_colitis.1",
"phh.irritable_bowel_disease",
"phh.coeliac_disease.1",
"phh.bacterial_stomach_infection",
"phh.viral_weeks_bacterial_stomach.1",
"phh.diabetes_type_1",
"phh.diabetes_type_2",
"phh.pain_due_to_diabetes",
"phh.dont_know.29",
"phh.prefer_not_to_answer.25",
"phh.none_of_the_above.29",
"phh.crohns_disease.2",
"phh.ulcerative_colitis.2",
"phh.irritable_bowel_disease.1",
"phh.coeliac_disease.2",
"phh.bacterial_stomach_infection.1",
"phh.viral_weeks_bacterial_stomach.2",
"phh.diabetes_type_1.1",
"phh.diabetes_type_2.1",
"phh.pain_due_to_diabetes.1",
"phh.dont_know.30",
"phh.prefer_not_to_answer.26",
"phh.none_of_the_above.30",
"phh.crohns_disease.3",
"phh.ulcerative_colitis.3",
"phh.irritable_bowel_disease.2",
"phh.coeliac_disease.3",
"phh.bacterial_stomach_infection.2",
"phh.viral_weeks_bacterial_stomach.3",
"phh.diabetes_type_1.2",
"phh.diabetes_type_2.2",
"phh.pain_due_to_diabetes.2",
"phh.dont_know.31",
"phh.prefer_not_to_answer.27",
"phh.none_of_the_above.31"


Ages

#neuro
"phh.epilepsy_or_convulsions.1",
"phh.migraines.1",
"phh.multiple_sclerosis.1",
"phh.parkinsons_disease.1",
"phh.brain_tumour.1",
"phh.severe_memory_loss",
"phh.cerebral_palsy.1",
"phh.dont_know.7",
"phh.prefer_not_to_answer.6",
"phh.none_of_the_above.7",

#osteo
"phh.ankylosing_spondylitis.1",
"phh.osteoporosis_or_thin_bones.1",
"phh.hypermobility",
"phh.osteoarthritis.1",
"phh.rheumatoid_arthritis.1",
"phh.other_arthritis.1",
"phh.prefer_not_to_answer.9",
"phh.none_of_the_above.10",
"phh.dont_know.10",

#resp
"phh.asthma.1",
"phh.pulmonary_fibrosis.1",
"phh.chronic_obstructive_pulmonary_disease",
"phh.cystic_fibrosis.1",
"phh.pleural_effusion.1",
"phh.pneumonia",
"phh.pulmonary_embolus",
"phh.emphysema_or_chronic_bronchitis.1",
"phh.other.1",
"phh.dont_know.13",
"phh.prefer_not_to_say.1",
"phh.none_of_the_above.13",

#cardio
"phh.heart_attack_angina.1",
"phh.high_blood_cholesterol.1",
"phh.high_blood_pressure.1",
"phh.atrial_fibrillation.1",
"phh.stroke.1",
"phh.paroxysmal_tachycardia_sydrome",
"phh.dont_know.16",
"phh.prefer_not_to_answer.12",
"phh.none_of_the_above.16",

#cancer
"phh.breast_cancer.1",
"phh.lung_cancer.1",
"phh.stomach_cancer.1",
"phh.colon_cancer.1",
"phh.uterus_cancer.1",
"phh.prostate_cancer.1",
"phh.bladder_cancer.1",
"phh.bowel_cancer.1",
"phh.rectal_cancer.1",
"phh.lymphoma.1",
"phh.melanoma.1",
"phh.skin_cancer.1",
"phh.ovarian_cancer.1",
"phh.none_of_the_above.19",
"phh.dont_know.19",
"phh.prefer_not_to_answer.15",

#derm
"phh.psoriasis.1",
"phh.vitiligo.1",
"phh.eczema.1",
"phh.thyroid_disease_.1",
"phh.pain_due_to_virus",
"phh.none_of_the_above.22",
"phh.dont_know.22",
"phh.prefer_not_to_answer.18",

#allergy
"phh.hay_fever.1",
"phh.drug_allergy_",
"phh.food_allergy_.1",
"phh.any_other_allergy_.1",
"phh.dont_know.25",
"phh.prefer_not_to_answer.21",
"phh.none_of_the_above.25",

#gastro
"phh.crohns_disease.1",
"phh.ulcerative_colitis.1",
"phh.irritable_bowel_disease",
"phh.coeliac_disease.1",
"phh.bacterial_stomach_infection",
"phh.viral_weeks_bacterial_stomach.1",
"phh.diabetes_type_1",
"phh.diabetes_type_2",
"phh.pain_due_to_diabetes",
"phh.dont_know.29",
"phh.prefer_not_to_answer.25",
"phh.none_of_the_above.29"



Text
"phh.nbsp",
"phh.nbsp.1",
"phh.",
"phh..1",
"phh..2",
"phh.nbsp.2",
"phh.nbsp.3",
"phh..3",
"phh..4",
"phh..5",
"phh.nbsp.4",
"phh.nbsp.5",
"phh..6",
"phh..7",
"phh..8",
"phh.drug_allergy_text.txt",
"phh.food_allergy_text.txt",
"phh.allergy_text.txt",
"phh.other_arthritistext.txt",
"phh.othertext.txt",
"phh.thyroid_disease_text.txt",
"phh.list_reason_taking_type.txt",
"phh.chronic_medical_conditions_diagnosis.txt"



Categorical
"phh.epilepsy_or_convulsions",
"phh.migraines",
"phh.multiple_sclerosis",
"phh.parkinsons_disease",
"phh.brain_tumour",
"phh.severe_memory_loss_",
"phh.cerebral_palsy",
"phh.dont_know",
"phh.prefer_not_to_answer",
"phh.none_of_the_above",
"phh.hay_fever",
"phh.drug_allergy",


"phh.food_allergy_",


"phh.any_other_allergy_",


"phh.dont_know.1",
"phh.prefer_not_to_answer.1",
"phh.none_of_the_above.1",
"phh.ankylosing_spondylitis",
"phh.osteoporosis_or_thin_bones",
"phh.hypermobility_",
"phh.osteoarthritis",
"phh.rheumatoid_arthritis",
"phh.other_arthritis",


"phh.none_of_the_above.2",
"phh.dont_know.2",
"phh.asthma",
"phh.pulmonary_fibrosis",
"phh.chronic_obstructive_pulmonary_disease_",
"phh.cystic_fibrosis",
"phh.pleural_effusion",
"phh.pneumonia_",
"phh.pulmonary_embolus_",
"phh.emphysema_or_chronic_bronchitis",
"phh.other",


"phh.dont_know.3",
"phh.prefer_not_to_say",
"phh.none_of_the_above.3",
"phh.heart_attack_angina",
"phh.high_blood_cholesterol",
"phh.high_blood_pressure",
"phh.atrial_fibrillation",
"phh.stroke",
"phh.paroxysmal_tachycardia_sydrome_",
"phh.dont_know.4",
"phh.prefer_not_to_answer.3",
"phh.none_of_the_above.4",
"phh.breast_cancer",
"phh.lung_cancer",
"phh.stomach_cancer",
"phh.colon_cancer",
"phh.uterus_cancer",
"phh.prostate_cancer",
"phh.bladder_cancer",
"phh.bowel_cancer",
"phh.rectal_cancer",
"phh.lymphoma",
"phh.melanoma",
"phh.skin_cancer",
"phh.ovarian_cancer",
"phh.none_of_the_above.5",
"phh.dont_know.5",
"phh.prefer_not_to_answer.4",
"phh.psoriasis",
"phh.vitiligo",
"phh.eczema",
"phh.thyroid_disease_",


"phh.pain_due_to_virus_",
"phh.none_of_the_above.6",
"phh.dont_know.6",
"phh.prefer_not_to_answer.5",


"phh.chronic_medical_conditions_mentioned",


"phh.longterm_prescription_medication",


"phh.non_steroid_antiinflammatory_drugs",
"phh.steroids",
"phh.immunosuppressants",
"phh.htr",
"phh.thyroid_hormones",
"phh.contraceptive_pill",
"phh.intrauterine_device",
"phh.intrauterine_system",
"phh.bronchodilators",


"phh.epilepsy_or_convulsions.2",
"phh.migraines.2",
"phh.multiple_sclerosis.2",
"phh.parkinsons_disease.2",
"phh.brain_tumour.2",
"phh.severe_memory_loss.1",
"phh.cerebral_palsy.2",
"phh.dont_know.8",
"phh.prefer_not_to_answer.7",
"phh.none_of_the_above.8",
"phh.epilepsy_or_convulsions.3",
"phh.migraines.3",
"phh.multiple_sclerosis.3",
"phh.parkinsons_disease.3",
"phh.brain_tumour.3",
"phh.severe_memory_loss.2",
"phh.cerebral_palsy.3",
"phh.dont_know.9",
"phh.prefer_not_to_answer.8",
"phh.none_of_the_above.9",


"phh.ankylosing_spondylitis.2",
"phh.osteoporosis_or_thin_bones.2",
"phh.hypermobility.1",
"phh.osteoarthritis.2",
"phh.rheumatoid_arthritis.2",
"phh.other_arthritis.2",
"phh.prefer_not_to_answer.10",
"phh.none_of_the_above.11",
"phh.dont_know.11",
"phh.ankylosing_spondylitis.3",
"phh.osteoporosis_or_thin_bones.3",
"phh.hypermobility.2",
"phh.osteoarthritis.3",
"phh.rheumatoid_arthritis.3",
"phh.other_arthritis.3",
"phh.prefer_not_to_answer.11",
"phh.none_of_the_above.12",
"phh.dont_know.12",


"phh.asthma.2",
"phh.pulmonary_fibrosis.2",
"phh.chronic_obstructive_pulmonary_disease.1",
"phh.cystic_fibrosis.2",
"phh.pleural_effusion.2",
"phh.pneumonia.1",
"phh.pulmonary_embolus.1",
"phh.emphysema_or_chronic_bronchitis.2",
"phh.other.2",
"phh.dont_know.14",
"phh.prefer_not_to_say.2",
"phh.none_of_the_above.14",
"phh.asthma.3",
"phh.pulmonary_fibrosis.3",
"phh.chronic_obstructive_pulmonary_disease.2",
"phh.cystic_fibrosis.3",
"phh.pleural_effusion.3",
"phh.pneumonia.2",
"phh.pulmonary_embolus.2",
"phh.emphysema_or_chronic_bronchitis.3",
"phh.other.3",
"phh.dont_know.15",
"phh.prefer_not_to_say.3",
"phh.none_of_the_above.15",


"phh.heart_attack_angina.2",
"phh.high_blood_cholesterol.2",
"phh.high_blood_pressure.2",
"phh.atrial_fibrillation.2",
"phh.stroke.2",
"phh.paroxysmal_tachycardia_sydrome.1",
"phh.dont_know.17",
"phh.prefer_not_to_answer.13",
"phh.none_of_the_above.17",
"phh.heart_attack_angina.3",
"phh.high_blood_cholesterol.3",
"phh.high_blood_pressure.3",
"phh.atrial_fibrillation.3",
"phh.stroke.3",
"phh.paroxysmal_tachycardia_sydrome.2",
"phh.dont_know.18",
"phh.prefer_not_to_answer.14",
"phh.none_of_the_above.18",


"phh.breast_cancer.2",
"phh.lung_cancer.2",
"phh.stomach_cancer.2",
"phh.colon_cancer.2",
"phh.uterus_cancer.2",
"phh.prostate_cancer.2",
"phh.bladder_cancer.2",
"phh.bowel_cancer.2",
"phh.rectal_cancer.2",
"phh.lymphoma.2",
"phh.melanoma.2",
"phh.skin_cancer.2",
"phh.ovarian_cancer.2",
"phh.none_of_the_above.20",
"phh.dont_know.20",
"phh.prefer_not_to_answer.16",
"phh.breast_cancer.3",
"phh.lung_cancer.3",
"phh.stomach_cancer.3",
"phh.colon_cancer.3",
"phh.uterus_cancer.3",
"phh.prostate_cancer.3",
"phh.bladder_cancer.3",
"phh.bowel_cancer.3",
"phh.rectal_cancer.3",
"phh.lymphoma.3",
"phh.melanoma.3",
"phh.skin_cancer.3",
"phh.ovarian_cancer.3",
"phh.none_of_the_above.21",
"phh.dont_know.21",
"phh.prefer_not_to_answer.17",


"phh.psoriasis.2",
"phh.vitiligo.2",
"phh.eczema.2",
"phh.thyroid_disease_.2",
"phh.pain_due_to_virus.1",
"phh.none_of_the_above.23",
"phh.dont_know.23",
"phh.prefer_not_to_answer.19",
"phh.psoriasis.3",
"phh.vitiligo.3",
"phh.eczema.3",
"phh.thyroid_disease_.3",
"phh.pain_due_to_virus.2",
"phh.none_of_the_above.24",
"phh.dont_know.24",
"phh.prefer_not_to_answer.20",


"phh.hay_fever.2",
"phh.drug_allergy_.1",
"phh.food_allergy_.2",
"phh.any_other_allergy_.2",
"phh.dont_know.26",
"phh.prefer_not_to_answer.22",
"phh.none_of_the_above.26",
"phh.hay_fever.3",
"phh.drug_allergy_.2",
"phh.food_allergy_.3",
"phh.any_other_allergy_.3",
"phh.dont_know.27",
"phh.prefer_not_to_answer.23",
"phh.none_of_the_above.27",
"phh.crohns_disease",
"phh.ulcerative_colitis",
"phh.irritable_bowel_disease_",
"phh.coeliac_disease",
"phh.bacterial_stomach_infection_",
"phh.viral_weeks_bacterial_stomach",
"phh.diabetes_type_1_",
"phh.diabetes_type_2_",
"phh.pain_due_to_diabetes_",
"phh.dont_know.28",
"phh.prefer_not_to_answer.24",
"phh.none_of_the_above.28",


"phh.crohns_disease.2",
"phh.ulcerative_colitis.2",
"phh.irritable_bowel_disease.1",
"phh.coeliac_disease.2",
"phh.bacterial_stomach_infection.1",
"phh.viral_weeks_bacterial_stomach.2",
"phh.diabetes_type_1.1",
"phh.diabetes_type_2.1",
"phh.pain_due_to_diabetes.1",
"phh.dont_know.30",
"phh.prefer_not_to_answer.26",
"phh.none_of_the_above.30",
"phh.crohns_disease.3",
"phh.ulcerative_colitis.3",
"phh.irritable_bowel_disease.2",
"phh.coeliac_disease.3",
"phh.bacterial_stomach_infection.2",
"phh.viral_weeks_bacterial_stomach.3",
"phh.diabetes_type_1.2",
"phh.diabetes_type_2.2",
"phh.pain_due_to_diabetes.2",
"phh.dont_know.31",
"phh.prefer_not_to_answer.27",
"phh.none_of_the_above.31"


All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except:
Study name (COVIDCNS) all caps
Capitalised first word

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = "scripts/functions/add_numeric_1.R")
source(file = "scripts/functions/remove_duplicates.R")
source(file = "scripts/functions/sumscores.R")
source(file = "scripts/functions/package_check.R")
source(file = "scripts/functions/imp_check_1.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in file with path to ilovecovidcns channel on teams}
source(file = "scripts/credentials/paths.R")
```

# Read in the data: Full Name of Questionnaire/Demographic
Change this heading to the name of your questionnaire/demographic
Load COVIDCNS data

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the issues spreadsheet "https://docs.google.com/spreadsheets/d/1a2gL8c0eH2pZXNTbnPzkDYQGeeVXbLKU8BUpYM0moe8/edit?usp=sharing"

- For variable names, use ONLY 'questionnaire.variable_name'
- For dataset, only use snake_case naming
- When using pipe operator '%>%', each function should begin on a new line
- Do not add empty lines at the beginning or end of a chunk
- Use only tidyverse functions wherever possible
- When naming chunks, begin with the name of the dataset (COVIDCNS)

## COVIDCNS data
```{r COVIDCNS load data}
covidcns_dat <- read_rds(
  file = paste0(ilovecovidcns, "/data_raw/latest_freeze/covid_cns/baseline/phh_covid_cns.rds")
  )
  
# Check variable names in dataframe
covidcns_dat %>%
  colnames()

# Inspect dimensions of dataframe 
covidcns_dat %>%
  dim()
```

Specify columns to be excluded from add_numeric function
Continuous variables should be excluded, as they are already numeric
```{r COVIDCNS specify excluded columns}
exclude_cols_numeric <- c(
  "ID",
  "sample",
  "startDate",
  "endDate",
  "phh.nbsp",
  "phh.nbsp.1",
  "phh.",
  "phh..1",
  "phh..2",
  "phh.nbsp.2",
  "phh.nbsp.3",
  "phh..3",
  "phh..4",
  "phh..5",
  "phh.nbsp.4",
  "phh.nbsp.5",
  "phh..6",
  "phh..7",
  "phh..8",
  "phh.epilepsy_or_convulsions.1",
  "phh.migraines.1",
  "phh.multiple_sclerosis.1",
  "phh.parkinsons_disease.1",
  "phh.brain_tumour.1",
  "phh.severe_memory_loss",
  "phh.cerebral_palsy.1",
  "phh.dont_know.7",
  "phh.prefer_not_to_answer.6",
  "phh.none_of_the_above.7",
  "phh.ankylosing_spondylitis.1",
  "phh.osteoporosis_or_thin_bones.1",
  "phh.hypermobility",
  "phh.osteoarthritis.1",
  "phh.rheumatoid_arthritis.1",
  "phh.other_arthritis.1",
  "phh.prefer_not_to_answer.9",
  "phh.none_of_the_above.10",
  "phh.dont_know.10",
  "phh.asthma.1",
  "phh.pulmonary_fibrosis.1",
  "phh.chronic_obstructive_pulmonary_disease",
  "phh.cystic_fibrosis.1",
  "phh.pleural_effusion.1",
  "phh.pneumonia",
  "phh.pulmonary_embolus",
  "phh.emphysema_or_chronic_bronchitis.1",
  "phh.other.1",
  "phh.dont_know.13",
  "phh.prefer_not_to_say.1",
  "phh.none_of_the_above.13",
  "phh.heart_attack_angina.1",
  "phh.high_blood_cholesterol.1",
  "phh.high_blood_pressure.1",
  "phh.atrial_fibrillation.1",
  "phh.stroke.1",
  "phh.paroxysmal_tachycardia_sydrome",
  "phh.dont_know.16",
  "phh.prefer_not_to_answer.12",
  "phh.none_of_the_above.16",
  "phh.breast_cancer.1",
  "phh.lung_cancer.1",
  "phh.stomach_cancer.1",
  "phh.colon_cancer.1",
  "phh.uterus_cancer.1",
  "phh.prostate_cancer.1",
  "phh.bladder_cancer.1",
  "phh.bowel_cancer.1",
  "phh.rectal_cancer.1",
  "phh.lymphoma.1",
  "phh.melanoma.1",
  "phh.skin_cancer.1",
  "phh.ovarian_cancer.1",
  "phh.none_of_the_above.19",
  "phh.dont_know.19",
  "phh.prefer_not_to_answer.15",
  "phh.psoriasis.1",
  "phh.vitiligo.1",
  "phh.eczema.1",
  "phh.thyroid_disease_.1",
  "phh.pain_due_to_virus",
  "phh.none_of_the_above.22",
  "phh.dont_know.22",
  "phh.prefer_not_to_answer.18",
  "phh.hay_fever.1",
  "phh.drug_allergy_",
  "phh.food_allergy_.1",
  "phh.any_other_allergy_.1",
  "phh.dont_know.25",
  "phh.prefer_not_to_answer.21",
  "phh.none_of_the_above.25",
  "phh.crohns_disease.1",
  "phh.ulcerative_colitis.1",
  "phh.irritable_bowel_disease",
  "phh.coeliac_disease.1",
  "phh.bacterial_stomach_infection",
  "phh.viral_weeks_bacterial_stomach.1",
  "phh.diabetes_type_1",
  "phh.diabetes_type_2",
  "phh.pain_due_to_diabetes",
  "phh.dont_know.29",
  "phh.prefer_not_to_answer.25",
  "phh.none_of_the_above.29",
  "phh.drug_allergy_text.txt",
  "phh.food_allergy_text.txt",
  "phh.allergy_text.txt",
  "phh.other_arthritistext.txt",
  "phh.othertext.txt",
  "phh.thyroid_disease_text.txt",
  "phh.list_reason_taking_type.txt",
  "phh.chronic_medical_conditions_diagnosis.txt"
  )
```

Select & rename relevant columns
```{r COVIDCNS select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "COVIDCNS",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         sample,
         startDate,
         endDate,
         phh.epilepsy_or_convulsions,
         phh.migraines,
         phh.multiple_sclerosis,
         phh.parkinsons_disease,
         phh.brain_tumour,
         phh.severe_memory_loss_,
         phh.cerebral_palsy,
         phh.dont_know,
         phh.prefer_not_to_answer,
         phh.none_of_the_above,
         phh.hay_fever,
         phh.drug_allergy,
         phh.drug_allergy_text.txt,
         phh.food_allergy_,
         phh.food_allergy_text.txt,
         phh.any_other_allergy_,
         phh.allergy_text.txt,
         phh.dont_know.1,
         phh.prefer_not_to_answer.1,
         phh.none_of_the_above.1,
         phh.ankylosing_spondylitis,
         phh.osteoporosis_or_thin_bones,
         phh.hypermobility_,
         phh.osteoarthritis,
         phh.rheumatoid_arthritis,
         phh.other_arthritis,
         phh.other_arthritistext.txt,
         phh.none_of_the_above.2,
         phh.dont_know.2,
         phh.asthma,
         phh.pulmonary_fibrosis,
         phh.chronic_obstructive_pulmonary_disease_,
         phh.cystic_fibrosis,
         phh.pleural_effusion,
         phh.pneumonia_,
         phh.pulmonary_embolus_,
         phh.emphysema_or_chronic_bronchitis,
         phh.other,
         phh.othertext.txt,
         phh.dont_know.3,
         phh.prefer_not_to_say,
         phh.none_of_the_above.3,
         phh.heart_attack_angina,
         phh.high_blood_cholesterol,
         phh.high_blood_pressure,
         phh.atrial_fibrillation,
         phh.stroke,
         phh.paroxysmal_tachycardia_sydrome_,
         phh.dont_know.4,
         phh.prefer_not_to_answer.3,
         phh.none_of_the_above.4,
         phh.breast_cancer,
         phh.lung_cancer,
         phh.stomach_cancer,
         phh.colon_cancer,
         phh.uterus_cancer,
         phh.prostate_cancer,
         phh.bladder_cancer,
         phh.bowel_cancer,
         phh.rectal_cancer,
         phh.lymphoma,
         phh.melanoma,
         phh.skin_cancer,
         phh.ovarian_cancer,
         phh.none_of_the_above.5,
         phh.dont_know.5,
         phh.prefer_not_to_answer.4,
         phh.psoriasis,
         phh.vitiligo,
         phh.eczema,
         phh.thyroid_disease_,
         phh.thyroid_disease_text.txt,
         phh.pain_due_to_virus_,
         phh.none_of_the_above.6,
         phh.dont_know.6,
         phh.prefer_not_to_answer.5,
         phh.list_reason_taking_type.txt,
         phh.chronic_medical_conditions_mentioned,
         phh.chronic_medical_conditions_diagnosis.txt,
         phh.nbsp,
         phh.nbsp.1,
         phh.,
         phh..1,
         phh..2,
         phh.nbsp.2,
         phh.nbsp.3,
         phh..3,
         phh..4,
         phh..5,
         phh.nbsp.4,
         phh.nbsp.5,
         phh..6,
         phh..7,
         phh..8,
         phh.longterm_prescription_medication,
         phh.non_steroid_antiinflammatory_drugs,
         phh.steroids,
         phh.immunosuppressants,
         phh.htr,
         phh.thyroid_hormones,
         phh.contraceptive_pill,
         phh.intrauterine_device,
         phh.intrauterine_system,
         phh.bronchodilators,
         phh.epilepsy_or_convulsions.1,
         phh.migraines.1,
         phh.multiple_sclerosis.1,
         phh.parkinsons_disease.1,
         phh.brain_tumour.1,
         phh.severe_memory_loss,
         phh.cerebral_palsy.1,
         phh.dont_know.7,
         phh.prefer_not_to_answer.6,
         phh.none_of_the_above.7,
         phh.epilepsy_or_convulsions.2,
         phh.migraines.2,
         phh.multiple_sclerosis.2,
         phh.parkinsons_disease.2,
         phh.brain_tumour.2,
         phh.severe_memory_loss.1,
         phh.cerebral_palsy.2,
         phh.dont_know.8,
         phh.prefer_not_to_answer.7,
         phh.none_of_the_above.8,
         phh.epilepsy_or_convulsions.3,
         phh.migraines.3,
         phh.multiple_sclerosis.3,
         phh.parkinsons_disease.3,
         phh.brain_tumour.3,
         phh.severe_memory_loss.2,
         phh.cerebral_palsy.3,
         phh.dont_know.9,
         phh.prefer_not_to_answer.8,
         phh.none_of_the_above.9,
         phh.ankylosing_spondylitis.1,
         phh.osteoporosis_or_thin_bones.1,
         phh.hypermobility,
         phh.osteoarthritis.1,
         phh.rheumatoid_arthritis.1,
         phh.other_arthritis.1,
         phh.prefer_not_to_answer.9,
         phh.none_of_the_above.10,
         phh.dont_know.10,
         phh.ankylosing_spondylitis.2,
         phh.osteoporosis_or_thin_bones.2,
         phh.hypermobility.1,
         phh.osteoarthritis.2,
         phh.rheumatoid_arthritis.2,
         phh.other_arthritis.2,
         phh.prefer_not_to_answer.10,
         phh.none_of_the_above.11,
         phh.dont_know.11,
         phh.ankylosing_spondylitis.3,
         phh.osteoporosis_or_thin_bones.3,
         phh.hypermobility.2,
         phh.osteoarthritis.3,
         phh.rheumatoid_arthritis.3,
         phh.other_arthritis.3,
         phh.prefer_not_to_answer.11,
         phh.none_of_the_above.12,
         phh.dont_know.12,
         phh.asthma.1,
         phh.pulmonary_fibrosis.1,
         phh.chronic_obstructive_pulmonary_disease,
         phh.cystic_fibrosis.1,
         phh.pleural_effusion.1,
         phh.pneumonia,
         phh.pulmonary_embolus,
         phh.emphysema_or_chronic_bronchitis.1,
         phh.other.1,
         phh.dont_know.13,
         phh.prefer_not_to_say.1,
         phh.none_of_the_above.13,
         phh.asthma.2,
         phh.pulmonary_fibrosis.2,
         phh.chronic_obstructive_pulmonary_disease.1,
         phh.cystic_fibrosis.2,
         phh.pleural_effusion.2,
         phh.pneumonia.1,
         phh.pulmonary_embolus.1,
         phh.emphysema_or_chronic_bronchitis.2,
         phh.other.2,
         phh.dont_know.14,
         phh.prefer_not_to_say.2,
         phh.none_of_the_above.14,
         phh.asthma.3,
         phh.pulmonary_fibrosis.3,
         phh.chronic_obstructive_pulmonary_disease.2,
         phh.cystic_fibrosis.3,
         phh.pleural_effusion.3,
         phh.pneumonia.2,
         phh.pulmonary_embolus.2,
         phh.emphysema_or_chronic_bronchitis.3,
         phh.other.3,
         phh.dont_know.15,
         phh.prefer_not_to_say.3,
         phh.none_of_the_above.15,
         phh.heart_attack_angina.1,
         phh.high_blood_cholesterol.1,
         phh.high_blood_pressure.1,
         phh.atrial_fibrillation.1,
         phh.stroke.1,
         phh.paroxysmal_tachycardia_sydrome,
         phh.dont_know.16,
         phh.prefer_not_to_answer.12,
         phh.none_of_the_above.16,
         phh.heart_attack_angina.2,
         phh.high_blood_cholesterol.2,
         phh.high_blood_pressure.2,
         phh.atrial_fibrillation.2,
         phh.stroke.2,
         phh.paroxysmal_tachycardia_sydrome.1,
         phh.dont_know.17,
         phh.prefer_not_to_answer.13,
         phh.none_of_the_above.17,
         phh.heart_attack_angina.3,
         phh.high_blood_cholesterol.3,
         phh.high_blood_pressure.3,
         phh.atrial_fibrillation.3,
         phh.stroke.3,
         phh.paroxysmal_tachycardia_sydrome.2,
         phh.dont_know.18,
         phh.prefer_not_to_answer.14,
         phh.none_of_the_above.18,
         phh.breast_cancer.1,
         phh.lung_cancer.1,
         phh.stomach_cancer.1,
         phh.colon_cancer.1,
         phh.uterus_cancer.1,
         phh.prostate_cancer.1,
         phh.bladder_cancer.1,
         phh.bowel_cancer.1,
         phh.rectal_cancer.1,
         phh.lymphoma.1,
         phh.melanoma.1,
         phh.skin_cancer.1,
         phh.ovarian_cancer.1,
         phh.none_of_the_above.19,
         phh.dont_know.19,
         phh.prefer_not_to_answer.15,
         phh.breast_cancer.2,
         phh.lung_cancer.2,
         phh.stomach_cancer.2,
         phh.colon_cancer.2,
         phh.uterus_cancer.2,
         phh.prostate_cancer.2,
         phh.bladder_cancer.2,
         phh.bowel_cancer.2,
         phh.rectal_cancer.2,
         phh.lymphoma.2,
         phh.melanoma.2,
         phh.skin_cancer.2,
         phh.ovarian_cancer.2,
         phh.none_of_the_above.20,
         phh.dont_know.20,
         phh.prefer_not_to_answer.16,
         phh.breast_cancer.3,
         phh.lung_cancer.3,
         phh.stomach_cancer.3,
         phh.colon_cancer.3,
         phh.uterus_cancer.3,
         phh.prostate_cancer.3,
         phh.bladder_cancer.3,
         phh.bowel_cancer.3,
         phh.rectal_cancer.3,
         phh.lymphoma.3,
         phh.melanoma.3,
         phh.skin_cancer.3,
         phh.ovarian_cancer.3,
         phh.none_of_the_above.21,
         phh.dont_know.21,
         phh.prefer_not_to_answer.17,
         phh.psoriasis.1,
         phh.vitiligo.1,
         phh.eczema.1,
         phh.thyroid_disease_.1,
         phh.pain_due_to_virus,
         phh.none_of_the_above.22,
         phh.dont_know.22,
         phh.prefer_not_to_answer.18,
         phh.psoriasis.2,
         phh.vitiligo.2,
         phh.eczema.2,
         phh.thyroid_disease_.2,
         phh.pain_due_to_virus.1,
         phh.none_of_the_above.23,
         phh.dont_know.23,
         phh.prefer_not_to_answer.19,
         phh.psoriasis.3,
         phh.vitiligo.3,
         phh.eczema.3,
         phh.thyroid_disease_.3,
         phh.pain_due_to_virus.2,
         phh.none_of_the_above.24,
         phh.dont_know.24,
         phh.prefer_not_to_answer.20,
         phh.hay_fever.1,
         phh.drug_allergy_,
         phh.food_allergy_.1,
         phh.any_other_allergy_.1,
         phh.dont_know.25,
         phh.prefer_not_to_answer.21,
         phh.none_of_the_above.25,
         phh.hay_fever.2,
         phh.drug_allergy_.1,
         phh.food_allergy_.2,
         phh.any_other_allergy_.2,
         phh.dont_know.26,
         phh.prefer_not_to_answer.22,
         phh.none_of_the_above.26,
         phh.hay_fever.3,
         phh.drug_allergy_.2,
         phh.food_allergy_.3,
         phh.any_other_allergy_.3,
         phh.dont_know.27,
         phh.prefer_not_to_answer.23,
         phh.none_of_the_above.27,
         phh.crohns_disease,
         phh.ulcerative_colitis,
         phh.irritable_bowel_disease_,
         phh.coeliac_disease,
         phh.bacterial_stomach_infection_,
         phh.viral_weeks_bacterial_stomach,
         phh.diabetes_type_1_,
         phh.diabetes_type_2_,
         phh.pain_due_to_diabetes_,
         phh.dont_know.28,
         phh.prefer_not_to_answer.24,
         phh.none_of_the_above.28,
         phh.crohns_disease.1,
         phh.ulcerative_colitis.1,
         phh.irritable_bowel_disease,
         phh.coeliac_disease.1,
         phh.bacterial_stomach_infection,
         phh.viral_weeks_bacterial_stomach.1,
         phh.diabetes_type_1,
         phh.diabetes_type_2,
         phh.pain_due_to_diabetes,
         phh.dont_know.29,
         phh.prefer_not_to_answer.25,
         phh.none_of_the_above.29,
         phh.crohns_disease.2,
         phh.ulcerative_colitis.2,
         phh.irritable_bowel_disease.1,
         phh.coeliac_disease.2,
         phh.bacterial_stomach_infection.1,
         phh.viral_weeks_bacterial_stomach.2,
         phh.diabetes_type_1.1,
         phh.diabetes_type_2.1,
         phh.pain_due_to_diabetes.1,
         phh.dont_know.30,
         phh.prefer_not_to_answer.26,
         phh.none_of_the_above.30,
         phh.crohns_disease.3,
         phh.ulcerative_colitis.3,
         phh.irritable_bowel_disease.2,
         phh.coeliac_disease.3,
         phh.bacterial_stomach_infection.2,
         phh.viral_weeks_bacterial_stomach.3,
         phh.diabetes_type_1.2,
         phh.diabetes_type_2.2,
         phh.pain_due_to_diabetes.2,
         phh.dont_know.31,
         phh.prefer_not_to_answer.27,
         phh.none_of_the_above.31
         ) %>%
  add_numeric_1(exclude = exclude_cols_numeric)

# Inspect colnames
covidcns_dat_id %>%
  colnames()
```

Look at number of people excluded
The number of people to be excluded should be negative
```{r COVIDCNS number excluded}
# Inspect dimensions of new data set
covidcns_dat_id %>%
  dim()

# Inspect number of rows dropped
covidcns_excluded <- dim(covidcns_dat_id)[1] - dim(covidcns_dat)[1]
covidcns_excluded
```

Check missingness by missmap
```{r COVIDCNS inspect missingness}
covidcns_miss_map <- covidcns_dat_id %>% 
  missmap()

covidcns_miss_map
```

Create dat as copy of covidcns_dat_id for brevity
This step gives you a 'reset' point: if your variable recoding screws up, re-run this chunk to give you a fresh 'dat' dataframe
```{r Create dat}
dat <- covidcns_dat_id 

# Check
dat %>% glimpse()
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(ends_with("numeric"),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)))
```

Create list of all unique values
```{r List unique values}
ulst <- sapply(dat, unique)
llst <- sapply(dat, levels)
```


# Cleaning Categorical Variables

Name your vectors in line with the chunks below
Number the vectors or name them intuitively if you have multiple vectors
Vectors of potential values should only contain possible values (exclude nonanswer values as appropriate)

Create sequential vectors of categorical values for variables
Save vectors to a list
Add variable names as names of list
```{r Vector categorical values}
vals_cat_1 <- c(
  
  NA
)

vals_cat_2 <- c(
  
  NA
)

vals_cat_3 <- c(
  
  NA
)

vals_cat_4 <- c(
  
  NA
)
```

Create list of numeric values vectors
```{r List categorical values vectors}
values_cat_list <- list(
  vals_cat_1,
  vals_cat_2,
  vals_cat_3,
  vals_cat_4
)
```

Create vector of categorical domains variables 
```{r Vector categorical variables}
variables_cat <- c(
  "questionnaire.variable_name"
)
```

Set names of list to variable names
```{r Set list names}
names(values_cat_list) <- variables_cat
```

Use imp_check iteratively to find if any implausible values
```{r Imp_check categorical variables}
# Create empty list
imp_list_cat <- list()

# Loop over each variable, checking against relevant set of values from list
# Add imp_message to list
for (i in 1:length(variables_cat)) {
  imp_list_cat[i] <- imp_check_1(data = dat,
                                 variables = names(values_cat_list)[i],
                                 values = values_cat_list[[i]]) 

}

# Name list with var names to correspond to imp_messages
names(imp_list_cat) <- variables_cat

# View list of imp_messages with corresponding var names
print(imp_list_cat)
```

Produce summary table of variables
```{r Summary table categorical variables}
dat %>%
  tbl_summary(
    include = all_of(variables_cat),
    missing_text = "Missing")
```


# Cleaning Numeric Variables

Name your vectors in line with the chunks below
Number the vectors or name them intuitively if you have multiple vectors
Vectors of potential values should only contain possible values (exclude nonanswer values as appropriate)

Create sequential vectors of numeric values for variables
Save vectors to a list
Add variable names as names of list
```{r Vector numeric values}
vals_num_1 <- c(
  
  NA
)

vals_num_2 <- c(
  
  NA
)
```

Create list of numeric values vectors
```{r List numeric values vectors}
values_num_list <- list(
  vals_num_1,
  vals_num_2
)
```

Create vector of categorical domains variables 
```{r Vector numeric variables}
variables_num <- c(
  "questionnaire.variable_name"
)
```

Set names of list to variable names
```{r Set list names}
names(values_num_list) <- variables_num
```

Use imp_check iteratively
Use imp_check iteratively to find if any implausible values
```{r Imp_check numeric variables}
# Create empty list
imp_list_num <- list()

# Loop over each variable, checking against relevant set of values from list
# Add imp_message to list
for (i in 1:length(variables_num)) {
  imp_list_num[i] <- imp_check_1(data = dat,
                                 variables = names(values_num_list)[i],
                                 values = values_num_list[[i]]) 

}

# Name list with var names to correspond to imp_messages
names(imp_list_num) <- variables_num

# View list of imp_messages with corresponding var names
print(imp_list_num)
```

Produce summary table of variables
```{r Summary table numeric variables}
dat %>%
  tbl_summary(
    include = all_of(variables_num),
    missing_text = "Missing")
```


# Recoding Incorrect Variables

Variable is coded wrong
```{r Inspect incorrect variable}
dat %>%
  select(
    questionnaire.variable_name,
    questionnaire.variable_name) %>%
  tbl_summary(missing_text = "Missing")
```

Recode incorrect variable
Can be removed after data recoded in qualtrics and after data export
If variables are found to be incorrect:
Report the error in the qualtrics issues spreadsheet
Add as action point on teams with yourself and Molly tagged
Recode the variable yourself using `case_when` as below
Continue cleaning your script with the recoded variable until fixed from source
DO NOT run this chunk multiple times: it will mess up the variable coding, requiring you to run the script again from the beginning
```{r Recode incorrect variable}
dat <- dat %>% 
  mutate(across(questionnaire.variable_name,
                ~case_when(
                  . == 1 ~ 0,
                  . == 2 ~ 1,
                  . == 3 ~ 2,
                  . == 4 ~ 3,
                  . == 5 ~ 4,
                  TRUE ~ .)))
```

Re-check variable coding
```{r Recheck variable coding}
dat %>%
  select(
    questionnaire.variable_name,
    questionnaire.variable_name) %>%
  tbl_summary(missing_text = "Missing")
```


# Cleaning Continuous Variables

Inspect range prior to cleaning
```{r Check range of values}
dat %>%
  select(variable_one) %>%
  tbl_summary()
```

Define limits for variable and list reasoning below
Variable name:
- Upper: reasoning
- Lower: reasoning

```{r Define limits}
variable_one_upper_limit = 
variable_one_lower_limit = 
```

Count number of outliers in variable
```{r Outlier count}
dat %>%
  filter(
    variable_one > variable_one_upper_limit | # bigger than the upper limit
      variable_one < variable_one_lower_limit & variable_one > -555 # smaller than the lower limit
      # or special conditions
    ) %>%
  nrow()
```

Recode variable outliers to -666
```{r Recode outliers to -666}
dat <- dat %>%
    mutate(
      variable_one = 
        if_else(
          variable_one > variable_one_upper_limit | # bigger than the upper limit
           variable_one < variable_one_lower_limit & variable_one > -555, # smaller than the lower limit
            # or special conditions
          true = -666,
          false = variable_one,
          missing = NA_real_
        )
    )
```

Re-inspect variable after cleaning
```{r Inspect after recoding to -666}
dat %>%
  select(variable_one) %>%
  tbl_summary()
```


# Cleaning Dates

Create vector of date variables
```{r Vector date variables}
variables_date <- c(
  "questionnaire.variable_name"
)
```

Inspect date variables
```{r COVIDCNS inspect dates}
dat %>%
  select(all_of(variables_date)) %>%
  glimpse()
```

Replace -77 values with NA as POSIX will reject -77 as a value when converting
```{r COVIDCNS recode -77 to NA}
dat <- dat %>% 
  mutate(across(
    all_of(variables_date),
    ~na_if(., "-77")
                )
         )
```

Parse dates using lubridate
```{r COVIDCNS parse dates}

dat <- dat %>% 
  mutate(across(
    all_of(variables_date),
    ~lubridate::parse_date_time(
    x = .,
    orders = c("d m y", "d/m/y", "d.m.y"),
    tz = "Europe/London"
    )
                )
         )
```

Recheck date variables
```{r COVIDCNS inspect dates}
dat %>%
  select(all_of(variables_date)) %>%
  tbl_summary(missing_text = "Missing")
```

Define limits for variable and list reasoning below
Variable name:
- Upper: latest data extraction, cannot have test in the future
- Lower: 30/01/2020, first confirmed UK COVID cases 

```{r Define limits}
upper_limit <- as.POSIXct("2022-02-22")
lower_limit <- as.POSIXct("2020-01-30")
```

Recode variable outliers to -666
```{r Recode outliers to NA}
dat <- dat %>%
    mutate(across(
    all_of(variables_date),
    ~ifelse(
      . > upper_limit | # bigger than the upper limit
        . < lower_limit, # smaller than the lower limit
      yes = NA_real_,
      no = .
        )
    )
) %>%
  mutate(across(
    all_of(variables_date),
    ~as.POSIXct(., origin = lubridate::origin))
  )
```

Re-check dates
```{r COVID CNS recheck dates}
dat %>%
  select(all_of(variables_date)) %>%
  tbl_summary(missing_text = "Missing")
```

# Text variables

Inspect text variables
```{r Inspect text vars}
variables_text <- c(
  phh.nbsp
phh.nbsp.1
phh.
phh..1
phh..2
phh.nbsp.2
phh.nbsp.3
phh..3
phh..4
phh..5
phh.nbsp.4
phh.nbsp.5
phh..6
phh..7
phh..8
  "phh.drug_allergy_text.txt",
  "phh.food_allergy_text.txt",
  "phh.allergy_text.txt",
  "phh.other_arthritistext.txt",
  "phh.othertext.txt",
  "phh.thyroid_disease_text.txt",
  "phh.list_reason_taking_type.txt",
  "phh.chronic_medical_conditions_diagnosis.txt"
)

covidcns_dat %>%
  select(all_of(variables_text)) %>%
  tbl_summary(
    missing_text = "Missing"
  )
```

# Save cleaned data

Check colnames before exporting final dataset
```{r Check colnames}
colnames(dat)
```

# COVIDCNS
```{r Write cleaned COVIDCNS variables to a .rds file}
dat %>%
  saveRDS(
    file = paste0(ilovecovidcns, "/data/latest_freeze/covidcns/location/questionnaire_covidcns_clean.rds")
    )
```
