---
title: "COVID CNS: Cleaning PHQ9"
author: "Jessica Mundy"
phq9_ide: "01/02/2022"
output: html_document
---

# Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

```{r Clear global environment}
rm(list=ls())
```

```{r Read in functions}
source(file = "scripts/functions/add_numeric.R")
source(file = "scripts/functions/sumscores.R")
source(file = "scripts/functions/package_check.R")
source(file = "scripts/functions/remove_duplicates.R")
source(file = "scripts/functions/imp_check.R")
```

Note: always load tidyverse last
```{r Install load dependencies}
packages = c(
  "summarytools",
  "sjlabelled",
  "Amelia",
  "knitr",
  "gtsummary",
  "tidyverse"
  )
package_check(packages)
```

```{r Get system date}
date <- Sys.Date()
date
```

```{r Source the credentials file}
source("scripts/credentials/paths.R")
```

# Read in the data 
```{r COVID CNS PHQ9 data}
phq9 <- read_rds(file = 
                   paste0(ilovecovidcns, "/data_raw/latest_freeze/baseline/phq9_covid_cns.rds")
                 )

# check
phq9 %>% 
  dim()

phq9 %>% 
  colnames()
```

Specify columns to be excluded from add_numeric function
Continuous variables should be excluded, as they are already numeric
```{r Specify columns to be excluded from add_numeric function}
exclude_cols_numeric <- c(
  "ID",
  "sample",
  "startDate",
  "endDate"
  )
```


## Select & rename relevant columns 
```{r Select and rename relevant columns}
phq9_id <- phq9 %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop NAs
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "COVIDCNS",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         sample,
         startDate,
         endDate,
         phq9.little_interest_or_pleasure_in_doing_things,
         phq9.feeling_down_depressed_or_hopeless,         
         phq9.staying_asleep_sleeping_trouble,            
         phq9.feeling_tired_or_having_little_energy,       
         phq9.poor_appetite_or_overeating,                
         phq9.feeling_bad_failure_family = phq9.feeling_bad_felt_family,                                 # renamed to match GLAD                   
         phq9.trouble_concentrating_reading_newspaper = phq9.trouble_concentrating_newspaper_reading,    # renamed to match GLAD            
         phq9.moving_fidgety_noticed_opposite = phq9.fidgety_opposite_slowly_restless,                   # renamed to match GLAD               
         phq9.dead_hurting_thoughts,                      
         phq9.problems_made_care_home,                     
         phq9.similar_experiences_thoughts_required
        ) %>%
   add_numeric(exclude = exclude_cols_numeric)

# Inspect colnames
phq9_id %>% 
  colnames()
```

```{r Number excluded}
# Inspect dimensions
dim(phq9_id)
# Differences
phq9_excluded <- dim(phq9_id)[1]-dim(phq9)[1]
phq9_excluded
```
`phq9_excluded` COVID CNS participants excluded due to missing data

### Inspect numeric variables
```{r Inspect numeric variables}
phq9_id %>%
  select(all_of(ends_with("numeric"))) %>%
  tbl_summary(missing_text = "Missing")

phq9_id %>% 
  select(ends_with("numeric")) %>% 
  freq()
```

# Data cleaning 

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
```{r Recode NA values}
phq9_id <- phq9_id %>%
   mutate(
     across(
       ends_with("numeric"),
             ~case_when(
             . == -55 ~ -555,   
             . == -77 ~ -777,
             . == -88 ~ -888,
             . == -99 ~ -999,
             TRUE ~ .)
   )
   )
```


## Numeric variables

### Select numeric PHQ9 variables for cleaning
This will select all of the PHQ9 numeric variables
```{r Select numeric PHQ9 variables for cleaning}
phq9_variables_numeric <- c(
  "phq9.little_interest_or_pleasure_in_doing_things_numeric",
  "phq9.feeling_down_depressed_or_hopeless_numeric",         
  "phq9.staying_asleep_sleeping_trouble_numeric",            
  "phq9.feeling_tired_or_having_little_energy_numeric",       
  "phq9.poor_appetite_or_overeating_numeric",                
  "phq9.feeling_bad_failure_family_numeric",                     
  "phq9.trouble_concentrating_reading_newspaper_numeric",    
  "phq9.moving_fidgety_noticed_opposite_numeric",            
  "phq9.dead_hurting_thoughts_numeric"          
)

# check
phq9_variables_numeric
```

### Vector of plausible numeric values for PHQ9 variables
```{r vector of plausible numeric values for PHQ9 variables}
phq9_vector_numeric <- c(
  0,
  1,
  2,
  3,
  -777,
  NA
  )
```

### Use imp_check function to find if any implausible values and obtain summary table of variables
```{r imp_check numeric PHQ9 variables}
imp_check(data = phq9_id,
          variables = phq9_variables_numeric,
          values = phq9_vector_numeric)
```

### Select numeric variable about problems
```{r Select numeric variable about problems}
phq9_problems_numeric <- c(
  "phq9.problems_made_care_home_numeric"      
)


# check
phq9_problems_numeric
```

### Vector of plausible numeric values for variable about problems
```{r Vector of plausible numeric values for variable about problems}
phq9_problems_vector_numeric <- c(
  1,
  2,
  3,
  4,
  -777,
  NA
  )
```
++JM I think these probably could be coded as 0, 1, 2 and 3 because 0 = "Not difficult at all". Jess will ask Lily and Dina to change in Qualtrics.

### Use imp_check function to find if any implausible values and obtain summary table of variables
```{r imp_check numeric problems variable}
imp_check(data = phq9_id,
          variables = phq9_problems_numeric,
          values = phq9_problems_vector_numeric)
```
### Select numeric variable about problems since COVID-19
```{r Select numeric variable about problems since COVID-19}
phq9_covid19_numeric <- c(
  "phq9.similar_experiences_thoughts_required_numeric"      
)


# check
phq9_problems_numeric
```

### Vector of plausible numeric values for variable about problems since COVID-19
```{r vector of plausible numeric values for variable about problems since COVID-19}
phq9_covid19_vector_numeric <- c(
  1,
  2,
  3,
  -777,
  NA
  )
```

### Use imp_check function to find if any implausible values and obtain summary table of variables
```{r imp_check numeric variable about problems since COVID-19}
imp_check(data = phq9_id,
          variables = phq9_covid19_numeric,
          values = phq9_covid19_vector_numeric)
```

## Non-numeric variables

### Select variables for cleaning
This will select all the PHQ9 variables
```{r Select PHQ9 variables for cleaning}
phq9_variables <- c(
  "phq9.little_interest_or_pleasure_in_doing_things",
  "phq9.feeling_down_depressed_or_hopeless",         
  "phq9.staying_asleep_sleeping_trouble",            
  "phq9.feeling_tired_or_having_little_energy",       
  "phq9.poor_appetite_or_overeating",                
  "phq9.feeling_bad_failure_family",                     
  "phq9.trouble_concentrating_reading_newspaper",    
  "phq9.moving_fidgety_noticed_opposite",            
  "phq9.dead_hurting_thoughts"          
)

  
# check
phq9_variables
```

### Vector of plausible values for PHQ9 variables
```{r vector of plausible values for PHQ9 variables}
phq9_vector <- c(
  "Not at all",
  "Several days",
  "More than half the days",
  "Nearly every day",
  "Seen but not answered",
  NA
  )
```


### Use imp_check function to find if any implausible values and obtain summary table of variables
```{r imp_check PHQ9 variables}
imp_check(data = phq9_id,
          variables = phq9_variables,
          values = phq9_vector)
```

### Select variable about problems
```{r Select variable about problems}
phq9_problems <- c(
  "phq9.problems_made_care_home"      
)


# check
phq9_problems
```

### Vector of plausible values for variable about problems
```{r vector of plausible values for variable about problems}
phq9_problems_vector <- c(
  "Not difficult at all",
  "Somewhat difficult",
  "Very difficult",
  "Extremely difficult",
  "Seen but not answered",
  NA
  )
```

### Use imp_check function to find if any implausible values and obtain summary table of variables
```{r imp_check problems variable}
imp_check(data = phq9_id,
          variables = phq9_problems,
          values = phq9_problems_vector)
```

### Select variable about problems since COVID-19
```{r Select variable about problems since COVID-19}
phq9_covid19 <- c(
  "phq9.similar_experiences_thoughts_required"      
)


# check
phq9_problems
```

### Vector of plausible values for variable about problems since COVID-19
```{r Vector of plausible values for variable about problems since COVID-19}
phq9_covid19_vector <- c(
  "Yes - they started after I had COVID-19 or during my infection with it",
  "No - I had these symptoms or experiences before I had COVID-19",
  "Don't know",
  "Seen but not answered",
  NA
  )
```

### Use imp_check function to find if any implausible values and obtain summary table of variables
```{r imp_check COVID19 variables}
imp_check(data = phq9_id,
          variables = phq9_covid19,
          values = phq9_covid19_vector)
```

# Produce sumscores

Reference to scoring guidance here: Kroenke K, Spitzer RL, Williams JB; The PHQ-9: validity of a brief depression severity measure. J Gen Intern Med. 2001 Sep 16(9):606-13.

## Sumscore inputs
```{r Sumscore inputs}
keys <- c(
  1, #1
  1, #2
  1, #3
  1, #4
  1, #5
  1, #6
  1, #7
  1, #8
  1 #9
  ) # should be 9 1s (none of the PHQ9 items are reverse coded)

sum_vars <- c(
  "phq9.dead_hurting_thoughts_numeric",
  "phq9.feeling_bad_failure_family_numeric",
  "phq9.feeling_down_depressed_or_hopeless_numeric",
  "phq9.feeling_tired_or_having_little_energy_numeric",
  "phq9.little_interest_or_pleasure_in_doing_things_numeric",
  "phq9.moving_fidgety_noticed_opposite_numeric",
  "phq9.poor_appetite_or_overeating_numeric",
  "phq9.staying_asleep_sleeping_trouble_numeric",
  "phq9.trouble_concentrating_reading_newspaper_numeric"
  )
```

## Generate sumscores
Generate sumscores from questionnaire data and add to dat as new column
sumscores assumes that all items in the questionnaire have the SAME minimum and maximum scores for ALL items, ensure that this is correct before proceeding

When adding the column name for your sumscore use "questionnaire.score_name"
```{r generate sumscore}
phq9_id <- phq9_id %>% 
  mutate(
    phq9.sum_score = 
         sumscores(input = phq9_id,
                   sum_vars = sum_vars,
                   coding_keys = keys,
                   na_allowed = 0,
                   min_item = 0,
                   max_item = 3,
                   min_score = 0,
                   max_score = 27
                   )[["scores"]]
         )

# check
phq9_id %>% 
  descr(phq9.sum_score)
```

# Clinical phenotyping of PHQ9

## Current depression
Create binary phenotypes based on PHQ9 scoring criteria
Validity has been assessed against an independent structured mental health professional (MHP) interview. PHQ-9 score ≥10 had a sensitivity of 88% and a specificity of 88% for major depression. 
```{r current major depression}
# numeric
phq9_id <- phq9_id %>% 
  mutate(
    phq9.binary_depression_numeric =
      case_when(
        phq9.sum_score >= 10 ~ 1, # current depression
        phq9.sum_score < 10 ~ 0 # no current depression
        )
    )

# recode as categorical 
phq9_id <- phq9_id %>% 
  mutate(
    phq9.binary_depression =
      recode_factor(phq9.binary_depression_numeric,
        "1" = "Current depression", # current depression
        "0" = "No current depression" # no current depression
        )
    )

# check
phq9_id %>% 
  select(
    phq9.binary_depression_numeric,
    phq9.binary_depression
    ) %>% 
   tbl_summary(missing_text = "Missing")

phq9_id %>% 
  select(
    phq9.binary_depression,
    phq9.binary_depression_numeric) %>% # variable is fine - just tbl_summary() giving wrong result 
  freq()
```

## Severity of depression
```{r severity of depression}
# numeric
phq9_id <- phq9_id %>% 
  mutate(
    phq9.severity_depression_numeric =
      case_when(
        phq9.sum_score <= 4 ~ 0,
        phq9.sum_score > 4 & phq9.sum_score <= 9 ~ 1,
        phq9.sum_score > 9 & phq9.sum_score <= 14 ~ 2,
        phq9.sum_score > 15 & phq9.sum_score <= 19 ~ 3,
        phq9.sum_score > 19 & phq9.sum_score <= 27 ~ 4
        )
    )

# recode as categorical
phq9_id <- phq9_id %>% 
  mutate(
    phq9.severity_depression =
      recode_factor(phq9.severity_depression_numeric,
        "0" = "None",
        "1" = "Mild",
        "2" = "Moderate",
        "3" = "Moderately severe",
        "4" = "Severe"
        )
    )

# check
phq9_id %>% 
  select(
    phq9.severity_depression,
    phq9.severity_depression_numeric
  ) %>% 
   tbl_summary(missing_text = "Missing")
```

# Save cleaned data

## Save variables for export
```{r Save variables for export}
export_variables <- c("ID",
                      "startDate",
                      "endDate",
                      "sample",
                      "phq9.dead_hurting_thoughts",                               
                      "phq9.feeling_bad_failure_family",                         
                      "phq9.feeling_down_depressed_or_hopeless",                  
                      "phq9.feeling_tired_or_having_little_energy",              
                      "phq9.little_interest_or_pleasure_in_doing_things",         
                      "phq9.moving_fidgety_noticed_opposite",                    
                      "phq9.poor_appetite_or_overeating",                        
                      "phq9.staying_asleep_sleeping_trouble",                    
                      "phq9.trouble_concentrating_reading_newspaper",             
                      "phq9.dead_hurting_thoughts_numeric",                      
                      "phq9.feeling_bad_failure_family_numeric",                  
                      "phq9.feeling_down_depressed_or_hopeless_numeric",         
                      "phq9.feeling_tired_or_having_little_energy_numeric",       
                      "phq9.little_interest_or_pleasure_in_doing_things_numeric",
                      "phq9.moving_fidgety_noticed_opposite_numeric",             
                      "phq9.poor_appetite_or_overeating_numeric",                
                      "phq9.staying_asleep_sleeping_trouble_numeric",             
                      "phq9.trouble_concentrating_reading_newspaper_numeric",    
                      "phq9.sum_score",                                           
                      "phq9.binary_depression",                                  
                      "phq9.binary_depression_numeric",                           
                      "phq9.severity_depression",                                
                      "phq9.severity_depression_numeric",
                      "phq9.problems_made_care_home",
                      "phq9.similar_experiences_thoughts_required",
                      "phq9.problems_made_care_home_numeric",
                      "phq9.similar_experiences_thoughts_required_numeric"
                      )


```

## Save cleaned data as .rds file
```{r Save cleaned data as .rds file}
phq9_id %>% 
  select(all_of(export_variables)) %>% 
  saveRDS(
    file = paste0(ilovecovidcns, "/data/latest_freeze/baseline/phq9_covidcns_clean.rds")
    )
```
