--
title: "COVIDCNS UPDRS Cleaning Script"
author: "Zain Ahmad"
date: "03/03/2022"
output: html_document
---


All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except:
Study name (COVIDCNS) all caps
Capitalised first word

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = "../functions/add_numeric.R")
source(file = "../functions/remove_duplicates.R")
source(file = "../functions/sumscores.R")
source(file = "../functions/package_check.R")
source(file = "../functions/imp_check_1.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in file with path to ilovecovidcns channel on teams}
source(file = "../credentials/paths.R")
```

# Read in the data: COVIDCNS Unified Parkinson's Disease Rating Scale
Change this heading to the name of your questionnaire/demographic
Load COVIDCNS data

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the issues spreadsheet "https://docs.google.com/spreadsheets/d/1a2gL8c0eH2pZXNTbnPzkDYQGeeVXbLKU8BUpYM0moe8/edit?usp=sharing"

- For variable names, use ONLY 'questionnaire.variable_name'
- For dataset, only use snake_case naming
- When using pipe operator '%>%', each function should begin on a new line
- Do not add empty lines at the beginning or end of a chunk
- Use only tidyverse functions wherever possible
- When naming chunks, begin with the name of the dataset (COVIDCNS)

## COVIDCNS data
```{r COVIDCNS load data}
covidcns_dat <- read_rds(
  file = paste0(ilovecovidcns, "/data_raw/latest_freeze/baseline/updrs_covid_cns.rds")
  )
  
# Check variable names in dataframe
covidcns_dat %>%
  colnames()
# Inspect dimensions of dataframe 
covidcns_dat %>%
  dim()
```

Specify columns to be excluded from add_numeric function
Continuous variables should be excluded, as they are already numeric
```{r COVIDCNS specify excluded columns}
exclude_cols_numeric <- c(
  "ID",
  "sample",
  "startDate",
  "endDate"
  )
```

Select & rename relevant columns
```{r COVIDCNS select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "COVIDCNS",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         sample,
         startDate,
         endDate,
         updrs.trouble_reading_handwriting_past,
         updrs.hobbies_trouble_past_week,
         updrs.trouble_turning_bed_past,
         updrs.shaking_tremor_past_week,
         updrs.left_arm,
         updrs.right_arm,
         updrs.left_leg,
         updrs.right_leg,
         updrs.whole_body,
         updrs.deep_chair_car_seat,
         updrs.balance_walking_past_week,
         updrs.feet_floor_freeze_stuck,
         updrs.speech_past_week_problems,
         updrs.awake_saliva_sleep_past,
         updrs.made_soft_chopped_avoid,
         updrs.trouble_handling_finger_foods,
         updrs.zippers_putting_problems_dressing,
         updrs.personal_hygiene_hair_slow,
         updrs.start_happening_required_question,
         updrs.start_happening_required_question.1,
         updrs.start_happening_required_question.2,
         updrs.start_happening_required_question.3,
         updrs.start_happening_required_question.4,
         updrs.start_happening_required_question.5,
         updrs.start_happening_required_question.6,
         updrs.start_happening_required_question.7,
         updrs.start_happening_required_question.8,
         updrs.start_happening_required_question.9,
         updrs.start_happening_required_question.10,
         updrs.start_happening_required_question.11,
         updrs.start_happening_required_question.12
         ) %>%
  add_numeric(exclude = exclude_cols_numeric)
# Inspect colnames
covidcns_dat_id %>%
  colnames()
```

Look at number of people excluded
The number of people to be excluded should be negative
```{r COVIDCNS number excluded}
# Inspect dimensions of new data set
covidcns_dat_id %>%
  dim()
# Inspect number of rows dropped
covidcns_excluded <- dim(covidcns_dat_id)[1] - dim(covidcns_dat)[1]
covidcns_excluded
```

Check missingness by missmap
```{r COVIDCNS inspect missingness}
covidcns_miss_map <- covidcns_dat_id %>% 
  missmap()
covidcns_miss_map
```

Create dat as copy of covidcns_dat_id for brevity
This step gives you a 'reset' point: if your variable recoding screws up, re-run this chunk to give you a fresh 'dat' dataframe
```{r Create dat}
dat <- covidcns_dat_id 
# Check
dat %>% glimpse()
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(ends_with("numeric"),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)))
```

Create list of all unique values
```{r List unique values}
ulst <- sapply(dat, unique)
llst <- sapply(dat, levels)
```


# Cleaning Categorical Variables

Name your vectors in line with the chunks below
Number the vectors or name them intuitively if you have multiple vectors
Vectors of potential values should only contain possible values (exclude nonanswer values as appropriate)

Create sequential vectors of categorical values for variables
Save vectors to a list
Add variable names as names of list
```{r Vector categorical values}
values_cat_list <- list(
  c(
    "Seen but not answered",
    "Normal - Not at all (no problems).",
    "Slight - My writing is slow, clumsy or uneven, but all words are clear.",
    "Mild - Some words are unclear and difficult to read.",
    "Moderate - Many words are unclear and difficult to read.",
    "Severe - Most or all words cannot be read.",
    NA
  ),
  
  c(
    "Seen but not answered",
    "Normal - Not at all (no problems).",
    "Slight - I am a bit slow but do these activities easily.",
    "Mild - I have some difficulty doing these activities.",
    "Moderate - I have major problems doing these activities, but still do most.",
    "Severe - I am unable to do most or all of these activities.",
    NA
  ),
  
  c(
    "Seen but not answered",
    "Normal - Not at all (no problems).",
    "Slight - I have a bit of trouble turning, but I do not need any help.",
    "Mild - I have a lot of trouble turning and need occasional help from someone else.",
    "Moderate - To turn over I often need help from someone else.",
    "Severe - I am unable to turn over without help from someone else.",
    NA
  ),
  
  c(
    "Seen but not answered",
    "Normal - Not at all. I have no shaking or tremor.",
    "Slight - Shaking or tremor occurs but does not cause problems with any activities.",
    "Mild - Shaking or tremor causes problems with only a few activities.",
    "Moderate - Shaking or tremor causes problems with many of my daily activities.",
    "Severe - Shaking or tremor causes problems with most or all activities.",
    NA
  ),
  
  c(
    "Not Left arm",
    "Left arm",
    NA
  ),
  
  c(
    "Not Right arm",
    "Right arm",
    NA
  ),
  
  c(
    "Not Left leg",
    "Left leg",
    NA
  ),
  
  c(
    "Not Right leg",
    "Right leg",
    NA
  ),
  
  c(
    "Not Whole body",
    "Whole body",
    NA
  ),
  
  c(
    "Seen but not answered",
    "Normal - Not at all (no problems).",
    "Slight - I am slow or awkward, but I usually can do it on my first try.",
    "Mild - I need more than one try to get up or need occasional help.",
    "Moderate - I sometimes need help to get up, but most times I can still do it on my own.",
    "Severe - I need help most or all of the time.",
    NA
  ),
  
  c(
    "Seen but not answered",
    "Normal - Not at all (no problems).",
    "Slight - I am slightly slow or may drag a leg. I never use a walking aid.",
    "Mild - I occasionally use a walking aid, but I do not need any help from another person.",
    "Moderate - I usually use a walking aid (cane, walker) to walk safely without falling. However, I do not usually need the support of another person.",
    "Severe - I usually use the support of another person to walk safely without falling.",
    NA
  ),
  
  c(
    "Seen but not answered",
    "Normal - Not at all (no problems).",
    "Slight - I briefly freeze but I can easily start to walk again. I do not need help from someone else or a walking aid (cane or walker) because of freezing.",
    "Mild - I freeze and have trouble starting to walk again, but I do not need someone's help or a walking aid (cane or walker) because of freezing.",
    "Moderate - When I freeze I have a lot of trouble starting to walk again and, because of freezing, I sometimes need to use a walking aid or need someone else's help.",
    "Severe - Because of freezing, most or all of the time, I need to use a walking aid or someone's help.",
    NA
  ),
  
  c(
    "Seen but not answered",
    "Normal - Not at all (no problems)",
    "Slight - My speech is soft, slurred or uneven, but it does not cause others to ask me to repeat myself.",
    "Mild - My speech causes people to ask me to occasionally repeat myself, but not everyday.",
    "Moderate - My speech is unclear enough that others ask me to repeat myself every day even though most of my speech is understood.",
    "Severe - Most or all of my speech cannot be understood.",
    NA
  ),
  
  c(
    "Seen but not answered",
    "Normal - Not at all (no problems).",
    "Slight - I have too much saliva, but do not drool.",
    "Mild - I have some drooling during sleep, but none when I am awake.",
    "Moderate - I have some drooling when I am awake, but I usually do not need tissues or a handkerchief.",
    "Severe - I have so much drooling that I regularly need to use tissues or a handkerchief to protect my clothes.",
    NA
  ),
  
  c(
    "Seen but not answered",
    "Normal - No problems.",
    "Slight - I am aware of slowness in my chewing or increased effort at swallowing, but I do not choke or need to have my food specially prepared.",
    "Mild - I need to have my pills cut or my food specially prepared because of chewing or swallowing problems, but I have not choked over the past week.",
    "Moderate - I choked at least once in the past week.",
    "Severe - Because of chewing and swallowing problems, I need a feeding tube.",
    NA
  ),
  
  c(
    "Seen but not answered",
    "Normal - Not at all (no problems).",
    "Slight - I am slow, but I do not need any help handling my food and have not had food spills while eating.",
    "Mild - I am slow with my eating and have occasional food spills. I may need help with a few tasks such as cutting meat.",
    "Moderate - I need help with many eating tasks but can manage some alone.",
    "Severe - I need help for most or all eating tasks.",
    NA
  ),
  
  c(
    "Seen but not answered",
    "Normal - Not at all (no problems).",
    "Slight - I am slow but I do not need help.",
    "Mild - I need someone else to help me with some dressing tasks.",
    "Moderate - I need help for many dressing tasks.",
    "Severe - I need help for most or all of my dressing tasks.",
    NA
  ),
  
  c(
    "Seen but not answered",
    "Normal - Not at all (no problems).",
    "Slight - I am slow but I do not need any help.",
    "Mild - I need someone else to help me with some hygiene tasks.",
    "Moderate - I need help for many hygiene tasks.",
    "Severe - I need help for most or all of my hygiene tasks.",
    NA
  ),
  
  c(
    "Don't know",
    "Seen but not answered",
    "No – I had this problem before I had COVID-19",
    "Yes – this problem started after I had COVID-19 or during my infection with it",
    NA
  ),
  c(
    "Don't know",
    "Seen but not answered",
    "No – I had this problem before I had COVID-19",
    "Yes – this problem started after I had COVID-19 or during my infection with it",
    NA
  ),
  
  c(
    "Don't know",
    "Seen but not answered",
    "No – I had this problem before I had COVID-19",
    "Yes – this problem started after I had COVID-19 or during my infection with it",
    NA
  ),
  c(
    "Don't know",
    "Seen but not answered",
    "No – I had this problem before I had COVID-19",
    "Yes – this problem started after I had COVID-19 or during my infection with it",
    NA
  ),
  
  c(
    "Don't know",
    "Seen but not answered",
    "No – I had this problem before I had COVID-19",
    "Yes – this problem started after I had COVID-19 or during my infection with it",
    NA
  ),
  c(
    "Don't know",
    "Seen but not answered",
    "No – I had this problem before I had COVID-19",
    "Yes – this problem started after I had COVID-19 or during my infection with it",
    NA
  ),
  
  c(
    "Don't know",
    "Seen but not answered",
    "No – I had this problem before I had COVID-19",
    "Yes – this problem started after I had COVID-19 or during my infection with it",
    NA
  ),
  c(
    "Don't know",
    "Seen but not answered",
    "No – I had this problem before I had COVID-19",
    "Yes – this problem started after I had COVID-19 or during my infection with it",
    NA
  ),
  
  c(
    "Don't know",
    "Seen but not answered",
    "No – I had this problem before I had COVID-19",
    "Yes – this problem started after I had COVID-19 or during my infection with it",
    NA
  ),
  c(
    "Don't know",
    "Seen but not answered",
    "No – I had this problem before I had COVID-19",
    "Yes – this problem started after I had COVID-19 or during my infection with it",
    NA
  ),
  
  c(
    "Don't know",
    "Seen but not answered",
    "No – I had this problem before I had COVID-19",
    "Yes – this problem started after I had COVID-19 or during my infection with it",
    NA
  ),
  c(
    "Don't know",
    "Seen but not answered",
    "No – I had this problem before I had COVID-19",
    "Yes – this problem started after I had COVID-19 or during my infection with it",
    NA
  ),
  
  c(
    "Don't know",
    "Seen but not answered",
    "No – I had this problem before I had COVID-19",
    "Yes – this problem started after I had COVID-19 or during my infection with it",
    NA
  )
)
```

Set names of list to variable names
```{r Set list names categorical variables}
names(values_cat_list) <- c(
  "updrs.trouble_reading_handwriting_past",
  "updrs.hobbies_trouble_past_week",
  "updrs.trouble_turning_bed_past",
  "updrs.shaking_tremor_past_week",
  "updrs.left_arm",
  "updrs.right_arm",
  "updrs.left_leg",
  "updrs.right_leg",
  "updrs.whole_body",
  "updrs.deep_chair_car_seat",
  "updrs.balance_walking_past_week",
  "updrs.feet_floor_freeze_stuck",
  "updrs.speech_past_week_problems",
  "updrs.awake_saliva_sleep_past",
  "updrs.made_soft_chopped_avoid",
  "updrs.trouble_handling_finger_foods",
  "updrs.zippers_putting_problems_dressing",
  "updrs.personal_hygiene_hair_slow",
  "updrs.start_happening_required_question",
  "updrs.start_happening_required_question.1",
  "updrs.start_happening_required_question.2",
  "updrs.start_happening_required_question.3",
  "updrs.start_happening_required_question.4",
  "updrs.start_happening_required_question.5",
  "updrs.start_happening_required_question.6",
  "updrs.start_happening_required_question.7",
  "updrs.start_happening_required_question.8",
  "updrs.start_happening_required_question.9",
  "updrs.start_happening_required_question.10",
  "updrs.start_happening_required_question.11",
  "updrs.start_happening_required_question.12"
)
```

Use imp_check iteratively to find if any implausible values
```{r Imp_check categorical variables}
# Create empty list
imp_list_cat <- list()
# Loop over each variable, checking against relevant set of values from list
# Add imp_message to list
for (i in 1:length(names(values_cat_list))) {
  imp_list_cat[i] <- imp_check_1(data = dat,
                                 variables = names(values_cat_list)[i],
                                 values = values_cat_list[[i]]) 
}
# Name list with var names to correspond to imp_messages
names(imp_list_cat) <- names(values_cat_list)
# View list of imp_messages with corresponding var names
print(imp_list_cat)
```

Produce summary table of variables
```{r Summary table categorical variables}
dat %>%
  tbl_summary(
    include = all_of(names(values_cat_list)),
    missing_text = "Missing")
```


# Cleaning Numeric Variables

Name your vectors in line with the chunks below
Number the vectors or name them intuitively if you have multiple vectors
Vectors of potential values should only contain possible values (exclude nonanswer values as appropriate)

Create sequential vectors of numeric values for variables
Save vectors to a list
Add variable names as names of list
```{r Vector numeric values}
vals_num_1 <- c(
  0,
  1,
  2,
  3,
  4,
  -777,
  NA
)
vals_num_2 <- c(
  0,
  1,
  -777,
  NA
)
vals_num_3 <- c(
  0,
  1,
  -777,
  -888,
  NA
)
```

Save values vectors to list
```{r List values vectors}
values_num_list <- list(
  vals_num_1,
  vals_num_1,
  vals_num_1,
  vals_num_1,
  vals_num_2,
  vals_num_2,
  vals_num_2,
  vals_num_2,
  vals_num_2,
  vals_num_1,
  vals_num_1,
  vals_num_1,
  vals_num_1,
  vals_num_1,
  vals_num_1,
  vals_num_1,
  vals_num_1,
  vals_num_1,
  vals_num_3,
  vals_num_3,
  vals_num_3,
  vals_num_3,
  vals_num_3,
  vals_num_3,
  vals_num_3,
  vals_num_3,
  vals_num_3,
  vals_num_3,
  vals_num_3,
  vals_num_3,
  vals_num_3
)
```

Remove values vectors from environment
```{r Remove values vectors}
rm(
  vals_num_1,
  vals_num_2,
  vals_num_3
)
```

Set names of list to variable names
```{r Set list names numeric variables}
names(values_num_list) <- c(
  "updrs.trouble_reading_handwriting_past_numeric",
  "updrs.hobbies_trouble_past_week_numeric",
  "updrs.trouble_turning_bed_past_numeric",
  "updrs.shaking_tremor_past_week_numeric",
  "updrs.left_arm_numeric",
  "updrs.right_arm_numeric",
  "updrs.left_leg_numeric",
  "updrs.right_leg_numeric",
  "updrs.whole_body_numeric",
  "updrs.deep_chair_car_seat_numeric",
  "updrs.balance_walking_past_week_numeric",
  "updrs.feet_floor_freeze_stuck_numeric",
  "updrs.speech_past_week_problems_numeric",
  "updrs.awake_saliva_sleep_past_numeric",
  "updrs.made_soft_chopped_avoid_numeric",
  "updrs.trouble_handling_finger_foods_numeric",
  "updrs.zippers_putting_problems_dressing_numeric",
  "updrs.personal_hygiene_hair_slow_numeric",
  "updrs.start_happening_required_question_numeric",
  "updrs.start_happening_required_question.1_numeric",
  "updrs.start_happening_required_question.2_numeric",
  "updrs.start_happening_required_question.3_numeric",
  "updrs.start_happening_required_question.4_numeric",
  "updrs.start_happening_required_question.5_numeric",
  "updrs.start_happening_required_question.6_numeric",
  "updrs.start_happening_required_question.7_numeric",
  "updrs.start_happening_required_question.8_numeric",
  "updrs.start_happening_required_question.9_numeric",
  "updrs.start_happening_required_question.10_numeric",
  "updrs.start_happening_required_question.11_numeric",
  "updrs.start_happening_required_question.12_numeric"
)
```

Use imp_check iteratively to find if any implausible values
```{r Imp_check numeric variables}
# Create empty list
imp_list_num <- list()
# Loop over each variable, checking against relevant set of values from list
# Add imp_message to list
for (i in 1:length(names(values_num_list))) {
  imp_list_num[i] <- imp_check_1(data = dat,
                                 variables = names(values_num_list)[i],
                                 values = values_num_list[[i]]) 
}
# Name list with var names to correspond to imp_messages
names(imp_list_num) <- names(values_num_list)
# View list of imp_messages with corresponding var names
print(imp_list_num)
```

Produce summary table of variables
```{r Summary table numeric variables}
dat %>%
  tbl_summary(
    include = all_of(names(values_num_list)),
    missing_text = "Missing")
```


# Produce sumscores

Reference the scoring guidance that you have used for your questionnaire here "link"

If changing na_limit, CHECK your guidance, na_limit > 0 will replace NAs with 0, ensure that this is correct for your scoring guidance before proceeding

Create vector of item coding
The coding_keys vector must contain 1s for all variables to be added and -1 for all variables to be subtracted.
Putting 0 in the vector will omit the variable at that position.
length(coding_keys) MUST be the same as the number of variables to be summed

sum_vars vector should contain ONLY and ALL variable names needed for scoring, do not add "ID" or "sample" etc.

If using reverse keying:
MAKE SURE that Reverse = TRUE is included as an argument, reverse keying will not work without this
reverse_vars should contain all variable names to be reverse keyed
If running multiple sumscores requiring reverse keying, a single reverse_vars vector containing all of the variable names to be reverse keyed is sufficient: `%in%` will pick the relevant variables for each sumscore

The warnings "Scores vector contains missing values." and "Input contains non-answer values. These will be converted to NA_real_ for this calculation." are normal. They are there to inform you that some sumscores have not been calculated due to non-answer values (e.g. -777) being present. Any other errors or warnings need to be investigated.

Create required variables for sumscore arguments
```{r Sumscores inputs}
keys <- c(
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1
  )
sum_vars <- c(
  "updrs.trouble_reading_handwriting_past_numeric",
  "updrs.hobbies_trouble_past_week_numeric",
  "updrs.trouble_turning_bed_past_numeric",
  "updrs.shaking_tremor_past_week_numeric",
  "updrs.left_arm_numeric",
  "updrs.right_arm_numeric",
  "updrs.left_leg_numeric",
  "updrs.right_leg_numeric",
  "updrs.whole_body_numeric",
  "updrs.deep_chair_car_seat_numeric",
  "updrs.balance_walking_past_week_numeric",
  "updrs.feet_floor_freeze_stuck_numeric",
  "updrs.speech_past_week_problems_numeric",
  "updrs.awake_saliva_sleep_past_numeric",
  "updrs.made_soft_chopped_avoid_numeric",
  "updrs.trouble_handling_finger_foods_numeric",
  "updrs.zippers_putting_problems_dressing_numeric",
  "updrs.personal_hygiene_hair_slow_numeric"
  )
```


Generate sumscores from questionnaire data and use mutate onto dat as new column
sumscores assumes that all items in the questionnaire have the SAME minimum and maximum scores for ALL items, ensure that this is correct before proceeding

When adding the column name for your sumscore use "questionnaire.score_name"

Generate sumscores and add as new column
```{r Generate sumscores}
dat <- dat %>% 
  mutate(
    updrs.sum_score = 
         sumscores(input = dat,
                   sum_vars = sum_vars,
                   coding_keys = keys,
                   na_allowed = 0,
                   min_item = 0,
                   max_item = 4,
                   min_score = 0,
                   max_score = 72
                   )[["scores"]]
         )
```

# Save cleaned data

Check colnames before exporting final dataset
```{r Check colnames}
colnames(dat)
```

# COVIDCNS
```{r Write cleaned COVIDCNS variables to a .rds file}
dat %>%
  saveRDS(
    file = paste0(ilovecovidcns, "/data/latest_freeze/baseline/updrs_covidcns_clean.rds")
    )
```
