---
title: "Covid CNS Glasgow Come Scale"
author: "Alish Palmos"
date: "14/01/2022"
output: html_document
---

All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = "../functions/add_numeric.R")
source(file = "../functions/remove_duplicates.R")
source(file = "../functions/sumscores.R")
source(file = "../functions/package_check.R")
source(file = "../functions/imp_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

Read in file with path to ilovedata channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in file with path to ilovedata channel on teams}
source("../../../covidcns_data_credentials.R")
```

# Read in the data: Full Name of Questionnaire/Demographic
Change this heading to the name of your questionnaire/demographic

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the issues spreadsheet "https://docs.google.com/spreadsheets/d/1a2gL8c0eH2pZXNTbnPzkDYQGeeVXbLKU8BUpYM0moe8/edit?usp=sharing"

- For variable names, use ONLY 'questionnaire.variable_name'
- For dataset, only use snake_case naming
- When using pipe operator '%>%', each function should begin on a new line
- Do not add empty lines at the beginning or end of a chunk
- Use only tidyverse functions wherever possible

## Data
```{r load data}
covidcns_dat <- read_rds(
  file = paste0(filepath_data_raw, "/data_raw/2021-07-12/core_neuro/gcs_outpatient_covid_cns.rds")
  )
  
# Check variable names in dataframe
covidcns_dat %>%
  colnames()
# Inspect dimensions of dataframe 
covidcns_dat %>%
  dim()
```

Specify columns to be excluded from add_numeric function
Continuous variables should be excluded, as they are already numeric
NB: If this is data from the COPING survey, add "_cop" to the end of each variable name
```{r specify excluded columns}
exclude_cols_numeric <- c(
  "ID",
  "sample",
  "startDate",
  "endDate"
 # other columns as required
  )
```

Select & rename relevant columns
```{r select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "COVID-CNS",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         sample,
         startDate,
         endDate,
         gcs_outpatient.eyes,
         gcs_outpatient.movements,
         gcs_outpatient.verbal
         # other columns as necessary
         ) %>%
  add_numeric(exclude = exclude_cols_numeric)
# Inspect colnames
covidcns_dat_id %>%
  colnames()
```

Look at number of people excluded
The number of people to be excluded should be negative
```{r number excluded}
# Inspect dimensions of new data set
covidcns_dat_id %>%
  dim()
# Inspect number of rows dropped
covidcns_excluded <- dim(covidcns_dat_id)[1] - dim(covidcns_dat)[1]
covidcns_excluded
```

Inspect numeric variables
```{r inspect numeric variables}
covidcns_dat_id %>%
  select(all_of(ends_with("numeric"))) %>%
  tbl_summary(missing_text = "Missing")
```

Check missingness by missmap
```{r GLAD inspect missingness}
covidcns_miss_map <- covidcns_dat_id %>% 
  missmap()
covidcns_miss_map
```

Recode incorrect variable
Can be removed after data recoded in qualtrics and after data export
If variables are found to be incorrect:
Report the error in the qualtrics issues spreadsheet
Add as action point on teams with yourself and Molly tagged
Recode the variable yourself using `case_when` as below
Continue cleaning your script with the recoded variable until fixed from source
DO NOT run this chunk multiple times: it will mess up the variable coding, requiring you to run the script again from the beginning
```{r recode incorrect variable}
covidcns_dat_id <- covidcns_dat_id %>% 
  mutate(across(gcs_outpatient.eyes_numeric,
                ~case_when(
                  . == 1 ~ 0,
                  . == 2 ~ 1,
                  . == 3 ~ 2,
                  . == 4 ~ 3,
                  TRUE ~ .)))

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(gcs_outpatient.eyes =
           recode_factor(gcs_outpatient.eyes_numeric,
                         "0" = "Does not open eyes",
                         "1" = "Opens eyes in response to pain",
                         "2" = "Opens eyes in response to voice",
                         "3" = "Opens eyes spontaneously",
                         "-77" = "Seen but not answered"
                         )
    )

covidcns_dat_id <- covidcns_dat_id %>% 
  mutate(across(gcs_outpatient.movements_numeric,
                ~case_when(
                  . == 1 ~ 0,
                  . == 2 ~ 1,
                  . == 3 ~ 2,
                  . == 4 ~ 3,
                  . == 5 ~ 4,
                  . == 6 ~ 5,
                  TRUE ~ .)))

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(gcs_outpatient.movements =
           recode_factor(gcs_outpatient.movements_numeric,
                         "0" = "Makes no movements",
                         "1" = "Extension to painful stimuli",
                         "2" = "Abnormal flexion to painful stimuli",
                         "3" = "Flexion/Withdrawal to painful stimuli",
                         "4" = "Localizes to painful stimuli",
                         "5" = "Obeys commands",
                         "-77" = "Seen but not answered"
                         )
    )

covidcns_dat_id <- covidcns_dat_id %>% 
  mutate(across(gcs_outpatient.verbal_numeric,
                ~case_when(
                  . == 1 ~ 0,
                  . == 2 ~ 1,
                  . == 3 ~ 2,
                  . == 4 ~ 3,
                  . == 5 ~ 4,
                  TRUE ~ .)))

covidcns_dat_id <- covidcns_dat_id %>%
    mutate(gcs_outpatient.verbal =
           recode_factor(gcs_outpatient.verbal_numeric,
                         "0" = "Makes no sounds",
                         "1" = "Makes sounds",
                         "2" = "Words",
                         "3" = "Confused, disoriented",
                         "4" = "Oriented, converses normally",
                         "-77" = "Seen but not answered"
                         )
    )
```

Re-check variable coding
```{r recheck variable coding}
covidcns_dat_id %>%
  select(all_of(starts_with("gcs_outpatient"))) %>%
  tbl_summary(missing_text = "Missing")
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
covidcns_dat_id <- covidcns_dat_id %>%
  mutate(across(ends_with("numeric"),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)))
```


# Save cleaned data

Check colnames before exporting final dataset
```{r check colnames}
colnames(covidcns_dat_id)
```

# COVID-CNS
```{r Write cleaned GLAD variables to a .rds file}
covidcns_dat_id %>% 
  filter(sample == "COVID-CNS") %>%  # select only GLAD participants
  saveRDS(
    file = paste0(filepath_data_raw, "/data/latest_freeze/core_neuro/gcs_outpatient_covid_cns_clean.rds")
    )
```

