---
title: "COVIDCNS Insert Title Here"
author: "Insert Your Full Name Here"
date: "DD/MM/YYYY"
output: html_document
---


All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except:
Study name (COVIDCNS) all caps
Capitalised first word
Chunk names MUST be unique
Points requiring user input are enclosed thus <>

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the recode_check function - used to check for implausible values when recoding
Add the imp_clean function - used to check variables for implausible values
Add the cont_clean function - used to check continuous variables for implausible values
```{r Read in functions}
source(file = "scripts/functions/add_numeric_1.R")
source(file = "scripts/functions/remove_duplicates.R")
source(file = "scripts/functions/sumscores.R")
source(file = "scripts/functions/package_check.R")
source(file = "scripts/functions/recode_check.R")
source(file = "scripts/functions/cont_clean.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("sjlabelled",
              "Amelia",
              "gtsummary",
              "tidyverse")
package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Source filepath to ilovecovidcns OneDrive}
source(file = "scripts/credentials/paths.R")
```

# Read in the data: <Full Name of Questionnaire/Demographic>

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the Teams Data Issues Tracker

- For variable names, use ONLY 'questionnaire.variable_name' syntax
- For dataset, only use snake_case naming
- When using pipe operator '%>%', each function should begin on a new line
- Do not add empty lines at the beginning or end of a chunk
- Use only tidyverse functions wherever possible

COVIDCNS data
```{r COVIDCNS load data}
covidcns_dat <- read_rds(
  file = paste0(ilovecovidcns, "</data_raw/latest_freeze/location/questionnaire_covid_cns.rds>")
  )
  
# Check variable names in dataframe
covidcns_dat %>%
  colnames()

# Inspect dimensions of dataframe 
covidcns_dat %>%
  dim()

# Count NAs in ID column
sum(is.na(covidcns_dat$externalDataReference))

# Count duplicates in ID column
sum(table(covidcns_dat$externalDataReference)-1)

# Report duplicates in ID column
table(covidcns_dat$externalDataReference)[table(covidcns_dat$externalDataReference)>1]
```

Create new df with renamed and de-duplicated/NA-removed ID column
```{r COVIDCNS select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  dplyr::rename(
    "ID" = "externalDataReference"
  )

# Inspect colnames
covidcns_dat_id %>%
  colnames()
```

Look at number of people excluded
The number of people to be excluded should be negative
```{r COVIDCNS number excluded}
# Inspect dimensions of new data set
covidcns_dat_id %>%
  dim()

# Inspect number of rows dropped
covidcns_excluded <- dim(covidcns_dat_id)[1] - dim(covidcns_dat)[1]
covidcns_excluded
```

Check missingness by missmap
```{r COVIDCNS missmap}
covidcns_dat_id %>% 
  missmap()
```

Create dat as copy of covidcns_dat_id for brevity
This step gives you a 'reset' point: if your variable recoding screws up, re-run this chunk to give you a fresh 'dat' dataframe
```{r Create dat}
dat <- covidcns_dat_id 
```

Extract and save labels
```{r Extract save labels}
# Save variable labels
question_labels <- sjlabelled::get_label(dat)

# Save value labels
answer_labels <- sjlabelled::get_labels(dat, values = "as.name")

# Change -77 to -777 in value labels names
chng <- rapply(sapply(answer_labels, names), function(x) ifelse(x==-77,-777,x), how = "replace")

# Add multiple lines here as necessary to change other nonanswer values in labels
#chng <- rapply(chng, function(x) ifelse(x==-88,-888,x), how = "replace")

# Substitute new value labels into answer_labels
for (i in 5:length(chng)){
  names(answer_labels[[i]]) <- chng[[i]]
}
```

Create list of all labels and attributes
This chunk supersedes all categorical/numeric cleaning
It gives you an output of c(the question label, all value-label pairs)
for each variable
Check for errors in the output of this chunk, including:
- Label spelling errors (for questions and answers)
- Incorrect values
- Mismatches between labels and values
- Scale errors
- Variable naming issues from the data extraction
- Any other issues you can see
All issues/changes need to be logged as a to-do on Teams
At this point, you also need to pick out any continuous, date or text variables 
to be cleaned in the later chunks
```{r List labels attrs}
lablst <- sapply(dat, function(x) c(attr(x, "label"), attr(x, "labels")))
lablst
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(where(is.numeric),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)
                )
         )

# Re-add labels after mutate
dat <- sjlabelled::set_label(dat, question_labels)
dat <- sjlabelled::set_labels(dat, labels = answer_labels)
```


# Rectifying Incorrect Variable Naming

View <incorrect variable>
<Note problem here and report on Teams>
```{r View <incorrect variable>}
str(dat$<incorrect variable>)
```

Rename <incorrect variable> using dplyr rename
```{r Rename <incorrect variable>}
dat <- dat %>%
  rename("<correct variable name>" = "<incorrect variable name>")
```

Reset <correct variable> variable label
```{r Reset <correct variable> label}
dat$<correct variable> <- set_label(dat$<correct variable>, c("<correct variable>" = "<existing label>"))
```

Check <correct variable> naming
```{r Recheck <correct variable> naming}
str(dat$<correct variable>)
```


# Rectifying Incorrect Variable Labelling

Check <incorrect variable> labels
<Note problem here and report on Teams>
```{r Check <incorrect variable> labelling}
str(dat$<incorrect variable>)
```

Rename value labels of <incorrect variable>
```{r Rename <incorrect variable> value labels}
# Named vector of correct labels
new_levels_vec <- c("<correct label>" = <value>, "<correct label>" = <value>)

# Assign new labels
dat$<incorrect variable> <- set_labels(dat$<incorrect variable>, labels = new_levels_vec)

# Remove labels vector
rm(new_levels_vec)
```

Recheck <incorrect variable> labelling
```{r Recheck <incorrect variable> labelling}
str(dat$<incorrect variable>)
```


# Recoding Incorrect Variables

View <incorrect variable>
<Note problem here and report on Teams>
```{r View <incorrect variable> values and labels}
attr(dat$<incorrect variable>, "labels")
```

Recode incorrect variable
Can be removed after data recoded in qualtrics and after data export
If variables are found to be incorrect:
Report the error in the issue log spreadsheet
Recode the variable yourself using `case_when` as below
Continue cleaning your script with the recoded variable until fixed from source
DO NOT run this chunk multiple times: it will mess up the variable coding, requiring you to run the script again from the beginning
```{r Recode <incorrect variable>}
dat <- dat %>% 
  mutate(across(<incorrect variable>,
                ~case_when(
                  . == <incorrect value> ~ <correct value>,
                  TRUE ~ .)))
```

Rename value labels of <incorrect variable>
```{r Relabel <incorrect variable>}
# Named vector of correct labels
new_levels_vec <- c("<correct label>" = <value>, "<correct label>" = <value>)

# Assign new labels
dat$<incorrect variable> <- set_labels(dat$<incorrect variable>, labels = new_levels_vec)

# Remove labels vector
rm(new_levels_vec)
```

Recheck variable coding
```{r Recheck <incorrect variable> values and labels}
attr(dat$<incorrect variable>, "labels")
```


# Cleaning Continuous Variables

Create vector of continuous variables
(I suggest adding variable names sorted by type e.g. all ages then all years
etc. to make your life easier when creating limits_mat)
```{r Create cont vars vector}
variables_cont <- c(
  "<questionnaire.variable_name>"
)

# Check length of vector (must match dim(limits_mat)[1])
length(variables_cont)
```

Inspect continuous variables
Use the question labels to ascertain context at this point and check for obvious outliers
The percentiles can be modified to exclude nonanswer values as appropriate to your data
```{r Initial inspect cont vars}
dat %>%
  select(all_of(variables_cont)) %>%
  tbl_summary(
    missing_text = "Missing",
    statistic = list(all_continuous() ~ "{median} ({p0}, {p5}, {p95}, {p100})"))
```

Check for text in continuous variables
This chunk outputs only the columns and rows that contain text
```{r Cont vars check text}
# Function to check for any text or spaces
check_for_string <- function(x){
  sum(str_detect(x, "[a-zA-Z\\s]+"), na.rm = TRUE) > 0}

dat %>%
  # select all continuous
  select(all_of(variables_cont)) %>%
  # select only vars containing text
  select(where(check_for_string)) %>%
  # filter only rows containing text
  filter(
    if_any(where(check_for_string),
           ~str_detect(., "[a-zA-Z\\s]+")
           )
    )
```

Manually clean continuous variables if necessary
IF the text data contains useful info that can be converted to numeric, clean manually
REMOVE THIS CHUNK IF NOT NECESSARY
```{r Cont vars manual clean}
dat <- dat %>%
  mutate(across(<questionnaire.variable_name>,
                ~case_when(str_detect(<questionnaire.variable_name>, "<pattern>") ~ "<1>",
                           TRUE ~ .)
                )
         )
```

Remove text from numeric variables automatically
ONLY use this chunk if there is no information to be gained from the text
```{r Cont vars remove text}
dat <- dat %>%
  mutate(across(all_of(variables_cont),
                ~str_remove(., "[a-zA-Z\\s]+")
                )
         )
```

Remove empty variables from variables_cont
These all contain only NAs and serve only to interfere with processing
```{r Cont vars remove empty}
rem_vars <- dat %>%
  select(all_of(variables_cont)) %>%
  select(where(~all(is.na(.))
               )
         ) %>%
  colnames()

variables_cont <- variables_cont[!variables_cont %in% rem_vars]
length(variables_cont)
```

Mutate variables to numeric after cleaning out text
This step is necessary to check for non-integer values
If you have correctly cleaned them above, this chunk should not have any failures to parse
```{r Cont vars to numeric}
dat <- dat %>%
  mutate(across(all_of(variables_cont),
                ~as.numeric(.)
                )
         )
```

Transform nonanswer values to 3 digit
```{r Cont vars nonanswer}
dat <- dat %>%
  mutate(across(where(is.numeric),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)
                )
         )

# Re-add labels after mutate
dat <- sjlabelled::set_label(dat, question_labels)
dat <- sjlabelled::set_labels(dat, labels = answer_labels)
```

Create matrix of limits for continuous variables
Matrix is series of vectors (lower, upper)
Define limits for variable and list reasoning below
Variable name: <add name>
- Lower: <add limit> <add justification>
- Upper: <add limit> <add justification>

Variable name: <add name>
- Lower: <add limit> <add justification>
- Upper: <add limit> <add justification>
```{r Create matrix limits}
# Create a vector of limits for each type of variable using rep
limits_1 <- rep(c(<lower>, <upper>), <number of vars>) 
limits_2 <- rep(c(<lower>, <upper>), <number of vars>) # make sure the number of variables add up!!
# add more as necessary

# Combine the vectors together
limits_vec <- c(limits_1,
                limits_2
                # more as necessary
                )

# Create matrix
limits_mat <- matrix(limits_vec, # take values from your vector of limits
                     nrow = 2, # upper and lower bound
                     ncol = length(variables_cont) # number of variables total
                     )

# Matrices are filled by columns, not rows, so must transpose
limits_mat <- t(limits_mat)

# Check dimensions
dim(limits_mat)
```

Set row and col names of limits_mat
This allows your to easily refer back to limits_mat for a summary
```{r Set lim_mat names}
rownames(limits_mat) <- variables_cont
colnames(limits_mat) <- c("Lower", "Upper")
```

Use cont_clean to check if any implausible values and provide replacement vectors
Cont_clean will not proceed if variables are not numeric type, clean manually above if necessary
This chunk reports any variables that contain implausible values
```{r Cont_clean cont vars}
# Execute cleaning function
cont_list <- cont_clean(
  variables = variables_cont,
  limits_mat = limits_mat,
  dat = dat
)

# Create empty list of variable names to check
imp_checklist <- c()

# Loop through function output
for (i in 1:length(variables_cont)){
  
  # Report only variables containing implausibles
  if(cont_list[[variables_cont[i]]]$Count > 0){
    
    # Add variable name to imp_checklist
    imp_checklist <- append(x = imp_checklist, variables_cont[i])
    
    # Report readout of implausible values
    print(paste0("Implausibles in ", variables_cont[i], ": ", cont_list[[variables_cont[i]]]$Count))
  }
}
```

Check unique values in variables containing implausible values
The sort() function allows you to see them more clearly

Check for any systematic errors at this stage
e.g. For 'age', participants may have entered a calendar year (e.g. 2001), instead of an age (e.g. 45)
It may be possible to gain data from errors like this, so DO NOT MUTATE TO IMPLAUSIBLE WITHOUT GOOD REASON
If you are unsure, RAISE IN THURSDAY DATA CLEANING MEETING
(You could import participant birth year and subtract to find age)
```{r Cont vars implausible unique}
dat %>%
  select(all_of(imp_checklist)) %>%
  sapply(., function(x) sort(unique(x)))
```

Mutate variables with implausible values removed
Repeat the mutate statements for as many variables as necessary
```{r Mutate cont vars}
dat <- dat %>%
  mutate(
    <questionnaire.variable_name> = cont_list$<questionnaire.variable_name>$Replacement
  )

dat <- dat %>%
  mutate(
    <questionnaire.variable_name> = cont_list$<questionnaire.variable_name>$Replacement
  )

# Re-add labels after mutate
dat <- sjlabelled::set_label(dat, question_labels)
dat <- sjlabelled::set_labels(dat, labels = answer_labels)
```

Re-inspect variables after cleaning
```{r Cont vars inspect after cleaning}
dat %>%
  select(all_of(variables_cont)) %>%
  tbl_summary(
    missing_text = "Missing",
    statistic = list(all_continuous() ~ "{median} ({p0}, {p5}, {p95}, {p100})")
  )
```


# Cleaning Textual Variables

Create vector of text variables
```{r Vector text vars}
variables_text <- c(
  "<questionnaire.variable_name>"
)
```

View text variables
```{r Check text vars}
dat %>%
  select(all_of(variables_text)) %>%
  tbl_summary(missing_text = "Missing")
```

Recode <text variable>
Repeat these chunks as necessary
```{r Recode <text variable>}
dat <- dat %>% 
  mutate(across(<questionnaire.variable_name>,
                ~case_when(
                  str_detect(<questionnaire.variable_name>, "<misspelling>")  ~ "<Correct Spelling>",
                  str_detect(<questionnaire.variable_name>, "<misspelling>")  ~ "<Correct Spelling>",
                  TRUE ~ .)))
```

Re-check <text variable>
Repeat these chunks as necessary
```{r Recheck coding <text variable>}
dat %>%
  select(<questionnaire.variable_name>) %>%
  tbl_summary(missing_text = "Missing")
```

Re-check all text variables
```{r Recheck text vars coding final}
dat %>%
  select(all_of(variables_text)) %>%
  tbl_summary(missing_text = "Missing")
```


# Cleaning Dates

Create vector of date variables
```{r Vector date vars}
variables_date <- c(
  "<questionnaire.variable_name>"
)
```

Check for text in date variables
This chunk outputs only the columns and rows that contain text
```{r Date vars check text}
# Function to check for any text or spaces
check_for_string <- function(x){
  sum(str_detect(x, "[a-zA-Z\\s]+"), na.rm = TRUE) > 0}

dat %>%
  # select all continuous
  select(all_of(variables_date)) %>%
  # select only vars containing text
  select(where(check_for_string)) %>%
  # filter only rows containing text
  filter(
    if_any(where(check_for_string),
           ~str_detect(., "[a-zA-Z\\s]+")
           )
    )
```

Manually clean date variables if necessary
IF the text data contains useful info that can be converted to date, clean manually
REMOVE THIS CHUNK IF NOT NECESSARY
```{r Date vars manual clean}
dat <- dat %>%
  mutate(across(<questionnaire.variable_name>,
                ~case_when(str_detect(<questionnaire.variable_name>, "<pattern>") ~ "<dd/mm/yyyy>",
                           TRUE ~ .)
                )
         )
```

Remove text from numeric variables automatically
ONLY use this chunk if there is no further information to be gained from the text by manual cleaning
```{r Date vars remove text}
dat <- dat %>%
  mutate(across(all_of(variables_date),
                ~str_remove(., "[a-zA-Z\\s]+")
                )
         )
```

Replace -77 values with NA: POSIX will reject -77 as a value when converting
```{r Date vars recode -77 to NA}
dat <- dat %>% 
  mutate(across(all_of(variables_date),
                ~na_if(., "-77")
                )
         )
```

Parse dates using lubridate
If you have worked correctly above, there should be no failures to parse
```{r Parse date vars}
dat <- dat %>% 
  mutate(across(all_of(variables_date),
                ~lubridate::parse_date_time(x = .,
                                            orders = c("d m y", "d/m/y", "d.m.y"),
                                            tz = "Europe/London")
                )
         )
```

Recheck date variables
```{r Recheck parsed date vars}
dat %>%
  select(all_of(variables_date)) %>%
  tbl_summary(missing_text = "Missing")
```

Define limits for variable and list reasoning below
Variable name:
- Upper: 
- Lower: 
```{r Date vars define limits}
upper_limit <- as.POSIXct("yyyy-mm-dd")
lower_limit <- as.POSIXct("yyyy-mm-dd")
```

Recode variable outliers to NA
```{r Date vars recode outliers to NA}
dat <- dat %>%
    mutate(across(all_of(variables_date),
                  ~ifelse(. > upper_limit | # bigger than the upper limit
                          . < lower_limit, # smaller than the lower limit
                          yes = NA_real_,
                          no = .)
                  )
           ) %>%
  mutate(across(all_of(variables_date),
                ~as.POSIXct(.,
                            origin = lubridate::origin)
                )
         )
```

Re-check dates
```{r Recheck cleaned date vars}
dat %>%
  select(all_of(variables_date)) %>%
  tbl_summary(missing_text = "Missing")
```


# Produce sumscores

Reference the scoring guidance that you have used for your questionnaire here "link"

If changing na_limit, CHECK your guidance, na_limit > 0 will replace NAs with 0, ensure that this is correct for your scoring guidance before proceeding

Create vector of item coding
The coding_keys vector must contain 1s for all variables to be added and -1 for all variables to be subtracted.
Putting 0 in the vector will omit the variable at that position.
length(coding_keys) MUST be the same as the number of variables to be summed

sum_vars vector should contain ONLY and ALL variable names needed for scoring, do not add "ID" or "sample" etc.

If using reverse keying:
MAKE SURE that Reverse = TRUE is included as an argument, reverse keying will not work without this
reverse_vars should contain all variable names to be reverse keyed
If running multiple sumscores requiring reverse keying, a single reverse_vars vector containing all of the variable names to be reverse keyed is sufficient: `%in%` will pick the relevant variables for each sumscore

The warnings "Scores vector contains missing values." and "Input contains non-answer values. These will be converted to NA_real_ for this calculation." are normal. They are there to inform you that some sumscores have not been calculated due to non-answer values (e.g. -777) being present. Any other errors or warnings need to be investigated.

Create required variables for sumscore arguments
```{r Sumscores inputs}
keys <- c(
  # should be a vector of 1s, 0s or -1s
  )
sum_vars <- c(
  "<questionnaire.variable_name>"
  # all variable names to add
  )
```

Generate sumscores from questionnaire data and use mutate onto dat as new column
sumscores assumes that all items in the questionnaire have the SAME minimum and maximum scores for ALL items, ensure that this is correct before proceeding

When adding the column name for your sumscore use "questionnaire.score_name"

Sumscores will produce a list of 2 elements, the first is "scores", the second is "na.count"

Generate sumscores
```{r Generate sumscores}
sum_out <- sumscores(input = dat,
                     sum_vars = sum_vars,
                     coding_keys = keys,
                     na_allowed = 0,
                     min_item = ,
                     max_item = ,
                     min_score = ,
                     max_score = 
                     )
```

Add sumscores as new column
```{r Add sumscores}
dat <- dat %>% 
  mutate(questionnaire.sum_score = sum_out$scores)
```


# Create phenotypes
Add explanation of phenotype here:

Create <phenotype variable>
```{r Create <phen var>}
dat <- dat %>%
  mutate(
    <questionnaire.phenotype> =
      case_when(
        <questionnaire.sum_score> >= <threshold> ~ 1,
        <questionnaire.sum_score> < <threshold> ~ 0
      )
  )
dat %>%
  select(<questionnaire.phenotype>) %>%
  tbl_summary()
```

Label <phenotype variable>
```{r Label <phen var>}
# Set question label
dat$<questionnaire.phenotype> <- sjlabelled::set_label(dat$<questionnaire.phenotype>, "<Phenotype Question>")

# Create vector of answer labels
<phen_var>_labels <- c("<No Phenotype>" = 0, "<Phenotype>" = 1)

# Set answer labels
dat$<questionnaire.phenotype> <- sjlabelled::set_labels(dat$<questionnaire.phenotype>,
                                                        labels = <phen_var>_labels)

# Remove vector of answer labels
rm(<phen_var>_labels)

# View variable to check
sjlabelled::as_label(dat) %>%
  select(<questionnaire.phenotype>) %>%
  tbl_summary(missing_text = "Missing")
```


# Add Numeric Variables

Specify columns to be excluded from add_numeric function
Continuous variables should be excluded, as they are already numeric
Text variables also need to be excluded
```{r Specify excluded columns}
exclude_cols_numeric <- c(
  # columns as required
  )
```

Add numeric columns
```{r Add numeric}
dat <- dat %>% 
  add_numeric_1(exclude = exclude_cols_numeric)

# Inspect colnames
dat %>%
  colnames()
```


# Save cleaned data

# COVIDCNS
```{r Write cleaned COVIDCNS variables to a .rds file}
dat %>%
  saveRDS(
    file = paste0(ilovecovidcns, "</data/latest_freeze/location/questionnaire_covidcns_clean.rds>")
    )
```