---
title: "COVIDCNS NCRF3 Diagnosis Cleaning Script"
author: "Zain Ahmad"
date: "14/06/2022"
output: html_document
---


All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except capitalised first word
Chunk names MUST be unique
Points requiring user input are enclosed thus <>

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_labelled_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the recode_check function - used to check for implausible values when recoding
Add the imp_clean function - used to check variables for implausible values
Add the cont_clean function - used to check continuous variables for implausible values
```{r Read in functions}
source(file = "scripts/functions/add_labelled_numeric.R")
source(file = "scripts/functions/remove_duplicates.R")
source(file = "scripts/functions/sumscores.R")
source(file = "scripts/functions/package_check.R")
source(file = "scripts/functions/recode_check.R")
source(file = "scripts/functions/cont_clean.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("sjlabelled",
              "Amelia",
              "gtsummary",
              "tidyverse")

package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Source filepath to ilovecovidcns OneDrive}
source(file = "scripts/credentials/paths.R")
```

# Read in the data: COVIDCNS Neuro Case Report Form Module 3 Diagnosis

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the Teams Data Issues Tracker

- For variable names, use ONLY 'questionnaire.variable_name' syntax
- When using pipe operator '%>%', each function should begin on a new line for clarity
- Do not add empty lines at the beginning or end of a chunk to keep the markdown as short as possible
- Use only tidyverse functions wherever possible, they run faster than base R

COVIDCNS data
```{r COVIDCNS load data}
covidcns_dat <- read_rds(
  file = paste0(ilovecovidcns, "/data_raw/latest_freeze/neuro_case_report/ncrf3_diag_covid_cns.rds")
  )
  
# Check variable names in dataframe
covidcns_dat %>%
  colnames()

# Inspect dimensions of dataframe 
covidcns_dat %>%
  dim()

# Report counts of duplicates in ID column
covidcns_dat %>%
  select(externalDataReference) %>%
  filter(duplicated(.)) %>%
  count(., externalDataReference)

# Report number of IDs to be dropped
covidcns_excluded <- covidcns_dat %>%
  select(externalDataReference) %>%
  filter(duplicated(.)) %>%
  count(., externalDataReference) %>%
  select("Dropped IDs" = "n") %>%
  colSums() + 1

covidcns_excluded
```

Create new df with renamed and de-duplicated/NA-removed ID column
```{r COVIDCNS select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  dplyr::rename(
    "ID" = "externalDataReference"
  )

# Inspect colnames
covidcns_dat_id %>%
  colnames()

# Inspect dimensions of new data set
covidcns_dat_id %>%
  dim()
```

Check missingness by missmap
```{r COVIDCNS missmap}
covidcns_dat_id %>% 
  missmap()
```

Create dat as copy of covidcns_dat_id for brevity
This step gives you a 'reset' point: if your variable recoding screws up, re-run this chunk to give you a fresh 'dat' dataframe
```{r Create dat}
dat <- covidcns_dat_id 
```

Extract and save labels
```{r Extract save labels}
# Save variable labels
question_labels <- sjlabelled::get_label(dat)

# Save value labels
answer_labels <- sjlabelled::get_labels(dat, values = "as.name")

# Change -77 to -777 in value labels names
chng <- rapply(sapply(answer_labels, names),
               function(x) ifelse(x==-77, -777, x),
               how = "replace")

# Add multiple lines here as necessary to change other nonanswer values in labels
chng <- rapply(chng,
               function(x) ifelse(x==-88, -888, x),
               how = "replace")

# Substitute new value labels into answer_labels
for (i in 1:length(chng)){
  if(!is.null(answer_labels[[i]])){
  names(answer_labels[[i]]) <- chng[[i]]
  }
}
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(where(is.numeric),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)
                )
         )

# Re-add labels after mutate
dat <- sjlabelled::set_label(dat, question_labels)
dat <- sjlabelled::set_labels(dat, labels = answer_labels)
```

Create list of all labels and attributes
This chunk supersedes all categorical/numeric cleaning
It gives you an output of c(the question label, all value-label pairs)
for each variable
Check for errors in the output of this chunk, including:
- Label spelling errors (for questions and answers)
- Incorrect values
- Mismatches between labels and values
- Scale errors
- Variable naming issues from the data extraction
- Any other issues you can see
All issues/changes need to be logged as a to-do on Teams
At this point, you also need to pick out any continuous, date or text variables 
to be cleaned in the later chunks
```{r List labels attrs}
label_list <- sapply(dat, function(x) c(attr(x, "label"), attr(x, "labels")))
label_list
```


# Cleaning Continuous Variables

Create vector of continuous variables
(I suggest adding variable names sorted by type e.g. all ages then all years
etc. to make your life easier when creating limits_mat)
```{r Create cont vars vector}
variables_cont <- c(
  "ncrf3_diag.number_of_days_in_itu.txt",
  "ncrf3_diag.number_of_days_on_ventilator.txt",
  "ncrf3_diag.continuous_number_of_days_in_any_hospital.txt",
  "ncrf3_diag.numbers_of_days_in_rehabilitation.txt",
  "ncrf3_diag.modified_rankin_score.txt"
)

# Check length of vector (must match dim(limits_mat)[1])
length(variables_cont)
```

Inspect continuous variables
Use the question labels to ascertain context at this point and check for obvious outliers
The percentiles can be modified to exclude nonanswer values as appropriate to your data
```{r Initial inspect cont vars}
dat %>%
  select(all_of(variables_cont)) %>%
  tbl_summary(
    missing_text = "Missing",
    statistic = list(all_continuous() ~ "{median} ({p0}, {p5}, {p95}, {p100})"))
```

Check for text in continuous variables
This chunk outputs only the columns and rows that contain text
```{r Cont vars check text}
# Function to check for any text or spaces
check_for_string <- function(x){
  sum(str_detect(x, "[a-zA-Z\\s\\(\\)\\/\\']+"), na.rm = TRUE) > 0}

dat %>%
  # select all continuous
  select(all_of(variables_cont)) %>%
  # select only vars containing text
  select(where(check_for_string)) %>%
  # filter only rows containing text
  filter(
    if_any(where(check_for_string),
           ~str_detect(., "[a-zA-Z\\s\\(\\)\\/\\']+")
           )
    )
```

Manually clean continuous variables if necessary
IF the text data contains useful info that can be converted to numeric, clean manually
REMOVE THIS CHUNK IF NOT NECESSARY
```{r Cont vars manual clean}
dat <- dat %>%
  mutate(across(ncrf3_diag.number_of_days_in_itu.txt,
                ~case_when(str_detect(ncrf3_diag.number_of_days_in_itu.txt, "13 days \\(11\\/08\\/21 - 23\\/08\\/21\\)") ~ "13",
                           str_detect(ncrf3_diag.number_of_days_in_itu.txt, "3 weeks") ~ "3",
                           TRUE ~ .)
                )
         )

dat <- dat %>%
  mutate(across(ncrf3_diag.number_of_days_on_ventilator.txt,
                ~case_when(str_detect(ncrf3_diag.number_of_days_on_ventilator.txt, "~ 25-30 days") ~ "28",
                           str_detect(ncrf3_diag.number_of_days_on_ventilator.txt, "1 month") ~ "30",
                           str_detect(ncrf3_diag.number_of_days_on_ventilator.txt, "11 days \\(13\\/8\\/21 - 23\\/8\\/21\\)") ~ "11",
                           str_detect(ncrf3_diag.number_of_days_on_ventilator.txt, "2 weeks") ~ "14",
                           str_detect(ncrf3_diag.number_of_days_on_ventilator.txt, "1-2") ~ "2",
                           TRUE ~ .)
                )
         )

dat <- dat %>%
  mutate(across(ncrf3_diag.continuous_number_of_days_in_any_hospital.txt,
                ~case_when(str_detect(ncrf3_diag.continuous_number_of_days_in_any_hospital.txt, "Admission 2 - 23/03/2020 > 29/05/2020") ~ "54",
                           str_detect(ncrf3_diag.continuous_number_of_days_in_any_hospital.txt, "8 days 13\\/08\\/2021-20\\/08\\/2021") ~ "8",
                           str_detect(ncrf3_diag.continuous_number_of_days_in_any_hospital.txt, "11 \\(16\\/08\\/21 - 26\\/08\\/21\\)") ~ "11",
                           str_detect(ncrf3_diag.continuous_number_of_days_in_any_hospital.txt, "38 \\(not including time in rehab unit\\)") ~ "38",
                           str_detect(ncrf3_diag.continuous_number_of_days_in_any_hospital.txt, ">126") ~ "126",
                           TRUE ~ .)
                )
         )

dat <- dat %>%
  mutate(across(ncrf3_diag.numbers_of_days_in_rehabilitation.txt,
                ~case_when(str_detect(ncrf3_diag.numbers_of_days_in_rehabilitation.txt, "8 days in Addenbrooke\\'s \\- patient repatriated to DGH for ongoing rehabilitation") ~ "54",
                           TRUE ~ .)
                )
         )
```




Remove text from numeric variables automatically
ONLY use this chunk if there is no information to be gained from the text
```{r Cont vars remove text}
dat <- dat %>%
  mutate(across(all_of(variables_cont),
                ~str_remove(., "[a-zA-Z\\s\\(\\)\\/\\']+")
                )
         )
```

Remove empty variables from variables_cont
These all contain only NAs and serve only to interfere with processing
```{r Cont vars remove empty}
variables_empty <- dat %>%
  select(all_of(variables_cont)) %>%
  select(where(~all(is.na(.))
               )
         ) %>%
  colnames()

variables_cont <- variables_cont[!variables_cont %in% variables_empty]
length(variables_cont)
```

Mutate variables to numeric after cleaning out text
This step is necessary to check for non-integer values
If you have correctly cleaned them above, this chunk should not have any failures to parse
@note - Failures to parse manually checked and cleared
```{r Cont vars to numeric}
dat <- dat %>%
  mutate(across(all_of(variables_cont),
                ~as.numeric(.)
                )
         )
```

Transform nonanswer values to 3 digit
```{r Cont vars nonanswer}
dat <- dat %>%
  mutate(across(where(is.numeric),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)
                )
         )


# Re-add labels after mutate
dat <- sjlabelled::set_label(dat, question_labels)
```

# Cleaning Textual Variables

Create vector of text variables
```{r Vector text vars}
variables_text <- c(
  "ncrf3_diag.othertext.txt",
  "ncrf3_diag.other_pathogen_of_public_interest_detected.txt",
  "ncrf3_diag.box_provide_report_additional.txt",
  "ncrf3_diag.any_other_issue_of_significance_to_note.txt"
)
```

View text variables
```{r Check text vars}
dat %>%
  select(all_of(variables_text)) %>%
  tbl_summary(missing_text = "Missing")
```


# Add Numeric Variables

Specify columns to be excluded from add_numeric function
Continuous variables should be excluded, as they are already numeric
Text variables also need to be excluded
Do not include ID and sample here
```{r Specify excluded columns}
exclude_cols_numeric <- c(
  variables_cont,
  variables_text
  )
```

Add labelled/numeric columns
Modify the leaders argument if necessary
```{r Add columns}
dat <- dat %>% 
  add_labelled_numeric(exclude = exclude_cols_numeric)

# Inspect colnames
dat %>%
  colnames()
```


# Save cleaned data

# COVIDCNS
```{r Write cleaned COVIDCNS variables to a .rds file}
dat %>%
  saveRDS(
    file = paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf3_diag_covidcns_clean.rds")
    )
```