---
title: "COVIDCNS NCRF Admission Vital Cleaning Script"
author: "Zain Ahmad"
date: "19/02/2022"
output: html_document
---


All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except:
Study name (COVIDCNS) all caps
Capitalised first word

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
Add the cont_clean function - used to check continuous variables for implausible values
```{r Read in functions}
source(file = "scripts/functions/add_numeric_1.R")
source(file = "scripts/functions/remove_duplicates.R")
source(file = "scripts/functions/sumscores.R")
source(file = "scripts/functions/package_check.R")
source(file = "scripts/functions/imp_check.R")
source(file = "scripts/functions/imp_check_1.R")
source(file = "scripts/functions/cont_clean.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in file with path to ilovecovidcns channel on teams}
source(file = "scripts/credentials/paths.R")
```

# Read in the data: Neuro Case Report Form Admission Vital
Change this heading to the name of your questionnaire/demographic
Load COVIDCNS data

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the issues spreadsheet "https://docs.google.com/spreadsheets/d/1a2gL8c0eH2pZXNTbnPzkDYQGeeVXbLKU8BUpYM0moe8/edit?usp=sharing"

- For variable names, use ONLY 'questionnaire.variable_name'
- For dataset, only use snake_case naming
- When using pipe operator '%>%', each function should begin on a new line
- Do not add empty lines at the beginning or end of a chunk
- Use only tidyverse functions wherever possible
- When naming chunks, begin with the name of the dataset (COVIDCNS)

## COVIDCNS data
```{r COVIDCNS load data}
covidcns_dat <- read_rds(
  file = paste0(ilovecovidcns, "/data_raw/latest_freeze/neuro_case_report/ncrf1_vital_covid_cns.rds")
  )
  
# Check variable names in dataframe
covidcns_dat %>%
  colnames()

# Inspect dimensions of dataframe 
covidcns_dat %>%
  dim()
```

Specify columns to be excluded from add_numeric function
Continuous variables should be excluded, as they are already numeric
```{r COVIDCNS specify excluded columns}
exclude_cols_numeric <- c(
  "ID",
  "sample",
  "startDate",
  "endDate",
  "ncrf1_vital.respiratory_symptom_onset.txt",
  "ncrf1_vital.fever_symptom_onset.txt",
  "ncrf1_vital.neurological_symptom_onset.txt",
  "ncrf1_vital.date_of_admission_to_this_facility.txt",
  "ncrf1_vital.which_disease.txt",
  "ncrf1_vital.vitals",
  "ncrf1_vital.vitals.1",
  "ncrf1_vital.vitals.2",
  "ncrf1_vital.vitals.3",
  "ncrf1_vital.vitals.4",
  "ncrf1_vital.oxygen_saturation.txt",
  "ncrf1_vital.oxygen_saturation.txt.1",
  "ncrf1_vital.glasgow_coma_score.txt",
  "ncrf1_vital.height.txt",
  "ncrf1_vital.weight.txt",
  "ncrf1_vital.any_other_issue_of_significance_to_note.txt"
  )
```

Select & rename relevant columns
```{r COVIDCNS select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "COVIDCNS",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         sample,
         startDate,
         endDate,
         ncrf1_vital.respiratory_symptom_onset.txt,
         ncrf1_vital.fever_symptom_onset.txt,
         ncrf1_vital.neurological_symptom_onset.txt,
         ncrf1_vital.date_of_admission_to_this_facility.txt,
         ncrf1_vital.admitted_for_covid_,
         ncrf1_vital.admitted_for_a_neurological_complication_,
         ncrf1_vital.admitted_for_another_disease,
         ncrf1_vital.which_disease.txt,
         ncrf1_vital.vitals,
         ncrf1_vital.vitals.1,
         ncrf1_vital.vitals.2,
         ncrf1_vital.vitals.3,
         ncrf1_vital.vitals.4,
         ncrf1_vital.severe_dehydration,
         ncrf1_vital.oxygen_saturation,
         ncrf1_vital.oxygen_saturation.txt,
         ncrf1_vital.oxygen_saturation.txt.1,
         ncrf1_vital.avpu,
         ncrf1_vital.glasgow_coma_score.txt,
         ncrf1_vital.malnutrition,
         ncrf1_vital.height.txt,
         ncrf1_vital.weight.txt,
         ncrf1_vital.admission_hours_severity_covid19,
         ncrf1_vital.any_other_issue_of_significance_to_note.txt,
         ncrf1_vital.admission_severity_worst_covid19,
         ncrf1_vital.time_worst_prior_neurological,
         ncrf1_vital.severity_prior_neurological_onset,
         ncrf1_vital.admitted_for_complication_post_vaccination
         ) %>%
  add_numeric_1(exclude = exclude_cols_numeric)

# Inspect colnames
covidcns_dat_id %>%
  colnames()
```

Look at number of people excluded
The number of people to be excluded should be negative
```{r COVIDCNS number excluded}
# Inspect dimensions of new data set
covidcns_dat_id %>%
  dim()

# Inspect number of rows dropped
covidcns_excluded <- dim(covidcns_dat_id)[1] - dim(covidcns_dat)[1]
covidcns_excluded
```

Check missingness by missmap
```{r COVIDCNS inspect missingness}
covidcns_miss_map <- covidcns_dat_id %>% 
  missmap()

covidcns_miss_map
```

Create dat as copy of covidcns_dat_id for brevity
This step gives you a 'reset' point: if your variable recoding screws up, re-run this chunk to give you a fresh 'dat' dataframe
```{r Create dat}
dat <- covidcns_dat_id 

# Check
dat %>% glimpse()
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(ends_with("numeric"),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)))
```

Create list of all unique values
```{r List unique values}
ulst <- sapply(dat, unique)
llst <- sapply(dat, levels)
```


# Cleaning Categorical Variables

Name your vectors in line with the chunks below
Number the vectors or name them intuitively if you have multiple vectors
Vectors of potential values should only contain possible values (exclude nonanswer values as appropriate)

Create sequential vectors of categorical values for variables
Save vectors to a list
Add variable names as names of list
```{r Vector categorical values}
vals_cat_1 <- c(
  "Yes",
  "No",
  "Seen but not answered",
  NA
)

vals_cat_2 <- c(
  "Yes",
  "No",
  "Seen but not answered",
  "Unknown",
  NA
)

vals_cat_3 <- c(
  "Unknown",
  "Seen but not answered",
  "Room air",
  "Oxygen therapy",
  NA
)

vals_cat_4 <- c(
  "Seen but not answered",
  "Awake",
  "Verbal",
  "Pain",
  "Unresponsive",
  NA
)

vals_cat_5 <- c(
  "Intubation and mechanical ventilation (pO2/FiO2 >= 150 or SpO2/FiO2 >= 200)",
  "Seen but not answered",
  "Hospitalised (Oxygen by mask or nasal prongs)",
  "Symptomatic (Independent)",
  "Symptomatic (Assistance needed)",
  "Hospitalised (No oxygen therapy)",
  "Hospitalised (Oxygen by NIV or high flow)",
  "Uninfected (No viral RNA detected)",
  "Asymptomatic (Viral RNA detected)",
  "Mechanical ventilation (pO2/FiO2 <150 or SpO2/FiO2 <200 or vasopressors)",
  "Mechanical ventilation (pO2/FiO2 <150 and vasopressors, dialysis or ECMO)",
  "Dead",
  NA
)

vals_cat_6 <- c(
  "Yes",
  "No",
  "Seen but not answered",
  "Not Applicable",
  NA
)
```

Create list of numeric values vectors
```{r List categorical values vectors}
values_cat_list <- list(
  vals_cat_1,
  vals_cat_1,
  vals_cat_1,
  vals_cat_2,
  vals_cat_3,
  vals_cat_4,
  vals_cat_2,
  vals_cat_5,
  vals_cat_5,
  vals_cat_6,
  vals_cat_5,
  vals_cat_1
)
```

Remove values vectors from environment
```{r Remove value vectors cat}
rm(
  vals_cat_1,
  vals_cat_2,
  vals_cat_3,
  vals_cat_4,
  vals_cat_5,
  vals_cat_6
)
```

Create vector of categorical domains variables 
```{r Vector categorical variables}
variables_cat <- c(
  "ncrf1_vital.admitted_for_covid_",
  "ncrf1_vital.admitted_for_a_neurological_complication_",
  "ncrf1_vital.admitted_for_another_disease",
  "ncrf1_vital.severe_dehydration",
  "ncrf1_vital.oxygen_saturation",
  "ncrf1_vital.avpu",
  "ncrf1_vital.malnutrition",
  "ncrf1_vital.admission_hours_severity_covid19",
  "ncrf1_vital.admission_severity_worst_covid19",
  "ncrf1_vital.time_worst_prior_neurological",
  "ncrf1_vital.severity_prior_neurological_onset",
  "ncrf1_vital.admitted_for_complication_post_vaccination"
)
```

Set names of list to variable names
```{r Set list names cat}
names(values_cat_list) <- variables_cat
```

Use imp_check iteratively to find if any implausible values
```{r Imp_check categorical variables}
# Create empty list
imp_list_cat <- list()

# Loop over each variable, checking against relevant set of values from list
# Add imp_message to list
for (i in 1:length(variables_cat)) {
  imp_list_cat[i] <- imp_check_1(data = dat,
                                 variables = names(values_cat_list)[i],
                                 values = values_cat_list[[i]]) 

}

# Name list with var names to correspond to imp_messages
names(imp_list_cat) <- variables_cat

# View list of imp_messages with corresponding var names
print(imp_list_cat)
```

Produce summary table of variables
```{r Summary table categorical variables}
dat %>%
  tbl_summary(
    include = all_of(variables_cat),
    missing_text = "Missing")
```


# Cleaning Numeric Variables

Name your vectors in line with the chunks below
Number the vectors or name them intuitively if you have multiple vectors
Vectors of potential values should only contain possible values (exclude nonanswer values as appropriate)

Create sequential vectors of numeric values for variables
Save vectors to a list
Add variable names as names of list
```{r Vector numeric values}
vals_num_1 <- c(
  0,
  1,
  -777,
  NA
)

vals_num_2 <- c(
  0,
  1,
  -777,
  -888,
  NA
)

vals_num_3 <- c(
  1,
  2,
  -777,
  -888,
  NA
)

vals_num_4 <- c(
  1,
  2,
  3,
  4,
  -777,
  NA
)

vals_num_5 <- c(
  0,
  1,
  2,
  3,
  4,
  5,
  6,
  7,
  8,
  9,
  -777,
  NA
)

vals_num_6 <- c(
  0,
  1,
  -555,
  -777,
  NA
)
```

Create list of numeric values vectors
```{r List numeric values vectors}
values_num_list <- list(
  vals_num_1,
  vals_num_1,
  vals_num_1,
  vals_num_2,
  vals_num_3,
  vals_num_4,
  vals_num_2,
  vals_num_5,
  vals_num_5,
  vals_num_6,
  vals_num_5,
  vals_num_1
)
```

Remove values vectors from environment
```{r Remove value vectors}
rm(
  vals_num_1,
  vals_num_2,
  vals_num_3,
  vals_num_4,
  vals_num_5,
  vals_num_6
)
```

Create vector of numeric variables 
```{r Vector numeric variables}
variables_num <- c(
  "ncrf1_vital.admitted_for_covid__numeric",
  "ncrf1_vital.admitted_for_a_neurological_complication__numeric",
  "ncrf1_vital.admitted_for_another_disease_numeric",
  "ncrf1_vital.severe_dehydration_numeric",
  "ncrf1_vital.oxygen_saturation_numeric",
  "ncrf1_vital.avpu_numeric",
  "ncrf1_vital.malnutrition_numeric",
  "ncrf1_vital.admission_hours_severity_covid19_numeric",
  "ncrf1_vital.admission_severity_worst_covid19_numeric",
  "ncrf1_vital.time_worst_prior_neurological_numeric",
  "ncrf1_vital.severity_prior_neurological_onset_numeric",
  "ncrf1_vital.admitted_for_complication_post_vaccination_numeric"
)
```

Set names of list to variable names
```{r Set list names}
names(values_num_list) <- variables_num
```

Use imp_check iteratively
Use imp_check iteratively to find if any implausible values
```{r Imp_check numeric variables}
# Create empty list
imp_list_num <- list()

# Loop over each variable, checking against relevant set of values from list
# Add imp_message to list
for (i in 1:length(variables_num)) {
  imp_list_num[i] <- imp_check_1(data = dat,
                                 variables = names(values_num_list)[i],
                                 values = values_num_list[[i]]) 

}

# Name list with var names to correspond to imp_messages
names(imp_list_num) <- variables_num

# View list of imp_messages with corresponding var names
print(imp_list_num)
```

Produce summary table of variables
```{r Summary table numeric variables}
dat %>%
  tbl_summary(
    include = all_of(variables_num),
    missing_text = "Missing")
```


# Cleaning Dates

Create vector of date variables
```{r Vector date variables}
variables_date <- c(
  "ncrf1_vital.respiratory_symptom_onset.txt",
  "ncrf1_vital.fever_symptom_onset.txt",
  "ncrf1_vital.neurological_symptom_onset.txt",
  "ncrf1_vital.date_of_admission_to_this_facility.txt"
)
```

Inspect date variables
```{r COVIDCNS inspect dates}
dat %>%
  select(all_of(variables_date)) %>%
  glimpse()
```

Replace -77 values with NA as POSIX will reject -77 as a value when converting
```{r COVIDCNS recode -77 to NA}
dat <- dat %>% 
  mutate(across(
    all_of(variables_date),
    ~na_if(., "-777")
                )
         )
```

Parse dates using lubridate
```{r COVIDCNS parse dates}
dat <- dat %>% 
  mutate(across(
    all_of(variables_date),
    ~lubridate::parse_date_time(
    x = .,
    orders = c("d m y", "d/m/y", "d.m.y"),
    tz = "Europe/London"
    )
                )
         )
```

Recheck date variables
```{r COVIDCNS reinspect dates}
dat %>%
  select(all_of(variables_date)) %>%
  tbl_summary(missing_text = "Missing")
```

Define limits for variable and list reasoning below
Variable name:
- Upper: latest data extraction, cannot have test in the future
- Lower: 30/01/2020, first confirmed UK COVID cases 

```{r Define limits}
upper_limit <- as.POSIXct("2022-11-22")
lower_limit <- as.POSIXct("2020-01-30")
```

Recode variable outliers to NA
```{r Recode outliers to NA}
dat <- dat %>%
    mutate(across(
    all_of(variables_date),
    ~ifelse(
      . > upper_limit | # bigger than the upper limit
      . < lower_limit, # smaller than the lower limit
      yes = NA_real_,
      no = .
        )
    )
) %>%
  mutate(across(all_of(variables_date),
                ~as.POSIXct(., origin = lubridate::origin)
                )
         )
```

Re-check dates
```{r COVID CNS recheck dates}
dat %>%
  select(all_of(variables_date)) %>%
  tbl_summary(missing_text = "Missing")
```


# Cleaning Continuous Variables

Create vector of continuous variables
```{r Create cont vars vector}
variables_cont <- c(
  "ncrf1_vital.vitals",
  "ncrf1_vital.vitals.1",
  "ncrf1_vital.vitals.2",
  "ncrf1_vital.vitals.3",
  "ncrf1_vital.vitals.4",
  "ncrf1_vital.oxygen_saturation.txt",
  "ncrf1_vital.oxygen_saturation.txt.1",
  "ncrf1_vital.glasgow_coma_score.txt",
  "ncrf1_vital.height.txt",
  "ncrf1_vital.weight.txt"
)
```

Inspect continuous variables
Use the question labels to ascertain context at this point and check for obvious outliers
The percentiles can be modified to exclude nonanswer values as appropriate to your data
```{r Inspect cont vars}
dat %>%
  select(all_of(variables_cont)) %>%
  tbl_summary(
    missing_text = "Missing",
    statistic = list(all_continuous() ~ "{median} ({p0}, {p5}, {p95}, {p100})"))
```

Check unique values in continuous variables
If the fields contain text at this point, use the chunk below to clean manually
```{r Cont vars unique}
dat %>%
  select(all_of(variables_cont)) %>%
  sapply(., unique)
```

Manually clean continuous variables to ensure parsing as numeric
Use the output from the chunk above and clean the variable manually here until there are no 'rogue' values
Case_when is type-specific so number must be specified as char and the variable mutated to numeric as below
REMOVE THIS CHUNK IF NOT NECESSARY
```{r Temperature manual clean}
dat <- dat %>%
  mutate(across(ncrf1_vital.vitals,
                ~case_when(str_detect(ncrf1_vital.vitals, "36.") ~ "36.0",
                           str_detect(ncrf1_vital.vitals, "36,5") ~ "36.5",
                           str_detect(ncrf1_vital.vitals, "38/8") ~ "38.8",
                           str_detect(ncrf1_vital.vitals, ">38") ~ "38.0",
                           str_detect(ncrf1_vital.vitals, "unknown") ~ "-77",
                           str_detect(ncrf1_vital.vitals, "37.3 - 37.4") ~ "37.4",
                           str_detect(ncrf1_vital.vitals, "not known") ~ "-77",
                           TRUE ~ .)
                )
         )
```

```{r Heart rate manual clean}
dat <- dat %>%
  mutate(across(ncrf1_vital.vitals.1,
                ~case_when(str_detect(ncrf1_vital.vitals.1, "82R") ~ "82",
                           str_detect(ncrf1_vital.vitals.1, "72R") ~ "72",
                           str_detect(ncrf1_vital.vitals.1, "unknown") ~ "-77",
                           str_detect(ncrf1_vital.vitals.1, "60-80") ~ "70",
                           str_detect(ncrf1_vital.vitals.1, "90-92") ~ "91",
                           str_detect(ncrf1_vital.vitals.1, "not known") ~ "-77",
                           str_detect(ncrf1_vital.vitals.1, "within target range") ~ "-77",
                           TRUE ~ .)
                )
         )
```

```{r Resp rate manual clean}
dat <- dat %>%
  mutate(across(ncrf1_vital.vitals.2,
                ~case_when(str_detect(ncrf1_vital.vitals.2, "ventilated") ~ "14",
                           str_detect(ncrf1_vital.vitals.2, ">30") ~ "30",
                           str_detect(ncrf1_vital.vitals.2, "unknown") ~ "-77",
                           str_detect(ncrf1_vital.vitals.2, "28-34") ~ "31",
                           str_detect(ncrf1_vital.vitals.2, "not known") ~ "-77",
                           str_detect(ncrf1_vital.vitals.2, "within target range") ~ "-77",
                           str_detect(ncrf1_vital.vitals.2, "40+") ~ "40",
                           TRUE ~ .)
                )
         )
```

```{r Sys BP manual clean}
dat <- dat %>%
  mutate(across(ncrf1_vital.vitals.3,
                ~case_when(str_detect(ncrf1_vital.vitals.3, "161/") ~ "161",
                           str_detect(ncrf1_vital.vitals.3, "unknown") ~ "-77",
                           str_detect(ncrf1_vital.vitals.3, "stable") ~ "-77",
                           str_detect(ncrf1_vital.vitals.3, "not known") ~ "-77",
                           TRUE ~ .)
                )
         )
```

Check for BP written in one box instead of 2
```{r Check for BP mistake}
dat %>%
  dplyr::select(ncrf1_vital.vitals.3, ncrf1_vital.vitals.4) %>%
  filter(str_detect(ncrf1_vital.vitals.3, "/"))
```

Split out BPs and sub back into df
```{r Correct BP issue}
bp_vec <- unlist(dat %>% dplyr::select(ncrf1_vital.vitals.3) %>% filter(str_detect(ncrf1_vital.vitals.3, "/")))

names(bp_vec) <- c()

bp_split <- strsplit(bp_vec, split = "/")


bp_indices <- which(str_detect(dat$ncrf1_vital.vitals.3, "/"))


for (i in 1:length(bp_split)){
  bp_split[[i]][3] <- bp_indices[i]
}

for(i in 1:length(bp_split)){
  dat[bp_split[[i]][3], "ncrf1_vital.vitals.3"] <- bp_split[[i]][1]
  dat[bp_split[[i]][3], "ncrf1_vital.vitals.4"] <- bp_split[[i]][2]
}

dat %>%
  dplyr::select(ncrf1_vital.vitals.3, ncrf1_vital.vitals.4) %>%
  slice(as.numeric(bp_indices))
```

```{r Dias BP manual clean}
dat <- dat %>%
  mutate(across(ncrf1_vital.vitals.4,
                ~case_when(str_detect(ncrf1_vital.vitals.4, "stable") ~ "-77",
                           str_detect(ncrf1_vital.vitals.4, "unknown") ~ "-77",
                           str_detect(ncrf1_vital.vitals.4, "not known") ~ "-77",
                           str_detect(ncrf1_vital.vitals.4, "7135") ~ "135",
                           TRUE ~ .)
                )
         )
```

```{r Sats Room manual clean}
dat <- dat %>%
  mutate(across(ncrf1_vital.oxygen_saturation.txt,
                ~case_when(str_detect(ncrf1_vital.oxygen_saturation.txt, "94-98") ~ "96",
                           str_detect(ncrf1_vital.oxygen_saturation.txt, "97% 15L O2") ~ "97",
                           str_detect(ncrf1_vital.oxygen_saturation.txt, "Yes") ~ "-77",
                           str_detect(ncrf1_vital.oxygen_saturation.txt, "96%") ~ "96",
                           str_detect(ncrf1_vital.oxygen_saturation.txt, "93-95") ~ "94",
                           str_detect(ncrf1_vital.oxygen_saturation.txt, "97%") ~ "97",
                           str_detect(ncrf1_vital.oxygen_saturation.txt, "90%") ~ "90",
                           str_detect(ncrf1_vital.oxygen_saturation.txt, "88%") ~ "88",
                           str_detect(ncrf1_vital.oxygen_saturation.txt, "95%") ~ "95",
                           str_detect(ncrf1_vital.oxygen_saturation.txt, "21%") ~ "21",
                           TRUE ~ .)
                )
         )
```

```{r Sats O2 manual clean}
dat <- dat %>%
  mutate(across(ncrf1_vital.oxygen_saturation.txt.1,
                ~case_when(str_detect(ncrf1_vital.oxygen_saturation.txt.1, "98% on 60% venturi") ~ "98",
                           str_detect(ncrf1_vital.oxygen_saturation.txt.1, "85-90") ~ "88",
                           str_detect(ncrf1_vital.oxygen_saturation.txt.1, "98% on 2L") ~ "98",
                           str_detect(ncrf1_vital.oxygen_saturation.txt.1, "92 on 4L") ~ "92",
                           str_detect(ncrf1_vital.oxygen_saturation.txt.1, "L") ~ "-77",
                           str_detect(ncrf1_vital.oxygen_saturation.txt.1, "30% FiO2") ~ "-77",
                           str_detect(ncrf1_vital.oxygen_saturation.txt.1, "89-90") ~ "90",
                           str_detect(ncrf1_vital.oxygen_saturation.txt.1, "2 Litres") ~ "-77",
                           str_detect(ncrf1_vital.oxygen_saturation.txt.1, "3L") ~ "-77",
                           str_detect(ncrf1_vital.oxygen_saturation.txt.1, "91%") ~ "91",
                           str_detect(ncrf1_vital.oxygen_saturation.txt.1, "96%") ~ "96",
                           str_detect(ncrf1_vital.oxygen_saturation.txt.1, "94%") ~ "94",
                           str_detect(ncrf1_vital.oxygen_saturation.txt.1, "93%") ~ "93",
                           str_detect(ncrf1_vital.oxygen_saturation.txt.1, "95%") ~ "95",
                           str_detect(ncrf1_vital.oxygen_saturation.txt.1, "60%") ~ "60",
                           str_detect(ncrf1_vital.oxygen_saturation.txt.1, "28%") ~ "28",
                           TRUE ~ .)
                )
         )
```

```{r GCS manual clean}
dat <- dat %>%
  mutate(across(ncrf1_vital.glasgow_coma_score.txt,
                ~case_when(str_detect(ncrf1_vital.glasgow_coma_score.txt, "15/15") ~ "15",
                           str_detect(ncrf1_vital.glasgow_coma_score.txt, "E4VtM6") ~ "15",
                           str_detect(ncrf1_vital.glasgow_coma_score.txt, "sedated and intubated") ~ "3",
                           str_detect(ncrf1_vital.glasgow_coma_score.txt, "11/15") ~ "11",
                           str_detect(ncrf1_vital.glasgow_coma_score.txt, "N/A") ~ "-77",
                           str_detect(ncrf1_vital.glasgow_coma_score.txt, "16") ~ "15",
                           str_detect(ncrf1_vital.glasgow_coma_score.txt, "15139") ~ "-77",
                           str_detect(ncrf1_vital.glasgow_coma_score.txt, "NK") ~ "-77",
                           str_detect(ncrf1_vital.glasgow_coma_score.txt, "Unkown") ~ "-77",
                           str_detect(ncrf1_vital.glasgow_coma_score.txt, "Not recorded") ~ "-77",
                           str_detect(ncrf1_vital.glasgow_coma_score.txt, "N/K") ~ "-77",
                           str_detect(ncrf1_vital.glasgow_coma_score.txt, "14/15") ~ "14",
                           TRUE ~ .)
                )
         )
```

```{r Height manual clean}
dat <- dat %>%
  mutate(across(ncrf1_vital.height.txt,
                ~case_when(str_detect(ncrf1_vital.height.txt, "1.93") ~ "193",
                           str_detect(ncrf1_vital.height.txt, "1.70") ~ "170",
                           str_detect(ncrf1_vital.height.txt, "1.80") ~ "180",
                           str_detect(ncrf1_vital.height.txt, "N/A") ~ "-77",
                           str_detect(ncrf1_vital.height.txt, "1.53") ~ "153",
                           str_detect(ncrf1_vital.height.txt, "17") ~ "-77",
                           str_detect(ncrf1_vital.height.txt, "unknown") ~ "-77",
                           . == "." ~ "-77",
                           str_detect(ncrf1_vital.height.txt, "1.73") ~ "173",
                           str_detect(ncrf1_vital.height.txt, "1.85") ~ "185",
                           str_detect(ncrf1_vital.height.txt, "NK") ~ "-77",
                           str_detect(ncrf1_vital.height.txt, "1.78") ~ "178",
                           str_detect(ncrf1_vital.height.txt, "16") ~ "-77",
                           . ==  "177 (April 2021)" ~ "177",
                           str_detect(ncrf1_vital.height.txt, "1.68") ~ "168",
                           str_detect(ncrf1_vital.height.txt, "Not recorded on PENS") ~ "-77",
                           str_detect(ncrf1_vital.height.txt, "1905") ~ "190.5",
                           str_detect(ncrf1_vital.height.txt, "Not recorded") ~ "-77",
                           str_detect(ncrf1_vital.height.txt, "not available") ~ "-77",
                           str_detect(ncrf1_vital.height.txt, "N/K") ~ "-77",
                           str_detect(ncrf1_vital.height.txt, "not known") ~ "-77",
                           TRUE ~ .)
                )
         )
```

```{r Weight manual clean}
dat <- dat %>%
  mutate(across(ncrf1_vital.weight.txt,
                ~case_when(. == "78.2 on Epic, 65 Estimated by dietician" ~ "78.2",
                           str_detect(ncrf1_vital.weight.txt, "85kg") ~ "85",
                           str_detect(ncrf1_vital.weight.txt, "unknown") ~ "-77",
                           . == "." ~ "-77",
                           str_detect(ncrf1_vital.weight.txt, "N") ~ "-77",
                           . == "morbid obesity mentioned" ~ "-77",
                           . == "120.5 (Estimate )" ~ "120.5",
                           . == "124.3 (April 2021)" ~ "124.3",
                           str_detect(ncrf1_vital.weight.txt, "N/A") ~ "-77",
                           str_detect(ncrf1_vital.weight.txt, "Not recorded") ~ "-77",
                           TRUE ~ .)
                )
         )
```

Mutate variables to numeric after cleaning manually
This step is necessary to check for non-integer values
Modify the all_of statement as required: DO NOT MUTATE TO NUMERIC UNNECESSARILY
REMOVE THIS CHUNK IF NOT NECESSARY
```{r Cont vars to numeric}
dat <- dat %>%
  mutate(across(all_of(variables_cont),
                ~as.numeric(.)
                )
         )
```

Transform nonanswer values to 3 digit
```{r Cont vars nonanswer}
dat <- dat %>%
  mutate(across(
    all_of(variables_cont),
    ~case_when(. == -55 ~ -555,
               . == -77 ~ -777,
               . == -88 ~ -888,
               . == -99 ~ -999,
               TRUE ~ .)
                )
         )
```

Recheck continuous variables
```{r Recheck cont vars}
dat %>%
  select(all_of(variables_cont)) %>%
  dplyr::mutate(across(all_of(variables_cont),
                       ~na_if(., -777)
                       )
                ) %>%
  tbl_summary(
    missing_text = "Missing",
    statistic = list(all_continuous() ~ "{median} ({p0}, {p5}, {p95}, {p100})"))
```


Create matrix of limits for continuous variables
Matrix is series of vectors (lower, upper)
```{r Create matrix limits}
limits_mat <- rbind(
  c(11, 47),
  c(0, 480),
  c(0, 200),
  c(0, 370),
  c(0, 360),
  c(0, 100),
  c(0, 100),
  c(3, 15),
  c(54, 251),
  c(0, 610)
  )
```

Set row and col names of limits_mat
This allows your to easily refer back to limits_mat for a summary
```{r Set lim_mat names}
rownames(limits_mat) <- variables_cont
colnames(limits_mat) <- c("Lower", "Upper")
```

Use cont_clean to check if any implausible values and provide replacement vectors
Cont_clean will not proceed if variables are not numeric type, clean manually above if necessary
```{r Cont_clean cont vars}
cont_list <- cont_clean(
  variables = variables_cont,
  limits_mat = limits_mat,
  dat = dat
)
for (i in 1:length(variables_cont)){
  print(paste0("Implausibles in ", variables_cont[i], ": ", cont_list[[variables_cont[i]]]$Count))
}
```

Recode variables with implausible values removed
```{r Recode cont vars}
dat <- dat %>%
  mutate(
    ncrf1_vital.vitals.1 = cont_list$ncrf1_vital.vitals.1$Replacement
  )

dat <- dat %>%
  mutate(
    ncrf1_vital.height.txt = cont_list$ncrf1_vital.height.txt$Replacement
  )
```

Re-inspect variables after cleaning
```{r Inspect after cleaning}
dat %>%
  select(all_of(variables_cont)) %>%
  dplyr::mutate(across(all_of(variables_cont),
                       ~na_if(., -777),
                       )
                ) %>%
  tbl_summary(
    missing_text = "Missing",
    statistic = list(all_continuous() ~ "{median} ({p0}, {p100})")
  )
```


# Text variables

Inspect text variables
```{r Inspect text vars}
variables_text <- c(
  "ncrf1_vital.which_disease.txt",
  "ncrf1_vital.any_other_issue_of_significance_to_note.txt"
)

dat %>%
  select(all_of(variables_text)) %>%
  tbl_summary(
    missing_text = "Missing"
  )
```


# Save cleaned data

Check colnames before exporting final dataset
```{r Check colnames}
colnames(dat)
```

# COVIDCNS
```{r Write cleaned COVIDCNS variables to a .rds file}
dat %>%
  saveRDS(
    file = paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_vital_covidcns_clean.rds")
    )
```
