---
title: "Neuro Case Report Medication questionnaire"
author: "Johan Zvrskovec"
date: "17/01/2022"
output: html_document
---


All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except:
Study name (e.g. GLAD/EDGI/NBR) all caps
Capitalised first word

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = "../functions/add_numeric.R")
source(file = "../functions/remove_duplicates.R")
source(file = "../functions/sumscores.R")
source(file = "../functions/package_check.R")
source(file = "../functions/imp_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Retrieve recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

Read in file with path to ilovedata channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in file with path to ilovedata channel on teams}
source(file = "../credentials/paths.R")
```

# Read in the data: Full Name of Questionnaire/Demographic
Change this heading to the name of your questionnaire/demographic
Load GLAD data first, then EDGI, then NBR, then RAMP

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the issues spreadsheet "https://docs.google.com/spreadsheets/d/1a2gL8c0eH2pZXNTbnPzkDYQGeeVXbLKU8BUpYM0moe8/edit?usp=sharing"

- For variable names, use ONLY 'questionnaire.variable_name'
- For dataset, only use snake_case naming
- When using pipe operator '%>%', each function should begin on a new line
- Do not add empty lines at the beginning or end of a chunk
- Use only tidyverse functions wherever possible
- When naming chunks, begin with the name of the dataset (GLAD, EDGI, NBR, RAMP)

## COVIDCNS data
```{r COVIDCNS load data}
covidcns_dat <- read_rds(
  file = paste0(ilovedata, "/data_raw/latest_freeze/covid_cns/neuro_case_report/ncrf_medication_covid_cns.rds")
  )
  
# Check variable names in dataframe
covidcns_dat %>%
  colnames()

# Inspect dimensions of dataframe 
covidcns_dat %>%
  dim()
```

Specify columns to be excluded from add_numeric function
Continuous variables should be excluded, as they are already numeric
NB: If this is data from the COPING survey, add "_cop" to the end of each variable name
```{r GLAD specify excluded columns}
exclude_cols_numeric <- c(
  "ID",
  "sample",
  "startDate",
  "endDate"
  )
```

Select & rename relevant columns
```{r COVIDCNS select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "COVIDCNS",
             .after = "externalDataReference") %>% # Create new sample column
  rename(
         ID = externalDataReference,
         ) %>%
  add_numeric(exclude = exclude_cols_numeric)

# Inspect colnames
covidcns_dat_id %>%
  colnames()
```

Look at number of people excluded
The number of people to be excluded should be negative
```{r COVIDCNS number excluded}
# Inspect dimensions of new data set
covidcns_dat_id %>%
  dim()

# Inspect number of rows dropped
covidcns_excluded <- dim(covidcns_dat_id)[1] - dim(covidcns_dat)[1]
covidcns_excluded
```

Inspect numeric variables
```{r COVIDCNS inspect numeric variables}
covidcns_dat_id %>%
  select(all_of(ends_with("numeric"))) %>%
  tbl_summary(missing_text = "Missing")
```

Check missingness by missmap
```{r GLAD inspect missingness}
covidcns_miss_map <- covidcns_dat_id %>% 
  missmap()

covidcns_miss_map
```
# Set dat
```{r Set dat}

dat <- covidcns_dat_id

```



# Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(ends_with("numeric") & is.numeric,
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)))

dat <- dat %>%
  mutate(across(ends_with("numeric") & is.character,
                ~case_when(
                  . == '-55' ~ '-555',
                  . == '-77' ~ '-777',
                  . == '-88' ~ '-888',
                  . == '-99' ~ '-999',
                  TRUE ~ .)))
```


# Cleaning Categorical variables

Name your vectors in line with the chunks below
Number the vectors or name them intuitively if you have multiple vectors
Vectors of potential values should only contain possible values (exclude nonanswer values as appropriate)

Create vector of categorical values for variables
```{r vector categorical values}
values_categorical <- c(
  "Yes",
  "No",
  "Unknown",
  "Seen but not answered"
  )
values_categorical
```

Create vector of variable names for categorical variables
```{r vector categorical variables}
variables_categorical <-
  c(
    "ncrf_medication.oralorogastrics_fluids",
    "ncrf_medication.antiviral",
    "ncrf_medication.antibiotic",
    "ncrf_medication.antimalarial",
    "ncrf_medication.nsaid",
    "ncrf_medication.angiotensin_receptor_blockers",
    "ncrf_medication.antipsychotic",
    "ncrf_medication.iv_fluids",
    "ncrf_medication.corticosteroid",
    "ncrf_medication.antifungal",
    "ncrf_medication.ace_inhibitor",
    "ncrf_medication.systemic_anticoagulation",
    "ncrf_medication.anxiolytic",
    "ncrf_medication.antidepressant",
    "ncrf_medication.patient_enrolled_clinical_trial",
    "ncrf_medication.immunomodulatory_medication"
    )
variables_categorical
```

Use imp_check function to find if any implausible values and obtain summary table of variables
```{r imp_check categorical variables}
imp_check(data = dat,
          variables = variables_categorical,
          values = values_categorical)

```

# Numeric variables

Name your vectors in line with the chunks below
Number the vectors or name them intuitively if you have multiple vectors
Vectors of potential values should only contain possible values (exclude nonanswer values as appropriate)

Create vector of numeric values 
```{r vector numeric values}
values_numeric <- c(
  # values as appropriate
  NA,
  0,
  1,
  -555,
  -777,
  -888,
  -999
  )
values_numeric
```

Create vector of variable names for numeric variables
```{r vector numeric variables}
variables_numeric <-
  c(
    "ncrf_medication.oralorogastrics_fluids_numeric",
    "ncrf_medication.antiviral_numeric",
    "ncrf_medication.antibiotic_numeric",
    "ncrf_medication.antimalarial_numeric",
    "ncrf_medication.nsaid_numeric",
    "ncrf_medication.angiotensin_receptor_blockers_numeric",
    "ncrf_medication.antipsychotic_numeric",
    "ncrf_medication.iv_fluids_numeric",
    "ncrf_medication.iv_fluids_numeric",
    "ncrf_medication.corticosteroid_numeric",
    "ncrf_medication.antifungal_numeric",
    "ncrf_medication.ace_inhibitor_numeric",
    "ncrf_medication.systemic_anticoagulation_numeric",
    "ncrf_medication.anxiolytic_numeric",
    "ncrf_medication.antidepressant_numeric",
    "ncrf_medication.patient_enrolled_clinical_trial_numeric",
    "ncrf_medication.immunomodulatory_medication_numeric"
    )
variables_numeric
```

Use imp_check function to find if any implausible values and obtain summary table of variables
```{r imp_check numeric variables}
imp_check(data = dat,
          variables = variables_numeric,
          values = values_numeric)

```

# Save cleaned data

Check colnames before exporting final dataset
```{r check colnames}
colnames(dat)
```

# COVIDCNS
```{r Write cleaned COVIDCNS variables to a .rds file}
dat %>% 
  filter(sample == "COVIDCNS") %>%  # select only COVIDCNS participants
  saveRDS(
    file = paste0(ilovedata, "/data/latest_freeze/covidcns/ncrf_medication_covidcns_clean.rds")
    )
```
