---
title: "ncrf3_diag"
author: "Chelsea Mika Malouf"
date: "04/03/2022"
output: html_document
---

# Set up
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

```{r Clear global environment}
remove(list = ls())
```

```{r Read in functions}
source(file = "../functions/add_numeric.R")
source(file = "../functions/remove_duplicates.R")
source(file = "../functions/sumscores.R")
source(file = "../functions/package_check.R")
source(file = "../functions/imp_check_1.R")
```

```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

```{r Read in file with path to ilovecovidcns channel on teams}
source(file = "../credentials/paths.R")
```


# Read in the data: NCRF2 Vital

## COVIDCNS data
```{r COVIDCNS load data}
covidcns_dat <- read_rds(
  file = paste0(ilovecovidcns, "/data_raw/latest_freeze/neuro_case_report/ncrf3_diag_covid_cns.rds")
  )
  
# Check variable names in dataframe
covidcns_dat %>%
  colnames()
# Inspect dimensions of dataframe 
covidcns_dat %>%
  dim()
```

```{r COVIDCNS specify excluded columns}
exclude_cols_numeric <- c(
  "ID",
  "sample",
  "startDate",
  "endDate",
  "ncrf3_diag.number_of_days_in_itu.txt",
  "ncrf3_diag.continuous_number_of_days_in_any_hospital.txt",
  "ncrf3_diag.any_other_issue_of_significance_to_note.txt"
  )
```

```{r COVIDCNS select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "COVIDCNS",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         sample,
         startDate,
         endDate,
         ncrf3_diag.number_of_days_in_itu.txt,
         ncrf3_diag.continuous_number_of_days_in_any_hospital.txt,
         ncrf3_diag.any_other_issue_of_significance_to_note.txt
         ) 
# Inspect colnames
covidcns_dat_id %>%
  colnames()
```

```{r COVIDCNS number excluded}
# Inspect dimensions of new data set
covidcns_dat_id %>%
  dim()
# Inspect number of rows dropped
covidcns_excluded <- dim(covidcns_dat_id)[1] - dim(covidcns_dat)[1]
covidcns_excluded
```

```{r COVIDCNS inspect missingness}
covidcns_miss_map <- covidcns_dat_id %>% 
  missmap()
covidcns_miss_map
```

```{r Create dat}
dat <- covidcns_dat_id 
# Check
dat %>% glimpse()
```


Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(ends_with("txt"),
                ~case_when(
                  . == "-55" ~ "-555",
                  . == "-77" ~ "-777",
                  . == "-88" ~ "-888",
                  . == "-99" ~ "-999",
                  TRUE ~ .)))
```


Create list of all unique values
```{r List unique values}
ulst <- sapply(dat, unique)
```

# Cleaning

Inspect variables as they are all textual and require individual cleaning
```{r COVIDCNS inspect variables}
dat %>%
  tbl_summary(include = c(
    ncrf3_diag.any_other_issue_of_significance_to_note.txt,
    ncrf3_diag.continuous_number_of_days_in_any_hospital.txt,
    ncrf3_diag.number_of_days_in_itu.txt
                          ),
              missing_text = "Missing")
```

# Recode incorrect variables
Can be removed after data recoded in qualtrics and after data export
If variables are found to be incorrect:
Report the error in the qualtrics issues spreadsheet
Add as action point on teams with yourself and Molly tagged
Recode the variable yourself using `case_when` as below
Continue cleaning your script with the recoded variable until fixed from source

## Number of days in ITU
```{r COVIDCNS recode number of days in ITU variable}
dat <- dat %>% 
  mutate(across(ncrf3_diag.number_of_days_in_itu.txt,
                ~case_when(
                  str_detect(ncrf3_diag.number_of_days_in_itu.txt, "none") |
                    str_detect(ncrf3_diag.number_of_days_in_itu.txt, "None") ~ "0",
                  str_detect(ncrf3_diag.number_of_days_in_itu.txt, " days") |
                    str_detect(ncrf3_diag.number_of_days_in_itu.txt, " Days") ~ "",
                  str_detect(ncrf3_diag.number_of_days_in_itu.txt, "n/a") |
                    str_detect(ncrf3_diag.number_of_days_in_itu.txt, "N/A") ~ "-555",
                  str_detect(ncrf3_diag.number_of_days_in_itu.txt, "n/k") |
                    str_detect(ncrf3_diag.number_of_days_in_itu.txt, "N/K") | 
                  str_detect(ncrf3_diag.number_of_days_in_itu.txt, "/") ~ "-888",
                  TRUE ~ .)))
```

### Recheck Number of days in ITU coding
```{r recheck coding for number of days in ITU coding}
dat %>%
  select(all_of(starts_with("ncrf3_diag.number_of_days_in_itu.txt"))) %>%
  tbl_summary(missing_text = "Missing")
```



## Number of Continuous Days in the Hospital
```{r COVIDCNS recode number of days in the hospital}
dat <- dat %>% 
  mutate(across(ncrf3_diag.continuous_number_of_days_in_any_hospital.txt,
                ~case_when(
                  str_detect(ncrf3_diag.continuous_number_of_days_in_any_hospital.txt, " days") |
                    str_detect(ncrf3_diag.continuous_number_of_days_in_any_hospital.txt, " day") |
                    str_detect(ncrf3_diag.continuous_number_of_days_in_any_hospital.txt, " day ") |
                    str_detect(ncrf3_diag.continuous_number_of_days_in_any_hospital.txt, " days ") |
                    str_detect(ncrf3_diag.continuous_number_of_days_in_any_hospital.txt, " Days") ~ "",
                  str_detect(ncrf3_diag.continuous_number_of_days_in_any_hospital.txt, "11 ") ~ "11",
                  str_detect(ncrf3_diag.continuous_number_of_days_in_any_hospital.txt, "110 ") ~ "110",
                  str_detect(ncrf3_diag.continuous_number_of_days_in_any_hospital.txt, "18 ") ~ "18",
                  str_detect(ncrf3_diag.continuous_number_of_days_in_any_hospital.txt, "03") ~ "3",
                  str_detect(ncrf3_diag.continuous_number_of_days_in_any_hospital.txt, "38 ") ~ "38",
                  TRUE ~ .)))
```

### Recheck number of Continuous Days in the Hospital
```{r recheck recode number of days in the hospital}
dat %>%
  select(all_of(starts_with("ncrf3_diag.continuous_number_of_days_in_any_hospital.txt"))) %>%
  tbl_summary(missing_text = "Missing")
```


## Any other issue
```{r COVIDCNS recode any other issues}
dat <- dat %>% 
  mutate(across(ncrf3_diag.any_other_issue_of_significance_to_note.txt,
                ~case_when(
                  str_detect(ncrf3_diag.any_other_issue_of_significance_to_note.txt, "NA") |
                    str_detect(ncrf3_diag.any_other_issue_of_significance_to_note.txt, "na") |
                    str_detect(ncrf3_diag.any_other_issue_of_significance_to_note.txt, "N/A") |
                    str_detect(ncrf3_diag.any_other_issue_of_significance_to_note.txt, "n/a") ~ "-555",
                  str_detect(ncrf3_diag.any_other_issue_of_significance_to_note.txt, "aatient") ~ "Patient",
                  str_detect(ncrf3_diag.any_other_issue_of_significance_to_note.txt, "No ") ~ "No",
                    TRUE ~ .)))
```

### Recheck Any other issue
```{r recheck recode any other issues}
dat %>%
  select(all_of(starts_with("ncrf3_diag.any_other_issue_of_significance_to_note.txt"))) %>%
  tbl_summary(missing_text = "Missing")
```

# Save cleaned data

Check colnames before exporting final dataset
```{r check colnames}
colnames(dat)
```

# COVIDCNS
```{r Write cleaned COVIDCNS variables to a .rds file}
dat %>%
  saveRDS(
    file = paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf3_diag_covidcns_clean.rds")
    )
```
