---
title: "COVIDCNS NCRF Module 2 Lab Results Cleaning Script"
author: "Zain Ahmad"
date: "24/02/2022"
output: html_document
---


All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except:
Study name (COVIDCNS) all caps
Capitalised first word

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = "../functions/add_numeric.R")
source(file = "../functions/remove_duplicates.R")
source(file = "../functions/sumscores.R")
source(file = "../functions/package_check.R")
source(file = "../functions/imp_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in file with path to ilovecovidcns channel on teams}
source(file = "../credentials/paths.R")
```

# Read in the data: NCRF Module 2 Lab Results
Change this heading to the name of your questionnaire/demographic
Load COVIDCNS data

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the issues spreadsheet "https://docs.google.com/spreadsheets/d/1a2gL8c0eH2pZXNTbnPzkDYQGeeVXbLKU8BUpYM0moe8/edit?usp=sharing"

- For variable names, use ONLY 'questionnaire.variable_name'
- For dataset, only use snake_case naming
- When using pipe operator '%>%', each function should begin on a new line
- Do not add empty lines at the beginning or end of a chunk
- Use only tidyverse functions wherever possible
- When naming chunks, begin with the name of the dataset (COVIDCNS)

## COVIDCNS data
```{r COVIDCNS load data}
covidcns_dat <- read_rds(
  file = paste0(ilovecovidcns, "/data_raw/latest_freeze/neuro_case_report/ncrf2_lab_covid_cns.rds")
  )
  
# Check variable names in dataframe
covidcns_dat %>%
  colnames()

# Inspect dimensions of dataframe 
covidcns_dat %>%
  dim()
```

Select & rename relevant columns
```{r COVIDCNS select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicate IDs
  add_column(sample = "COVIDCNS",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         sample,
         startDate,
         endDate,
         ncrf2_lab.hemoglobin,
         ncrf2_lab.wbc_count,
         ncrf2_lab.hematocrit,
         ncrf2_lab.platelets,
         ncrf2_lab.apttaptr,
         ncrf2_lab.pt,
         ncrf2_lab.inr,
         ncrf2_lab.astsgot,
         ncrf2_lab.total_bilirubin,
         ncrf2_lab.urea,
         ncrf2_lab.lactate,
         ncrf2_lab.po2,
         ncrf2_lab.lowest_po2,
         ncrf2_lab.pco2,
         ncrf2_lab.csf_wcc,
         ncrf2_lab.csf_protein,
         ncrf2_lab.creatinine,
         ncrf2_lab.sodium,
         ncrf2_lab.potassium,
         ncrf2_lab.procalcitonin,
         ncrf2_lab.crp,
         ncrf2_lab.ldh,
         ncrf2_lab.creatine_kinase,
         ncrf2_lab.troponin,
         ncrf2_lab.esr,
         ncrf2_lab.ddimer,
         ncrf2_lab.ferritin,
         ncrf2_lab.ph,
         ncrf2_lab.bicarbonate,
         ncrf2_lab.csf_rcc,
         ncrf2_lab.csfserum_glucose,
         ncrf2_lab.csf_autoantibodies,
         ncrf2_lab.csf_pcr,
         ncrf2_lab.serum_autoantibodies,
         ncrf2_lab.csf_antiviral_antibodies,
         ncrf2_lab.csf_autoantibodies_.txt,
         ncrf2_lab.csf_pcr_.txt,
         ncrf2_lab.serum_autoantibodies_.txt,
         ncrf2_lab.csf_antiviral_antibodies_.txt,
         ncrf2_lab.any_other_issue_of_significance_to_note.txt
         )

# Inspect colnames
covidcns_dat_id %>%
  colnames()
```

Look at number of people excluded
The number of people to be excluded should be negative
```{r COVIDCNS number excluded}
# Inspect dimensions of new data set
covidcns_dat_id %>%
  dim()

# Inspect number of rows dropped
covidcns_excluded <- dim(covidcns_dat_id)[1] - dim(covidcns_dat)[1]
covidcns_excluded
```

Check missingness by missmap
```{r COVIDCNS inspect missingness}
covidcns_miss_map <- covidcns_dat_id %>% 
  missmap()

covidcns_miss_map
```

Create dat as copy of covidcns_dat_id for brevity
This step gives you a 'reset' point: if your variable recoding screws up, re-run this chunk to give you a fresh 'dat' dataframe
```{r Create dat}
dat <- covidcns_dat_id 

# Check
dat %>% glimpse()
```

Convert chr to numeric
```{r COVIDCNS convert text to numeric}
dat <- dat %>%
  mutate(across(starts_with("ncrf2") & !ends_with("txt"),
                ~round(as.numeric(.), digits = 1)
                )
    
        )
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(starts_with("ncrf2") & !ends_with("txt"),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)))
```

Create list of all unique values
```{r List unique values}
ulst <- sapply(dat, unique)
```

Recode -777 to NA for continuous cleaning
```{r Recode nonanswer values}
dat <- dat %>%
  mutate(across(starts_with("ncrf2") & !ends_with("txt"),
                ~case_when(
                  . == -777 ~ NA_real_,
                  TRUE ~ .)))
```


# Cleaning Continuous Variables

Inspect range prior to cleaning
```{r Check range of values}
dat %>%
  select(starts_with("ncrf2") & !ends_with("txt")) %>%
  tbl_summary()
```

Define limits for variable and list reasoning below
All Variables
- Lower: 0, values should not be negative but no reasonable upper limits

Count number of outliers in variable
No outliers
```{r Outlier count}
dat %>%
  select(starts_with("ncrf2") & !ends_with("txt")) %>%
  filter(. < 0) %>%
  nrow()
```


# Save cleaned data

Check colnames before exporting final dataset
```{r Check colnames}
colnames(dat)
```

# COVIDCNS
```{r Write cleaned COVIDCNS variables to a .rds file}
dat %>%
  saveRDS(
    file = paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf2_lab_covidcns_clean.rds")
    )
```
