---
title: "COVIDCNS NCRF2 Vital Signs Cleaning Script"
author: "Zain Ahmad"
date: "17/05/2022"
output: html_document
---


All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except:
Study name (COVIDCNS) all caps
Capitalised first word

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the recode_check function - used to check for implausible values when recoding
Add the imp_clean function - used to check variables for implausible values
Add the cont_clean function - used to check continuous variables for implausible values
```{r Read in functions}
source(file = "scripts/functions/add_numeric_1.R")
source(file = "scripts/functions/remove_duplicates.R")
source(file = "scripts/functions/sumscores.R")
source(file = "scripts/functions/package_check.R")
source(file = "scripts/functions/recode_check.R")
source(file = "scripts/functions/imp_clean.R")
source(file = "scripts/functions/cont_clean.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in file with path to ilovecovidcns channel on teams}
source(file = "scripts/credentials/paths.R")
```

# Read in the data: Neuro Case Report Form Module 2: Vital Signs
Change this heading to the name of your questionnaire/demographic
Load COVIDCNS data

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the issues spreadsheet "https://docs.google.com/spreadsheets/d/1a2gL8c0eH2pZXNTbnPzkDYQGeeVXbLKU8BUpYM0moe8/edit?usp=sharing"

- For variable names, use ONLY 'questionnaire.variable_name'
- For dataset, only use snake_case naming
- When using pipe operator '%>%', each function should begin on a new line
- Do not add empty lines at the beginning or end of a chunk
- Use only tidyverse functions wherever possible
- When naming chunks, begin with the name of the dataset (COVIDCNS)

## COVIDCNS data
```{r COVIDCNS load data}
covidcns_dat <- read_rds(
  file = paste0(ilovecovidcns, "/data_raw/latest_freeze/neuro_case_report/ncrf2_vital_covid_cns.rds")
  )
  
# Check variable names in dataframe
covidcns_dat %>%
  colnames()

# Inspect dimensions of dataframe 
covidcns_dat %>%
  dim()
```

Specify columns to be excluded from add_numeric function
Continuous variables should be excluded, as they are already numeric
```{r COVIDCNS specify excluded columns}
exclude_cols_numeric <- c(
  "ID",
  "sample",
  "startDate",
  "endDate",
  "ncrf2_vital.date.txt",
  "ncrf2_vital.vitals",
  "ncrf2_vital.vitals.1",
  "ncrf2_vital.vitals.2",
  "ncrf2_vital.vitals.3",
  "ncrf2_vital.vitals.4",
  "ncrf2_vital.room_airtext.txt",
  "ncrf2_vital.oxygen_therapytext.txt",
  "ncrf2_vital.glasgow_coma_score.txt",
  "ncrf2_vital.lowest_gcs_during_admission.txt",
  "ncrf2_vital.any_other_issue_of_significance_to_note.txt"
  )
```

Select & rename relevant columns
```{r COVIDCNS select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "COVIDCNS",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         sample,
         startDate,
         endDate,
         ncrf2_vital.date.txt,
         ncrf2_vital.vitals,
         ncrf2_vital.vitals.1,
         ncrf2_vital.vitals.2,
         ncrf2_vital.vitals.3,
         ncrf2_vital.vitals.4,
         ncrf2_vital.severe_dehydration,
         ncrf2_vital.room_air,
         ncrf2_vital.room_airtext.txt,
         ncrf2_vital.oxygen_therapy,
         ncrf2_vital.oxygen_therapytext.txt,
         ncrf2_vital.unknown,
         ncrf2_vital.avpu,
         ncrf2_vital.glasgow_coma_score.txt,
         ncrf2_vital.lowest_gcs_during_admission.txt,
         ncrf2_vital.any_other_issue_of_significance_to_note.txt,
         ncrf2_vital.was_the_patient_intubated_and_ventilated,
         ncrf2_vital.was_the_patient_under_sedation
         ) %>%
  add_numeric_1(exclude = exclude_cols_numeric)

# Inspect colnames
covidcns_dat_id %>%
  colnames()
```

Look at number of people excluded
The number of people to be excluded should be negative
```{r COVIDCNS number excluded}
# Inspect dimensions of new data set
covidcns_dat_id %>%
  dim()

# Inspect number of rows dropped
covidcns_excluded <- dim(covidcns_dat_id)[1] - dim(covidcns_dat)[1]
covidcns_excluded
```

Check missingness by missmap
```{r COVIDCNS inspect missingness}
covidcns_miss_map <- covidcns_dat_id %>% 
  missmap()

covidcns_miss_map
```

Create dat as copy of covidcns_dat_id for brevity
This step gives you a 'reset' point: if your variable recoding screws up, re-run this chunk to give you a fresh 'dat' dataframe
```{r Create dat}
dat <- covidcns_dat_id 

# Check
dat %>% glimpse()
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(ends_with("numeric"),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)))
```

Create lists of all unique values and levels
Use the unique list as a reference for numeric variables
Use the levels list as a reference for categorical variables
```{r List unique values levels}
ulst <- sapply(dat, unique)
llst <- sapply(dat, levels)
```


# Cleaning Categorical Variables

Name your vectors in line with the chunks below
Number the vectors or name them intuitively if you have multiple vectors
Vectors of potential values should only contain possible values (exclude nonanswer values as appropriate)

Create sequential vectors of categorical values
```{r Vector categorical values}
vals_cat_1 <- c(
  "Yes",
  "No",
  "Seen but not answered",
  "Unknown",
  NA
)

vals_cat_2 <- c(
  "Room air",
  "Not Room air",
  NA
)

vals_cat_3 <- c(
  "Oxygen therapy",
  "Not Oxygen therapy",
  NA
)

vals_cat_4 <- c(
  "Unknown",
  "Not Unknown",
  NA
)

vals_cat_5 <- c(
  "Seen but not answered",
  "Awake",
  "Verbal",
  "Pain",
  "Unresponsive",
  NA
)

vals_cat_6 <- c(
  "Seen but not answered",
  "Yes",
  "No",
  NA
)
```

Create list of categorical values vectors
```{r List categorical values vectors}
values_cat_list <- list(
  vals_cat_1,
  vals_cat_2,
  vals_cat_3,
  vals_cat_4,
  vals_cat_5,
  vals_cat_6,
  vals_cat_6
)
```

Remove values vectors from environment
```{r Remove categorical values vectors}
rm(
  vals_cat_1,
  vals_cat_2,
  vals_cat_3,
  vals_cat_4,
  vals_cat_5,
  vals_cat_6
)
```

Set names of list to variable names
```{r Set list names categorical}
names(values_cat_list) <- c(
  "ncrf2_vital.severe_dehydration",
  "ncrf2_vital.room_air",
  "ncrf2_vital.oxygen_therapy",
  "ncrf2_vital.unknown",
  "ncrf2_vital.avpu",
  "ncrf2_vital.was_the_patient_intubated_and_ventilated",
  "ncrf2_vital.was_the_patient_under_sedation"
)
```

Use imp_clean to find if any implausible values
```{r Imp_clean categorical variables}
imp_clean(values_list = values_cat_list,
          dat = dat)
```

Produce summary table of variables
```{r Summary table categorical variables}
dat %>%
  tbl_summary(
    include = all_of(names(values_cat_list)),
    missing_text = "Missing")
```


# Cleaning Numeric Variables

Name your vectors in line with the chunks below
Number the vectors or name them intuitively if you have multiple vectors
Vectors of potential values should only contain possible values (exclude nonanswer values as appropriate)

Create sequential vectors of numeric values
```{r Vector numeric values}
vals_num_1 <- c(
  0,
  1,
  -777,
  -888,
  NA
)

vals_num_2 <- c(
  0,
  1,
  -777,
  NA
)

vals_num_3 <- c(
  1,
  2,
  3,
  4,
  -777,
  NA
)
```

Create list of numeric values vectors
```{r List numeric values vectors}
values_num_list <- list(
  vals_num_1,
  vals_num_2,
  vals_num_2,
  vals_num_2,
  vals_num_3,
  vals_num_2,
  vals_num_2
)
```

Remove values vectors from environment
```{r Remove numeric values vectors}
rm(
  vals_num_1,
  vals_num_2,
  vals_num_3
)
```

Set names of list to variable names
```{r Set list names numeric}
names(values_num_list) <- c(
  "ncrf2_vital.severe_dehydration_numeric",
  "ncrf2_vital.room_air_numeric",
  "ncrf2_vital.oxygen_therapy_numeric",
  "ncrf2_vital.unknown_numeric",
  "ncrf2_vital.avpu_numeric",
  "ncrf2_vital.was_the_patient_intubated_and_ventilated_numeric",
  "ncrf2_vital.was_the_patient_under_sedation_numeric"
)
```

Use imp_clean to find if any implausible values
```{r Imp_clean numeric variables}
imp_clean(values_list = values_num_list,
          dat = dat)
```

Produce summary table of variables
```{r Summary table numeric variables}
dat %>%
  tbl_summary(
    include = all_of(names(values_num_list)),
    missing_text = "Missing")
```

# Cleaning Continuous Variables

Create vector of continuous variables
```{r Create cont vars vector}
variables_cont <- c(
  "ncrf2_vital.vitals", #temp
  "ncrf2_vital.vitals.1", #HR
  "ncrf2_vital.vitals.2", #RR
  "ncrf2_vital.vitals.3", #BP sys
  "ncrf2_vital.vitals.4", #BP dias
  "ncrf2_vital.room_airtext.txt", #sats on room air
  "ncrf2_vital.oxygen_therapytext.txt", #sats on O2 therapy
  "ncrf2_vital.glasgow_coma_score.txt",
  "ncrf2_vital.lowest_gcs_during_admission.txt"
)
```

Inspect continuous variables
Use the question labels to ascertain context at this point and check for obvious outliers
The percentiles can be modified to exclude nonanswer values as appropriate to your data
```{r Inspect cont vars}
dat %>%
  select(all_of(variables_cont)) %>%
  tbl_summary(
    missing_text = "Missing",
    statistic = list(all_continuous() ~ "{median} ({p0}, {p5}, {p95}, {p100})"))
```

Check unique values in continuous variables
If the fields contain text at this point, use the chunk below to clean manually
```{r Cont vars unique}
dat %>%
  select(all_of(variables_cont)) %>%
  sapply(., unique) #%>%
  #sort() %>%
  #.[sapply(., function(x) nchar(x) != 2)]
```

Manually clean continuous variables to ensure parsing as numeric
Use the output from the chunk above and clean the variable manually here until there are no 'rogue' values
Case_when is type-specific so number must be specified as char and the variable mutated to numeric as below
REMOVE THIS CHUNK IF NOT NECESSARY
```{r Temperature manual clean}
dat <- dat %>%
  mutate(across(ncrf2_vital.vitals,
                ~case_when(str_detect(ncrf2_vital.vitals, "A") ~ "-77",
                           str_detect(ncrf2_vital.vitals, "N") ~ "-77",
                           str_detect(ncrf2_vital.vitals, "a") ~ "-77",
                           str_detect(ncrf2_vital.vitals, "n") ~ "-77",
                           TRUE ~ .)
                )
         )
```

```{r Heart rate manual clean}
dat <- dat %>%
  mutate(across(ncrf2_vital.vitals.1,
                ~case_when(str_detect(ncrf2_vital.vitals.1, "n") ~ "-77",
                           str_detect(ncrf2_vital.vitals.1, "r") ~ "-77",
                           str_detect(ncrf2_vital.vitals.1, "N") ~ "-77",
                           str_detect(ncrf2_vital.vitals.1, "-") ~ "90",
                           . == "59R" ~ "59",
                           . == "60R" ~ "60",
                           . == "64R" ~ "64",
                           . == "84R" ~ "84",
                           TRUE ~ .)
                )
         )
```

```{r Resp rate manual clean}
dat <- dat %>%
  mutate(across(ncrf2_vital.vitals.2,
                ~case_when(str_detect(ncrf2_vital.vitals.2, "IV") ~ "20",
                           str_detect(ncrf2_vital.vitals.2, "n") ~ "-77",
                           str_detect(ncrf2_vital.vitals.2, "N") ~ "-77",
                           . == "36.7" ~ "-77",
                           TRUE ~ .)
                )
         )
```

```{r Sys BP manual clean}
dat <- dat %>%
  mutate(across(ncrf2_vital.vitals.3,
                ~case_when(. == "105/" ~ "105",
                           . == "11*" ~ "118",
                           . == "134`65" ~ "134/65",
                           str_detect(ncrf2_vital.vitals.3, "n") ~ "-77",
                           str_detect(ncrf2_vital.vitals.3, "N") ~ "-77",
                           TRUE ~ .)
                )
         )
```

Check for BP written in one box instead of 2
```{r Check for BP mistake}
dat %>%
  dplyr::select(ncrf2_vital.vitals.3, ncrf2_vital.vitals.4) %>%
  filter(str_detect(ncrf2_vital.vitals.3, "/"))
```

Split out BPs and sub back into df
```{r Correct BP issue}
bp_vec <- unlist(dat %>% dplyr::select(ncrf2_vital.vitals.3) %>% filter(str_detect(ncrf2_vital.vitals.3, "/")))

names(bp_vec) <- c()

bp_split <- strsplit(bp_vec, split = "/")


bp_indices <- which(str_detect(dat$ncrf2_vital.vitals.3, "/"))


for (i in 1:length(bp_split)){
  bp_split[[i]][3] <- bp_indices[i]
}

for(i in 1:length(bp_split)){
  dat[bp_split[[i]][3], "ncrf2_vital.vitals.3"] <- bp_split[[i]][1]
  dat[bp_split[[i]][3], "ncrf2_vital.vitals.4"] <- bp_split[[i]][2]
}

dat %>%
  dplyr::select(ncrf2_vital.vitals.3, ncrf2_vital.vitals.4) %>%
  slice(as.numeric(bp_indices))
```

```{r Dias BP manual clean}
dat <- dat %>%
  mutate(across(ncrf2_vital.vitals.4,
                ~case_when(str_detect(ncrf2_vital.vitals.4, "n") ~ "-77",
                           str_detect(ncrf2_vital.vitals.4, "N") ~ "-77",
                           TRUE ~ .)
                )
         )
```

```{r Sats room air manual clean}
dat <- dat %>%
  mutate(across(ncrf2_vital.room_airtext.txt,
                ~case_when(. == "92-96" ~ "94",
                           . == "<95" ~ "94",
                           . == "97%" ~ "97",
                           . == "95%" ~ "95",
                           . == "21%" ~ "21",
                           TRUE ~ .)
                )
         )
```

```{r Sats O2 therapy manual clean}
dat <- dat %>%
  mutate(across(ncrf2_vital.oxygen_therapytext.txt,
                ~case_when(. == "100%"  ~ "100",
                           . == "15L NRB"  ~ "-77",
                           . == "1L" ~ "-77",
                           . == "3L" ~ "-77",
                           . == "2" ~ "-77",
                           . == "4" ~ "-77",
                           . == "40%"  ~ "40",
                           . == "45/l pm"  ~ "-77",
                           . == "5LPM" ~ "-77",
                           . == "6L" ~ "-77",
                           . == "7Litres" ~ "-77",
                           . == "90%" ~ "90",
                           . == "90% on wall flow mask 6L" ~ "90",
                           . == "91%" ~ "91",
                           . == "92-93" ~ "93",
                           . == "94%" ~ "94",
                           . == "94% 2L" ~ "94",
                           . == "94% on 35% venturi mask weaned from HFNO" ~ "94",
                           . == "95 on 2L" ~ "95",
                           . == "96% on 2L" ~ "96",
                           . == "97%" ~ "97",
                           . == "97% on 2 litres of oxygen" ~ "97",
                           . == "97% on 4 L/min via Nasal Cannula" ~ "97",
                           . == "99% saturations on 2L via nasal cannulae" ~ "99",
                           . == "intubated" ~ "-77",
                           TRUE ~ .)
                )
         )
```

```{r GCS manual clean}
dat <- dat %>%
  mutate(across(ncrf2_vital.glasgow_coma_score.txt,
                ~case_when(str_detect(ncrf2_vital.glasgow_coma_score.txt, "-") ~ "-77",
                           str_detect(ncrf2_vital.glasgow_coma_score.txt, "n") ~ "-77",
                           str_detect(ncrf2_vital.glasgow_coma_score.txt, "N") ~ "-77",
                           str_detect(ncrf2_vital.glasgow_coma_score.txt, "I") ~ "-77",
                           . == "04" ~ "4",
                           . == "10 (tracheostomy)" ~ "10",
                           . == "11 (E4, Vt, M6)" ~ "11",
                           . == "11 (trachy)" ~ "11",
                           . == "12/15" ~ "12",
                           . == "13/15" ~ "13",
                           . == "15/15" ~ "15",
                           . == "3 (intubated)" ~ "3",
                           . == "3 (sedated)" ~ "3",
                           . == "6 (E4VtM1)" ~ "6",
                           . == "E4 Vt M6" ~ "11",
                           TRUE ~ .)
                )
         )
```

```{r Lowest GCS manual clean}
dat <- dat %>%
  mutate(across(ncrf2_vital.lowest_gcs_during_admission.txt,
                ~case_when(str_detect(ncrf2_vital.lowest_gcs_during_admission.txt, "-") ~ "-77",
                           str_detect(ncrf2_vital.lowest_gcs_during_admission.txt, "k") ~ "-77",
                           str_detect(ncrf2_vital.lowest_gcs_during_admission.txt, "K") ~ "-77",
                           str_detect(ncrf2_vital.lowest_gcs_during_admission.txt, "A") ~ "-77",
                           . == "04" ~ "4",
                           . == "1" ~ "-77",
                           . == "10 (when not sedated and ventilated)" ~ "10",
                           . == "14/15" ~ "14",
                           . == "15/15" ~ "15",
                           . == "3 (E1, Vt, M1) when ventilated and deeply sedated" ~ "3",
                           . == "3 (intubated)" ~ "3",
                           . == "3 (sedated)" ~ "3",
                           . == "4 (E2vtM1)" ~ "4",
                           . == "5 (E4VTM1)" ~ "5",
                           . == "8/15" ~ "8",
                           . == "E Vt M6" ~ "-77",
                           TRUE ~ .)
                )
         )
```

Mutate variables to numeric after cleaning manually
This step is necessary to check for non-integer values
Modify the all_of statement as required: DO NOT MUTATE TO NUMERIC UNNECESSARILY
REMOVE THIS CHUNK IF NOT NECESSARY
```{r Cont vars to numeric}
dat <- dat %>%
  mutate(across(all_of(variables_cont),
                ~as.numeric(.)
                )
         )
```

Transform nonanswer values to 3 digit
```{r Cont vars nonanswer}
dat <- dat %>%
  mutate(across(
    all_of(variables_cont),
    ~case_when(. == -55 ~ -555,
               . == -77 ~ -777,
               . == -88 ~ -888,
               . == -99 ~ -999,
               TRUE ~ .)
                )
         )
```

Recheck continuous variables
```{r Recheck cont vars}
dat %>%
  select(all_of(variables_cont)) %>%
  dplyr::mutate(across(all_of(variables_cont),
                       ~na_if(., -777)
                       )
                ) %>%
  tbl_summary(
    missing_text = "Missing",
    statistic = list(all_continuous() ~ "{median} ({p0}, {p5}, {p95}, {p100})"))
```

Create matrix of limits for continuous variables
Matrix is series of vectors (lower, upper)
```{r Create matrix limits}
limits_mat <- rbind(
  c(11, 47),
  c(0, 480),
  c(0, 200),
  c(0, 370),
  c(0, 360),
  c(0, 100),
  c(0, 100),
  c(3, 15),
  c(3, 15)
  )
```

Set row and col names of limits_mat
This allows your to easily refer back to limits_mat for a summary
```{r Set lim_mat names}
rownames(limits_mat) <- variables_cont
colnames(limits_mat) <- c("Lower", "Upper")
```

Use cont_clean to check if any implausible values and provide replacement vectors
Cont_clean will not proceed if variables are not numeric type, clean manually above if necessary
```{r Cont_clean cont vars}
cont_list <- cont_clean(
  variables = variables_cont,
  limits_mat = limits_mat,
  dat = dat
)
for (i in 1:length(variables_cont)){
  print(paste0("Implausibles in ", variables_cont[i], ": ", cont_list[[variables_cont[i]]]$Count))
}
```

Re-inspect variables after cleaning
```{r Inspect after cleaning}
dat %>%
  select(all_of(variables_cont)) %>%
  dplyr::mutate(across(all_of(variables_cont),
                       ~na_if(., -777),
                       )
                ) %>%
  tbl_summary(
    missing_text = "Missing",
    statistic = list(all_continuous() ~ "{median} ({p0}, {p100})")
  )
```


# Cleaning Dates

Create vector of date variables
```{r Vector date vars}
variables_date <- c(
  "ncrf2_vital.date.txt"
)
```

Inspect date variables
```{r Inspect date vars}
dat %>%
  select(all_of(variables_date)) %>%
  tbl_summary()
```

Check unique values in date variables
If the fields contain text at this point, use the chunk below to clean manually
```{r Date vars unique}
dat %>%
  select(all_of(variables_date)) %>%
  sapply(., unique) %>%
  sort() #%>%
  #.[sapply(., function(x) nchar(x) != 10)]
  #.[sapply(., function(x) str_detect(x, ""))]
```


Manually clean date variables to ensure parsing as dttm
Use the output from the chunk above and clean the variable manually here until there are no 'rogue' values
Case_when is type-specific so number must be specified as char and the variable mutated to numeric as below
REMOVE THIS CHUNK IF NOT NECESSARY
```{r Date manual clean}
dat <- dat %>%
  mutate(across(ncrf2_vital.date.txt,
                ~case_when(. == "01/06/20" ~ "01/06/2020",
                           . == "06/03/20201" ~ "-77",
                           . == "06/12/21" ~ "06/12/2021",
                           . == "07/1/2021" ~ "07/01/2021",
                           . == "08/03/21" ~ "08/03/2021",
                           . == "12/04/21" ~ "12/04/2021",
                           . == "14" ~ "-77",
                           . == "149/03/2021" ~ "14/03/2021",
                           . == "15/7/2020" ~ "15/07/2020",
                           . == "17 Jan 2021" ~ "17/01/2021",
                           . == "19/02/202" ~ "-77",
                           . == "19/08/2021 (03:00)" ~ "19/08/2021",
                           . == "20/03/2020 - same data as admission data (only one day of hospital admission)" ~ "20/03/2020",
                           . == "20/11/20" ~ "20/11/2020",
                           . == "20/3/2020" ~ "20/03/2020",
                           . == "22/04/21" ~ "22/04/2021",
                           . == "23/11/21" ~ "23/11/2021",
                           . == "27/7/2021" ~ "27/07/2021",
                           . == "29/01/2022 - discharged the day after admission" ~ "29/01/2022",
                           . == "29/08/21" ~ "29/08/2021",
                           . == "29/10/220" ~ "-77",
                           . == "30/08/21" ~ "30/08/2021",
                           . == "4/03/2021" ~ "04/03/2021",
                           . == "4/12/2021" ~ "04/12/2021",
                           . == "5/12/2021" ~ "05/12/2021",
                           . == "6/11/2021" ~ "06/11/2021",
                           . == "01/15/2021" ~ "-77",
                           . == "30.01.2021" ~ "30/01/2021",
                           . == "22.12.2020" ~ "22/12/2020",
                           . == "08/30/2021" ~ "30/08/2021",
                           TRUE ~ .)
                )
         )
```

Replace -77 values with NA: POSIX will reject -77 as a value when converting
```{r Date vars recode -77 to NA}
dat <- dat %>% 
  mutate(across(all_of(variables_date),
                ~na_if(., "-77")
                )
         )
```

Check dates for remaining unparsable values
```{r Check unparsable}
my_dates <- unlist(dat %>% select(ncrf2_vital.date.txt) %>% drop_na())
names(my_dates) <- c()

for(i in 1:length(my_dates)){
   print(i)
   stopifnot(!is.na(lubridate::dmy(my_dates[i])))
}
```

Find unparsable value where for loop fails and add to case_when
```{r Find unparsable value}
my_dates[278]
```

Parse dates using lubridate
```{r Parse date vars}
dat <- dat %>% 
  mutate(across(all_of(variables_date),
                ~lubridate::parse_date_time(x = .,
                                            orders = c("d/m/y"),
                                            tz = "Europe/London")
                )
         )
```

Recheck date variables
```{r Recheck parsed date vars}
dat %>%
  select(all_of(variables_date)) %>%
  tbl_summary(missing_text = "Missing")
```

Define limits for variable and list reasoning below
Variable name:
- Upper: latest data extraction, cannot have test in the future
- Lower: 30/01/2020, first confirmed UK COVID cases 

```{r Define limits}
upper_limit <- as.POSIXct("2022-05-09")
lower_limit <- as.POSIXct("2020-01-30")
```

Recode variable outliers to NA
```{r Date vars recode outliers to NA}
dat <- dat %>%
    mutate(across(all_of(variables_date),
                  ~ifelse(. > upper_limit | # bigger than the upper limit
                          . < lower_limit, # smaller than the lower limit
                          yes = NA,
                          no = .)
                  )
           ) %>%
  mutate(across(all_of(variables_date),
                ~as.POSIXct(.,
                            origin = lubridate::origin)
                )
         )
```

Re-check dates
```{r Recheck cleaned date vars}
dat %>%
  select(all_of(variables_date)) %>%
  tbl_summary(missing_text = "Missing")
```


# Cleaning Textual Variables

Create vector of text variables
```{r Vector text vars}
variables_text <- c(
  "ncrf2_vital.any_other_issue_of_significance_to_note.txt"
)
```

View text variables
```{r View text vars}
dat %>%
  select(all_of(variables_text)) %>%
  tbl_summary()
```


# Save cleaned data

Check colnames before exporting final dataset
```{r Check colnames}
colnames(dat)
```

# COVIDCNS
```{r Write cleaned COVIDCNS variables to a .rds file}
dat %>%
  saveRDS(
    file = paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf2_vital_covidcns_clean.rds")
    )
```
