---
title: "HLQ Joining Script"
author: "Zain Ahmad"
date: "2022-08-01"
output: html_document
---


This R markdown:
1) Joins COVID-CNS questionnaires together
2) Creates on rds file with matching variables
3) One rds file for the biomarker work
4) One rds file for Greta's work

# Set up

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = "scripts/functions/add_numeric.R")
source(file = "scripts/functions/remove_duplicates.R")
source(file = "scripts/functions/sumscores.R")
source(file = "scripts/functions/package_check.R")
source(file = "scripts/functions/imp_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c(
  "summarytools",
  "sjlabelled",
  "gtsummary",
  "tidyverse"
  )

package_check(packages)
```

Retrieve the recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date = Sys.Date()
date
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in file with path to ilovecovidcns channel on teams}
source(file = "scripts/credentials/paths.R")
```

Exclude these variables
```{r Exclude variables vector}
exclude_variables <-
  c(
    "startDate",
    "endDate"
    )
```


# Read in the data

### dem_covidcns_clean
Read in & variable names
```{r dem_covidcns_clean Read in data & variable names}
dem_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/dem_covidcns_clean.rds")
  )

dem_covidcns_clean %>%
  dim()
```

Select columns for joining
```{r dem_covidcns_clean Select columns for joining}
dem_covidcns_clean_selected <-
  dem_covidcns_clean

dem_covidcns_clean_selected %>%
  slice(1:5)
```


### fam_covidcns_clean
Read in & variable names
```{r fam_covidcns_clean Read in data & variable names}
fam_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/fam_covidcns_clean.rds")
  )

fam_covidcns_clean %>%
  dim()
```

Select columns for joining
```{r fam_covidcns_clean Select columns for joining}
fam_covidcns_clean_selected <-
  fam_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

fam_covidcns_clean_selected %>%
  slice(1:5)
```


### mhd_covidcns_clean
Read in & variable names
```{r mhd_covidcns_clean Read in data & variable names}
mhd_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/mhd_covidcns_clean.rds")
  )


mhd_covidcns_clean %>%
  dim()
```

Select columns for joining
```{r mhd_covidcns_clean Select columns for joining}
mhd_covidcns_clean_selected <- mhd_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

mhd_covidcns_clean_selected %>%
  slice(1:5)
```


### phh_covidcns_clean
Read in & variable names
```{r phh_covidcns_clean Read in data & variable names}
phh_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/phh_covidcns_clean.rds")
  )

phh_covidcns_clean %>%
  dim()
```

Select columns for joining
```{r phh_covidcns_clean Select columns for joining}
phh_covidcns_clean_selected <- phh_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

phh_covidcns_clean_selected %>%
  slice(1:5)
```

### sub_covidcns_clean
Read in & variable names
```{r sub_covidcns_clean Read in data & variable names}
sub_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/sub_covidcns_clean.rds")
  )

sub_covidcns_clean %>%
  dim()
```

Select columns for joining
```{r sub_covidcns_clean Select columns for joining}
sub_covidcns_clean_selected <-
  sub_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

sub_covidcns_clean_selected %>%
  slice(1:5)
```



# Joining process

## List of tibbles to join, not including website data
```{r List of tibbles to join}
tibble_list <- 
  list(
    dem_covidcns_clean_selected,
    fam_covidcns_clean_selected,
    mhd_covidcns_clean_selected,
    phh_covidcns_clean_selected,
    sub_covidcns_clean_selected
    )
```

Joining of demographics and questionnaires, not including website data
```{r Joining of demographics and questionnaires}
hlq_data_joined <- 
  plyr::join_all(
    dfs =  tibble_list,
    by = c("ID"),
    type = "full"
    )
```



# Change/remove Incorrect IDs from Qualtrics

Change IDs with newline char
```{r}
hlq_data_joined$ID[hlq_data_joined$ID == "\nCNS02002"] <- "CNS02002"
hlq_data_joined$ID[hlq_data_joined$ID == "\nCNS01004"] <- "CNS01004"
```

Import swapping IDs excel sheet and remove problem IDs
```{r Remove swapping ids}
# Read in excel sheet of IDs to change as data frame
swapped_ids <- readxl::read_xlsx(path = paste0(ilovecovidcns, "/data_raw/ids/incorrect_ids.xlsx"),
                                 sheet = "Sheet1")

# Remove ids with issues
hlq_data_joined <- hlq_data_joined %>%
  filter(!ID %in% swapped_ids$incorrect_ID)
```



# Select only columns required for HLQ

Import var names for HLQ
```{r Import var names}
hlq_var_names <- read_lines(
  file = "scripts/ref_ranges/hlq_var_names.txt"
)
```

Select HLQ columns from dataset
```{r Select hlq cols}
hlq_data_joined <- hlq_data_joined %>%
  select(
    ID,
    startDate,
    endDate,
    all_of(hlq_var_names),
    all_of(colnames(fam_covidcns_clean_selected)[2:length(colnames(fam_covidcns_clean_selected))])
  )
```



# Save HLQ data set
```{r Save HLQ data set}
write_csv(
  x = hlq_data_joined, 
  file = paste0(ilovecovidcns, "/data/hlq/covidcns_hlq_data.csv")
)
```