---
title: "COVIDCNS Joining Script"
author: "Zain Ahmad"
date: "20/12/2022"
output: html_document
---

# Standards
All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except:
Study name (e.g. GLAD/EDGI/NBR) all caps
Capitalised first word
Chunk names MUST be unique

Add only one empty line between chunks
Add one extra line when starting a new section
Use hash syntax as appropriate for headings and subheadings, as per markdown syntax

Points requiring user input are enclosed thus <>

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in paths file}
source(file = "scripts/credentials/paths.R")
```

Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = paste0(ilovecovidcns_local, "/remove_duplicates.R"))
source(file = paste0(ilovecovidcns_local, "/package_check.R"))
source(file = paste0(ilovecovidcns_local, "/join_dataset.R"))
source(file = paste0(ilovecovidcns_local, "/variable_extract.R"))
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("tidyverse")
package_check(packages)
```


# Produce joined datasets

Produce joined dataset for each module
```{r Produce joined datasets}
# Website data
assessment_joined <- join_dataset("/data/assessment_status")

# Cognitron data
cognitron_joined <- join_dataset("/data/cognitron/scores")

# Qualtrics data
baseline_joined <- join_dataset("/data/latest_freeze/baseline")
clin_neuro_joined <- join_dataset("/data/latest_freeze/clin_neuro")
core_neuro_joined <- join_dataset("/data/latest_freeze/core_neuro")
fbc_joined <- join_dataset("/data/latest_freeze/fbc")
mh_case_report_joined <- join_dataset("/data/latest_freeze/mh_case_report")
moca_joined <- join_dataset("/data/latest_freeze/moca")
neuro_case_report_joined <- join_dataset("/data/latest_freeze/neuro_case_report")

# All qualtrics data
qualtrics_joined <- join_dataset("/data/latest_freeze")
```

Consolidate objects into single list
```{r Create joined_list}
joined_list <- list(
  assessment_joined,
  cognitron_joined,
  baseline_joined,
  clin_neuro_joined,
  core_neuro_joined,
  fbc_joined,
  mh_case_report_joined,
  moca_joined,
  neuro_case_report_joined,
  qualtrics_joined
)

names(joined_list) <- c(
  "assessment_joined",
  "cognitron_joined",
  "baseline_joined",
  "clin_neuro_joined",
  "core_neuro_joined",
  "fbc_joined",
  "mh_case_report_joined",
  "moca_joined",
  "neuro_case_report_joined",
  "qualtrics_joined"
)

# Remove objects to declutter environment
rm(
  assessment_joined,
  cognitron_joined,
  baseline_joined,
  clin_neuro_joined,
  core_neuro_joined,
  fbc_joined,
  mh_case_report_joined,
  moca_joined,
  neuro_case_report_joined,
  qualtrics_joined
)
```

Import case definitions data
```{r Import case defs}
case_def_dat <- readxl::read_xlsx(
  path = paste0(ilovecovidcns, "/data_raw/case_definitions/Feb_Analysis_Case_Status.xlsx"),
  sheet = "ea")

case_def_dat <- case_def_dat %>%
  select(
    ID,
    `diagnostic_group` = `Final Update Group`,
    `diagnosis` = `Final Update Diagnosis`
  )
```


# Post processing steps

Remove NFU withdrawals from all data
```{r Remove NFU}
nfu_withdrawals <- c(
  "CNS01057",
  "CNS02073",
  "CNS01079",
  "CNS02007",
  "CNS02098",
  "CNS03034",
  "CNS01002",
  "CNS02040",
  "CNS02032",
  "CNS02113",
  "CNS02104",
  "CNS02127",
  "CNS02109",
  "CNS07058", # dual recruit missing cognitron
  "CNS02098", # added later
  "CNS04011" # dummy participant
  )

for (i in 1:length(joined_list)){
  joined_list[[i]][["data"]] <- joined_list[[i]][["data"]] %>% filter(!ID %in% nfu_withdrawals)
}
```

Replace newline characters with correct IDs
```{r Replace newline}
for (i in 1:length(joined_list)){
  if ("\nCNS01004" %in% joined_list[[i]][["data"]][["ID"]]){
    joined_list[[i]][["data"]][["ID"]][joined_list[[i]][["data"]][["ID"]] == "\nCNS01004"] <- "CNS01004"
    }
  if ("\nCNS02002" %in% joined_list[[i]][["data"]][["ID"]]){
    joined_list[[i]][["data"]][["ID"]][joined_list[[i]][["data"]][["ID"]] == "\nCNS02002"] <- "CNS02002"
    }
}
```

Coalesce age and sex demographic variables from baseline and ncrf dem
```{r Coalesce age sex dem}
joined_list[["qualtrics_joined"]][["data"]] <- joined_list[["qualtrics_joined"]][["data"]] %>%
  mutate(
    dem.dob_age = coalesce(
      dem.dob_age,
      ncrf1_dem.dob_age),
    
    dem.sex_at_birth = coalesce(
      dem.sex_at_birth,
      ncrf1_dem.sex_at_birth),
    
    dem.sex_at_birth_numeric = coalesce(
      dem.sex_at_birth_numeric,
      ncrf1_dem.sex_at_birth_numeric),
    
    dem.simplified_ethnicity = coalesce(
      dem.simplified_ethnicity,
      ncrf1_dem.simplified_ethnicity)
  )
```


# Final joining

Combine website data, qualtrics, cognitron, case definitions
```{r Create overall joined data file}
data_joined <- plyr::join_all(
  dfs = list(
    joined_list[["assessment_joined"]][["data"]],
    joined_list[["qualtrics_joined"]][["data"]],
    joined_list[["cognitron_joined"]][["data"]],
    case_def_dat
  ),
  by = c("ID"),
  type = "full"
)
```

Create cognitron matching dataset
```{r Create cognitron matching}
data_export_matching <- data_joined %>%
  select(
      ID,
      dem.dob_age,
      dem.how_old_are_you_now.txt,
      dem.sex_at_birth,
      dem.sex_at_birth_numeric,
      dem.is_english_your_first_language,
      dem.is_english_your_first_language_numeric,
      dem.what_is_your_first_language.txt,
      dem.what_is_your_first_language_numeric,
      dem.highest_education,
      dem.highest_education_numeric,
      impact.current_employment_status,
      impact.current_employment_status_numeric
      )

data_export_matching %>%
  slice(1:5)
```


# Save joined datasets

Save full dataset
```{r Save full dataset}
saveRDS(
  object = data_joined,
  file = paste0(ilovecovidcns, "/data/joined/covidcns_data_joined.rds")
)

saveRDS(
  object = data_joined,
  file = paste0(ilovecovidcns, "/data_sharing/liverpool/covidcns-cog-analysis/data_raw/covidcns_greta.rds")
)
```

Save ncrf export
```{r Save ncrf export}
saveRDS(
  object = joined_list[["neuro_case_report_joined"]][["data"]],
  file = paste0(ilovecovidcns, "/data/joined/covidcns_ncrf.rds")
)

saveRDS(
  object = joined_list[["neuro_case_report_joined"]][["data"]], 
  file = paste0(ilovecovidcns, "/data_sharing/ncrf/covidcns_ncrf.rds")
)

write_csv(
  x = joined_list[["neuro_case_report_joined"]][["data"]], 
  file = paste0(ilovecovidcns, "/data_sharing/ncrf/covidcns_ncrf.csv")
)
```

Save baseline export
```{r Save baseline export}
saveRDS(
  object = joined_list[["baseline_joined"]][["data"]],
  file = paste0(ilovecovidcns, "/data/joined/covidcns_baseline.rds")
)

saveRDS(
  object = joined_list[["baseline_joined"]][["data"]], 
  file = paste0(ilovecovidcns, "/data_sharing/baseline/covidcns_baseline.rds")
)

write_csv(
  x = joined_list[["baseline_joined"]][["data"]], 
  file = paste0(ilovecovidcns, "/data_sharing/baseline/covidcns_baseline.csv")
)
```

Save matching export
```{r Save matching export}
saveRDS(
  object = data_export_matching, 
  file = paste0(ilovecovidcns, "/data/joined/covidcns_matching.rds")
)

saveRDS(
  object = data_export_matching, 
  file = paste0(ilovecovidcns, "/data_sharing/matching/covidcns_matching.rds")
)
```