---
title: "Joining script"
author: "Christopher Huebel"
date: "20/02/2022"
output: html_document
---

This R markdown:
1) Joins COVID-CNS questionnaires together
2) Creates on rds file with matching variables
3) One rds file for the biomarker work
4) One rds file for Greta's work

# Set up

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = "scripts/functions/add_numeric.R")
source(file = "scripts/functions/remove_duplicates.R")
source(file = "scripts/functions/sumscores.R")
source(file = "scripts/functions/package_check.R")
source(file = "scripts/functions/imp_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c(
  "summarytools",
  "sjlabelled",
  "gtsummary",
  "tidyverse"
  )

package_check(packages)
```

Retrieve the recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date = Sys.Date()
date
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in file with path to ilovecovidcns channel on teams}
source(file = "scripts/credentials/paths.R")
```

Exclude these variables
```{r Exclude variables vector}
exclude_variables <-
  c(
    "sample",
    "startDate",
    "endDate"
  )
```


# Read in the data

## Assessment status

### COVID_CNS_combined_website_data_clean
Read in & variable names
```{r COVID_CNS_combined_website_data_clean Read in data & variable names}
COVID_CNS_combined_website_data_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/assessment_status/COVID_CNS_combined_website_data_clean.rds")
  )

COVID_CNS_combined_website_data_clean %>%
  dim()
```

Dimensions
```{r COVID_CNS_combined_website_data_clean Dimensions}
COVID_CNS_combined_website_data_clean %>%
  colnames()
```

Select columns for joining
```{r COVID_CNS_combined_website_data_clean Select columns for joining}
COVID_CNS_combined_website_data_clean_selected <-
  COVID_CNS_combined_website_data_clean

COVID_CNS_combined_website_data_clean_selected %>%
  slice(1:5)
```


## Demographics


### als_covidcns_clean
Read in & variable names
```{r als_covidcns_clean Read in data & variable names}
als_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/als_covidcns_clean.rds")
  )

als_covidcns_clean %>%
  dim()
```

Dimensions
```{r als_covidcns_clean Dimensions}
als_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r als_covidcns_clean Select columns for joining}
als_covidcns_clean_selected <-
  als_covidcns_clean %>%
  select(
    -c("startDate",
       "endDate")
  )

als_covidcns_clean_selected %>%
  slice(1:5)
```



### cage_covidcns_clean
Read in & variable names
```{r cage_covidcns_clean Read in data & variable names}
cage_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/cage_covidcns_clean.rds")
  )

cage_covidcns_clean %>%
  dim()
```

Dimensions
```{r cage_covidcns_clean Dimensions}
cage_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r cage_covidcns_clean Select columns for joining}
cage_covidcns_clean_selected <-
  cage_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

cage_covidcns_clean_selected %>%
  slice(1:5)
```


### catatonia_covidcns_clean
Read in & variable names
```{r catatonia_covidcns_clean Read in data & variable names}
catatonia_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/catatonia_covidcns_clean.rds")
  )

catatonia_covidcns_clean %>%
  dim()
```

Dimensions
```{r catatonia_covidcns_clean Dimensions}
catatonia_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r catatonia_covidcns_clean Select columns for joining}
catatonia_covidcns_clean_selected <-
  catatonia_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

catatonia_covidcns_clean_selected %>%
  slice(1:5)
```


### cfs_covidcns_clean
Read in & variable names
```{r cfs_covidcns_clean Read in data & variable names}
cfs_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/cfs_covidcns_clean.rds")
  )

cfs_covidcns_clean %>%
  dim()
```

Dimensions
```{r cfs_covidcns_clean Dimensions}
cfs_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r cfs_covidcns_clean Select columns for joining}
cfs_covidcns_clean_selected <-
  cfs_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

cfs_covidcns_clean_selected %>%
  slice(1:5)
```



### dem_covidcns_clean
Read in & variable names
```{r dem_covidcns_clean Read in data & variable names}
dem_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/dem_covidcns_clean.rds")
  )

dem_covidcns_clean %>%
  dim()
```

Dimensions 
```{r dem_covidcns_clean Dimensions}
dem_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r dem_covidcns_clean Select columns for joining}
dem_covidcns_clean_selected <-
  dem_covidcns_clean

dem_covidcns_clean_selected %>%
  slice(1:5)
```


### impact_covidcns_clean
Read in & variable names
```{r impact_covidcns_clean Read in data & variable names}
impact_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/impact_covidcns_clean.rds")
  )

impact_covidcns_clean %>%
  dim()
```

Dimensions
```{r impact_covidcns_clean Dimensions}
impact_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r impact_covidcns_clean Select columns for joining}
impact_covidcns_clean_selected <-
  impact_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

impact_covidcns_clean_selected %>%
  slice(1:5)
```


### facial_covidcns_clean
Read in & variable names
```{r facial_covidcns_clean Read in data & variable names}
facial_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/facial_covidcns_clean.rds")
  )

facial_covidcns_clean %>%
  dim()
```

Dimensions
```{r facial_covidcns_clean Dimensions}
facial_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r facial_covidcns_clean Select columns for joining}
facial_covidcns_clean_selected <-
  facial_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

facial_covidcns_clean_selected %>%
  slice(1:5)
```


### gad7_covidcns_clean
Read in & variable names
```{r gad7_covidcns_clean Read in data & variable names}
gad7_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/gad7_covidcns_clean.rds")
  )

gad7_covidcns_clean %>%
  dim()
```

Dimensions
```{r gad7_covidcns_clean Dimensions}
gad7_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r gad7_covidcns_clean Select columns for joining}
gad7_covidcns_clean_selected <- gad7_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

gad7_covidcns_clean_selected %>%
  slice(1:5)
```



### nonmotor_covidcns_clean
Read in & variable names
```{r nonmotor_covidcns_clean Read in data & variable names}
nonmotor_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/nonmotor_covidcns_clean.rds")
  )

nonmotor_covidcns_clean %>%
  dim()
```

Dimensions
```{r nonmotor_covidcns_clean Dimensions}
nonmotor_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r nonmotor_covidcns_clean Select columns for joining}
nonmotor_covidcns_clean_selected <-
  nonmotor_covidcns_clean %>%
  select(
    -"sample",
    -"startDate"
  )

nonmotor_covidcns_clean_selected %>%
  slice(1:5)
```




### MHD
Read in & variable names
```{r mhd Read in data & variable names}
mhd <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/mhd_covidcns_clean.rds")
  )


mhd %>%
  dim()
```

Dimensions
```{r mhd Dimensions, eval=FALSE, include=FALSE}
mhd %>%
  colnames()
```

Select columns for joining
```{r mhd Select columns for joining}
mhd_selected <- mhd %>%
  select(
    -startDate,
    -endDate
  )

mhd_selected %>%
  slice(1:5)
```


### phh
Read in & variable names
```{r phh Read in data & variable names}
phh <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/phh_covidcns_clean.rds")
  )

phh %>%
  dim()
```

Dimensions
```{r phh Dimensions, eval=FALSE, include=FALSE}
phh %>%
  colnames()
```

Select columns for joining
```{r phh Select columns for joining}
phh_selected <- phh %>%
  select(
    -startDate,
    -endDate
  )

phh_selected %>%
  slice(1:5)
```


### pcl5_covidcns_clean
Read in & variable names
```{r pcl5_covidcns_clean Read in data & variable names}
pcl5_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/pcl5_covidcns_clean.rds")
  )

pcl5_covidcns_clean %>%
  dim()
```

Dimensions
```{r pcl5_covidcns_clean Dimensions}
pcl5_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r pcl5_covidcns_clean Select columns for joining}
pcl5_covidcns_clean_selected <-
  pcl5_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

pcl5_covidcns_clean_selected %>%
  slice(1:5)
```



### phq9_covidcns_clean
Read in & variable names
```{r phq9_covidcns_clean Read in data & variable names}
phq9_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/phq9_covidcns_clean.rds")
  )

phq9_covidcns_clean %>%
  dim()
```

Dimensions
```{r phq9_covidcns_clean Dimensions}
phq9_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r phq9_covidcns_clean Select columns for joining}
phq9_covidcns_clean_selected <- phq9_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )


phq9_covidcns_clean_selected %>%
  slice(1:5)
```


### smelltaste_covidcns_clean
Read in & variable names
```{r smelltaste_covidcns_clean Read in data & variable names}
smelltaste_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/smelltaste_covidcns_clean.rds")
  )

smelltaste_covidcns_clean %>%
  dim()
```

Dimensions
```{r smelltaste_covidcns_clean Dimensions}
smelltaste_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r smelltaste_covidcns_clean Select columns for joining}
smelltaste_covidcns_clean_selected <- smelltaste_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

smelltaste_covidcns_clean_selected %>%
  slice(1:5)
```


### trauma_covidcns_clean
Read in & variable names
```{r trauma_covidcns_clean Read in data & variable names}
trauma_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/trauma_covidcns_clean.rds")
  )

trauma_covidcns_clean %>%
  dim()
```

Dimensions
```{r trauma_covidcns_clean Dimensions}
trauma_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r trauma_covidcns_clean Select columns for joining}
trauma_covidcns_clean_selected <-
  trauma_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

trauma_covidcns_clean_selected %>%
  slice(1:5)
```

### updrs_covidcns_clean
Read in & variable names
```{r updrs_covidcns_clean Read in data & variable names}
updrs_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/updrs_covidcns_clean.rds")
  )

updrs_covidcns_clean %>%
  dim()
```

Dimensions
```{r updrs_covidcns_clean Dimensions}
updrs_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r updrs_covidcns_clean Select columns for joining}
updrs_covidcns_clean_selected <-
  updrs_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

updrs_covidcns_clean_selected %>%
  slice(1:5)
```


### vaccine_covidcns_clean
Read in & variable names
```{r vaccine_covidcns_clean Read in data & variable names}
vaccine_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/vaccine_covidcns_clean.rds")
  )

vaccine_covidcns_clean %>%
  dim()
```

Dimensions
```{r vaccine_covidcns_clean Dimensions}
vaccine_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r vaccine_covidcns_clean Select columns for joining}
vaccine_covidcns_clean_selected <- vaccine_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

vaccine_covidcns_clean_selected %>%
  slice(1:5)
```



## Clin Neuro


### clinical_na_inp_covidcns_clean
Read in & variable names
```{r clinical_na_inp_covidcns_clean Read in data & variable names}
clinical_na_inp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/clin_neuro/clinical_na_inp_covidcns_clean.rds")
  )

clinical_na_inp_covidcns_clean %>%
  dim()
```

Dimensions
```{r clinical_na_inp_covidcns_clean Dimensions}
clinical_na_inp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r clinical_na_inp_covidcns_clean Select columns for joining}
clinical_na_inp_covidcns_clean_selected <-
  clinical_na_inp_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

clinical_na_inp_covidcns_clean_selected %>%
  slice(1:5)
```


### clinical_na_outp_covidcns_clean
Read in & variable names
```{r clinical_na_outp_covidcns_clean Read in data & variable names}
clinical_na_outp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/clin_neuro/clinical_na_outp_covidcns_clean.rds")
  )

clinical_na_outp_covidcns_clean %>%
  dim()
```

Dimensions
```{r clinical_na_outp_covidcns_clean Dimensions}
clinical_na_outp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r clinical_na_outp_covidcns_clean Select columns for joining}
clinical_na_outp_covidcns_clean_selected <-
  clinical_na_outp_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

clinical_na_outp_covidcns_clean_selected %>%
  slice(1:5)
```



## Core Neuro


### fourat_inp_covidcns_clean
Read in & variable names
```{r fourat_inp_covidcns_clean Read in data & variable names}
fourat_inp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/core_neuro/fourat_inp_covidcns_clean.rds")
  )

fourat_inp_covidcns_clean %>%
  dim()
```

Dimensions
```{r fourat_inp_covidcns_clean Dimensions}
fourat_inp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r fourat_inp_covidcns_clean Select columns for joining}
fourat_inp_covidcns_clean_selected <-
  fourat_inp_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

fourat_inp_covidcns_clean_selected %>%
  slice(1:5)
```


### fourat_outp_covidcns_clean
Read in & variable names
```{r fourat_outp_covidcns_clean Read in data & variable names}
fourat_outp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/core_neuro/fourat_outp_covidcns_clean.rds")
  )

fourat_outp_covidcns_clean %>%
  dim()
```

Dimensions
```{r fourat_outp_covidcns_clean Dimensions}
fourat_outp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r fourat_outp_covidcns_clean Select columns for joining}
fourat_outp_covidcns_clean_selected <-
  fourat_outp_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

fourat_outp_covidcns_clean_selected %>%
  slice(1:5)
```


### gcs_inp_covidcns_clean
Read in & variable names
```{r gcs_inp_covidcns_clean Read in data & variable names}
gcs_inp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/core_neuro/gcs_inp_covidcns_clean.rds")
  )

gcs_inp_covidcns_clean %>%
  dim()
```

Dimensions
```{r gcs_inp_covidcns_clean Dimensions}
gcs_inp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r gcs_inp_covidcns_clean Select columns for joining}
gcs_inp_covidcns_clean_selected <-
  gcs_inp_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

gcs_inp_covidcns_clean_selected %>%
  slice(1:5)
```


### gcs_outp_covidcns_clean
Read in & variable names
```{r gcs_outp_covidcns_clean Read in data & variable names}
gcs_outp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/core_neuro/gcs_outp_covidcns_clean.rds")
  )

gcs_outp_covidcns_clean %>%
  dim()
```

Dimensions
```{r gcs_outp_covidcns_clean Dimensions}
gcs_outp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r gcs_outp_covidcns_clean Select columns for joining}
gcs_outp_covidcns_clean_selected <-
  gcs_outp_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

gcs_outp_covidcns_clean_selected %>%
  slice(1:5)
```


### neuro_add_inp_covidcns_clean
Read in & variable names
```{r neuro_add_inp_covidcns_clean Read in data & variable names}
neuro_add_inp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/core_neuro/neuro_add_inp_covidcns_clean.rds")
  )

neuro_add_inp_covidcns_clean %>%
  dim()
```

Dimensions
```{r neuro_add_inp_covidcns_clean Dimensions}
neuro_add_inp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r neuro_add_inp_covidcns_clean Select columns for joining}
neuro_add_inp_covidcns_clean_selected <-
  neuro_add_inp_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

neuro_add_inp_covidcns_clean_selected %>%
  slice(1:5)
```


### neuro_add_outp_covidcns_clean
Read in & variable names
```{r neuro_add_outp_covidcns_clean Read in data & variable names}
neuro_add_outp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/core_neuro/neuro_add_outp_covidcns_clean.rds")
  )

neuro_add_outp_covidcns_clean %>%
  dim()
```

Dimensions
```{r neuro_add_outp_covidcns_clean Dimensions}
neuro_add_outp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r neuro_add_outp_covidcns_clean Select columns for joining}
neuro_add_outp_covidcns_clean_selected <-
  neuro_add_outp_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

neuro_add_outp_covidcns_clean_selected %>%
  slice(1:5)
```


### nis_inp_covidcns_clean
Read in & variable names
```{r nis_inp_covidcns_clean Read in data & variable names}
nis_inp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/core_neuro/nis_inp_covidcns_clean.rds")
  )

nis_inp_covidcns_clean %>%
  dim()
```

Dimensions
```{r nis_inp_covidcns_clean Dimensions}
nis_inp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r nis_inp_covidcns_clean Select columns for joining}
nis_inp_covidcns_clean_selected <-
  nis_inp_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

nis_inp_covidcns_clean_selected %>%
  slice(1:5)
```



### nis_outp_covidcns_clean
Read in & variable names
```{r nis_outp_covidcns_clean Read in data & variable names}
nis_outp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/core_neuro/nis_outp_covidcns_clean.rds")
  )

nis_outp_covidcns_clean %>%
  dim()
```

Dimensions
```{r nis_outp_covidcns_clean Dimensions}
nis_outp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r nis_outp_covidcns_clean Select columns for joining}
nis_outp_covidcns_clean_selected <-
  nis_outp_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

nis_outp_covidcns_clean_selected %>%
  slice(1:5)
```



## mh_case_report


### psy_neuro_scr_covidcns_clean
Read in & variable names
```{r psy_neuro_scr_covidcns_clean Read in data & variable names}
psy_neuro_scr_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/mh_case_report/psy_neuro_scr_covidcns_clean.rds")
  )

psy_neuro_scr_covidcns_clean %>%
  dim()
```

Dimensions
```{r psy_neuro_scr_covidcns_clean Dimensions}
psy_neuro_scr_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r psy_neuro_scr_covidcns_clean Select columns for joining}
psy_neuro_scr_covidcns_clean_selected <-
  psy_neuro_scr_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

psy_neuro_scr_covidcns_clean_selected %>%
  slice(1:5)
```


### moca_inp_covidcns_clean
Read in & variable names
```{r moca_inp_covidcns_clean Read in data & variable names}
moca_inp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/mh_case_report/moca_inp_covidcns_clean.rds")
  )

moca_inp_covidcns_clean %>%
  dim()
```

Dimensions
```{r moca_inp_covidcns_clean Dimensions}
moca_inp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r moca_inp_covidcns_clean Select columns for joining}
moca_inp_covidcns_clean_selected <-
  moca_inp_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

moca_inp_covidcns_clean_selected %>%
  slice(1:5)
```


## moca

### cognitron_outp_covidcns_clean
Read in & variable names
```{r cognitron_outp_covidcns_clean Read in data & variable names}
cognitron_outp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/moca/cognitron_outp_covidcns_clean.rds")
  )

cognitron_outp_covidcns_clean %>%
  dim()
```

Dimensions
```{r cognitron_outp_covidcns_clean Dimensions}
cognitron_outp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r cognitron_outp_covidcns_clean Select columns for joining}
cognitron_outp_covidcns_clean_selected <-
  cognitron_outp_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

cognitron_outp_covidcns_clean_selected %>%
  slice(1:5)
```


### moca_outp_covidcns_clean
Read in & variable names
```{r moca_outp_covidcns_clean Read in data & variable names}
moca_outp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/moca/moca_outp_covidcns_clean.rds")
  )

moca_outp_covidcns_clean %>%
  dim()
```

Dimensions
```{r moca_outp_covidcns_clean Dimensions}
moca_outp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r moca_outp_covidcns_clean Select columns for joining}
moca_outp_covidcns_clean_selected <-
  moca_outp_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

moca_outp_covidcns_clean_selected %>%
  slice(1:5)
```


## ncrf


## Module 1


### ncrf1_admission_covidcns_clean
Read in & variable names
```{r ncrf1_admission_covidcns_clean Read in data & variable names}
ncrf1_admission_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_admission_covidcns_clean.rds")
  )

ncrf1_admission_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf1_admission_covidcns_clean Dimensions}
ncrf1_admission_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf1_admission_covidcns_clean Select columns for joining}
ncrf1_admission_covidcns_clean_selected <- 
  ncrf1_admission_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

ncrf1_admission_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf1_care_covidcns_clean
Read in & variable names
```{r ncrf1_care_covidcns_clean Read in data & variable names}
ncrf1_care_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_care_covidcns_clean.rds")
  )

ncrf1_care_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf1_care_covidcns_clean Dimensions}
ncrf1_care_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf1_care_covidcns_clean Select columns for joining}
ncrf1_care_covidcns_clean_selected <-
  ncrf1_care_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

ncrf1_care_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf1_cic_covidcns_clean
Read in & variable names
```{r ncrf1_cic_covidcns_clean Read in data & variable names}
ncrf1_cic_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_cic_covidcns_clean.rds")
  )

ncrf1_cic_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf1_cic_covidcns_clean Dimensions}
ncrf1_cic_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf1_cic_covidcns_clean Select columns for joining}
ncrf1_cic_covidcns_clean_selected <-
  ncrf1_cic_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

ncrf1_cic_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf1_comorbid_covidcns_clean
Read in & variable names
```{r ncrf1_comorbid_covidcns_clean Read in data & variable names}
ncrf1_comorbid_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_comorbid_covidcns_clean.rds")
  )

ncrf1_comorbid_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf1_comorbid_covidcns_clean Dimensions}
ncrf1_comorbid_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf1_comorbid_covidcns_clean Select columns for joining}
ncrf1_comorbid_covidcns_clean_selected <-
  ncrf1_comorbid_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

ncrf1_comorbid_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf1_dem_covidcns_clean
Read in & variable names
```{r ncrf1_dem_covidcns_clean Read in data & variable names}
ncrf1_dem_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_dem_covidcns_clean.rds")
  )

ncrf1_dem_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf1_dem_covidcns_clean Dimensions}
ncrf1_dem_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf1_dem_covidcns_clean Select columns for joining}
ncrf1_dem_covidcns_clean_selected <-
  ncrf1_dem_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

ncrf1_dem_covidcns_clean_selected %>%
  slice(1:5)
```



### ncrf1_lab_covidcns_clean
Read in & variable names
```{r ncrf1_lab_covidcns_clean Read in data & variable names}
ncrf1_lab_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_lab_covidcns_clean.rds")
  )

ncrf1_lab_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf1_lab_covidcns_clean Dimensions}
ncrf1_lab_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf1_lab_covidcns_clean Select columns for joining}
ncrf1_lab_covidcns_clean_selected <-
  ncrf1_lab_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

ncrf1_lab_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf1_newsymp_covidcns_clean
Read in & variable names
```{r ncrf1_newsymp_covidcns_clean Read in data & variable names}
ncrf1_newsymp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_newsymp_covidcns_clean.rds")
  )

ncrf1_newsymp_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf1_newsymp_covidcns_clean Dimensions}
ncrf1_newsymp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf1_newsymp_covidcns_clean Select columns for joining}
ncrf1_newsymp_covidcns_clean_selected <-
  ncrf1_newsymp_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

ncrf1_newsymp_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf1_pre_med_covidcns_clean
Read in & variable names
```{r ncrf1_pre_med_covidcns_clean Read in data & variable names}
ncrf1_pre_med_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_pre_med_covidcns_clean.rds")
  )

ncrf1_pre_med_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf1_pre_med_covidcns_clean Dimensions}
ncrf1_pre_med_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf1_pre_med_covidcns_clean Select columns for joining}
ncrf1_pre_med_covidcns_clean_selected <-
  ncrf1_pre_med_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

ncrf1_pre_med_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf1_vital_covidcns_clean
Read in & variable names
```{r ncrf1_vital_covidcns_clean Read in data & variable names}
ncrf1_vital_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_vital_covidcns_clean.rds")
  )

ncrf1_vital_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf1_vital_covidcns_clean Dimensions}
ncrf1_vital_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf1_vital_covidcns_clean Select columns for joining}
ncrf1_vital_covidcns_clean_selected <-
  ncrf1_vital_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

ncrf1_vital_covidcns_clean_selected %>%
  slice(1:5)
```



## Module 2

  

### ncrf2_care_covidcns_clean
Read in & variable names
```{r ncrf2_care_covidcns_clean Read in data & variable names}
ncrf2_care_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf2_care_covidcns_clean.rds")
  )

ncrf2_care_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf2_care_covidcns_clean Dimensions}
ncrf2_care_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf2_care_covidcns_clean Select columns for joining}
ncrf2_care_covidcns_clean_selected <-
  ncrf2_care_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

ncrf2_care_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf2_lab_covidcns_clean
Read in & variable names
```{r ncrf2_lab_covidcns_clean Read in data & variable names}
ncrf2_lab_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf2_lab_covidcns_clean.rds")
  )

ncrf2_lab_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf2_lab_covidcns_clean Dimensions}
ncrf2_lab_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf2_lab_covidcns_clean Select columns for joining}
ncrf2_lab_covidcns_clean_selected <-
  ncrf2_lab_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

ncrf2_lab_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf2_med_covidcns_clean
Read in & variable names
```{r ncrf2_med_covidcns_clean Read in data & variable names}
ncrf2_med_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf2_med_covidcns_clean.rds")
  )

ncrf2_med_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf2_med_covidcns_clean Dimensions}
ncrf2_med_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf2_med_covidcns_clean Select columns for joining}
ncrf2_med_covidcns_clean_selected <-
  ncrf2_med_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

ncrf2_med_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf2_newsymp_covidcns_clean
Read in & variable names
```{r ncrf2_newsymp_covidcns_clean Read in data & variable names}
ncrf2_newsymp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf2_newsymp_covidcns_clean.rds")
  )

ncrf2_newsymp_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf2_newsymp_covidcns_clean Dimensions}
ncrf2_newsymp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf2_newsymp_covidcns_clean Select columns for joining}
ncrf2_newsymp_covidcns_clean_selected <-
  ncrf2_newsymp_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

ncrf2_newsymp_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf2_vital_covidcns_clean
Read in & variable names
```{r ncrf2_vital_covidcns_clean Read in data & variable names}
ncrf2_vital_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf2_vital_covidcns_clean.rds")
  )

ncrf2_vital_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf2_vital_covidcns_clean Dimensions}
ncrf2_vital_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf2_vital_covidcns_clean Select columns for joining}
ncrf2_vital_covidcns_clean_selected <-
  ncrf2_vital_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

ncrf2_vital_covidcns_clean_selected %>%
  slice(1:5)
```



## Module 3



### ncrf3_compli_covidcns_clean
Read in & variable names
```{r ncrf3_compli_covidcns_clean Read in data & variable names}
ncrf3_compli_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf3_compli_covidcns_clean.rds")
  )

ncrf3_compli_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf3_compli_covidcns_clean Dimensions}
ncrf3_compli_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf3_compli_covidcns_clean Select columns for joining}
ncrf3_compli_covidcns_clean_selected <-
  ncrf3_compli_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

ncrf3_compli_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf3_diag_covidcns_clean
Read in & variable names
```{r ncrf3_diag_covidcns_clean Read in data & variable names}
ncrf3_diag_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf3_diag_covidcns_clean.rds")
  )

ncrf3_diag_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf3_diag_covidcns_clean Dimensions}
ncrf3_diag_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf3_diag_covidcns_clean Select columns for joining}
ncrf3_diag_covidcns_clean_selected <-
  ncrf3_diag_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

ncrf3_diag_covidcns_clean_selected %>%
  slice(1:5)
```


# Cognitron

### cognitron_scores_and_demographics
Read in & variable names
```{r cognitron_scores_and_demographics Read in data & variable names}
cognitron_scores_and_demographics <-
  readRDS(
    paste0(ilovecovidcns, "/data/cognitron/scores/cognitron_scores_and_demographics.rds")
  )

cognitron_scores_and_demographics %>%
  dim()
```

Dimensions
```{r cognitron_scores_and_demographics Dimensions}
cognitron_scores_and_demographics %>%
  colnames()
```

Select columns for joining
```{r cognitron_scores_and_demographics Select columns for joining}
cognitron_scores_and_demographics_selected <- cognitron_scores_and_demographics %>%
  dplyr::rename(
    "ID" = "user_id"
  )

cognitron_scores_and_demographics_selected %>%
  slice(1:5)
```


### cognitron DfE_composite_scores
Read in & variable names
```{r DfE_composite_scores Read in data & variable names}
DfE_composite_scores <-
  readRDS(
    paste0(ilovecovidcns, "/data/cognitron/scores/DfE_composite_scores.rds")
  )

DfE_composite_scores %>%
  dim()
```

Dimensions
```{r DfE_composite_scores Dimensions}
DfE_composite_scores %>%
  colnames()
```

Select columns for joining
```{r DfE_composite_scores Select columns for joining}
DfE_composite_scores_selected <- DfE_composite_scores %>%
  dplyr::rename(
    "ID" = "user_id"
  )

DfE_composite_scores_selected %>%
  slice(1:5)
```


### cognitron DfE_task_scores
Read in & variable names
```{r DfE_task_scores Read in data & variable names}
DfE_task_scores <-
  readRDS(
    paste0(ilovecovidcns, "/data/cognitron/scores/DfE_task_scores.rds")
  )

DfE_task_scores %>%
  dim()
```

Dimensions
```{r DfE_task_scores Dimensions}
colnames(DfE_task_scores) <- paste(colnames(DfE_task_scores), "dfe", sep = "_")

DfE_task_scores %>%
  colnames()
```

Select columns for joining
```{r DfE_task_scores Select columns for joining}
DfE_task_scores_selected <- DfE_task_scores %>%
  dplyr::rename(
    "ID" = "user_id_dfe"
  )

DfE_task_scores_selected %>%
  slice(1:5)
```




# Joining process

## List of tibbles to join, not including website data
```{r List of tibbles to join}
tibble_list <- 
  list(
    als_covidcns_clean_selected,
    cage_covidcns_clean_selected,
    catatonia_covidcns_clean_selected,
    cfs_covidcns_clean_selected,
    dem_covidcns_clean_selected,
    impact_covidcns_clean_selected,
    facial_covidcns_clean_selected,
    gad7_covidcns_clean_selected,
    nonmotor_covidcns_clean_selected,
    mhd_selected,
    phh_selected,
    pcl5_covidcns_clean_selected,
    phq9_covidcns_clean_selected,
    smelltaste_covidcns_clean_selected,
    trauma_covidcns_clean_selected,
    updrs_covidcns_clean_selected,
    vaccine_covidcns_clean_selected,
    # clin_neuro
    clinical_na_inp_covidcns_clean_selected,
    clinical_na_outp_covidcns_clean_selected,
    # core_neuro
    fourat_inp_covidcns_clean_selected,
    fourat_outp_covidcns_clean_selected,
    gcs_inp_covidcns_clean_selected,
    gcs_outp_covidcns_clean_selected,
    neuro_add_inp_covidcns_clean_selected,
    neuro_add_outp_covidcns_clean_selected,
    nis_inp_covidcns_clean_selected,
    nis_outp_covidcns_clean_selected,
    # mh_case_report
    psy_neuro_scr_covidcns_clean_selected,
    moca_inp_covidcns_clean_selected,
    # moca
    cognitron_outp_covidcns_clean_selected,
    moca_outp_covidcns_clean_selected,
    # neuro_case_report
    ncrf2_med_covidcns_clean_selected,
    # ncrf1
    ncrf1_admission_covidcns_clean_selected,
    ncrf1_care_covidcns_clean_selected,
    ncrf1_cic_covidcns_clean_selected,
    ncrf1_comorbid_covidcns_clean_selected,
    ncrf1_dem_covidcns_clean_selected,
    ncrf1_lab_covidcns_clean_selected,
    ncrf1_newsymp_covidcns_clean_selected,
    ncrf1_pre_med_covidcns_clean_selected,
    ncrf1_vital_covidcns_clean_selected,
    # ncrf2
    ncrf2_care_covidcns_clean_selected,
    ncrf2_lab_covidcns_clean_selected,
    ncrf2_med_covidcns_clean_selected,
    ncrf2_newsymp_covidcns_clean_selected,
    ncrf2_vital_covidcns_clean_selected,
    # ncrf3    
    ncrf3_compli_covidcns_clean_selected,
    ncrf3_diag_covidcns_clean_selected
    )
```

Joining of demographics and questionnaires, not including website data
```{r Joining of demographics and questionnaires}
qualtrics_data_joined <- 
  plyr::join_all(
    dfs =  tibble_list,
    by = c("ID"),
    type = "full"
    )
```


# Change/remove Incorrect IDs from Qualtrics

Change IDs with newline char
```{r}
qualtrics_data_joined$ID[qualtrics_data_joined$ID == "\nCNS02002"] <- "CNS02002"
qualtrics_data_joined$ID[qualtrics_data_joined$ID == "\nCNS01004"] <- "CNS01004"
```


Joining of qualtrics and cognitron, not including website data
```{r Joining of qualtrics and cognitron}
qualtrics_data_joined <- 
  plyr::join_all(
    dfs = list(qualtrics_data_joined,
               cognitron_scores_and_demographics_selected,
               DfE_composite_scores_selected,
               DfE_task_scores_selected),
    by = c("ID"),
    type = "full"
    )
```

Import swapping IDs excel sheet and remove problem IDs
```{r Remove swapping ids}
# Read in excel sheet of IDs to change as data frame
swapped_ids <- readxl::read_xlsx(path = paste0(ilovecovidcns, "/data_raw/ids/incorrect_ids.xlsx"),
                                 sheet = "Sheet1")

# Remove ids with issues
qualtrics_data_joined <- qualtrics_data_joined %>%
  filter(!ID %in% swapped_ids$incorrect_ID)
```

# Coalesce demographics

Coalesce age and sex demographic variables from baseline and ncrf dem
```{r Coalesce age sex dem}
qualtrics_data_joined <- qualtrics_data_joined %>%
  mutate(
    dem.dob_age = coalesce(
      dem.dob_age,
      ncrf1_dem.dob_age),
    
    dem.sex_at_birth = coalesce(
      dem.sex_at_birth,
      ncrf1_dem.sex_at_birth),
    
    dem.sex_at_birth_numeric = coalesce(
      dem.sex_at_birth_numeric,
      ncrf1_dem.sex_at_birth_numeric),
    
    dem.simplified_ethnicity = coalesce(
      dem.simplified_ethnicity,
      ncrf1_dem.simplified_ethnicity)
  )
```

# Add website data

Joining of website data
```{r Joining of website data}
data_joined_1 <- 
  plyr::join_all(
    dfs =  list(COVID_CNS_combined_website_data_clean_selected, qualtrics_data_joined),
    by = c("ID"),
    type = "full"
    )
```



```{r}
qualtrics_data_joined %>%
  select(
   dem.dob_age,
   dem.sex_at_birth,
   dem.simplified_ethnicity
  ) %>%
  tbl_summary()
```


# Add case definitions

Import case definitions data
```{r Import case defs}
case_def_dat <- readxl::read_xlsx(
  path = paste0(ilovecovidcns, "/data_raw/case_definitions/Final Case Definitions.xlsx"),
  sheet = "Sheet1")

case_def_dat <- case_def_dat %>%
  select(
    ID,
    `diagnostic_group` = `Diagnostic Group`,
    `diagnosis` = `Diagnosis`
  )
```

Joining of case definitions data
```{r Joining of case defs}
data_joined <- 
  plyr::join_all(
    dfs =  list(data_joined_1, case_def_dat),
    by = c("ID"),
    type = "full"
    )
```

Check dimensions of joined tibble
```{r Check dimensions of joined tibble}
data_joined %>%
  dim()
```

Check for duplicated columns
```{r Check for duplicated columns}
data_joined %>%
  colnames() %>%
  duplicated() %>%
  summary()
```


# Select Columns

Select columns for data extraction
```{r matching Select columns}
data_export_matching <- data_joined %>%
  select(
      "ID",
      
      # Age
      "dem.dob_age",
      "dem.how_old_are_you_now.txt",
      
      # Sex
      "dem.sex_at_birth",
      "dem.sex_at_birth_numeric",
      
      # Language
      "dem.is_english_your_first_language",
      "dem.what_is_your_first_language.txt",
      "dem.what_is_your_first_language_numeric",
      "dem.is_english_your_first_language_numeric",
      
      # Education
      "dem.highest_education",
      "dem.highest_education_numeric",
      
      # impact
      "impact.fulltime_employed",
      "impact.unemployed",
      "impact.stayathome_parent_or_carer",
      "impact.contract_or_freelance_work",
      "impact.receiving_state_income",
      "impact.student_",
      "impact.prefer_not_to_say",
      "impact.parttime_employed",
      "impact.zerohours_contract",
      "impact.selfemployed",
      "impact.small_business_owner",
      "impact.retired",
      "impact.student_.1"
      )


data_export_matching %>%
  slice(1:5)
```

Select columns for neuro data extraction
```{r matching Select columns}
data_export_glynn_dem <- qualtrics_data_joined %>%
  select(
      "ID",
      "startDate",
      "endDate",
      
      # Age
      "dem.dob_age",
      
      # Sex
      "dem.sex_at_birth",
      
      # Ethnicity
      "dem.nhs_ethnicity",
      "dem.simplified_ethnicity",
      
      # Language
      "dem.is_english_your_first_language",
      
      # Education
      "dem.highest_education",
      
      # Employment
      "impact.current_employment_status"
      )

data_export_neuro_inp <- 
  plyr::join_all(
    dfs =  list(
      clinical_na_inp_covidcns_clean_selected,
      nis_inp_covidcns_clean_selected,
      neuro_add_inp_covidcns_clean_selected
      ),
    by = c("ID"),
    type = "full"
    )

data_export_neuro_outp <- 
  plyr::join_all(
    dfs =  list(
      clinical_na_outp_covidcns_clean_selected,
      nis_outp_covidcns_clean_selected,
      neuro_add_outp_covidcns_clean_selected
      ),
    by = c("ID"),
    type = "full"
    )
```


Join neuro data to demographics
```{r Join to demographics inpatient}
data_export_glynn_inp <- 
  plyr::join_all(
    dfs =  list(
      data_export_glynn_dem,
      data_export_neuro_inp
      ),
    by = c("ID"),
    type = "right"
    )

data_export_glynn_inp %>%
  slice(1:5)
```

Join neuro data to demographics
```{r Join to demographics outpatient}
data_export_glynn_outp <- 
  plyr::join_all(
    dfs =  list(
      data_export_glynn_dem,
      data_export_neuro_outp
      ),
    by = c("ID"),
    type = "right"
    )


data_export_glynn_outp %>%
  slice(1:5)
```


# Save joined data set
```{r matching Save joint data set}
saveRDS(
  object = data_export_matching, 
  file = paste0(ilovecovidcns, "/data/joined/covidcns_matching.rds")
)
```

```{r matching Save joint data set sharing}
saveRDS(
  object = data_export_matching, 
  file = paste0(ilovecovidcns, "/data_sharing/matching/covidcns_matching.rds")
)
```


# Save joined data set
```{r glynn Save joint data set}
saveRDS(
  object = data_export_glynn_inp, 
  file = paste0(ilovecovidcns, "/data_sharing/glynn/glynn_neuro_inp.rds")
)
saveRDS(
  object = data_export_glynn_outp, 
  file = paste0(ilovecovidcns, "/data_sharing/glynn/glynn_neuro_outp.rds")
)
```


# Save joined data set
```{r greta Save joint data set}
saveRDS(
  object = data_joined, 
  file = paste0(ilovecovidcns, "/data/joined/covidcns_greta.rds")
)
```

```{r greta Save joint data set sharing}
saveRDS(
  object = data_joined, 
  file = paste0(ilovecovidcns, "/data_sharing/liverpool/covidcns-cog-analysis/data_raw/covidcns_greta.rds")
)
```