---
title: "Joining script"
author: "Christopher Huebel"
date: "20/02/2022"
output: html_document
---

This R markdown:
1) Joins COVID-CNS questionnaires together
2) Creates on rds file with matching variables
3) One rds file for the biomarker work
4) One rds file for Greta's work

# Set up

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = "scripts/functions/add_numeric.R")
source(file = "scripts/functions/remove_duplicates.R")
source(file = "scripts/functions/sumscores.R")
source(file = "scripts/functions/package_check.R")
source(file = "scripts/functions/imp_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c(
  "summarytools",
  "sjlabelled",
  "gtsummary",
  "tidyverse"
  )

package_check(packages)
```

Retrieve the recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date = Sys.Date()
date
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in file with path to ilovecovidcns channel on teams}
source(file = "scripts/credentials/paths.R")
```

Exclude these variables
```{r Exclude variables vector}
exclude_variables <-
  c(
    "sample",
    "startDate",
    "endDate"
  )
```


# Read in the data

## Assessment status

### COVID_CNS_combined_website_data_clean
Read in & variable names
```{r COVID_CNS_combined_website_data_clean Read in data & variable names}
COVID_CNS_combined_website_data_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/assessment_status/COVID_CNS_combined_website_data_clean.rds")
  )

COVID_CNS_combined_website_data_clean %>%
  dim()
```

Dimensions
```{r COVID_CNS_combined_website_data_clean Dimensions}
COVID_CNS_combined_website_data_clean %>%
  colnames()
```

Select columns for joining
```{r COVID_CNS_combined_website_data_clean Select columns for joining}
COVID_CNS_combined_website_data_clean_selected <-
  COVID_CNS_combined_website_data_clean

COVID_CNS_combined_website_data_clean_selected %>%
  slice(1:5)
```


## Demographics


### als_covidcns_clean
Read in & variable names
```{r als_covidcns_clean Read in data & variable names}
als_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/als_covidcns_clean.rds")
  )

als_covidcns_clean %>%
  dim()
```

Dimensions
```{r als_covidcns_clean Dimensions}
als_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r als_covidcns_clean Select columns for joining}
als_covidcns_clean_selected <-
  als_covidcns_clean %>%
  select(
    -c("startDate",
       "endDate")
  )

als_covidcns_clean_selected %>%
  slice(1:5)
```



### cage_covidcns_clean
Read in & variable names
```{r cage_covidcns_clean Read in data & variable names}
cage_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/cage_covidcns_clean.rds")
  )

cage_covidcns_clean %>%
  dim()
```

Dimensions
```{r cage_covidcns_clean Dimensions}
cage_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r cage_covidcns_clean Select columns for joining}
cage_covidcns_clean_selected <-
  cage_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

cage_covidcns_clean_selected %>%
  slice(1:5)
```


### catatonia_covidcns_clean
Read in & variable names
```{r catatonia_covidcns_clean Read in data & variable names}
catatonia_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/catatonia_covidcns_clean.rds")
  )

catatonia_covidcns_clean %>%
  dim()
```

Dimensions
```{r catatonia_covidcns_clean Dimensions}
catatonia_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r catatonia_covidcns_clean Select columns for joining}
catatonia_covidcns_clean_selected <-
  catatonia_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

catatonia_covidcns_clean_selected %>%
  slice(1:5)
```


### cfs_covidcns_clean
Read in & variable names
```{r cfs_covidcns_clean Read in data & variable names}
cfs_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/cfs_covidcns_clean.rds")
  )

cfs_covidcns_clean %>%
  dim()
```

Dimensions
```{r cfs_covidcns_clean Dimensions}
cfs_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r cfs_covidcns_clean Select columns for joining}
cfs_covidcns_clean_selected <-
  cfs_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

cfs_covidcns_clean_selected %>%
  slice(1:5)
```



### dem_covidcns_clean
Read in & variable names
```{r dem_covidcns_clean Read in data & variable names}
dem_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/dem_covidcns_clean.rds")
  )

dem_covidcns_clean %>%
  dim()
```

Dimensions 
```{r dem_covidcns_clean Dimensions}
dem_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r dem_covidcns_clean Select columns for joining}
dem_covidcns_clean_selected <-
  dem_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

dem_covidcns_clean_selected %>%
  slice(1:5)
```


### impact_covidcns_clean
Read in & variable names
```{r impact_covidcns_clean Read in data & variable names}
impact_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/impact_covidcns_clean.rds")
  )

impact_covidcns_clean %>%
  dim()
```

Dimensions
```{r impact_covidcns_clean Dimensions}
impact_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r impact_covidcns_clean Select columns for joining}
impact_covidcns_clean_selected <-
  impact_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

impact_covidcns_clean_selected %>%
  slice(1:5)
```


### facial_covidcns_clean
Read in & variable names
```{r facial_covidcns_clean Read in data & variable names}
facial_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/facial_covidcns_clean.rds")
  )

facial_covidcns_clean %>%
  dim()
```

Dimensions
```{r facial_covidcns_clean Dimensions}
facial_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r facial_covidcns_clean Select columns for joining}
facial_covidcns_clean_selected <-
  facial_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

facial_covidcns_clean_selected %>%
  slice(1:5)
```


### gad7_covidcns_clean
Read in & variable names
```{r gad7_covidcns_clean Read in data & variable names}
gad7_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/gad7_covidcns_clean.rds")
  )

gad7_covidcns_clean %>%
  dim()
```

Dimensions
```{r gad7_covidcns_clean Dimensions}
gad7_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r gad7_covidcns_clean Select columns for joining}
gad7_covidcns_clean_selected <- gad7_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

gad7_covidcns_clean_selected %>%
  slice(1:5)
```



### nis_outp_covidcns_clean
Read in & variable names
```{r nis_outp_covidcns_clean Read in data & variable names}
nis_outp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/core_neuro/nis_outp_covidcns_clean.rds")
  )

nis_outp_covidcns_clean %>%
  dim()
```

Dimensions
```{r nis_outp_covidcns_clean Dimensions}
nis_outp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r nis_outp_covidcns_clean Select columns for joining}
nis_outp_covidcns_clean_selected <-
  nis_outp_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

nis_outp_covidcns_clean_selected %>%
  slice(1:5)
```


### nonmotor_covidcns_clean
Read in & variable names
```{r nonmotor_covidcns_clean Read in data & variable names}
nonmotor_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/nonmotor_covidcns_clean.rds")
  )

nonmotor_covidcns_clean %>%
  dim()
```

Dimensions
```{r nonmotor_covidcns_clean Dimensions}
nonmotor_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r nonmotor_covidcns_clean Select columns for joining}
nonmotor_covidcns_clean_selected <-
  nonmotor_covidcns_clean %>%
  select(
    -"sample",
    -"startDate"
  )

nonmotor_covidcns_clean_selected %>%
  slice(1:5)
```




### MHD
Read in & variable names
```{r mhd Read in data & variable names}
mhd <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/mhd_covidcns_clean.rds")
  )


mhd %>%
  dim()
```

Dimensions
```{r mhd Dimensions, eval=FALSE, include=FALSE}
mhd %>%
  colnames()
```

Select columns for joining
```{r mhd Select columns for joining}
mhd_selected <- mhd %>%
  select(
    -startDate,
    -endDate
  )

mhd_selected %>%
  slice(1:5)
```


### phh
Read in & variable names
```{r phh Read in data & variable names}
phh <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/phh_covidcns_clean.rds")
  )

phh %>%
  dim()
```

Dimensions
```{r phh Dimensions, eval=FALSE, include=FALSE}
phh %>%
  colnames()
```

Select columns for joining
```{r phh Select columns for joining}
phh_selected <- phh %>%
  select(
    -all_of(exclude_variables)
  )

phh_selected %>%
  slice(1:5)
```


### pcl5_covidcns_clean
Read in & variable names
```{r pcl5_covidcns_clean Read in data & variable names}
pcl5_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/pcl5_covidcns_clean.rds")
  )

pcl5_covidcns_clean %>%
  dim()
```

Dimensions
```{r pcl5_covidcns_clean Dimensions}
pcl5_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r pcl5_covidcns_clean Select columns for joining}
pcl5_covidcns_clean_selected <-
  pcl5_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

pcl5_covidcns_clean_selected %>%
  slice(1:5)
```



### phq9_covidcns_clean
Read in & variable names
```{r phq9_covidcns_clean Read in data & variable names}
phq9_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/phq9_covidcns_clean.rds")
  )

phq9_covidcns_clean %>%
  dim()
```

Dimensions
```{r phq9_covidcns_clean Dimensions}
phq9_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r phq9_covidcns_clean Select columns for joining}
phq9_covidcns_clean_selected <- phq9_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )


phq9_covidcns_clean_selected %>%
  slice(1:5)
```


### smelltaste_covidcns_clean
Read in & variable names
```{r smelltaste_covidcns_clean Read in data & variable names}
smelltaste_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/smelltaste_covidcns_clean.rds")
  )

smelltaste_covidcns_clean %>%
  dim()
```

Dimensions
```{r smelltaste_covidcns_clean Dimensions}
smelltaste_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r smelltaste_covidcns_clean Select columns for joining}
smelltaste_covidcns_clean_selected <- smelltaste_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

smelltaste_covidcns_clean_selected %>%
  slice(1:5)
```


### trauma_covidcns_clean
Read in & variable names
```{r trauma_covidcns_clean Read in data & variable names}
trauma_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/trauma_covidcns_clean.rds")
  )

trauma_covidcns_clean %>%
  dim()
```

Dimensions
```{r trauma_covidcns_clean Dimensions}
trauma_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r trauma_covidcns_clean Select columns for joining}
trauma_covidcns_clean_selected <-
  trauma_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

trauma_covidcns_clean_selected %>%
  slice(1:5)
```

### updrs_covidcns_clean
Read in & variable names
```{r updrs_covidcns_clean Read in data & variable names}
updrs_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/updrs_covidcns_clean.rds")
  )

updrs_covidcns_clean %>%
  dim()
```

Dimensions
```{r updrs_covidcns_clean Dimensions}
updrs_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r updrs_covidcns_clean Select columns for joining}
updrs_covidcns_clean_selected <-
  updrs_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

updrs_covidcns_clean_selected %>%
  slice(1:5)
```


### vaccine_covidcns_clean
Read in & variable names
```{r vaccine_covidcns_clean Read in data & variable names}
vaccine_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/vaccine_covidcns_clean.rds")
  )

vaccine_covidcns_clean %>%
  dim()
```

Dimensions
```{r vaccine_covidcns_clean Dimensions}
vaccine_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r vaccine_covidcns_clean Select columns for joining}
vaccine_covidcns_clean_selected <- vaccine_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

vaccine_covidcns_clean_selected %>%
  slice(1:5)
```


## Core Neuro

### fourat_outp_covidcns_clean
Read in & variable names
```{r fourat_outp_covidcns_clean Read in data & variable names}
fourat_outp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/core_neuro/fourat_outp_covidcns_clean.rds")
  )

fourat_outp_covidcns_clean %>%
  dim()
```

Dimensions
```{r fourat_outp_covidcns_clean Dimensions}
fourat_outp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r fourat_outp_covidcns_clean Select columns for joining}
fourat_outp_covidcns_clean_selected <-
  fourat_outp_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

fourat_outp_covidcns_clean_selected %>%
  slice(1:5)
```


## mh_case_report

### moca_inp_covidcns_clean
Read in & variable names
```{r moca_inp_covidcns_clean Read in data & variable names}
moca_inp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/mh_case_report/moca_inp_covidcns_clean.rds")
  )

moca_inp_covidcns_clean %>%
  dim()
```

Dimensions
```{r moca_inp_covidcns_clean Dimensions}
moca_inp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r moca_inp_covidcns_clean Select columns for joining}
moca_inp_covidcns_clean_selected <-
  moca_inp_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

moca_inp_covidcns_clean_selected %>%
  slice(1:5)
```


## moca

### cognitron_outp_covidcns_clean
Read in & variable names
```{r cognitron_outp_covidcns_clean Read in data & variable names}
cognitron_outp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/moca/cognitron_outp_covidcns_clean.rds")
  )

cognitron_outp_covidcns_clean %>%
  dim()
```

Dimensions
```{r cognitron_outp_covidcns_clean Dimensions}
cognitron_outp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r cognitron_outp_covidcns_clean Select columns for joining}
cognitron_outp_covidcns_clean_selected <-
  cognitron_outp_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

cognitron_outp_covidcns_clean_selected %>%
  slice(1:5)
```


### moca_outp_covidcns_clean
Read in & variable names
```{r moca_outp_covidcns_clean Read in data & variable names}
moca_outp_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/moca/moca_outp_covidcns_clean.rds")
  )

moca_outp_covidcns_clean %>%
  dim()
```

Dimensions
```{r moca_outp_covidcns_clean Dimensions}
moca_outp_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r moca_outp_covidcns_clean Select columns for joining}
moca_outp_covidcns_clean_selected <-
  moca_outp_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

moca_outp_covidcns_clean_selected %>%
  slice(1:5)
```


## ncrf


### ncrf2_med_covidcns_clean
Read in & variable names
```{r ncrf2_med_covidcns_clean Read in data & variable names}
ncrf2_med_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf2_med_covidcns_clean.rds")
  )

ncrf2_med_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf2_med_covidcns_clean Dimensions}
ncrf2_med_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf2_med_covidcns_clean Select columns for joining}
ncrf2_med_covidcns_clean_selected <-
  ncrf2_med_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

ncrf2_med_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf1_admission_covidcns_clean
Read in & variable names
```{r ncrf1_admission_covidcns_clean Read in data & variable names}
ncrf1_admission_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_admission_covidcns_clean.rds")
  )

ncrf1_admission_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf1_admission_covidcns_clean Dimensions}
ncrf1_admission_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf1_admission_covidcns_clean Select columns for joining}
ncrf1_admission_covidcns_clean_selected <- 
  ncrf1_admission_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

ncrf1_admission_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf1_care_covidcns_clean
Read in & variable names
```{r ncrf1_care_covidcns_clean Read in data & variable names}
ncrf1_care_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_care_covidcns_clean.rds")
  )

ncrf1_care_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf1_care_covidcns_clean Dimensions}
ncrf1_care_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf1_care_covidcns_clean Select columns for joining}
ncrf1_care_covidcns_clean_selected <-
  ncrf1_care_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

ncrf1_care_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf1_cic_covidcns_clean
Read in & variable names
```{r ncrf1_cic_covidcns_clean Read in data & variable names}
ncrf1_cic_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_cic_covidcns_clean.rds")
  )

ncrf1_cic_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf1_cic_covidcns_clean Dimensions}
ncrf1_cic_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf1_cic_covidcns_clean Select columns for joining}
ncrf1_cic_covidcns_clean_selected <-
  ncrf1_cic_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

ncrf1_cic_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf1_comorbid_covidcns_clean
Read in & variable names
```{r ncrf1_comorbid_covidcns_clean Read in data & variable names}
ncrf1_comorbid_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_comorbid_covidcns_clean.rds")
  )

ncrf1_comorbid_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf1_comorbid_covidcns_clean Dimensions}
ncrf1_comorbid_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf1_comorbid_covidcns_clean Select columns for joining}
ncrf1_comorbid_covidcns_clean_selected <-
  ncrf1_comorbid_covidcns_clean %>%
  select(
    -startDate,
    -endDate
  )

ncrf1_comorbid_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf1_dem_covidcns_clean
Read in & variable names
```{r ncrf1_dem_covidcns_clean Read in data & variable names}
ncrf1_dem_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_dem_covidcns_clean.rds")
  )

ncrf1_dem_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf1_dem_covidcns_clean Dimensions}
ncrf1_dem_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf1_dem_covidcns_clean Select columns for joining}
ncrf1_dem_covidcns_clean_selected <-
  ncrf1_dem_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

ncrf1_dem_covidcns_clean_selected %>%
  slice(1:5)
```



### ncrf1_lab_covidcns_clean
Read in & variable names
```{r ncrf1_lab_covidcns_clean Read in data & variable names}
ncrf1_lab_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_lab_covidcns_clean.rds")
  )

ncrf1_lab_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf1_lab_covidcns_clean Dimensions}
ncrf1_lab_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf1_lab_covidcns_clean Select columns for joining}
ncrf1_lab_covidcns_clean_selected <-
  ncrf1_lab_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

ncrf1_lab_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf1_pre_med_covidcns_clean
Read in & variable names
```{r ncrf1_pre_med_covidcns_clean Read in data & variable names}
ncrf1_pre_med_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_pre_med_covidcns_clean.rds")
  )

ncrf1_pre_med_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf1_pre_med_covidcns_clean Dimensions}
ncrf1_pre_med_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf1_pre_med_covidcns_clean Select columns for joining}
ncrf1_pre_med_covidcns_clean_selected <-
  ncrf1_pre_med_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

ncrf1_pre_med_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf1_vital_covidcns_clean
Read in & variable names
```{r ncrf1_vital_covidcns_clean Read in data & variable names}
ncrf1_vital_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_vital_covidcns_clean.rds")
  )

ncrf1_vital_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf1_vital_covidcns_clean Dimensions}
ncrf1_vital_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf1_vital_covidcns_clean Select columns for joining}
ncrf1_vital_covidcns_clean_selected <-
  ncrf1_vital_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

ncrf1_vital_covidcns_clean_selected %>%
  slice(1:5)
```



  

### ncrf2_care_covidcns_clean
Read in & variable names
```{r ncrf2_care_covidcns_clean Read in data & variable names}
ncrf2_care_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf2_care_covidcns_clean.rds")
  )

ncrf2_care_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf2_care_covidcns_clean Dimensions}
ncrf2_care_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf2_care_covidcns_clean Select columns for joining}
ncrf2_care_covidcns_clean_selected <-
  ncrf2_care_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

ncrf2_care_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf2_lab_covidcns_clean
Read in & variable names
```{r ncrf2_lab_covidcns_clean Read in data & variable names}
ncrf2_lab_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf2_lab_covidcns_clean.rds")
  )

ncrf2_lab_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf2_lab_covidcns_clean Dimensions}
ncrf2_lab_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf2_lab_covidcns_clean Select columns for joining}
ncrf2_lab_covidcns_clean_selected <-
  ncrf2_lab_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

ncrf2_lab_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf2_vital_covidcns_clean
Read in & variable names
```{r ncrf2_vital_covidcns_clean Read in data & variable names}
ncrf2_vital_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf2_vital_covidcns_clean.rds")
  )

ncrf2_vital_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf2_vital_covidcns_clean Dimensions}
ncrf2_vital_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf2_vital_covidcns_clean Select columns for joining}
ncrf2_vital_covidcns_clean_selected <-
  ncrf2_vital_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

ncrf2_vital_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf3_compli_covidcns_clean
Read in & variable names
```{r ncrf3_compli_covidcns_clean Read in data & variable names}
ncrf3_compli_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf3_compli_covidcns_clean.rds")
  )

ncrf3_compli_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf3_compli_covidcns_clean Dimensions}
ncrf3_compli_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf3_compli_covidcns_clean Select columns for joining}
ncrf3_compli_covidcns_clean_selected <-
  ncrf3_compli_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

ncrf3_compli_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf3_diag_covidcns_clean
Read in & variable names
```{r ncrf3_diag_covidcns_clean Read in data & variable names}
ncrf3_diag_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf3_diag_covidcns_clean.rds")
  )

ncrf3_diag_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf3_diag_covidcns_clean Dimensions}
ncrf3_diag_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf3_diag_covidcns_clean Select columns for joining}
ncrf3_diag_covidcns_clean_selected <-
  ncrf3_diag_covidcns_clean %>%
  select(
    -all_of(exclude_variables)
  )

ncrf3_diag_covidcns_clean_selected %>%
  slice(1:5)
```


# Cognitron

### cognitron_scores_and_demographics
Read in & variable names
```{r cognitron_scores_and_demographics Read in data & variable names}
cognitron_scores_and_demographics <-
  readRDS(
    paste0(ilovecovidcns, "/data/cognitron/scores/cognitron_scores_and_demographics.rds")
  )

cognitron_scores_and_demographics %>%
  dim()
```

Dimensions
```{r cognitron_scores_and_demographics Dimensions}
cognitron_scores_and_demographics %>%
  colnames()
```

Select columns for joining
```{r cognitron_scores_and_demographics Select columns for joining}
cognitron_scores_and_demographics_selected <- cognitron_scores_and_demographics %>%
  dplyr::rename(
    "ID" = "user_id"
  )

cognitron_scores_and_demographics_selected %>%
  slice(1:5)
```


### cognitron DfE_composite_scores
Read in & variable names
```{r DfE_composite_scores Read in data & variable names}
DfE_composite_scores <-
  readRDS(
    paste0(ilovecovidcns, "/data/cognitron/scores/DfE_composite_scores.rds")
  )

DfE_composite_scores %>%
  dim()
```

Dimensions
```{r DfE_composite_scores Dimensions}
DfE_composite_scores %>%
  colnames()
```

Select columns for joining
```{r DfE_composite_scores Select columns for joining}
DfE_composite_scores_selected <- DfE_composite_scores %>%
  dplyr::rename(
    "ID" = "user_id"
  )

DfE_composite_scores_selected %>%
  slice(1:5)
```


### cognitron DfE_task_scores
Read in & variable names
```{r DfE_task_scores Read in data & variable names}
DfE_task_scores <-
  readRDS(
    paste0(ilovecovidcns, "/data/cognitron/scores/DfE_task_scores.rds")
  )

DfE_task_scores %>%
  dim()
```

Dimensions
```{r DfE_task_scores Dimensions}
colnames(DfE_task_scores) <- paste(colnames(DfE_task_scores), "dfe", sep = "_")

DfE_task_scores %>%
  colnames()
```

Select columns for joining
```{r DfE_task_scores Select columns for joining}
DfE_task_scores_selected <- DfE_task_scores %>%
  dplyr::rename(
    "ID" = "user_id_dfe"
  )

DfE_task_scores_selected %>%
  slice(1:5)
```





## List of tibbles to join, not including website data
```{r List of tibbles to join}
tibble_list <- 
  list(
    als_covidcns_clean_selected,
    cage_covidcns_clean_selected,
    catatonia_covidcns_clean_selected,
    cfs_covidcns_clean_selected,
    dem_covidcns_clean_selected,
    impact_covidcns_clean_selected,
    facial_covidcns_clean_selected,
    gad7_covidcns_clean_selected,
    nonmotor_covidcns_clean_selected,
    mhd_selected,
    phh_selected,
    pcl5_covidcns_clean_selected,
    phq9_covidcns_clean_selected,
    smelltaste_covidcns_clean_selected,
    trauma_covidcns_clean_selected,
    updrs_covidcns_clean_selected,
    vaccine_covidcns_clean_selected,
    # core_neuro
    fourat_outp_covidcns_clean_selected,
    nis_outp_covidcns_clean_selected,
   # mh_case_report
    moca_inp_covidcns_clean_selected,
    # moca
    cognitron_outp_covidcns_clean_selected,
    moca_outp_covidcns_clean_selected,
    # neuro_case_report
    ncrf2_med_covidcns_clean_selected,
    # ncrf1
    ncrf1_admission_covidcns_clean_selected,
    ncrf1_care_covidcns_clean_selected,
    ncrf1_cic_covidcns_clean_selected,
    ncrf1_comorbid_covidcns_clean_selected,
    ncrf1_dem_covidcns_clean_selected,
    ncrf1_lab_covidcns_clean_selected,
    ncrf1_pre_med_covidcns_clean_selected,
    ncrf1_vital_covidcns_clean_selected,
    # ncrf2
    ncrf2_care_covidcns_clean_selected,
    ncrf2_lab_covidcns_clean_selected,
    ncrf2_vital_covidcns_clean_selected,
    # ncrf3    
    ncrf3_compli_covidcns_clean_selected,
    ncrf3_diag_covidcns_clean_selected,
   # cognitron
    cognitron_scores_and_demographics_selected,
    DfE_composite_scores_selected,
    DfE_task_scores_selected
    )
```

Joining of demographics and questionnaires, not including website data
```{r Joining of demographics and questionnaires}
qualtrics_data_joined <- 
  plyr::join_all(
    dfs =  tibble_list,
    by = c("ID"),
    type = "full"
    )
```

Check dimensions of joined tibble
```{r Check dimensions of joined tibble}
qualtrics_data_joined %>%
  dim()
```

Check for duplicated columns
```{r Check for duplicated columns}
qualtrics_data_joined %>%
  colnames() %>%
  duplicated() %>%
  summary()
```


# Change Incorrect IDs from Qualtrics

Import swapping IDs excel sheet
```{r Import swapping ids}
# Read in excel sheet of IDs to change as data frame
swapped_ids <- readxl::read_xlsx(path = paste0(ilovecovidcns, "/data_raw/ids/Swapped IDs.xlsx"),
                                 sheet = "Sheet1")

# Set sensical column names
colnames(swapped_ids) <- c("correct_ID", "incorrect_ID")

swapped_ids
```

Find rows to swap in order to check after swapping
```{r Find swapping rows}
# Initial empty vector of rows to change IDs for in qualtrics_data_joined
swapping_rows <- c()

# Create vector of rows corresponding to IDs that need changing
for (i in swapped_ids$incorrect_ID) {
  swapping_rows <- append(x = swapping_rows, values = which(qualtrics_data_joined$ID == i))
}

swapping_rows
```

Use gsub to replace in df
```{r Replace IDs}
for (i in 1:nrow(swapped_ids)){
  qualtrics_data_joined$ID <- gsub(pattern = swapped_ids$incorrect_ID[i],
                                   replacement = swapped_ids$correct_ID[i],
                                   x = qualtrics_data_joined$ID
                                   )
}
```

Test data frame IDs against correct IDs from sheet
```{r Test ID swap}
qualtrics_data_joined %>%
  select(ID) %>%
  slice(swapping_rows) == swapped_ids$correct_ID
```

Coalesce age and sex demographic variables from baseline and ncrf dem
```{r Coalesce age sex dem}
qualtrics_data_joined <- qualtrics_data_joined %>%
  mutate(
    dem.dob_age = coalesce(
      dem.dob_age,
      ncrf1_dem.dob_age),
    
    dem.sex_at_birth = coalesce(
      dem.sex_at_birth,
      ncrf1_dem.sex_at_birth),
    
    dem.sex_at_birth_numeric = coalesce(
      dem.sex_at_birth_numeric,
      ncrf1_dem.sex_at_birth_numeric)
  )
```

Summary tables to check missingness before joining to website data
```{r Summary table qualtrics data only}
tbl_summary(qualtrics_data_joined,
            include = c(dem.dob_age,
                        dem.sex_at_birth,
                        ncrf1_vital.admission_severity_worst_covid19,
                        ncrf1_comorbid.clinical_frailty_scale,
                        ncrf1_admission.date_of_inpatient_admission.txt),
            missing_text = "Missing"
            )
```


Joining of website data
```{r Joining of website data}
data_joined <- 
  plyr::join_all(
    dfs =  list(COVID_CNS_combined_website_data_clean_selected, qualtrics_data_joined),
    by = c("ID"),
    type = "full"
    )
```


Summary tables to check missingness before joining to website data
```{r Summary table qualtrics website}
covidcns_sumtable <- data_joined %>%
  
  # Coalesce controls into single category
  mutate(across(case_control_vaccine,
                ~case_when(str_detect(case_control_vaccine, "Control") ~ "Control",
                           TRUE ~ .)
                )
         ) %>%
  
  # Convert NAs to explicit factor to show in table per category
  dplyr::mutate(dem.sex_at_birth = factor(dem.sex_at_birth) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(ncrf1_vital.admission_severity_worst_covid19 = factor(ncrf1_vital.admission_severity_worst_covid19) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(ncrf1_comorbid.clinical_frailty_scale = factor(ncrf1_comorbid.clinical_frailty_scale) %>%
                  forcats::fct_explicit_na()) %>%

  # Create summary table with stats to match Kuha's table
  tbl_summary(by = case_control_vaccine,
              include = c(dem.dob_age,
                          dem.sex_at_birth,
                          ncrf1_vital.admission_severity_worst_covid19,
                          ncrf1_comorbid.clinical_frailty_scale,
                          ncrf1_admission.date_of_inpatient_admission.txt),
              type = all_continuous() ~ "continuous2",
              missing = "no",
              statistic = list(all_continuous() ~ c("{median} ({p25}, {p75})", "{N_miss} ({p_miss}%)"))
              ) %>%
  modify_table_body(dplyr::mutate,
                    label = ifelse(label == "N missing (% missing)", "Missing", label)
                    )

# Save table
#gt::gtsave(as_gt(covidcns_sumtable), file = "covidcns_sumtable.png")
covidcns_sumtable
```

Select columns for data extraction
```{r matching Select columns}
data_export_matching <- data_joined %>%
  select(
      "ID",
      
      # Age
      "dem.dob_age",
      "dem.how_old_are_you_now.txt",
      
      # Sex
      "dem.sex_at_birth",
      "dem.sex_at_birth_numeric",
      
      # Language
      "dem.is_english_your_first_language",
      "dem.what_is_your_first_language.txt",
      "dem.what_is_your_first_language_numeric",
      "dem.is_english_your_first_language_numeric",
      
      # Education
      "dem.highest_education",
      "dem.highest_education_numeric",
      
      # impact
      "impact.fulltime_employed",
      "impact.unemployed",
      "impact.stayathome_parent_or_carer",
      "impact.contract_or_freelance_work",
      "impact.receiving_state_income",
      "impact.student_",
      "impact.prefer_not_to_say",
      "impact.parttime_employed",
      "impact.zerohours_contract",
      "impact.selfemployed",
      "impact.small_business_owner",
      "impact.retired",
      "impact.student_.1"
      )


data_export_matching %>%
  slice(1:5)
```

# Save joined data set
```{r matching Save joint data set}
saveRDS(
  object = data_export_matching, 
  file = paste0(ilovecovidcns, "/data/joined/covidcns_matching.rds")
)
```

```{r matching Save joint data set sharing}
saveRDS(
  object = data_export_matching, 
  file = paste0(ilovecovidcns, "/data_sharing/matching/covidcns_matching.rds")
)
```

Select columns for data extraction
```{r greta Select columns}
data_export_greta <- data_joined #%>%
#  select(
#    
#  )
```

# Save joined data set
```{r greta Save joint data set}
saveRDS(
  object = data_export_greta, 
  file = paste0(ilovecovidcns, "/data/joined/covidcns_greta.rds")
)
```

```{r greta Save joint data set sharing}
saveRDS(
  object = data_export_greta, 
  file = paste0(ilovecovidcns, "/data_sharing/liverpool/covidcns_greta.rds")
)
```


Select columns for data extraction
```{r yun Select columns, eval=FALSE, include=FALSE}
data_export_yun <- data_joined %>%
  select(
    
  )
```

# Save joined data set
```{r yun Save joint data set, eval=FALSE, include=FALSE}
saveRDS(
  object = data_export_yun, 
  file = paste0(ilovecovidcns, "/data/joined/covidcns_yun.rds")
)
```