

# Check problematic participants

nCRF acts as pseudo-master-list of participants
Check which participants are missing nCRF but exist in overall qualtrics sample
Check which surveys they have and which are absent
```{r Check problem repeats, eval=FALSE, include=FALSE}
missing_ncrf <- setdiff(
  joined_list[["qualtrics_joined"]][["data"]]$ID,
  joined_list[["neuro_case_report_joined"]][["data"]]$ID
  )

for (i in 1:length(joined_list)){
  print(names(joined_list)[i])
  for (j in 1:length(missing_ncrf)){
    if (missing_ncrf[j] %in% joined_list[[i]][["data"]][["ID"]]){
      print(paste(missing_ncrf[j], "YES"))
    }
    else{print(paste(missing_ncrf[j], "NO"))}
  }
}
```

Check which are missing website data
```{r Check missing website, eval=FALSE, include=FALSE}
missing_website <- setdiff(
  joined_list[["qualtrics_joined"]][["data"]]$ID,
  joined_list[["assessment_joined"]][["data"]]$ID
  )

for (i in 1:length(joined_list)){
  print(names(joined_list)[i])
  for (j in 1:length(missing_website)){
    if (missing_website[j] %in% joined_list[[i]][["data"]][["ID"]]){
      print(paste(missing_website[j], "YES"))
    }
    else{print(paste(missing_website[j], "NO"))}
  }
}
```

Check participants who appeared to be missing baseline but exist in overall qualtrics sample
Check which surveys they have and which are absent
```{r Check missing baseline, eval=FALSE, include=FALSE}
missing_baselines <- c(
  #"CNS01001",
  #"CNS01004",
  #"CNS01132",
  #"CNS02002",
  #"CNS02057",
  #"CNS02072",
  #"CNS02084",
  #"CNS02094",
  #"CNS02112",
  #"CNS02135",
  #"CNS02136",
  #"CNS05024",
  "CNS05043",
  #"CNS06006",
  #"CNS06011",
  #"CNS06048",
  #"CNS07033",
  #"CNS09004",
  #"CNS11007",
  "CNS16001"
)

for (i in 1:length(joined_list)){
  print(names(joined_list)[i])
  for (j in 1:length(missing_baselines)){
    if (missing_baselines[j] %in% joined_list[[i]][["data"]][["ID"]]){
      print(paste(missing_baselines[j], "YES"))
    }
    else{print(paste(missing_baselines[j], "NO"))}
  }
}
```

Check participants who are missing demographics for cognitron
Check which surveys they have and which are absent
```{r Check missing cognitron, eval=FALSE, include=FALSE}
missing_cog <- readRDS(paste0(ilovecovidcns, "/data/cognitron_matching_missing.rds")) %>%
  select(user_id) %>%
  unlist() %>%
  unname()

for (i in 1:length(joined_list)){
  print(names(joined_list)[i])
  for (j in 1:length(missing_cog)){
    if (missing_cog[j] %in% joined_list[[i]][["data"]][["ID"]]){
      print(paste(missing_cog[j], "YES"))
    }
    else{print(paste(missing_cog[j], "NO"))}
  }
}
```

```{r eval=FALSE, include=FALSE}
problem_ids <- c("CNS02084", "CNS01001", "CNS01118", "CNS01132", "CNS06006", "CNS06011", "CNS09004")

joined_list[["baseline_joined"]][["data"]] %>%
  filter(ID %in% problem_ids) %>%
  select(
    ID,
    dem.dob_age,
    dem.sex_at_birth,
    dem.is_english_your_first_language,
    dem.highest_education)
```