---
title: "COVIDCNS Variable Extraction Script"
author: "Zain Ahmad"
date: "19/12/2022"
output: html_document
---

# Standards
All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except:
Study name (e.g. GLAD/EDGI/NBR) all caps
Capitalised first word
Chunk names MUST be unique

Add only one empty line between chunks
Add one extra line when starting a new section
Use hash syntax as appropriate for headings and subheadings, as per markdown syntax

Points requiring user input are enclosed thus <>

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in paths file}
source(file = "scripts/credentials/paths.R")
```

Add the variable_extract function - used to produce data extractions
```{r Read in functions}
source(file = paste0(ilovecovidcns_local, "/variable_extract.R"))
```

Run variable extraction for Daniel
```{r Extraction Daniel}
variable_extract("Daniel_van_Wamelen_covidcns_fatigue_15122022.txt", "covidcns_data_joined.rds", "daniel")
```