---
title: "COVIDCNS Case Control Data Cleaning Script"
author: "Zain Ahmad"
date: "24/03/2022"
output: html_document
---


All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except:
Study name (COVIDCNS) all caps
Capitalised first word

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = "../functions/package_check.R")
source(file = "../functions/imp_check_1.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Read in file with path to ilovedata channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in file with path to ilovedata channel on teams}
source(file = "../credentials/paths.R")
```

# Read in the data: COVIDCNS Case Control Data
Change this heading to the name of your questionnaire/demographic
Load COVIDCNS data

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the issues spreadsheet "https://docs.google.com/spreadsheets/d/1a2gL8c0eH2pZXNTbnPzkDYQGeeVXbLKU8BUpYM0moe8/edit?usp=sharing"

- For variable names, use ONLY 'questionnaire.variable_name'
- For dataset, only use snake_case naming
- When using pipe operator '%>%', each function should begin on a new line
- Do not add empty lines at the beginning or end of a chunk
- Use only tidyverse functions wherever possible
- When naming chunks, begin with the name of the dataset (COVIDCNS)

## COVIDCNS data
```{r COVIDCNS load data}
covidcns_dat <- read_csv(
  file = paste0(ilovedata, "/data_raw/covidcns/COVID_CNS_case_control_status_04.03.2022.csv"),
  col_types = list(
    identifier = col_character(),
    type = col_character(),
    updated_at = col_character()
  )
  )
  
# Check variable names in dataframe
covidcns_dat %>%
  colnames()

# Inspect dimensions of dataframe 
covidcns_dat %>%
  dim()
```

Select & rename relevant columns
```{r COVIDCNS select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  drop_na(identifier) %>% # Drop participants with no ID
  distinct(identifier, .keep_all = TRUE) %>% # Remove duplicate IDs
  add_column(sample = "COVIDCNS",
             .after = "identifier") %>% # Create new sample column
  select(
         ID = identifier, # ID
         case_control = type,
         updated_at
         )

# Inspect colnames
covidcns_dat_id %>%
  colnames()
```

Look at number of people excluded
The number of people to be excluded should be negative
```{r COVIDCNS number excluded}
# Inspect dimensions of new data set
covidcns_dat_id %>%
  dim()

# Inspect number of rows dropped
covidcns_excluded <- dim(covidcns_dat_id)[1] - dim(covidcns_dat)[1]
covidcns_excluded
```

Check missingness by missmap
```{r COVIDCNS inspect missingness}
covidcns_miss_map <- covidcns_dat_id %>% 
  missmap()

covidcns_miss_map
```

Create dat as copy of covidcns_dat_id for brevity
This step gives you a 'reset' point: if your variable recoding screws up, re-run this chunk to give you a fresh 'dat' dataframe
```{r Create dat}
dat <- covidcns_dat_id 

# Check
dat %>% glimpse()
```

Create list of all unique values
```{r List unique values}
ulst <- sapply(dat, unique)
```


# Cleaning Categorical Variables

Name your vectors in line with the chunks below
Number the vectors or name them intuitively if you have multiple vectors
Vectors of potential values should only contain possible values (exclude nonanswer values as appropriate)

Create sequential vectors of categorical values for variables
Save vectors to a list
Add variable names as names of list
```{r Vector categorical values}
vals_cat_1 <- c(
  "Case: COVID-19 positive (i.e. neurological or psychiatric complication)",
  "Vaccine: COVID-19 vaccine complication (i.e. neurological or psychiatric complication)",
  "Control: COVID-19 positive (i.e. NO neurological or psychiatric complication)",
  "Control: COVID-19 negative (e.g. pneumonia  sepsis)",
  "Control",
  NA
)

```

Create list of numeric values vectors
```{r List categorical values vectors}
values_cat_list <- list(
  vals_cat_1
)
```

Create vector of categorical domains variables 
```{r Vector categorical variables}
variables_cat <- c(
  "case_control"
)
```

Set names of list to variable names
```{r Set list names}
names(values_cat_list) <- variables_cat
```

Use imp_check iteratively to find if any implausible values
```{r Imp_check categorical variables}
# Create empty list
imp_list_cat <- list()

# Loop over each variable, checking against relevant set of values from list
# Add imp_message to list
for (i in 1:length(variables_cat)) {
  imp_list_cat[i] <- imp_check_1(data = dat,
                                 variables = names(values_cat_list)[i],
                                 values = values_cat_list[[i]]) 

}

# Name list with var names to correspond to imp_messages
names(imp_list_cat) <- variables_cat

# View list of imp_messages with corresponding var names
print(imp_list_cat)
```

Produce summary table of variables
```{r Summary table categorical variables}
dat %>%
  tbl_summary(
    include = all_of(variables_cat),
    missing_text = "Missing")
```



# Cleaning Dates

Create vector of date variables
```{r Vector date variables}
variables_date <- c(
  "updated_at"
)
```

Inspect date variables
```{r COVIDCNS inspect dates}
dat %>%
  select(all_of(variables_date)) %>%
  glimpse()
```

Parse dates using lubridate
```{r COVIDCNS parse dates}
dat <- dat %>% 
  mutate(across(
    all_of(variables_date),
    ~lubridate::parse_date_time(
    x = .,
    orders = c("%d/%m/%y %H:%M"),
    tz = "Europe/London"
    )
                )
         )
```

Recheck date variables
```{r COVIDCNS inspect dates}
dat %>%
  select(all_of(variables_date)) %>%
  tbl_summary(missing_text = "Missing")
```

Define limits for variable and list reasoning below
Variable name:
- Upper: date of file creation
- Lower: 30/01/2020, first confirmed UK COVID cases 

```{r Define limits}
upper_limit <- as.POSIXct("2022-03-04")
lower_limit <- as.POSIXct("2020-01-30")
```

Recode variable outliers to -666
```{r Recode outliers to NA}
dat <- dat %>%
    mutate(across(
    all_of(variables_date),
    ~ifelse(
      . > upper_limit | # bigger than the upper limit
        . < lower_limit, # smaller than the lower limit
      yes = NA_real_,
      no = .
        )
    )
) %>%
  mutate(across(
    all_of(variables_date),
    ~as.POSIXct(., origin = lubridate::origin))
  )
```

Re-check dates
```{r COVID CNS recheck dates}
dat %>%
  select(all_of(variables_date)) %>%
  tbl_summary(missing_text = "Missing")
```


# Save cleaned data

Check colnames before exporting final dataset
```{r Check colnames}
colnames(dat)
```

# COVIDCNS
```{r Write cleaned COVIDCNS variables to a .rds file}
dat %>%
  saveRDS(
    file = paste0(ilovedata, "/data/covidcns/COVID_CNS_casecontrol_clean.rds")
    )
```
