---
title: "COVIDCNS Combined Website Data Cleaning Script"
author: "Zain Ahmad"
date: "24/03/2022"
output: html_document
---


Cleaning script for combined:
1. Case control status
2. Neuroimaging metadata

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the package_check function - used to install and load dependencies
Add the imp_clean function - used to check variables for implausible values
Add the recode_check function - used to check for implausible values when recoding
```{r Read in functions}
source(file = "scripts/functions/package_check.R")
source(file = "scripts/functions/imp_clean.R")
source(file = "scripts/functions/recode_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in file with path to ilovecovidcns channel on teams}
source(file = "scripts/credentials/paths.R")
```

# Read in the data: COVIDCNS Case Control Status and Neuroimaging Metadata

## COVIDCNS data
```{r COVIDCNS load data}
covidcns_dat <- read_csv(
  file = paste0(ilovecovidcns, "/data_raw/assessment_status/RV5_covid-cns_comb_17.06.2022.csv"),
  col_types = list(
    kit_id = col_character(),
    primary_site = col_character(),
    site_name = col_character(),
    recurited_at_site = col_character(),
    recurited_at_site_name = col_character(),
    processing_problems = col_character(),
    notes = col_character(),
    site_reference_id = col_character(),
    type = col_character(),
    updated_at = col_character()
  )
  )

  
# Check variable names in dataframe
covidcns_dat %>%
  colnames()

# Inspect dimensions of dataframe 
covidcns_dat %>%
  dim()
```

Select & rename relevant columns
```{r COVIDCNS select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  drop_na(kit_id) %>% # Drop participants with no ID
  distinct(kit_id, .keep_all = TRUE) %>% # Remove duplicate IDs
  add_column(sample = "COVIDCNS",
             .after = "kit_id") %>% # Create new sample column
  select(
         ID = kit_id, # ID
         primary_site_code = primary_site,
         primary_site_name = site_name,
         recruitment_site_code = recurited_at_site,
         recruitment_site_name = recurited_at_site_name,
         processing_problems,
         notes,
         site_reference_id,
         case_control_vaccine = type,
         updated_at
         )

# Inspect colnames
covidcns_dat_id %>%
  colnames()
```

Look at number of people excluded
The number of people to be excluded should be negative
```{r COVIDCNS number excluded}
# Inspect dimensions of new data set
covidcns_dat_id %>%
  dim()

# Inspect number of rows dropped
covidcns_excluded <- dim(covidcns_dat_id)[1] - dim(covidcns_dat)[1]
covidcns_excluded
```

Check missingness by missmap
```{r COVIDCNS inspect missingness}
covidcns_dat_id %>% 
  missmap()
```

Create dat as copy of covidcns_dat_id for brevity
This step gives you a 'reset' point: if your variable recoding screws up, re-run this chunk to give you a fresh 'dat' dataframe
```{r Create dat}
dat <- covidcns_dat_id 

# Check
dat %>% glimpse()
```

Create list of all unique values
```{r List unique values}
ulst <- sapply(dat, unique)
```


# Cleaning Categorical Variables

Name your vectors in line with the chunks below
Number the vectors or name them intuitively if you have multiple vectors
Vectors of potential values should only contain possible values (exclude nonanswer values as appropriate)

Create sequential vectors of categorical values for variables
Save vectors to a list
Add variable names as names of list
```{r Vector categorical values}
vals_cat_1 <- c(
  "RJZ",
  "RET",
  "RGT",
  "RM3",
  "RV5",
  "RTH",
  "RJ1",
  "7A4",
  "RHQ",
  "RRV",
  NA
)

vals_cat_2 <- c(
  "KCH",
  "Liverpool",
  "Cambridge",
  "Salford Royal",
  "SLaM",
  "Oxford",
  "GSTT",
  "Cardiff",
  "Sheffield",
  "UCLH",
  NA
)

vals_cat_3 <- c(
  "RJZ01",
  "RET20",
  "RGT01",
  "REM21",
  "REMRQ",
  "RM301",
  "RV504",
  "RTH08",
  "RJ122",
  "7A4BV",
  "RHQHH",
  "RRVNQ",
  NA
)

vals_cat_4 <- c(
  "King's College Hospital (Denmark Hill)",
  "The Walton Centre",
  "Addenbrooke's Hospital",
  "Aintree University Hospital",
  "The Royal Liverpool University Hospital",
  "Salford Royal Hospital",
  "Maudsley Hospital",
  "John Radcliffe Hospital",
  "St Thomas' Hospital",
  "University Hospital of Wales",
  "Royal Hallamshire Hospital",
  "The National Hospital for Neurology and Neurosurgery",
  NA
)

vals_cat_5 <- c(
  "Case: COVID-19 positive (i.e. neurological or psychiatric complication)",
  "Vaccine: COVID-19 vaccine complication (i.e. neurological or psychiatric complication)",
  "Control: COVID-19 positive (i.e. NO neurological or psychiatric complication)",
  "Control: COVID-19 negative (e.g. pneumonia  sepsis)",
  "Control",
  NA
)
```

Create list of numeric values vectors
```{r List categorical values vectors}
values_cat_list <- list(
  vals_cat_1,
  vals_cat_2,
  vals_cat_3,
  vals_cat_4,
  vals_cat_5
)
```

Set names of list to variable names
```{r Set list names}
names(values_cat_list) <- c(
  "primary_site_code",
  "primary_site_name",
  "recruitment_site_code",
  "recruitment_site_name",
  "case_control_vaccine"
)
```

Use imp_clean to find if any implausible values
```{r Imp_clean categorical variables}
imp_clean(values_list = values_cat_list,
          dat = dat)
```

Produce summary table of variables
```{r Summary table categorical variables}
dat %>%
  tbl_summary(
    include = all_of(names(values_cat_list)),
    missing_text = "Missing")
```

# Recoding Incorrect Variables

Variable is coded wrong
```{r Inspect incorrect variable}
dat %>%
  select(
    recruitment_site_name) %>%
  tbl_summary(missing_text = "Missing")
```

Recode incorrect variable
```{r Recode incorrect variable}
dat <- dat %>% 
  mutate(across(recruitment_site_name,
                ~case_when(
                  . == "THE ROYAL LIVERPOOL UNIVERSITY HOSPITAL (RLUH NHS TRUST)" ~ "The Royal Liverpool University Hospital",
                  TRUE ~ .)))
```

Re-check variable coding
```{r Recheck variable coding}
recode_check(variables = "recruitment_site_name",
          values = vals_cat_4,
          data = dat)
```

Add column for attempted scan (all in list)
```{r Add attempted scan column}
dat <- dat %>%
  mutate(attempted_scan = 1)

dat %>%
  tbl_summary(include = attempted_scan)
```



# Text variables

Inspect text variables
```{r Inspect text vars}
variables_text <- c(
  "processing_problems",
  "notes"
)

dat %>%
  select(all_of(variables_text)) %>%
  tbl_summary(
    missing_text = "Missing"
  )
```

# Save cleaned data

Check colnames before exporting final dataset
```{r Check colnames}
colnames(dat)
```

# COVIDCNS
```{r Write cleaned COVIDCNS variables to a .rds file}
dat %>%
  saveRDS(
    file = paste0(ilovecovidcns, "/data/assessment_status/COVID_CNS_combined_website_data_clean.rds")
    )
```
