---
title: "COVID-CNS wrapper"
author: "Christopher Huebel"
date: "09/05/2022"
output: html_document
---

All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except:
Study name (COVIDCNS) all caps
Capitalised first word

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the package_check function - used to install and load dependencies
Add the imp_clean function - used to check variables for implausible values
```{r Read in functions}
source(file = "functions/package_check.R")
source(file = "functions/imp_clean.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Read in file with path to ilovedata channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in file with path to ilovedata channel on teams}
source(file = "credentials/paths.R")
```


# Running of individual cleaning files which creates sum scores and t-scores

# assessment_status

## casecontrol_status
```{r casecontrol_status Cleaning the individual questionnaires}
source(knitr::purl("assessment_status/casecontrol_status.Rmd"))
```

## neuroimaging_metadata
```{r neuroimaging_metadata Cleaning the individual questionnaires}
source(knitr::purl("assessment_status/neuroimaging_metadata.Rmd"))
```

# baseline

## Age
```{r Age Cleaning the individual questionnaires}
source(knitr::purl("baseline/Age.Rmd"))
```

## ALS
```{r ALS Cleaning the individual questionnaires}
source(knitr::purl("baseline/ALS.Rmd"))
```

## CAGE
```{r CAGE Cleaning the individual questionnaires}
source(knitr::purl("baseline/CAGE.Rmd"))
```

## catatonia
```{r catatonia Cleaning the individual questionnaires}
source(knitr::purl("baseline/catatonia.Rmd"))
```

## CFS
```{r CFS Cleaning the individual questionnaires}
source(knitr::purl("baseline/CFS.Rmd"))
```

## Covid19
```{r Covid19 Cleaning the individual questionnaires}
source(knitr::purl("baseline/Covid19.Rmd"))
```

## dem_covidpositive
```{r dem_covidpositive Cleaning the individual questionnaires}
source(knitr::purl("baseline/dem_covidpositive.Rmd"))
```

## dem_ethnicity
```{r dem_ethnicity Cleaning the individual questionnaires}
source(knitr::purl("baseline/dem_ethnicity.Rmd"))
```

## dem_highest_qualification
```{r dem_highest_qualification Cleaning the individual questionnaires}
source(knitr::purl("baseline/dem_highest_qualification.Rmd"))
```

## dem_language
```{r dem_language Cleaning the individual questionnaires}
source(knitr::purl("baseline/dem_language.Rmd"))
```

## dem_memory
```{r dem_memory Cleaning the individual questionnaires}
source(knitr::purl("baseline/dem_memory.Rmd"))
```

## dem_quality_life
```{r dem_quality_life Cleaning the individual questionnaires}
source(knitr::purl("baseline/dem_quality_life.Rmd"))
```

## dem_sex_gender_sexuality
```{r dem_sex_gender_sexuality Cleaning the individual questionnaires}
source(knitr::purl("baseline/dem_sex_gender_sexuality.Rmd"))
```

## dem_visionhearing
```{r dem_visionhearing Cleaning the individual questionnaires}
source(knitr::purl("baseline/dem_visionhearing.Rmd"))
```

## facial
```{r facial Cleaning the individual questionnaires}
source(knitr::purl("baseline/facial.Rmd"))
```

## GAD7
```{r GAD7 Cleaning the individual questionnaires}
source(knitr::purl("baseline/GAD7.Rmd"))
```

## impact
```{r impact Cleaning the individual questionnaires}
source(knitr::purl("baseline/impact.Rmd"))
```

## mhd_numericonly
```{r mhd_numericonly Cleaning the individual questionnaires}
source(knitr::purl("baseline/mhd_numericonly.Rmd"))
```

## nonmotor
```{r nonmotor Cleaning the individual questionnaires}
source(knitr::purl("baseline/nonmotor.Rmd"))
```

## PCL5
```{r PCL5 Cleaning the individual questionnaires}
source(knitr::purl("baseline/PCL5.Rmd"))
```

## PHH_forgreta.Rmd
```{r PHH_forgreta.Rmd Cleaning the individual questionnaires}
source(knitr::purl("baseline/PHH_forgreta.Rmd.Rmd"))
```

## PHQ9
```{r PHQ9 Cleaning the individual questionnaires}
source(knitr::purl("baseline/PHQ9.Rmd"))
```

## smelltaste
```{r smelltaste Cleaning the individual questionnaires}
source(knitr::purl("baseline/smelltaste.Rmd"))
```

## trauma
```{r trauma Cleaning the individual questionnaires}
source(knitr::purl("baseline/trauma.Rmd"))
```

## UPDRS
```{r UPDRS Cleaning the individual questionnaires}
source(knitr::purl("baseline/UPDRS.Rmd"))
```

## vaccine
```{r vaccine Cleaning the individual questionnaires}
source(knitr::purl("baseline/vaccine.Rmd"))
```

# cognitron_pipeline

## main
```{r main Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/main.R"))
```

# core_neuro
## fourAT_outpatient
```{r fourAT_outpatient Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/fourAT_outpatient.Rmd"))
```

## gcs_outp
```{r gcs_outp Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/gcs_outp.Rmd"))
```

## NIS_outpatient
```{r NIS_outpatient Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/NIS_outpatient.Rmd"))
```

# mh_case_report

## MoCA_inpatient
```{r MoCA_inpatient Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/MoCA_inpatient.Rmd"))
```

# moca

## cognitron_outp_info
```{r cognitron_outp_info Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/cognitron_outp_info.Rmd"))
```

## MoCA_outpatient
```{r MoCA_outpatient Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/MoCA_outpatient.Rmd"))
```

# neuro_case_report

## clinical_frailty
```{r clinical_frailty Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/clinical_frailty.Rmd"))
```

## ncrf_supportive
```{r ncrf_supportive Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/ncrf_supportive.Rmd"))
```

## ncrf1_admission
```{r ncrf1_admission Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/ncrf1_admission.Rmd"))
```

## ncrf1_cic
```{r ncrf1_cic Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/ncrf1_cic.Rmd"))
```

## ncrf1_comorbid
```{r ncrf1_comorbid Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/ncrf1_comorbid.Rmd"))
```

## ncrf1_labresults
```{r ncrf1_labresults Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/ncrf1_labresults.Rmd"))
```

## ncrf1_pre_med
```{r ncrf1_pre_med Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/ncrf1_pre_med.Rmd"))
```

## ncrf1_vital
```{r ncrf1_vital Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/ncrf1_vital.Rmd"))
```

## ncrf2_labresults
```{r ncrf2_labresults Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/ncrf2_labresults.Rmd"))
```

## ncrf2_med
```{r ncrf2_med Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/ncrf2_med.Rmd"))
```

## ncrf2_vital
```{r ncrf2_vital Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/ncrf2_vital.Rmd"))
```

## ncrf3_compli
```{r ncrf3_compli Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/ncrf3_compli.Rmd"))
```

## ncrf3_diag
```{r ncrf3_diag Cleaning the individual questionnaires}
source(knitr::purl("cognitron_pipeline/ncrf3_diag.Rmd"))
```

