---
title: "COVIDCNS Followup 3 Cleaning Script"
author: "Zain Ahmad"
date: "17/07/2024"
output: html_document
---


All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except capitalised first word
Chunk names MUST be unique
Points requiring user input are enclosed thus <>

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_labelled_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the recode_check function - used to check for implausible values when recoding
Add the imp_clean function - used to check variables for implausible values
Add the cont_clean function - used to check continuous variables for implausible values
```{r Read in functions}
source(file = "scripts/functions/add_labelled_numeric.R")
source(file = "scripts/functions/remove_duplicates.R")
source(file = "scripts/functions/sumscores.R")
source(file = "scripts/functions/package_check.R")
source(file = "scripts/functions/recode_check.R")
source(file = "scripts/functions/cont_clean.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("sjlabelled",
              "Amelia",
              "gtsummary",
              "tidyverse")

package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Source filepath to ilovecovidcns OneDrive}
source(file = "scripts/credentials/paths.R")
```

# Read in the data: COVIDCNS Followup 3

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the Teams Data Issues Tracker

- For variable names, use ONLY 'questionnaire.variable_name' syntax
- When using pipe operator '%>%', each function should begin on a new line for clarity
- Do not add empty lines at the beginning or end of a chunk to keep the markdown as short as possible
- Use only tidyverse functions wherever possible, they run faster than base R

COVIDCNS data
```{r COVIDCNS load data}
# Generate data path
data_path <- "/Users/zainahmad/Library/CloudStorage/OneDrive-SharedLibraries-King'sCollegeLondon/MT-BioResource - Covid-CNS Data Extraction - Extraction/data_raw/2024-07-17/followup3"
  
# Read rds file names
rds_files <- dir(path = data_path, pattern = "*rds", recursive = TRUE)

# Create rds object names
rds_object_names <- rds_files %>% stringr::str_remove(pattern = ".rds")

# Read in rds to list
rds_list <- rds_files %>% map(~read_rds(file = file.path(data_path, .)))

# Name dfs in list
names(rds_list) <- rds_object_names

# Deduplicate IDs
for (i in 1:length(names(rds_list))){
  rds_list[[i]] <- rds_list[[i]] %>%
    remove_duplicates("externalDataReference") %>%
    dplyr::rename("ID" = "externalDataReference")
}

# Remove startDate endDate sample
if (length(rds_list) > 1){
  for (i in 2:length(names(rds_list))){
    if ("startDate" %in% colnames(rds_list[[i]])){
      rds_list[[i]] <- rds_list[[i]] %>% select(-startDate)
    }
    if ("endDate" %in% colnames(rds_list[[i]])){
      rds_list[[i]] <- rds_list[[i]] %>% select(-endDate)
    }
  }
}

# Remove sample
for (i in 1:length(names(rds_list))){
  if ("_recordId" %in% colnames(rds_list[[i]])){
    rds_list[[i]] <- rds_list[[i]] %>% select(-"_recordId")
  }
}

# Full join dfs
dat <- rds_list %>% reduce(full_join, by = c("ID"))
```

Extract and save labels
```{r Extract save labels}
# Save variable labels
question_labels <- sjlabelled::get_label(dat)

# Save value labels
answer_labels <- sjlabelled::get_labels(dat, values = "as.name")

# Change -77 to -777 in value labels names
chng <- rapply(sapply(answer_labels, names),
               function(x) ifelse(x==-77, -777, x),
               how = "replace")

# Add multiple lines here as necessary to change other nonanswer values in labels
# chng <- rapply(chng,
#                function(x) ifelse(x==-88, -888, x),
#                how = "replace")

# Substitute new value labels into answer_labels
for (i in 1:length(chng)){
  if(!is.null(answer_labels[[i]])){
  names(answer_labels[[i]]) <- chng[[i]]
  }
}
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(where(is.numeric),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)
                )
         )

# Re-add labels after mutate
dat <- sjlabelled::set_label(dat, question_labels)
dat <- sjlabelled::set_labels(dat, labels = answer_labels)
```

Create list of all labels and attributes
This chunk supersedes all categorical/numeric cleaning
It gives you an output of c(the question label, all value-label pairs)
for each variable
Check for errors in the output of this chunk, including:
- Label spelling errors (for questions and answers)
- Incorrect values
- Mismatches between labels and values
- Scale errors
- Variable naming issues from the data extraction
- Any other issues you can see
All issues/changes need to be logged as a to-do on Teams
At this point, you also need to pick out any continuous, date or text variables 
to be cleaned in the later chunks
```{r List labels attrs}
label_list <- sapply(dat, function(x) c(attr(x, "label"), attr(x, "labels")))
label_list
```


# Cleaning Textual Variables

Create vector of text variables
```{r Vector text vars}
variables_text <- c(
  "csri.service_consultations_practitioners_months.txt.other_doctor_specify_text",
"csri.practitioners_number_consultations_contacts.general_practitioner_gp",
"csri.practitioners_number_consultations_contacts.general_practitioner_gp.1",
"csri.practitioners_number_consultations_contacts.neurologist",
"csri.practitioners_number_consultations_contacts.neurologist.1",
"csri.practitioners_number_consultations_contacts.psychiatrist",
"csri.practitioners_number_consultations_contacts.psychiatrist.1",
"csri.practitioners_number_consultations_contacts.other_doctor_specify",
"csri.practitioners_number_consultations_contacts.other_doctor_specify.1",
"csri.practitioners_number_consultations_contacts.txt.other_doctor_specify_text",
"csri.practitioners_number_consultations_contacts.practice_nurse",
"csri.practitioners_number_consultations_contacts.practice_nurse.1",
"csri.practitioners_number_consultations_contacts.pharmacist",
"csri.attended_times_months.txt",
"csri.health_problems_friends_relatives.txt.other_specify_text",
"csri.week_hours_consequence_tasks.childcare_select_no_if_you_have_no_children",
"csri.week_hours_consequence_tasks.personal_care_e.g._washing_dressing",
"csri.week_hours_consequence_tasks.help_inaround_the_home_e.g._cooking_cleaning_etc.",
"csri.week_hours_consequence_tasks.help_outside_the_home_e.g._shopping_transport",
"csri.week_hours_consequence_tasks.other_specify",
"csri.week_hours_consequence_tasks.txt.other_specify_text",
"csri.what_is_your_current_employment_status.txt",
"csri.employment_status_changed.txt",
"csri.work_days_months_physical.txt",
"csri.mental_health_problems_work.txt",
"csri.service_consultations_practitioners_months.txt.other_specify_text",
"csri.practitioners_number_consultations_contacts.physiotherapist",
"csri.practitioners_number_consultations_contacts.physiotherapist.1",
"csri.practitioners_number_consultations_contacts.social_worker",
"csri.practitioners_number_consultations_contacts.social_worker.1",
"csri.practitioners_number_consultations_contacts.community_mental_health_worker",
"csri.practitioners_number_consultations_contacts.community_mental_health_worker.1",
"csri.practitioners_number_consultations_contacts.acupuncturist",
"csri.practitioners_number_consultations_contacts.acupuncturist.1",
"csri.practitioners_number_consultations_contacts.osteopath",
"csri.practitioners_number_consultations_contacts.osteopath.1",
"csri.practitioners_number_consultations_contacts.homeopathherbalist",
"csri.practitioners_number_consultations_contacts.homeopathherbalist.1",
"csri.practitioners_number_consultations_contacts.occupational_therapist",
"csri.practitioners_number_consultations_contacts.occupational_therapist.1",
"csri.practitioners_number_consultations_contacts.other_specify",
"csri.practitioners_number_consultations_contacts.other_specify.1",
"csri.practitioners_number_consultations_contacts.txt.other_specify_text",
"csri.consultations_contact_months_practitioners.physiotherapist",
"csri.consultations_contact_months_practitioners.community_mental_health_worker",
"csri.consultations_contact_months_practitioners.osteopath",
"csri.consultations_contact_months_practitioners.occupational_therapist",
"csri.consultations_contact_months_practitioners.txt.other_specify_text",
"csri.months_medication_medications_list.1",
"csri.months_medication_medications_list.2",
"csri.months_medication_medications_list.3",
"csri.months_medication_medications_list.4",
"csri.months_medication_medications_list.5",
"csri.months_medication_medications_list.6",
"csri.months_medication_medications_list.7",
"csri.months_medication_medications_list.8",
"csri.months_medication_medications_list.9",
"csri.months_medication_medications_list.10",
"csri.months_medication_medications_list.11",
"csri.months_medication_medications_list.12",
"csri.months_medication_medications_list.13",
"csri.months_medication_medications_list.14",
"csri.months_medication_medications_list.15",
"csri.months_medication_medications_list.16",
"csri.months_medication_medications_list.17",
"csri.months_medication_medications_list.18",
"csri.months_medication_medications_list.19",
"csri.months_medication_medications_list.20",
"csri.long_medication_medications_list.1",
"csri.long_medication_medications_list.2",
"csri.long_medication_medications_list.3",
"csri.long_medication_medications_list.4",
"csri.long_medication_medications_list.5",
"csri.long_medication_medications_list.6",
"csri.long_medication_medications_list.7",
"csri.long_medication_medications_list.8",
"csri.long_medication_medications_list.9",
"csri.long_medication_medications_list.10",
"csri.long_medication_medications_list.11",
"csri.long_medication_medications_list.12",
"csri.long_medication_medications_list.13",
"csri.long_medication_medications_list.14",
"csri.long_medication_medications_list.15",
"csri.long_medication_medications_list.16",
"csri.long_medication_medications_list.17",
"csri.long_medication_medications_list.18",
"csri.long_medication_medications_list.19",
"csri.long_medication_medications_list.20",
"ses.left_home_describes_select.txt",
"ses.left_home_describes_select.txt.1"
)
```


# Add Numeric Variables

Specify columns to be excluded from add_numeric function
Continuous variables should be excluded, as they are already numeric
Text variables also need to be excluded
Do not include ID and sample here
```{r Specify excluded columns}
exclude_cols_numeric <- c(
  variables_text
  )
```

Add labelled/numeric columns
Modify the leaders argument if necessary
```{r Add columns}
dat <- dat %>% 
  add_labelled_numeric(exclude = exclude_cols_numeric)

# Inspect colnames
dat %>%
  colnames()
```


# Save cleaned data

# COVIDCNS
```{r Write cleaned COVIDCNS variables to a .rds file}
dat %>%
  saveRDS(
    file = paste0(ilovecovidcns, "/data/joined/covidcns_followup3_joined.rds")
    )
```