---
title: "COVIDCNS Montreal Cognitive Assessment Cleaning Script (Inpatient)"
author: "Zain Ahmad"
date: "24/02/2022"
output: html_document
---


All arguments should be in their own row, including the first argument
Closing bracket should have its own row
Functions with a single argument can have this on the same line
One argument can be hashed out per line for debugging errors

Chunk names should be all lower case except:
Study name (COVIDCNS) all caps
Capitalised first word

Ensure that you have deleted/untracked .DS_Store before your initial commit
Ensure that your  .gitignore contains "**/.DS_Store" before your initial commit

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the add_numeric function - used to convert character variables into numeric variables
Add the remove_duplicates function - used to deduplicate and remove NAs from IDs
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
Add the imp_check function - used to check variables for implausible values
```{r Read in functions}
source(file = "scripts/functions/add_numeric.R")
source(file = "scripts/functions/remove_duplicates.R")
source(file = "scripts/functions/sumscores.R")
source(file = "scripts/functions/package_check.R")
source(file = "scripts/functions/cont_clean.R")
source(file = "scripts/functions/imp_check_1.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("summarytools", "sjlabelled", "Amelia", "gtsummary", "tidyverse")
package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in file with path to ilovecovidcns channel on teams}
source(file = "scripts/credentials/paths.R")
```

# Read in the data: COVIDCNS Montreal Cognitive Assessment (Inpatient)
Change this heading to the name of your questionnaire/demographic
Load COVIDCNS data

Do not change variable names from the NLP names that are produced by the extraction
EXCEPT in exceptional circumstances
Document ANY changes to variable names in the issues spreadsheet "https://docs.google.com/spreadsheets/d/1a2gL8c0eH2pZXNTbnPzkDYQGeeVXbLKU8BUpYM0moe8/edit?usp=sharing"

- For variable names, use ONLY 'questionnaire.variable_name'
- For dataset, only use snake_case naming
- When using pipe operator '%>%', each function should begin on a new line
- Do not add empty lines at the beginning or end of a chunk
- Use only tidyverse functions wherever possible
- When naming chunks, begin with the name of the dataset (COVIDCNS)

## COVIDCNS data
```{r COVIDCNS load data}
covidcns_dat <- read_rds(
  file = paste0(ilovecovidcns, "/data_raw/latest_freeze/mh_case_report/moca_inp_covid_cns.rds")
  )
  
# Check variable names in dataframe
covidcns_dat %>%
  colnames()

# Inspect dimensions of dataframe 
covidcns_dat %>%
  dim()
```

Select & rename relevant columns
```{r COVIDCNS select}
covidcns_dat_id <- covidcns_dat %>% #new dataset with ID
  drop_na(externalDataReference) %>% # Drop participants with no ID
  remove_duplicates("externalDataReference") %>% # Remove duplicate IDs
  add_column(sample = "COVIDCNS",
             .after = "externalDataReference") %>% # Create new sample column
  select(
         ID = externalDataReference, # ID
         sample,
         startDate,
         endDate,
         moca_inp.visuospatialexecutive.txt,
         moca_inp.naming.txt,
         moca_inp.attention,
         moca_inp.attention.1,
         moca_inp.attention.2,
         moca_inp.language,
         moca_inp.language.1,
         moca_inp.abstraction.txt,
         moca_inp.uncued_recall_scored_delayed.txt,
         moca_inp.orientation.txt,
         moca_inp.total_score.txt
         )

# Inspect colnames
covidcns_dat_id %>%
  colnames()
```

Look at number of people excluded
The number of people to be excluded should be negative
```{r COVIDCNS number excluded}
# Inspect dimensions of new data set
covidcns_dat_id %>%
  dim()

# Inspect number of rows dropped
covidcns_excluded <- dim(covidcns_dat_id)[1] - dim(covidcns_dat)[1]
covidcns_excluded
```

Check missingness by missmap
```{r COVIDCNS inspect missingness}
covidcns_miss_map <- covidcns_dat_id %>% 
  missmap()

covidcns_miss_map
```

Create dat as copy of covidcns_dat_id for brevity
This step gives you a 'reset' point: if your variable recoding screws up, re-run this chunk to give you a fresh 'dat' dataframe
```{r Create dat}
dat <- covidcns_dat_id 

# Check
dat %>% glimpse()
```

MoCA requires unorthodox strategy for cleaning:
- Variables are encoded as 'chr' so text must first be transformed to numeric
non-answer codes
- Variables then transformed to numeric
- Variables then cleaned to ascertain implausible values according to MoCA
scoring

```{r COVIDCNS convert text to nonanswer}
dat <- dat %>%
  mutate(across(starts_with("moca_inp"),
                ~case_when(
                  . == "RE" ~ "-777",
                  . == "ATT" ~ "-777",
                  . == "STR" ~ "1",
                  . == "LE" ~ "16",
                  . == "CAN" ~ "-777",
                  TRUE ~ .)
                )
        )
```

```{r COVIDCNS convert text to numeric}
dat <- dat %>%
  mutate(across(starts_with("moca_inp"),
                ~as.numeric(.)
                )
    
        )
```

Recode Non-answer values to 3 digits
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(starts_with("moca_inp"),
                ~case_when(
                  . == -55 ~ -555,
                  . == -77 ~ -777,
                  . == -88 ~ -888,
                  . == -99 ~ -999,
                  TRUE ~ .)))
```

Create list of all unique values
```{r List unique values}
ulst <- sapply(dat, unique)
```


# Cleaning Continuous Variables

Create vector of continuous variables
(I suggest adding variable names sorted by type e.g. all ages then all years
etc. to make your life easier when creating limits_mat)
```{r Create cont vars vector}
variables_cont <- c(
  "moca_inp.visuospatialexecutive.txt",
  "moca_inp.naming.txt",
  "moca_inp.attention",
  "moca_inp.attention.1",
  "moca_inp.attention.2",
  "moca_inp.language",
  "moca_inp.language.1",
  "moca_inp.abstraction.txt",
  "moca_inp.uncued_recall_scored_delayed.txt",
  "moca_inp.orientation.txt",
  "moca_inp.total_score.txt"
)

# Check length of vector (must match dim(limits_mat)[1])
length(variables_cont)
```

Inspect continuous variables
Use the question labels to ascertain context at this point and check for obvious outliers
The percentiles can be modified to exclude nonanswer values as appropriate to your data
```{r Initial inspect cont vars}
dat %>%
  select(all_of(variables_cont)) %>%
  tbl_summary(
    missing_text = "Missing",
    statistic = list(all_continuous() ~ "{median} ({p0}, {p5}, {p95}, {p100})"))
```

Check for text in continuous variables
This chunk outputs only the columns and rows that contain text
```{r Cont vars check text}
# Function to check for any text or spaces
check_for_string <- function(x){
  sum(str_detect(x, "[a-zA-Z\\s]+"), na.rm = TRUE) > 0}

dat %>%
  # select all continuous
  select(all_of(variables_cont)) %>%
  # select only vars containing text
  select(where(check_for_string)) %>%
  # filter only rows containing text
  filter(
    if_any(where(check_for_string),
           ~str_detect(., "[a-zA-Z\\s]+")
           )
    )
```

Create matrix of limits for continuous variables
Matrix is series of vectors (lower, upper)
```{r Create matrix limits}
# Create a vector of limits for each type of variable using rep
limits_1 <- rep(c(0,5), 1)
limits_2 <- rep(c(0,3), 1) 
limits_3 <- rep(c(0,2), 1) 
limits_4 <- rep(c(0,1), 1) 
limits_5 <- rep(c(0,3), 1) 
limits_6 <- rep(c(0,2), 1) 
limits_7 <- rep(c(0,1), 1) 
limits_8 <- rep(c(0,2), 1) 
limits_9 <- rep(c(0,5), 1) 
limits_10 <- rep(c(0,6), 1) 
limits_11 <- rep(c(0,30), 1)

# Combine the vectors together
limits_vec <- c(limits_1,
                limits_2,
                limits_3,
                limits_4,
                limits_5,
                limits_6,
                limits_7,
                limits_8,
                limits_9,
                limits_10,
                limits_11
                # add more as necessary
                )

# Create matrix, matrices are filled by columns, not rows, so must transpose
limits_mat <- t(matrix(limits_vec, # take values from your vector of limits
                       nrow = 2, # upper and lower bounds
                       ncol = length(variables_cont) # number of variables total
                       ))

# Check dimensions
dim(limits_mat)
```

Set row and col names of limits_mat
This allows your to easily refer back to limits_mat for a summary
```{r Set lim_mat names}
rownames(limits_mat) <- variables_cont
colnames(limits_mat) <- c("Lower", "Upper")
```

Use cont_clean to check if any implausible values and provide replacement vectors
Cont_clean will not proceed if variables are not numeric type, clean manually above if necessary
This chunk reports any variables that contain implausible values
```{r Cont_clean cont vars}
# Execute cleaning function
cont_list <- cont_clean(
  variables = variables_cont,
  limits_mat = limits_mat,
  dat = dat
)

# Create empty list of variable names to check
implaus_checklist <- c()

# Loop through function output
for (i in 1:length(variables_cont)){
  
  # Report only variables containing implausibles
  if(cont_list[[variables_cont[i]]]$Count > 0){
    
    # Add variable name to imp_checklist
    implaus_checklist <- append(x = implaus_checklist, variables_cont[i])
    
    # Report readout of implausible values
    print(paste0("Implausibles in ", variables_cont[i], ": ", cont_list[[variables_cont[i]]]$Count))
  }
}
```

Check unique values in variables containing implausible values
The sort() function allows you to see them more clearly

Check for any systematic errors at this stage
e.g. For 'age', participants may have entered a calendar year (e.g. 2001), instead of an age (e.g. 45)
It may be possible to gain data from errors like this, so DO NOT MUTATE TO IMPLAUSIBLE WITHOUT GOOD REASON
If you are unsure, RAISE IN THURSDAY DATA CLEANING MEETING
(You could import participant birth year and subtract to find age, for example)
```{r Cont vars implausible unique}
dat %>%
  select(all_of(implaus_checklist)) %>%
  sapply(., function(x) sort(unique(x)))
```

Mutate variables with implausible values removed
Repeat the mutate statements for as many variables as necessary
```{r Mutate cont vars}
dat <- dat %>%
  mutate(
    moca_inp.attention.1 = cont_list$moca_inp.attention.1$Replacement
  )

dat <- dat %>%
  mutate(
    moca_inp.attention.2 = cont_list$moca_inp.attention.2$Replacement
  )

dat <- dat %>%
  mutate(
    moca_inp.language = cont_list$moca_inp.language$Replacement
  )

dat <- dat %>%
  mutate(
    moca_inp.uncued_recall_scored_delayed.txt = cont_list$moca_inp.uncued_recall_scored_delayed.txt$Replacement
  )

```

Re-inspect variables after cleaning
```{r Cont vars inspect after cleaning}
dat %>%
  select(all_of(variables_cont)) %>%
  tbl_summary(
    missing_text = "Missing",
    statistic = list(all_continuous() ~ "{median} ({p0}, {p5}, {p95}, {p100})")
  )
```

# Produce sumscores

MoCA dataset already contains total scores but due to implausible values,
sumscores must be recalculated to exclude these participants



Reference the scoring guidance that you have used for your questionnaire here "https://www.parkinsons.va.gov/resources/MoCA-Instructions-English.pdf"

If changing na_limit, CHECK your guidance, na_limit > 0 will replace NAs with 0, ensure that this is correct for your scoring guidance before proceeding

Create vector of item coding
The coding_keys vector must contain 1s for all variables to be added and -1 for all variables to be subtracted.
Putting 0 in the vector will omit the variable at that position.
length(coding_keys) MUST be the same as the number of variables to be summed

sum_vars vector should contain ONLY and ALL variable names needed for scoring, do not add "ID" or "sample" etc.

If using reverse keying:
MAKE SURE that Reverse = TRUE is included as an argument, reverse keying will not work without this
reverse_vars should contain all variable names to be reverse keyed
If running multiple sumscores requiring reverse keying, a single reverse_vars vector containing all of the variable names to be reverse keyed is sufficient: `%in%` will pick the relevant variables for each sumscore

The warnings "Scores vector contains missing values." and "Input contains non-answer values. These will be converted to NA_real_ for this calculation." are normal. They are there to inform you that some sumscores have not been calculated due to non-answer values (e.g. -777) being present. Any other errors or warnings need to be investigated.

Create required variables for sumscore arguments
```{r Sumscores inputs}
keys <- c(
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1,
  1
  )

sum_vars <- c(
  "moca_inp.visuospatialexecutive.txt",
  "moca_inp.naming.txt",
  "moca_inp.attention",
  "moca_inp.attention.1",
  "moca_inp.attention.2",
  "moca_inp.language",
  "moca_inp.language.1",
  "moca_inp.abstraction.txt",
  "moca_inp.uncued_recall_scored_delayed.txt",
  "moca_inp.orientation.txt"
  )
```


Generate sumscores from questionnaire data and use mutate onto dat as new column
sumscores assumes that all items in the questionnaire have the SAME minimum and maximum scores for ALL items, ensure that this is correct before proceeding

When adding the column name for your sumscore use "questionnaire.score_name"

Generate sumscores and add as new column
```{r Generate sumscores}
dat <- dat %>% 
  mutate(
    moca_inp.adj_sum_score = 
         sumscores(input = dat,
                   sum_vars = sum_vars,
                   coding_keys = keys,
                   na_allowed = 0,
                   min_item = 0,
                   max_item = 6,
                   min_score = 0,
                   max_score = 30
                   )[["scores"]]
         )

```

# Create binary phenotypes
Add explanation of binary phenotype here:
MoCA score ≥ 26 = Normal Cognition 

Create numeric binary phenotype variable
```{r Numeric binary phenotype}
dat <- dat %>%
  mutate(
    moca_inp.cognition_numeric =
      case_when(
        moca_inp.adj_sum_score >= 26 ~ 1,
        moca_inp.adj_sum_score < 26 ~ 0
      )
  )
dat %>%
  select(moca_inp.cognition_numeric) %>%
  tbl_summary()
```

Create categorical binary phenotype variable
```{r Categorical binary phenotype variable}
dat <- dat %>%
  mutate(
    moca_inp.cognition =
      recode_factor(
        moca_inp.cognition_numeric,
        "0" = "Not Normal Cognition",
        "1" = "Normal Cognition"
      )
  )
dat %>%
  select(moca_inp.cognition) %>%
  tbl_summary()
```


# Save cleaned data

Check colnames before exporting final dataset
```{r Check colnames}
colnames(dat)
```

# COVIDCNS
```{r Write cleaned COVIDCNS variables to a .rds file}
dat %>%
  saveRDS(
    file = paste0(ilovecovidcns, "/data/latest_freeze/mh_case_report/moca_inp_covidcns_clean.rds")
    )
```
