---
title: "Monika Data Request"
author: "Zain Ahmad"
date: "13/04/2022"
output: html_document
---

Data request for ethnicity and covid positive date

# Set up

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = "scripts/functions/package_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c(
  "summarytools",
  "sjlabelled",
  "xlsx",
  "tidyverse"
  )

package_check(packages)
```

Retrieve the recent date
We are using the recent date to save files with paste0() as an extension to not overwrite old versions
```{r Recent date}
date <- Sys.Date()
date
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in file with path to ilovecovidcns channel on teams}
source(file = "scripts/credentials/paths.R")
```

### ethnicity_covidcns_clean
Read in & variable names
```{r ethnicity_covidcns_clean Read in data & variable names}
ethnicity_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/baseline/dem_ethnicity_covidcns_clean.rds")
  )

ethnicity_covidcns_clean %>%
  dim()
```

Dimensions
```{r ethnicity_covidcns_clean Dimensions}
ethnicity_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ethnicity_covidcns_clean Select columns for joining}
ethnicity_covidcns_clean_selected <-
  ethnicity_covidcns_clean

ethnicity_covidcns_clean_selected %>%
  slice(1:5)
```


### ncrf1_admission_covidcns_clean
Read in & variable names
```{r ncrf1_admission_covidcns_clean Read in data & variable names}
ncrf1_admission_covidcns_clean <-
  read_rds(
    file = 
      paste0(ilovecovidcns, "/data/latest_freeze/neuro_case_report/ncrf1_admission_covidcns_clean.rds")
  )

ncrf1_admission_covidcns_clean %>%
  dim()
```

Dimensions
```{r ncrf1_admission_covidcns_clean Dimensions}
ncrf1_admission_covidcns_clean %>%
  colnames()
```

Select columns for joining
```{r ncrf1_admission_covidcns_clean Select columns for joining}
ncrf1_admission_covidcns_clean_selected <- 
  ncrf1_admission_covidcns_clean

ncrf1_admission_covidcns_clean_selected %>%
  slice(1:5)
```


## List of tibbles to join
```{r List of tibbles to join}
tibble_list <- 
  list(
    ethnicity_covidcns_clean_selected,
    ncrf1_admission_covidcns_clean_selected
    )
```

Joining of demographics and questionnaires
```{r Joining of demographics and questionnaires}
data_joined <- 
  plyr::join_all(
    tibble_list,
    by = c(
      "ID"
      )
    )
```

Check dimensions of joined tibble
```{r Check dimensions of joined tibble}
data_joined %>%
  dim()
```

```{r}
data_joined %>% 
  colnames()
```

# Save joined data set
```{r monika Save joint data set}
write.xlsx(x = data_joined,
           file = paste0(ilovecovidcns, "/data_requests/monika_ethnicity_ncrfadmission.xlsx"))
```
